### 2020-06-06 manuscript/manuscript.Rmd
Initial almost-done draft

---
title: "Who Cares About Crackdowns? Exploring Individual Donor Responses to Closing Civic Space Abroad"
short-title: "Who Cares About Crackdowns?"
author:
- name: Suparna Chaudhry
  affiliation: Lewis & Clark College
  url: http://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
- name: Marc Dotson
  affiliation: Brigham Young University
  url: https://marriottschool.byu.edu/directory/details?id=50683
  email: marc_dotson@byu.edu
- name: Andrew Heiss
  affiliation: Georgia State University
  url: https://www.andrewheiss.com/
  email: aheiss@gsu.edu
date: "June 5, 2020"
published: Working paper.
git-repo: https://example.com
abstract: >-
  TODO: UPDATE THIS: Over the past decade, international nonprofit organizations (INGOs) have faced increasing legal scrutiny and closed civic space abroad. While we know this has negatively impacted public funding flows, we know little about how this has affected private funding flows, especially be individuals. This turn to private aid introduces potentially new dynamics in INGO fundraising strategies, since individuals have a range of demographic characteristics and past experiences with philanthropy that shape their propensity to donate. Which demographic and experiential factors influence the decision to donate to legally besieged NGOs? We investigate this question using nationally representative results from a vignette-based experiment and a conjoint experiment conducted on individuals with a history of charitable-giving. Our findings have practical implications for INGOs that hope to raise funds from the general public amid closing civic space. 
reference-section-title: References
toc: false
mainfont: Lora
sansfont: IBM Plex Sans
---

<!-- manuscript.md is generated from manuscript.Rmd. Only edit the .Rmd file, *not* the .md file. -->

In Human Rights Watch's 2016 annual report, Executive Director Kenneth Roth argued that civil society was under more aggressive attack than at any time in recent memory. Over the past few decades, governments across the globe have been cracking down on civil society organizations (CSOs)—a phenomenon known as "closing civic space" in the policy arena [@CarothersBrechenmacher:2014; @CIVICUS:2017]. Consequently, official aid flows to NGOs have decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018]. While we know that there has been a negative impact on funding flows from public sector organizations like USAID, DFID, and others, we know relatively little about how this global crackdown affects private funding flows, in particular from individual donors.

Existing scholarship on the determinants of individual-level philanthropy to domestic causes is quite robust across a variety of contexts. But the dynamics of *international* giving are under-examined in the literature on individual donor preferences.[^exceptions]. Research on the determinants of philanthropy towards international causes—particularly for organizations working in challenging environments—is still in its infancy due to the absence of expansive and high-quality data [@greenhill2013]. Understanding why individuals donate to international causes is especially essential to understand, given that such philanthropy can be harder to motivate because the number of recipients are large and far removed from the donor [@CasaleBaumann:2015, 100].

The amount of money donated by private individuals to CSOs working abroad, however, has steadily increased over time. 
Total aggregate philanthropy in the United States has grown substantially over time, reaching more than \$400 billion in 2018 (@fig:giving-aggregate). In 2018, total private giving to CSOs working specifically in international affairs reached $22.08 billion. More importantly, organizations working in the area of international affairs are one of the only two types of recipient organizations that have continued experiencing substantial growth in giving—even at a time when giving to religious institutions, education, human services and arts, culture and society has been on the decline [@givingusa:2019].[^intlaffairs]

![Aggregate philanthopic giving in the United States, 1977–2017. Source: Giving USA.](output/figures/giving_aggregate.pdf){#fig:giving-aggregate}

While this may be a cause for optimism among CSOs working internationally, we know little about the individuals who donate to CSOs working in other countries. We also lack any systematic understanding of how such giving is affected by an increasingly restricted civic space abroad. Given these challenges, what is the optimal mix of individual-level donor attributes for international NGOs working in restricted political environments interested in maximizing donations? What kinds of individual donors are more or less likely to consider a CSO's host country political environment, its transparency and accountability practices, and its funding structure when making the decision to donate? How do individual-level donor characteristics such as political ideology, knowledge, activism and other demographic characteristics interact with organizational-level attributes to influence philanthropic decisions?

TODO ANDREW: [METHOD AND FINDINGS] We investigate these questions using a nationally representative survey of individuals in the U.S. with a previous history of charitable-giving. ONE LINE ABOUT EXPERIMENT. WHAT WE FIND

This study contributes to both to scholarship and practice in public policy, nonprofits and philanthropic-giving. Individual-level philanthropic giving abroad can help bridge socioeconomic disparities worldwide, especially given the stark inequality in global distribution of income. Knowledge of demographic traits and prior experiences that make certain individuals more likely to donate can be very important to nonprofits, as this information can help them craft more effective and targeted marketing strategies [@Rajan:2009, 414]. Most CSOs and nongovernmental organizations (NGOs) working internationally have previously relied on government and foundation funding. But in the era of closing civic space, these groups may need to readjust their fundraising strategies to cater to private individuals.

Framing is particularly important in this regard—how people process information affects their willingness to donate.[^framing] However, we lack systematic studies of which frames may be effective when making appeals to individual donors considering international philanthropy. Since our study looks at multiple factors, it can help these CSOs frame their appeals.

More broadly, while research in public policy and nonprofit studies has focused on charitable giving, philanthropy is not seen as relevant by international relations as a discipline [@youde2019]. However, philanthropy—particularly donations received by international non-governmental organizations (INGOs)—can help us understand changes in the dynamics of global governance. Private individuals exercise power and influence in unique ways that differ from other non-state actors. As @youde2019 [p. 44] points out, it changes our conceptions of individuals being passive recipients to active entities that are not merely objects of governance, thus shedding light on the changing logic of global governance.

TODO ANDREW: [ROADMAP] Below, we first explain the different fundings for CSOs working internationally, examining trends in individual donor to philanthropy to such causes. We then take a look at the state of the existing literature on the key drivers of philanthropy by individuals. We describe our survey experiment. FINISH ROADMAP.

# Sustaining civil society organizations abroad

Foreign aid to civil society, primarily via NGOs, has been steadily increasing over time. This is because many donors perceive that NGOs have superior ability to achieve intended outcomes. In countries with weak institutions and poor governance, where direct aid transfers to governments raise issues of misuse and bureaucratic inefficiency, donors specifically seek out NGOs for projects [@Dietrich2013]. These groups provide services to large parts of the population in the Global South, especially where governments are unable to do so on a consistent basis. More broadly, a robust civil society is also considered to be one of the necessary preconditions for a healthy, functioning democracy due to its ability to generate social capital and hold governments accountable [@Putnam:1995].

## Sources of foreign aid

Thousands of international NGOs and CSOs in the Global South receive funds from a variety of public and private sources each year. Public funds (more commonly known as traditional donor aid) channels funds from official aid agencies through a variety of bilateral and multilateral institutions. Private funds, also newer international donors, included foundations, private corporations and individuals. In this paper, we specifically look at individual-level determinants to foreign giving. This is important to investigate as individual private donors may not necessarily mirror public donor choices. Surveys show that the American public is notoriously misinformed about US foreign aid [@norris:2017]. Further, foreign aid and democracy aid is often considered unresponsive to developments on the ground [@brainard2007; @Carothers:2015] and public aid decisions - especially on final recipients are not easily accessible. There may also be heterogeneity within how donor governments allocate funds. Emerging donor government differ from established donors in that they demand fewer human rights, governance or environmental conditions preferred by Western donors [@fenglerkharas].

With the advent of funding restrictions on NGOs globally and a consequent decline in official government aid and foundation funding, many groups are being forced to foreign individual donors. Giving to international affairs has been steadily increasing over the past two decades, with a noticeable increase over the past decade. Between 2014 and 2016, giving to international affairs increased by 14.1% [@givingusa2017report]. Most of this is driven by individuals making small-scale donations. In 2017, individuals gave \$286.7 billion - or approximately 70% of total giving to international affairs. This further increased to \$427.71 billion in 2018 - 85.7% of which was through individuals [givingusa:2019]. Given that a majority of this research is restricted to elite, high net-worth donors [@USTrust2014], these figures show that it is imperative to understand motivations and attributes of small-scale donors as well.

## Key drivers of individual-level philanthropy

A vast literature in philanthropic-giving looks at organizational-level factors that motivate individuals to donate [@BilodeauSlivinski:1997; @TBPrakash:2017]. However, the decision to donate to an NGO is not determined solely by an organization's characteristics. Donors have particular personality traits, preferences, and experiences that make them more or less likely to engage in philanthropy. A robust literature in nonprofit studies has looked at individual donor behavior and characteristics for giving to local-rather than international-causes. This literature has primarily focused on the importance of three main factors, especially when considering charitable behavior towards international causes: (1) social capital; (2) the role of higher education; (3) levels of religiosity; (4) wealth; and (5) national group attachment.

One major area of inquiry in philanthropic studies looks at the role of social capital, or the "networks, norms, and social trust that facilitate coordination and cooperation for mutual benefit" [@Putnam:1995, 67]. While quite broad, the literature further concentrates on a specific kind of social capital-associational capital, which refers to, "the networks of formal and informal relationships to which people are associated." [@havens2007, 240]. Prior research has found that those who participate in a variety of associations are more likely to make larger donations [@hossainlamb2017]. Further, those who volunteer their time (compared to those who did not), were both more likely to make charitable donations and make bigger donations. This is because volunteering exposes individuals to the need for donations to charities and nonprofits and made them feel more compelled to do so [@hossainlamb2012].

Higher education can also play an important role in philanthropic-giving decisions as such education fosters prosocial motivations. It also brings people into particular social networks that entail a higher level of solicitations [@BekkersWiepking:2011]. This in turn has been shown to be particularly vital in giving to international causes. @Micklewright:2009 show that higher education matters more for donating to international relief organizations than donating to domestic organizations. An additional year of education has been shown to increase the likelihood of giving to international causes by about 2 percentage points [@OktenOsili:2007].

Higher education can also play an important role in determining the kinds of causes that people donate to globally. A number of NGOs facing crackdowns abroad work on issues that may be seen as "contentious" - these include human rights, elections, corruption, advocacy, media freedom - causes that may have a harder time attracting funds due to their non-essential nature when compared to causes like health, education, sanitation, and social services. However, additional education has been shown to increase abstract thinking [@wiepkingmaas, 1978], which may be necessary to donate to causes that do not have quantifiable goals - which is particularly important for organizations with more "contentious" causes as part of their missions [@Bush:2015].

Levels of religiosity are also a significant predictor of the likelihood and level of giving. People who regularly attention religious services are more likely to have prosocial values, face a stronger norm of charitable-giving, and may feel pressure to conform that group and community standard [@wiepking2010]. Regular attendance may also strengthen individuals' beliefs in organizations' missions. However, religiosity does not necessarily have the same effect on giving to all causes. @neumayrhandy2019 find that religiosity is negatively associated with giving to environmental issues and animal welfare, while having an insignificant effect on giving to international relief.

Finally, recent research has also looked at how a sense of ethnonationalism and national group attachment affects the decision to donate to domestic and international charities. Looking at UK respondents, @hartrobson2019 find that whereas nationalists have a preference for domestic charities, they are not necessarily averse to donating to international causes, whereas internationalists have a strong preference for donating to causes and groups working abroad. More specifically, research finds that immigrant households are more likely to contribute to international aid organizations [@OktenOsili:2007], and that immigrants can find value in donating to both home and host cultures, especially if family members are still residing in the home country [@burgoyne2005].

Overall, individuals with higher levels of income, education, and greater religious proclivities have been shown to not only be more likely to give internationally, but also to give higher amounts [@Rajan:2009; @CasaleBaumann:2015]. INSERT LINE ABOUT while we expect these determinants to hold similar significance in our survey, we do not specifically lay out hypotheses because this is exploratory/descriptive/we barely know about international giving so we don't have specific expectations about international giving during crackdown. BUT ALSO WHAT ARE WE DOING THAT HASN'T BEEN DONE YET.

TODO ANDREW: NEW GROUNDBREAKING STUFF = combining individual-level characteristics with organization characteristics - Looking at a persona is not typical - we often look at the effect of a single covariate, not a combination of them. But looking at the impact of a persona — which in all reality is a fabricated individual — has interesting appeal.

# Data and methods

## Conjoint survey experiment

We use a conjoint survey experiment to simultaneously study the effects of organizational characteristics and individual attributes on individuals' preferences to donate to a nonprofit organization. Conjoint analysis methods are well suited for the questions we explore, as they allow us to elicit donor preferences without forcing respondents to explicitly state their exact preferences. Conjoint analysis is commonly used in marketing research to reveal consumer preferences for different mixes of products. It has also been increasingly used in political science and public policy to assess citizen perceptions of political communication [@Helfer:2016; @Mummolo:2016; @KnudsenJohannesson:2019]. Because we are interested in exploring the complexity behind the decision to donate, we apply conjoint methods to the study of nonprofits and philanthropy.

After collecting baseline information on respondent demographics and attitudes toward charity and voluntarism, we presented respondents with four randomly selected international nonprofit organizations with four randomly assigned features.^[See the appendix for a copy of the survey.] We included organizations that are associated with a range of contentious and noncontentious issues: Amnesty International, Greenpeace, Oxfam, and the International Committee of the Red Cross. We then displayed various combinations of features, including one of four issue areas (emergency response, environmental advocacy, human rights advocacy, and refugee relief), one of two organizational practices (financial transparency and third-party accountability audits), one of three funding sources (many small private donations, a handful of wealthy private donors, and government grants), and one of three relationships with host governments (friendly, criticized by the government, and under government crackdown). We presented twelve sets of four hypothetical combinations of organizational features, and because our partial fractional factorial design resulted in 288 (4 × 4 × 2 × 3 × 3) possible combinations of organizations and features, no single respondent was offered every combination.

We recruited survey respondents through Centiment, a commercial provider of high quality non-probability opt-in survey panels. Sentiment ensures panel quality by actively recruiting representative samples of the US population and rewards participants with monetary incentives. To participate in the study, respondents were first screened based on their charitable activities. Those who indicated that they gave to charity once every few years or never were disqualified. After screening, we collected a sample of 1,016 respondents, which is sufficient for model estimation.[^sample-size]

```{r child = "output/tables/tbl-sample-details.md"}

```

@tbl:sample-details provides a summary of the individual characteristics of survey respondents. Because we limited the sample to people who regularly make charitable contributions, most respondents have a favorable opinion of nonprofits and charities, with more than half reporting a 5 or greater level of trust in charities (on a 7-point scale). Moreover, nearly 90% indicated that it is important to trust charities. Additionally, the majority of respondents volunteer at least once a year, donate to charity at least once a year, and give between \$1–\$999 annually. Most rarely attend church, but feel that religion is important. Respondents are also engaged civically (three quarters voted in the last election) and follow national news closely (70% follow the news daily). Respondents are fairly balanced ideologically, with the majority reporting a 3, 4, or 5 on a 7-point scale of liberal–conservative political ideology.

We analyze the effect of different combinations of organizational features and individual respondent attributes with a two-stage hierarchical Bayesian multinomial logit model.[^model-details] Simply put, the first level of the model predicts individual donor preferences for various combinations of features (e.g. the combination of human rights issues, financial transparency, government funding, and government crackdown), while the second level of the model uses these fitted preferences to predict the ultimate choice of donation.

## Simulated philanthropy market

In previous work [@ChaudhryDotsonHeiss:2019], we use the results of this survey experiment to measure how the organizational characteristics of an NGO can influence donor preferences. We find that donors prefer to give money to organizations that engage in transparency and accountability practices, receive funding from many individual donors, and that work on humanitarian issues like disaster and refugee relief. Importantly, we also find that donors are less likely to be interested in donating to NGOs facing government crackdown abroad. These results provide unique insight for NGOs looking to raise money from private donors and can influence how these organizations might frame their calls for fundraising.

However, the findings in @ChaudhryDotsonHeiss:2019 focus only on organizational attributes and do not distinguish between different types and specific characteristics of donors. As part of the survey experiment, we collected information about the survey respondents themselves, including their demographic characteristics and their interest and involvement in public affairs, charity, voluntarism, politics, and religion.

In this paper, we focus instead on exploring which kinds of donors are more or less likely to consider an NGO's issue area, funding sources, and host country politics when deciding to donate. Disentangling the effect of every individual level-characteristics on every combination of organizational characteristics is unwieldy and near impossible. Given the organizational attributes presented in our experiment, and the possible individual characteristics that respondents could select, there are billions of possible combinations and iterations of organizational and individual attributes.

Instead of trying to work through all these countless combinations—most of which rarely occur in the actual population of potential donors—we rely on simulation methods to examine the effect of more general combinations of individual characteristics. We use market segmentation methods to construct simulated personas that interact with simulated organizations in a market for charitable contributions. To simplify the many possible combinations of individual characteristics, we generate 32 distinct personas with attributes that vary along different dimensions of demographics, politics and public affairs experience, and social attitudes (see Table XXX). We also generate 24 simulated organizations that vary by issue area, relationship with host government, and source of funding. This combination of personas and organizations yields 768 hypothetical scenarios where potential donors can interact with different organizations.

TODO ANDREW: Simplified persona table + organization table

We then combine these different scenarios of donor and organization attributes with the coefficients from a multinomial multilevel regression model to calculate the probability that each simulated persona has of giving to specific combinations of organizational attributes. Any individual characteristics that we do not explicitly vary in Table X are held at their means or modal values from the survey sample. Table X provides an example of the simulation output, showing how two different personas are predicted to allocate donations to organizations with various characteristics. The proportion of donations from each persona sums to 100%, as every persona is guaranteed to make a donation.

TODO ANDREW: Two simplified sample personas

Relying on simulation methods offers useful analytic benefits. Rather than interpret individual marginal effects from a regression model, we can explore multiple moving parts from the same model simultaneously to understand how characteristics interact with each other. This allows us to more fully explore our key research questions and see which kinds of donors are more or less likely to consider specific organizational attributes when deciding to donate, and which donor characteristics are associated with the propensity to donate. Importantly, each persona is an artificial construct. While some survey respondents might match an exact persona profile, most do not. This is acceptable in simulations, and each combination of persona characteristics is plausible in the real world. Our analysis uses the characteristics of our sample to model the effects of various salient attributes while holding others constant, and thus allows us to explore multiple attributes at once. Also importantly, our findings are not causal. Rather, they are the descriptive results of simulated data from a nationally representative sample of people who regularly donate to charity. The insights from this simulation, however, still reveal interesting patterns of donor preferences when faced with organizations focusing on a variety of issues, funding sources, and legal restrictions abroad.

# Results

Our market simulation reveals which combination of organizational features each persona is most likely to express a preference for donation to. We examine the results of the simulation in three stages, looking at how personas with different (1) demographic characteristics, (2) public affairs knowledge and experience, and (3) levels of trust in government, charitable work, and associational life change their donation preferences across different organizational issue areas, relationships with host governments, and funding sources.

## Demographics

We begin by looking at differences in donation preferences across a range of basic demographic characteristics. The three panels of @fig:demographics shows the average predicted market share for different organizational issue areas, relationships with governments, and funding sources. Though we varied gender across the different personas, gender has no significant effect on any of the simulated outcomes—males and females follow nearly identical patterns across all organizational and individual characteristics. As such, in @fig:demographics, we only vary income. Personas with high income earn \$100,000 a year, while those with less income earn \$50,000 annually.

![Average predicted donation market shares across all personas, segmented by individual persona income and organizational issue area, relationship with host government, and funding sources](output/figures/income-all.pdf){#fig:demographics}

Wealthier personas respond better to human rights organizations over refugee assistance and environmental advocacy organizations, while personas that earn less money tend to prefer donating to refugee and environmental organizations. As we explore below, this is likely because income correlates with interest in public affairs and political activity—individuals who are wealthier arguably have more time and resources to follow the news and be continuously engaged in their communities and in other activist causes.

There are also sizable income-based differences across different NGO host-country relationships. Wealthier donors are more likely to prefer donating to organizations that are criticized by their host governments. This falls in line with their preference for human rights organizations which have more contentious missions and are more likely to receive government criticism. This support, however, appears to evaporate as civil society crackdown intensifies. High income personas are the least likely demographic to prefer donating to NGOs under crackdown. Their lower income counterparts, on the other hand, are generally unfazed by NGOs' relationships with government, maintaining the same average market share across all three types of host country relationships. Finally, as seen in the right panel of @fig:demographics, there are no sizable differences in donation preferences by income across different forms of NGO funding. Income thus appears to influence preferences particularly for NGOs facing criticism and crackdown abroad—wealthier donors are perhaps fair-weather friends that are more likely to pull their support when an organization's work becomes more difficult.

*(Note: We also plan on examining religiosity and education in the very near future)*

## Public affairs knowledge, experience, and social trust

We next look at how differences in public affairs knowledge, experience, and political ideology influence a persona's propensity to donate to an organization. We vary personas along two dimensions: (1) political ideology, with semi liberal and semi conservative political leanings (2 and 5 on a 7-point scale), and (2) knowledge and experience with public affairs and the news, with personas that either follow national and international news and that have travelled abroad or personas that do not follow the news or travel.

We also combine these dimensions with an additional set of donor characteristics that vary a persona's level of social trust. Personas with high levels of trust have high trust in political institutions and charities, thinks people should be more charitable, frequently volunteers, donates to charity once a month, has a history of political activism, and is a member of an association. Personas with low levels of trust have the opposite characteristics: they do not trust political institutions or charities, rarely donate or volunteer, and are not members or other associations.

![Average predicted donation market shares across all personas, segmented by persona public affairs knowledge, political ideology, and social trust across different NGO issue areas](output/figures/issue-social.pdf){#fig:issue-social}

Figures @fig:issue-social, @fig:relationship-social, and @fig:funding-social show the results of the market simulation across these three dimensions of persona characteristics, varying public affairs knowledge, political ideology, and social trust. Personas respond differently to organizational issue areas. In @fig:issue-social, those who follow the news and travel abroad are more likely to prefer donating to human rights organizations than their less knowledgable and less travelled counterparts. Personas who do not follow the news or travel show a greater preference for emergency response and refugee relief organization, similar to the income effects seen previously. There are no strong ideological effects across issue areas. Both conservative and liberal personas tend to follow similar patterns of preference across NGO issue. Social trust plays a substantial role in determining simulated market share, however. Those who trust social and charitable institutions are very likely to prefer donating to human rights organizations, regardless of their public affairs knowledge or political leanings. In all circumstances, those with high levels of trust have between a 7–10% chance of donating to a human rights organization, on average. Personas with low levels of trust, on the other hand, strongly avoid human rights organizations and prefer instead to donate to refugee and emergency response NGOs. The difference is substantial—a liberal persona with high levels of public affairs knowledge and experience will give to a human rights organization 10% of the time, on average if they have high levels of trust, but less than 3% of the time if they are less trusting. Trust in charities and institutions is a key factor in deciding to donate to more contentious human rights organizations.

![Average predicted donation market shares across all personas, segmented by persona public affairs knowledge, political ideology, and social trust across different NGO–host government relationships](output/figures/relationship-social.pdf){#fig:relationship-social}

Figure @fig:relationship-social shows how personas respond to different NGO–host government relationships. Public affairs knowledge and experience has little effect on donor preferences—the average market shares are roughly identical across the two columns of the figure. Similarly, there are no ideological differences across the rows of the figure. Persona preferences toward friendly, criticized, and legally suppressed organizations do not change much across different ideological views. The strongest, most overriding factor in determining donor preferences when considering an organization's relationship with its host country is social trust. Personas with high levels of social trust are overwhelmingly most likely to donate to organizations with friendly relationships with their host governments, while those with low levels of trust avoid friendly NGOs almost entirely.

This stark difference in attitudes towards friendly NGOs likely reflects the underlying levels of trust in the model. For those who trust charities to do the right thing and have a positive influence on society, a friendly relationship with a host government is a manifestation of that belief and a sign that the organization is living up to its idea. Once the organization faces criticism or crackdown, however, support deteriorates rapidly, since such a crackdown could be perceived as a violation of the persona's trust in the charity—that is, the organization must be doing something wrong to deserve criticism. Personas with low levels of trust, on the other hand, are eschew friendly organizations entirely and are far more willing to donate to organizations facing criticism and crackdown, likely because they do not assume that charities must always be above reproach. The global crackdown on NGOs could thus counterintuitively sour NGOs' most trusting donors.

![Average predicted donation market shares across all personas, segmented by persona public affairs knowledge, political ideology, and social trust across different forms of NGO funding](output/figures/funding-social.pdf){#fig:funding-social}

Finally, @fig:funding-social shows the average share of persona market shares across different forms of NGO funding. There are only insignificant differences in donor preferences across public affairs knowledge and experience, political ideology, and social trust. On average, it appears that the source of NGO funding does not play an important role in a donor's preference for the organization. Other organizational factors—in particular issue area and host government relationship—have a much larger influence in shaping donor preferences.

# Implications and conclusion

With the turn towards private philanthropy in the face of the global crackdown on civil society and declining official aid and official development assistance, INGOs need to be aware of the dynamics of individual donor preferences. WHAT WE FIND

??Individuals may also be more likely to donate to causes seen as vital to ongoing public services in countries across the Global South - such as health and education, rather than donate to more "contentious" causes such as corruption, advocacy, media freedoms and human rights. This has the potential to leave organizations focusing on the latter without adequate funding to continue their operations.??

Finally, it is important to acknowledge the role played by civil society organizations in dealing with health, poverty, and disaster - social needs that are tremendously important during the COVID-19 pandemic. This survey was conducted in July (?) 2019 - can we expect insights from this survey to hold even during this time period, even as the world sees an economic recession? We argue that this is the case for two main reasons. First, prior research demonstrates that altruism and prosocial behavior are more common during and after disasters (cite?). Second, the most recent instance of the 2008 recession did not uniformly impact all demographic groups in the U.S. - individuals with lower levels of education, income, or wealth showed a statistically significant decline in charitable-giving. However, philanthropic patterns were not significantly different for other income brackets.

Thus, while giving to international causes is likely to be sensitive to economic changes and disaster, this may not substantively amount to a huge difference given that while 5% of US households support international causes, more than double - 11% of US high net worth households donated to international causes between 2016-18. [^highnetworth]. (TODO IU July 2019 - where is this paper?) In terms of overall giving, individuals with graduate degrees gave largest percentage of income both before and after the recession.

[^exceptions]: For exceptions, see @Micklewright:2009 on the UK, @Rajan:2009 on Canada, @wiepking2010 on Netherlands, @CasaleBaumann:2015 on the USA.

[^highnetworth]: High-net worth households are defined as having greater than \$200,000 in annual household income and/or with more than \$1,000,000 in assets, excluding primary residence.

[^framing]: Framing is the process through which actors present information to influence perceptions or behavior. Previous research has shown that which frames are employed can have a significant effect on individuals' attitudes and behaviors [@BenfordSnow:2000; @ChongDruckman:2007].

[^intlaffairs]: Giving USA defines the sector of international affairs to include any nonprofit organization working in international development, international relief services, disaster relief, international human rights, international peace and security, foreign policy research and analysis, and international exchange programs.

[^sample-size]:	A sample size of at least 500 respondents is typical when using conjoint data in a hierarchical Bayesian model. We doubled this amount because we are interested in analyzing subpopulations of respondents, which requires a larger sample.

[^model-details]:	Specifically,

    $$
    \begin{aligned}
    \beta &\sim \operatorname{Multivariate} \mathcal{N}(Z \Gamma, \xi) \\
    y &\sim \operatorname{Multinomial\ logit}(X \beta, \varepsilon)
    \end{aligned}
    $$

    where $y$ = which alternative the respondent chooses to donate to, $X$ = design matrix of attribute levels (i.e. organizations, issue areas, organizational practices, funding sources, and government relations), $\beta$ = latent individual preferences for the attribute levels, $Z$ = matrix of individual-level covariates (i.e. demographics, political knowledge, attitudes towards charity, etc.), $\Gamma$ = matrix of coefficients mapping individual-level covariates onto the latent individual-level preferences, and $\varepsilon$ and $\xi$ = errors.

### 2020-06-07 manuscript/manuscript.Rmd
Finish most remaining TODOs

@@
 abstract: >-
-  TODO: UPDATE THIS: Over the past decade, international nonprofit organizations (INGOs) have faced increasing legal scrutiny and closed civic space abroad.
+  Over the past decade, international nonprofit organizations (INGOs) have faced increasing legal scrutiny and closed civic space abroad.
 While we know this has negatively impacted public funding flows, we know little about how this has affected private funding flows, especially be individuals.
@@
 Which demographic and experiential factors influence the decision to donate to legally besieged NGOs?
-We investigate this question using nationally representative results from a vignette-based experiment and a conjoint experiment conducted on individuals with a history of charitable-giving.
+We investigate this question using a market simulation based on a nationally representative conjoint survey experiment conducted on individuals with a history of charitable giving.
+We find that trust in political institutions and charities is enormously influential in shaping donor preferences.
+Donor profiles with high levels of social trust are likely to donate to human rights INGOs with friendly relationships with host governments, but that support evaporates if INGOs face criticism or crackdown.
+In contrast, donor profiles with lower levels of social trust prefer to donate to organizations that do face criticism or crackdown abroad.
 Our findings have practical implications for INGOs that hope to raise funds from the general public amid closing civic space.
@@
 Over the past few decades, governments across the globe have been cracking down on civil society organizations (CSOs)—a phenomenon known as "closing civic space" in the policy arena [@CarothersBrechenmacher:2014; @CIVICUS:2017].
-Consequently, official aid flows to NGOs have decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
+Consequently, official aid flows to nongovernmental organizations (NGOs) have decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
 While we know that there has been a negative impact on funding flows from public sector organizations like USAID, DFID, and others, we know relatively little about how this global crackdown affects private funding flows, in particular from individual donors.
@@
 
-TODO ANDREW: [METHOD AND FINDINGS] We investigate these questions using a nationally representative survey of individuals in the U.S.
-with a previous history of charitable-giving.
-ONE LINE ABOUT EXPERIMENT.
-WHAT WE FIND
+We explore these questions using a simulated market for philanthropic donations, based on data and models from a nationally representative sample of individuals in the United States who regularly donate to charity.
+We adapt methods used in marketing research to generate dozens of distinct simulated personas that represent typical donor profiles, and we vary these personas along different dimensions of demographic, political, and social attributes.
+We find that specific individual characteristics help shape donor preferences for donating to international NGOs, and that an INGO's target issue area and its relationship with host government interact strongly with these characteristics.
+In particular, personas with high levels of trust in political and charitable institutions and who are actively engaged in charity and volunteerism tend to prefer donating to human rights organizations that have friendly relationships with their host governments.
+In contrast, personas with low levels of social trust eschew both human rights organizations *and* any type of NGO with friendly relationships with host governments and prefer instead to donate to NGOs facing more restrictions and working on less contentious issues like emergency response and refugee relief.
+This may indicate that donors with high trust and support for NGOs could be fair-weather friends that drop their support when their preferred organizations meet resistance abroad.
 
-This study contributes to both to scholarship and practice in public policy, nonprofits and philanthropic-giving.
+This study contributes to both to scholarship and practice in public policy, nonprofits and charitable giving.
 Individual-level philanthropic giving abroad can help bridge socioeconomic disparities worldwide, especially given the stark inequality in global distribution of income.
 Knowledge of demographic traits and prior experiences that make certain individuals more likely to donate can be very important to nonprofits, as this information can help them craft more effective and targeted marketing strategies [@Rajan:2009, 414].
-Most CSOs and nongovernmental organizations (NGOs) working internationally have previously relied on government and foundation funding.
+Most CSOs and NGOs working internationally have previously relied on government and foundation funding.
 But in the era of closing civic space, these groups may need to readjust their fundraising strategies to cater to private individuals.
@@
 More broadly, while research in public policy and nonprofit studies has focused on charitable giving, philanthropy is not seen as relevant by international relations as a discipline [@youde2019].
-However, philanthropy—particularly donations received by international non-governmental organizations (INGOs)—can help us understand changes in the dynamics of global governance.
+However, philanthropy—particularly donations received by international nongovernmental organizations (INGOs)—can help us understand changes in the dynamics of global governance.
 Private individuals exercise power and influence in unique ways that differ from other non-state actors.
@@
 
-TODO ANDREW: [ROADMAP] Below, we first explain the different fundings for CSOs working internationally, examining trends in individual donor to philanthropy to such causes.
-We then take a look at the state of the existing literature on the key drivers of philanthropy by individuals.
-We describe our survey experiment.
-FINISH ROADMAP.
+Below, we first explore how the global crackdown on civil society has led many CSOs working internationally to shift their fundraising strategies towards individual private donors rather than more restricted government and foundation sources.
+We then examine the state of the existing literature on the key drivers of individual charitable giving, as understanding what motivates private donations is crucial to more effective CSO fundraising.
+We then describe our survey experiment and simulation methods and explore the results.
+We conclude with a discussion of the implications our findings have on general INGO funding in the age of constrained civil society space.
 
@@
 
-Foreign aid to civil society, primarily via NGOs, has been steadily increasing over time.
-This is because many donors perceive that NGOs have superior ability to achieve intended outcomes.
+Foreign aid to civil society—and NGOs in particular—has steadily increased over time.
+One primary reason for this turn to civil society is that many government and foundation donors perceive that NGOs have a superior ability to achieve intended outcomes.
 In countries with weak institutions and poor governance, where direct aid transfers to governments raise issues of misuse and bureaucratic inefficiency, donors specifically seek out NGOs for projects [@Dietrich2013].
@@
 Thousands of international NGOs and CSOs in the Global South receive funds from a variety of public and private sources each year.
-Public funds (more commonly known as traditional donor aid) channels funds from official aid agencies through a variety of bilateral and multilateral institutions.
-Private funds, also newer international donors, included foundations, private corporations and individuals.
-In this paper, we specifically look at individual-level determinants to foreign giving.
+Public funds (more commonly known as traditional donor aid) channel money from official aid agencies through a variety of bilateral and multilateral institutions.
+Private sources include foundations, private corporations, and individuals.
+In this paper, we are most interested in individuals as a funding source, and we examine individual-level determinants to foreign giving.
 This is important to investigate as individual private donors may not necessarily mirror public donor choices.
 Surveys show that the American public is notoriously misinformed about US foreign aid [@norris:2017].
-Further, foreign aid and democracy aid is often considered unresponsive to developments on the ground [@brainard2007; @Carothers:2015] and public aid decisions - especially on final recipients are not easily accessible.
-There may also be heterogeneity within how donor governments allocate funds.
-Emerging donor government differ from established donors in that they demand fewer human rights, governance or environmental conditions preferred by Western donors [@fenglerkharas].
+Further, foreign aid and democracy aid is often considered unresponsive to developments on the ground [@brainard2007; @Carothers:2015] and public aid decisions—especially on final recipients— are not easily accessible.
+There is also substantial variety in how donor governments allocate funds.
+Emerging donor governments differ from established donors in that they demand fewer human rights, governance or environmental conditions preferred by Western donors [@fenglerkharas].
 
-With the advent of funding restrictions on NGOs globally and a consequent decline in official government aid and foundation funding, many groups are being forced to foreign individual donors.
-Giving to international affairs has been steadily increasing over the past two decades, with a noticeable increase over the past decade.
+With the advent of funding restrictions on NGOs globally and a subsequent decline in official government aid and foundation funding, many organizations are being forced to individual donors abroad.
+Donations to international affairs organizations has steadily increased over the past two decades, with a noticeable rise in the past decade.
 Between 2014 and 2016, giving to international affairs increased by 14.1% [@givingusa2017report].
 Most of this is driven by individuals making small-scale donations.
-In 2017, individuals gave \$286.7 billion - or approximately 70% of total giving to international affairs.
-This further increased to \$427.71 billion in 2018 - 85.7% of which was through individuals [givingusa:2019].
+In 2017, individuals gave \$286.7 billion, or approximately 70% of total giving to organizations working in international affairs.
+This further increased to \$427.71 billion in 2018, 85.7% of which was through individuals [givingusa:2019].
 Given that a majority of this research is restricted to elite, high net-worth donors [@USTrust2014], these figures show that it is imperative to understand motivations and attributes of small-scale donors as well.
@@
 
-A vast literature in philanthropic-giving looks at organizational-level factors that motivate individuals to donate [@BilodeauSlivinski:1997; @TBPrakash:2017].
+A vast literature in charitable giving looks at organizational-level factors that motivate individuals to donate [@BilodeauSlivinski:1997; @TBPrakash:2017].
 However, the decision to donate to an NGO is not determined solely by an organization's characteristics.
 Donors have particular personality traits, preferences, and experiences that make them more or less likely to engage in philanthropy.
-A robust literature in nonprofit studies has looked at individual donor behavior and characteristics for giving to local-rather than international-causes.
+A robust literature in nonprofit studies has looked at individual donor behavior and characteristics for giving to local—rather than international—causes.
 This literature has primarily focused on the importance of three main factors, especially when considering charitable behavior towards international causes: (1) social capital; (2) the role of higher education; (3) levels of religiosity; (4) wealth; and (5) national group attachment.
 
-One major area of inquiry in philanthropic studies looks at the role of social capital, or the "networks, norms, and social trust that facilitate coordination and cooperation for mutual benefit" [@Putnam:1995, 67].
-While quite broad, the literature further concentrates on a specific kind of social capital-associational capital, which refers to, "the networks of formal and informal relationships to which people are associated." [@havens2007, 240].
+One major area of inquiry in philanthropic studies examines the role of social capital, or the "networks, norms, and social trust that facilitate coordination and cooperation for mutual benefit" [@Putnam:1995, 67].
+While quite broad, the literature further concentrates on a specific kind of social capital—associational capital, or "the networks of formal and informal relationships to which people are associated." [@havens2007, 240].
 Prior research has found that those who participate in a variety of associations are more likely to make larger donations [@hossainlamb2017].
-Further, those who volunteer their time (compared to those who did not), were both more likely to make charitable donations and make bigger donations.
+Further, those who volunteer their time (compared to those who did not) were both more likely to make charitable donations and make bigger donations.
 This is because volunteering exposes individuals to the need for donations to charities and nonprofits and made them feel more compelled to do so [@hossainlamb2012].
 
-Higher education can also play an important role in philanthropic-giving decisions as such education fosters prosocial motivations.
+Higher education can also play an important role in charitable giving decisions as such education fosters prosocial motivations.
 It also brings people into particular social networks that entail a higher level of solicitations [@BekkersWiepking:2011].
@@
 
-Higher education can also play an important role in determining the kinds of causes that people donate to globally.
-A number of NGOs facing crackdowns abroad work on issues that may be seen as "contentious" - these include human rights, elections, corruption, advocacy, media freedom - causes that may have a harder time attracting funds due to their non-essential nature when compared to causes like health, education, sanitation, and social services.
-However, additional education has been shown to increase abstract thinking [@wiepkingmaas, 1978], which may be necessary to donate to causes that do not have quantifiable goals - which is particularly important for organizations with more "contentious" causes as part of their missions [@Bush:2015].
+Higher education also helps determine the kinds of causes that people donate to globally.
+A number of NGOs facing crackdowns abroad work on issues that may be seen as "contentious," including human rights, elections, corruption, advocacy, media freedom—all issues that may have a harder time attracting funds due to their non-essential nature when compared to causes like health, education, sanitation, and social services.
+However, additional education has been shown to increase abstract thinking [@wiepkingmaas, 1978], which may be necessary to donate to causes that do not have quantifiable goals, which is particularly important for organizations with more "contentious" causes as part of their missions [@Bush:2015].
 
 Levels of religiosity are also a significant predictor of the likelihood and level of giving.
-People who regularly attention religious services are more likely to have prosocial values, face a stronger norm of charitable-giving, and may feel pressure to conform that group and community standard [@wiepking2010].
+People who regularly attention religious services are more likely to have prosocial values, face a stronger norm of charitable giving, and may feel pressure to conform that group and community standard [@wiepking2010].
 Regular attendance may also strengthen individuals' beliefs in organizations' missions.
@@
 Overall, individuals with higher levels of income, education, and greater religious proclivities have been shown to not only be more likely to give internationally, but also to give higher amounts [@Rajan:2009; @CasaleBaumann:2015].
-INSERT LINE ABOUT while we expect these determinants to hold similar significance in our survey, we do not specifically lay out hypotheses because this is exploratory/descriptive/we barely know about international giving so we don't have specific expectations about international giving during crackdown.
-BUT ALSO WHAT ARE WE DOING THAT HASN'T BEEN DONE YET.
-
-TODO ANDREW: NEW GROUNDBREAKING STUFF = combining individual-level characteristics with organization characteristics - Looking at a persona is not typical - we often look at the effect of a single covariate, not a combination of them.
-But looking at the impact of a persona — which in all reality is a fabricated individual — has interesting appeal.
+While we expect these determinants to be reflected in our survey experiment, we do not lay out specific hypotheses.
+Because there is so little research about international donations during legal crackdown by host governments, our analysis and results are exploratory and descriptive.
+Our innovative experimental approach, however, provides rich quantitative details of individual and organizational characteristics simultaneously and reveals unique insights into donor motivations that both confirm and expand previous research.
 
@@
 
-We recruited survey respondents through Centiment, a commercial provider of high quality non-probability opt-in survey panels.
+In June 2019, We recruited survey respondents through Centiment, a commercial provider of high quality non-probability opt-in survey panels.
 Sentiment ensures panel quality by actively recruiting representative samples of the US population and rewards participants with monetary incentives.
@@
 
+\newpage
+
 ```{r child = "output/tables/tbl-sample-details.md"}
-
 ```
@@
 Most rarely attend church, but feel that religion is important.
-Respondents are also engaged civically (three quarters voted in the last election) and follow national news closely (70% follow the news daily).
+Respondents are also civically engaged (three quarters voted in the last election) and follow national news closely (70% follow the news daily).
 Respondents are fairly balanced ideologically, with the majority reporting a 3, 4, or 5 on a 7-point scale of liberal–conservative political ideology.
@@
 Disentangling the effect of every individual level-characteristics on every combination of organizational characteristics is unwieldy and near impossible.
-Given the organizational attributes presented in our experiment, and the possible individual characteristics that respondents could select, there are billions of possible combinations and iterations of organizational and individual attributes.
+Given the organizational attributes presented in our experiment, and the possible individual characteristics that respondents could select, there are billions of possible combinations and iterations of organizational and individual attributes—many of which rarely occur in the actual population of potential donors.
+In our previous work—and in most research that relies on regression model—the analytic focus is on individual regression coefficients and the effect of single covariates of interest.
+To more fully explore the relationships between different organizational- and individual-level attributes, we turn to simulation methods that allow us to examine the impact of multiple covariates at simultaneously
 
-Instead of trying to work through all these countless combinations—most of which rarely occur in the actual population of potential donors—we rely on simulation methods to examine the effect of more general combinations of individual characteristics.
 We use market segmentation methods to construct simulated personas that interact with simulated organizations in a market for charitable contributions.
-To simplify the many possible combinations of individual characteristics, we generate 32 distinct personas with attributes that vary along different dimensions of demographics, politics and public affairs experience, and social attitudes (see Table XXX).
-We also generate 24 simulated organizations that vary by issue area, relationship with host government, and source of funding.
+To simplify the many possible combinations of individual characteristics, we generate 32 distinct personas with attributes that vary along different dimensions of demographics, politics and public affairs experience, and social attitudes (see @tbl:persona-attributes).
+We also generate 24 simulated organizations that vary by issue area, relationship with host government, and source of funding (see @tbl:organization-attributes).
 This combination of personas and organizations yields 768 hypothetical scenarios where potential donors can interact with different organizations.
 
-TODO ANDREW: Simplified persona table + organization table
+```{r child = "output/tables/tbl-persona-attributes.md"}
+```
+
+```{r child = "output/tables/tbl-organization-attributes.md"}
+```
 
 We then combine these different scenarios of donor and organization attributes with the coefficients from a multinomial multilevel regression model to calculate the probability that each simulated persona has of giving to specific combinations of organizational attributes.
-Any individual characteristics that we do not explicitly vary in Table X are held at their means or modal values from the survey sample.
-Table X provides an example of the simulation output, showing how two different personas are predicted to allocate donations to organizations with various characteristics.
+Any individual characteristics that we do not explicitly vary in  @tbl:persona-attributes are held at their means or modal values from the survey sample.
+@tbl:sim-output provides an example of the simulation output, showing how two different personas are predicted to allocate donations to organizations with various characteristics.
 The proportion of donations from each persona sums to 100%, as every persona is guaranteed to make a donation.
 
-TODO ANDREW: Two simplified sample personas
+```{r child = "output/tables/tbl-sim-output.md"}
+```
 
@@
 Personas respond differently to organizational issue areas.
-In @fig:issue-social, those who follow the news and travel abroad are more likely to prefer donating to human rights organizations than their less knowledgable and less travelled counterparts.
+In @fig:issue-social, those who follow the news and travel abroad are more likely to prefer donating to human rights organizations than their less knowledgeable and less traveled counterparts.
 Personas who do not follow the news or travel show a greater preference for emergency response and refugee relief organization, similar to the income effects seen previously.
@@
 Figure @fig:relationship-social shows how personas respond to different NGO–host government relationships.
-Public affairs knowledge and experience has little effect on donor preferences—the average market shares are roughly identical across the two columns of the figure.
+Public affairs knowledge and experience has little effect on donor preferences, as the average market shares are roughly identical across the two columns of the figure.
 Similarly, there are no ideological differences across the rows of the figure.
@@
 With the turn towards private philanthropy in the face of the global crackdown on civil society and declining official aid and official development assistance, INGOs need to be aware of the dynamics of individual donor preferences.
-WHAT WE FIND
+Based on our simulated market of 24 organizations and 32 persona profiles, we find several important trends.
+On average, human rights organizations tend to attract personas who are wealthier, follow national and international news, and travel abroad, while donors who are less wealthy, follow the news less often, and do not travel are more attracted to organizations working on  less contentious like emergency response and refugee relief.
+More importantly, we found that trust in political institutions and in charitable organizations in general matters substantially in shaping donor preferences.
+Personas with high levels of social and charitable trust prefer donating to human rights organizations that have friendly relationships with their host governments, while personas with low trust are drawn more to NGOs emergency response and refugee relief organizations with unfriendly relationships with their host governments.
+Personas with low social trust rarely prefer to donate to any type of organization with friendly host-country relationships, while personas with high social trust tend to avoid organizations with unfriendly relationships.
+This could imply that donors that are the most trusting and involved might be fair-weather friends that drop their support when charities face government criticism and crackdown.
+
+TODO: All this conclusionary stuff + so what/implications?
 
@@
 Finally, it is important to acknowledge the role played by civil society organizations in dealing with health, poverty, and disaster - social needs that are tremendously important during the COVID-19 pandemic.
-This survey was conducted in July (?) 2019 - can we expect insights from this survey to hold even during this time period, even as the world sees an economic recession?
+This survey was conducted in June 2019 - can we expect insights from this survey to hold even during this time period, even as the world sees an economic recession?
 We argue that this is the case for two main reasons.

### 2020-09-17 manuscript/manuscript.Rmd
Suparna edits

@@
 ---
-title: "Who Cares About Crackdowns? Exploring Individual Donor Responses to Closing Civic Space Abroad"
+title: "Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy"
 short-title: "Who Cares About Crackdowns?"
@@
   email: aheiss@gsu.edu
-date: "June 5, 2020"
+date: "June 8, 2020"
 published: Working paper.
@@
 abstract: >-
-  Over the past decade, international nonprofit organizations (INGOs) have faced increasing legal scrutiny and closed civic space abroad.
-While we know this has negatively impacted public funding flows, we know little about how this has affected private funding flows, especially be individuals.
-This turn to private aid introduces potentially new dynamics in INGO fundraising strategies, since individuals have a range of demographic characteristics and past experiences with philanthropy that shape their propensity to donate.
-Which demographic and experiential factors influence the decision to donate to legally besieged NGOs?
+  Over the past two decades, international nonprofit organizations (INGOs) have faced increasing legal scrutiny abroad, which has negatively impacted public funding flows.
+Consequently, INGOs may feel the need to fundraise from individuals.
+Which demographic and experiential factors influence the decision of individuals to donate to legally besieged NGOs?
 We investigate this question using a market simulation based on a nationally representative conjoint survey experiment conducted on individuals with a history of charitable giving.
@@
 In Human Rights Watch's 2016 annual report, Executive Director Kenneth Roth argued that civil society was under more aggressive attack than at any time in recent memory.
-Over the past few decades, governments across the globe have been cracking down on civil society organizations (CSOs)—a phenomenon known as "closing civic space" in the policy arena [@CarothersBrechenmacher:2014; @CIVICUS:2017].
-Consequently, official aid flows to nongovernmental organizations (NGOs) have decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
-While we know that there has been a negative impact on funding flows from public sector organizations like USAID, DFID, and others, we know relatively little about how this global crackdown affects private funding flows, in particular from individual donors.
+Over the past few decades, governments across the globe have been cracking down on civil society organizations (CSOs) and non-governmental organizations (NGOs)—a phenomenon known as "closing civic space" in the policy arena [@CarothersBrechenmacher:2014; @CIVICUS:2017].[^NGOdef] As part of this phenomenon, CSOs, particularly NGOs, face increasing obstacles to their work, including legal restrictions and threats to their freedom of association, expression and speech.
+Legal restrictions-a core part of these efforts-create barriers to entry, funding, and advocacy for NGOs in an effort to control, obstruct or repress these organizations-what we refer to as legal crackdowns in this paper.
 
-Existing scholarship on the determinants of individual-level philanthropy to domestic causes is quite robust across a variety of contexts.
-But the dynamics of *international* giving are under-examined in the literature on individual donor preferences.[^exceptions].
-Research on the determinants of philanthropy towards international causes—particularly for organizations working in challenging environments—is still in its infancy due to the absence of expansive and high-quality data [@greenhill2013].
-Understanding why individuals donate to international causes is especially essential to understand, given that such philanthropy can be harder to motivate because the number of recipients are large and far removed from the donor [@CasaleBaumann:2015, 100].
+As a result of these legal crackdowns, official aid flows to NGOs have decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
+While this has negatively impacted funding flows from public organizations like USAID, DFID, and other OECD funding agencies, philanthropy from private donors, in particular, foundations, appears to not be as adversely affected [@McGill:2018].
+Given this trend of closing civic space, NGOs need access to multiple sources of funding and individual-level giving can serve as one such source of funds.
+What individual donor characteristics and attributes are most salient for INGOs interested in maximizing philanthropy towards their operations abroad?
 
-The amount of money donated by private individuals to CSOs working abroad, however, has steadily increased over time. 
+Existing scholarship on the determinants of individual-level philanthropy to domestic causes is robust across a variety of contexts.
+But the dynamics of *international* giving to NGOs are under-examined in the literature on individual donor attributes and preferences.[^exceptions] Research on the determinants of philanthropy towards international causes—particularly for organizations working in challenging environments—is still in its infancy due to the absence of expansive and high-quality data [@greenhill2013].
+Understanding why individuals donate to international causes is essential as it can be harder to motivate as the number of recipients are large and far removed from the donor [@CasaleBaumann:2015, 100].
+
+Individual giving is also important to understand because the amount of money donated by private individuals to CSOs working abroad has steadily increased over time.
 Total aggregate philanthropy in the United States has grown substantially over time, reaching more than \$400 billion in 2018 (@fig:giving-aggregate).
-In 2018, total private giving to CSOs working specifically in international affairs reached $22.08 billion.
-More importantly, organizations working in the area of international affairs are one of the only two types of recipient organizations that have continued experiencing substantial growth in giving—even at a time when giving to religious institutions, education, human services and arts, culture and society has been on the decline [@givingusa:2019].[^intlaffairs]
+In 2018, total private giving to CSOs working specifically in international affairs reached \$22.08 billion.
+Moreover, organizations working in the area of international affairs are one of the only two types of recipient organizations that have continued experiencing substantial growth in giving [@givingusa:2019].[^intlaffairs] Most of this is driven by individuals making small-scale or micro-donations.[^small donors] In 2017, individuals gave \$286.7 billion, or approximately 70% of total giving to organizations working in international affairs.
+This further increased to \$427.71 billion in 2018, 85.7% of which was through individuals [@givingusa:2019].
+However, we lack a systematic understanding of which individual donors may be further motivated or deterred to donate under an increasingly restricted civic space abroad.
+What is the optimal mix of individual-level donor attributes for international NGOs working in restricted political environments interested in maximizing donations?
+What kinds of individual donors are more or less likely to consider an NGO's host country political environment when making the decision to donate?
 
@@
 
-While this may be a cause for optimism among CSOs working internationally, we know little about the individuals who donate to CSOs working in other countries.
-We also lack any systematic understanding of how such giving is affected by an increasingly restricted civic space abroad.
-Given these challenges, what is the optimal mix of individual-level donor attributes for international NGOs working in restricted political environments interested in maximizing donations?
-What kinds of individual donors are more or less likely to consider a CSO's host country political environment, its transparency and accountability practices, and its funding structure when making the decision to donate?
-How do individual-level donor characteristics such as political ideology, knowledge, activism and other demographic characteristics interact with organizational-level attributes to influence philanthropic decisions?
-
-We explore these questions using a simulated market for philanthropic donations, based on data and models from a nationally representative sample of individuals in the United States who regularly donate to charity.
+We explore these questions using a simulated market for philanthropic donations, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity.
 We adapt methods used in marketing research to generate dozens of distinct simulated personas that represent typical donor profiles, and we vary these personas along different dimensions of demographic, political, and social attributes.
 We find that specific individual characteristics help shape donor preferences for donating to international NGOs, and that an INGO's target issue area and its relationship with host government interact strongly with these characteristics.
-In particular, personas with high levels of trust in political and charitable institutions and who are actively engaged in charity and volunteerism tend to prefer donating to human rights organizations that have friendly relationships with their host governments.
-In contrast, personas with low levels of social trust eschew both human rights organizations *and* any type of NGO with friendly relationships with host governments and prefer instead to donate to NGOs facing more restrictions and working on less contentious issues like emergency response and refugee relief.
+Personas with high levels of trust in political and charitable institutions and who are actively engaged in charity and volunteerism prefer donating to human rights organizations that have friendly relationships with their host governments.
+In contrast, personas with low levels of social trust eschew both human rights organizations *and* any type of NGO with friendly relationships with host governments, preferring instead to donate to NGOs facing more restrictions and working on less contentious issues like emergency response and refugee relief.
 This may indicate that donors with high trust and support for NGOs could be fair-weather friends that drop their support when their preferred organizations meet resistance abroad.
 
-This study contributes to both to scholarship and practice in public policy, nonprofits and charitable giving.
+This study contributes to both to scholarship and practice in public policy, nonprofits and charitable-giving.
 Individual-level philanthropic giving abroad can help bridge socioeconomic disparities worldwide, especially given the stark inequality in global distribution of income.
-Knowledge of demographic traits and prior experiences that make certain individuals more likely to donate can be very important to nonprofits, as this information can help them craft more effective and targeted marketing strategies [@Rajan:2009, 414].
-Most CSOs and NGOs working internationally have previously relied on government and foundation funding.
-But in the era of closing civic space, these groups may need to readjust their fundraising strategies to cater to private individuals.
+Knowledge of demographic traits and its impact on funding can help nonprofits craft more effective and targeted marketing strategies [@Rajan:2009, 414].
+Most NGOs working internationally have previously relied on government and foundation funding.
+But in the era of closing civic space, these groups may need to readjust their fundraising strategies to cater to individuals.
+Framing is important in this regard—how people process information affects their willingness to donate.[^framing] However, we lack systematic studies of which frames may be effective when making appeals to individual donors considering international philanthropy.
+Since our study looks at multiple organizational-level factors, it can help these CSOs frame their appeals.
 
-Framing is particularly important in this regard—how people process information affects their willingness to donate.[^framing] However, we lack systematic studies of which frames may be effective when making appeals to individual donors considering international philanthropy.
-Since our study looks at multiple factors, it can help these CSOs frame their appeals.
-
-More broadly, while research in public policy and nonprofit studies has focused on charitable giving, philanthropy is not seen as relevant by international relations as a discipline [@youde2019].
+More broadly, while research in public policy and nonprofit studies has focused on giving to NGOs, philanthropy is not seen as relevant by international relations as a discipline [@youde2019].
 However, philanthropy—particularly donations received by international nongovernmental organizations (INGOs)—can help us understand changes in the dynamics of global governance.
@@
 
-Below, we first explore how the global crackdown on civil society has led many CSOs working internationally to shift their fundraising strategies towards individual private donors rather than more restricted government and foundation sources.
-We then examine the state of the existing literature on the key drivers of individual charitable giving, as understanding what motivates private donations is crucial to more effective CSO fundraising.
+Below, we first examine the state of the existing literature on the key drivers of individual charitable giving, as understanding what motivates private donations is crucial to more effective NGO fundraising.
 We then describe our survey experiment and simulation methods and explore the results.
@@
 Foreign aid to civil society—and NGOs in particular—has steadily increased over time.
-One primary reason for this turn to civil society is that many government and foundation donors perceive that NGOs have a superior ability to achieve intended outcomes.
-In countries with weak institutions and poor governance, where direct aid transfers to governments raise issues of misuse and bureaucratic inefficiency, donors specifically seek out NGOs for projects [@Dietrich2013].
+Many government and foundation donors perceive that NGOs have a superior ability to achieve intended outcomes.
+Therefore, in countries with weak institutions and poor governance, where direct aid transfers to governments raise issues of misuse and bureaucratic inefficiency, donors specifically seek out NGOs for projects [@Dietrich2013].
 These groups provide services to large parts of the population in the Global South, especially where governments are unable to do so on a consistent basis.
-More broadly, a robust civil society is also considered to be one of the necessary preconditions for a healthy, functioning democracy due to its ability to generate social capital and hold governments accountable [@Putnam:1995].
 
-## Sources of foreign aid
+## Sources of funding
 
-Thousands of international NGOs and CSOs in the Global South receive funds from a variety of public and private sources each year.
+Thousands of INGOs in the Global South receive funds from a variety of public and private sources each year.
 Public funds (more commonly known as traditional donor aid) channel money from official aid agencies through a variety of bilateral and multilateral institutions.
 Private sources include foundations, private corporations, and individuals.
-In this paper, we are most interested in individuals as a funding source, and we examine individual-level determinants to foreign giving.
-This is important to investigate as individual private donors may not necessarily mirror public donor choices.
-Surveys show that the American public is notoriously misinformed about US foreign aid [@norris:2017].
-Further, foreign aid and democracy aid is often considered unresponsive to developments on the ground [@brainard2007; @Carothers:2015] and public aid decisions—especially on final recipients— are not easily accessible.
-There is also substantial variety in how donor governments allocate funds.
-Emerging donor governments differ from established donors in that they demand fewer human rights, governance or environmental conditions preferred by Western donors [@fenglerkharas].
+While INGOs have not been passive in responding to the crackdown on civil society, they face increasing obstacles especially from a funding perspective.
+Official aid donors have reduced the amount of aid channeled to countries with legal restrictions @DupuyPrakash:2018].
+In addition, official donors have also redirected funds within restrictive countries, decreasing funds for politically sensitive causes in favor of tamer issues that are more compatible with the governments of other countries [@ChaudhryHeiss:2018].
+However, it is notable that private funding towards international nonprofits has not been as adversely affected.
+Many foundations have continued channeling funds to countries with hostile legal environments [@FoundationCenter2018].
 
-With the advent of funding restrictions on NGOs globally and a subsequent decline in official government aid and foundation funding, many organizations are being forced to individual donors abroad.
-Donations to international affairs organizations has steadily increased over the past two decades, with a noticeable rise in the past decade.
-Between 2014 and 2016, giving to international affairs increased by 14.1% [@givingusa2017report].
-Most of this is driven by individuals making small-scale donations.
-In 2017, individuals gave \$286.7 billion, or approximately 70% of total giving to organizations working in international affairs.
-This further increased to \$427.71 billion in 2018, 85.7% of which was through individuals [givingusa:2019].
-Given that a majority of this research is restricted to elite, high net-worth donors [@USTrust2014], these figures show that it is imperative to understand motivations and attributes of small-scale donors as well.
+The advent of funding restrictions on NGOs globally and a subsequent decline in government and foundation funding has made the role and value of individual philanthropy in sustaining NGOs even clearer.[^phildef] NGOs need access to a diverse array of funds and individual donations to international affairs organizations have steadily increased over the past two decades.
+Between 2014-2016, giving to organizations working in international affairs increased by 14.1% [@givingusa2017report].
+Moreover, at least in the U.S.
+context, donations from individuals far outstripped foundation and corporate giving.
+In 2018, individual donations amounted to \$292.09 billion, compared to \$75.86 billion from foundations and \$20.05 billion from corporations [Source from NVSQ].
+Given that a majority of research is restricted to elite high net-worth donors [@USTrust2014], these figures show that it is imperative to understand motivations and attributes of small-scale donors as well.
+In this paper, we therefore look at which kinds of individual donors—beyond high-net worth donors—are most likely to give abroad.[^highnetworth]
 
@@
 
-A vast literature in charitable giving looks at organizational-level factors that motivate individuals to donate [@BilodeauSlivinski:1997; @TBPrakash:2017].
-However, the decision to donate to an NGO is not determined solely by an organization's characteristics.
-Donors have particular personality traits, preferences, and experiences that make them more or less likely to engage in philanthropy.
+A vast literature on philanthropy looks at organizational-level factors that motivate individuals to donate [@BilodeauSlivinski:1997; @TBPrakash:2017].
+However, donation decisions are not determined solely by an organization's characteristics.
+Donors have personality traits, preferences, and experiences that make them more or less likely to engage in philanthropy.
 A robust literature in nonprofit studies has looked at individual donor behavior and characteristics for giving to local—rather than international—causes.
-This literature has primarily focused on the importance of three main factors, especially when considering charitable behavior towards international causes: (1) social capital; (2) the role of higher education; (3) levels of religiosity; (4) wealth; and (5) national group attachment.
+This literature focuses on the importance of five main attributes: (1) social capital; (2) the role of higher education; (3) levels of religiosity; (4) wealth; and (5) national group attachment.
 
-One major area of inquiry in philanthropic studies examines the role of social capital, or the "networks, norms, and social trust that facilitate coordination and cooperation for mutual benefit" [@Putnam:1995, 67].
-While quite broad, the literature further concentrates on a specific kind of social capital—associational capital, or "the networks of formal and informal relationships to which people are associated." [@havens2007, 240].
-Prior research has found that those who participate in a variety of associations are more likely to make larger donations [@hossainlamb2017].
+One major area of inquiry in philanthropic studies examines the role of social capital, particularly associational capital, or "the networks of formal and informal relationships to which people are associated." [@havens2007, 240].
+Research finds that those who participate in a variety of associations are more likely to make larger donations [@hossainlamb2017].
 Further, those who volunteer their time (compared to those who did not) were both more likely to make charitable donations and make bigger donations.
-This is because volunteering exposes individuals to the need for donations to charities and nonprofits and made them feel more compelled to do so [@hossainlamb2012].
+Volunteering exposes individuals to the need for donations, making them feel more compelled to donate [@hossainlamb2012].
 
-Higher education can also play an important role in charitable giving decisions as such education fosters prosocial motivations.
-It also brings people into particular social networks that entail a higher level of solicitations [@BekkersWiepking:2011].
-This in turn has been shown to be particularly vital in giving to international causes.
+Higher education can also play an important role in charitable-giving decisions as it fosters prosocial motivations.
+It also brings people into particular social networks that entail a higher level of solicitations, which is vital in giving to international causes [@BekkersWiepking:2011].
 @Micklewright:2009 show that higher education matters more for donating to international relief organizations than donating to domestic organizations.
-An additional year of education has been shown to increase the likelihood of giving to international causes by about 2 percentage points [@OktenOsili:2007].
 
 Higher education also helps determine the kinds of causes that people donate to globally.
-A number of NGOs facing crackdowns abroad work on issues that may be seen as "contentious," including human rights, elections, corruption, advocacy, media freedom—all issues that may have a harder time attracting funds due to their non-essential nature when compared to causes like health, education, sanitation, and social services.
+A number of NGOs facing crackdowns abroad work on issues that may be seen as "contentious," including human rights, elections, corruption, advocacy, media freedom—issues that may have a harder time attracting funds due to their non-essential nature when compared to causes like health, education, sanitation, and social services.
 However, additional education has been shown to increase abstract thinking [@wiepkingmaas, 1978], which may be necessary to donate to causes that do not have quantifiable goals, which is particularly important for organizations with more "contentious" causes as part of their missions [@Bush:2015].
@@
 Regular attendance may also strengthen individuals' beliefs in organizations' missions.
-However, religiosity does not necessarily have the same effect on giving to all causes.
-@neumayrhandy2019 find that religiosity is negatively associated with giving to environmental issues and animal welfare, while having an insignificant effect on giving to international relief.
 
-Finally, recent research has also looked at how a sense of ethnonationalism and national group attachment affects the decision to donate to domestic and international charities.
+Finally, recent research looks at how a sense of ethnonationalism and national group attachment affects the decision to donate to domestic and international charities.
 Looking at UK respondents, @hartrobson2019 find that whereas nationalists have a preference for domestic charities, they are not necessarily averse to donating to international causes, whereas internationalists have a strong preference for donating to causes and groups working abroad.
-More specifically, research finds that immigrant households are more likely to contribute to international aid organizations [@OktenOsili:2007], and that immigrants can find value in donating to both home and host cultures, especially if family members are still residing in the home country [@burgoyne2005].
+More specifically, immigrant households are more likely to contribute to international aid organizations [@OktenOsili:2007], and that immigrants can find value in donating to both home and host cultures, especially if their family members still reside in the home country [@burgoyne2005].
 
-Overall, individuals with higher levels of income, education, and greater religious proclivities have been shown to not only be more likely to give internationally, but also to give higher amounts [@Rajan:2009; @CasaleBaumann:2015].
+Overall, individuals with higher levels of income, education, and greater religious proclivities are not only more likely to give internationally, but also give higher amounts [@Rajan:2009; @CasaleBaumann:2015].
 While we expect these determinants to be reflected in our survey experiment, we do not lay out specific hypotheses.
@@
 After collecting baseline information on respondent demographics and attitudes toward charity and voluntarism, we presented respondents with four randomly selected international nonprofit organizations with four randomly assigned features.^[See the appendix for a copy of the survey.] We included organizations that are associated with a range of contentious and noncontentious issues: Amnesty International, Greenpeace, Oxfam, and the International Committee of the Red Cross.
+These organizations are commonly used in surveys on TODO TODO, in addition to other organizations such as MSF, World Vision (LOOK UP SAVED PAPERS - I THINK NVSQ).
 We then displayed various combinations of features, including one of four issue areas (emergency response, environmental advocacy, human rights advocacy, and refugee relief), one of two organizational practices (financial transparency and third-party accountability audits), one of three funding sources (many small private donations, a handful of wealthy private donors, and government grants), and one of three relationships with host governments (friendly, criticized by the government, and under government crackdown).
@@
 
-In June 2019, We recruited survey respondents through Centiment, a commercial provider of high quality non-probability opt-in survey panels.
-Sentiment ensures panel quality by actively recruiting representative samples of the US population and rewards participants with monetary incentives.
+In June 2019, we recruited survey respondents through Centiment, a commercial provider of high quality non-probability opt-in survey panels.
+Centiment ensures panel quality by actively recruiting representative samples of the US population and rewards participants with monetary incentives.
 To participate in the study, respondents were first screened based on their charitable activities.
@@
 
-In previous work [@ChaudhryDotsonHeiss:2019], we use the results of this survey experiment to measure how the organizational characteristics of an NGO can influence donor preferences.
-We find that donors prefer to give money to organizations that engage in transparency and accountability practices, receive funding from many individual donors, and that work on humanitarian issues like disaster and refugee relief.
-Importantly, we also find that donors are less likely to be interested in donating to NGOs facing government crackdown abroad.
-These results provide unique insight for NGOs looking to raise money from private donors and can influence how these organizations might frame their calls for fundraising.
-
-However, the findings in @ChaudhryDotsonHeiss:2019 focus only on organizational attributes and do not distinguish between different types and specific characteristics of donors.
-As part of the survey experiment, we collected information about the survey respondents themselves, including their demographic characteristics and their interest and involvement in public affairs, charity, voluntarism, politics, and religion.
-
-In this paper, we focus instead on exploring which kinds of donors are more or less likely to consider an NGO's issue area, funding sources, and host country politics when deciding to donate.
-Disentangling the effect of every individual level-characteristics on every combination of organizational characteristics is unwieldy and near impossible.
+In this paper, we look at which kinds of donors are more or less likely to consider an NGO's issue area, funding sources, and host country politics when deciding to donate.
+Disentangling the effect of every individual level-characteristics measured in the survey on every combination of organizational characteristics presented in the conjoint experiment is unwieldy and near impossible.
 Given the organizational attributes presented in our experiment, and the possible individual characteristics that respondents could select, there are billions of possible combinations and iterations of organizational and individual attributes—many of which rarely occur in the actual population of potential donors.
-In our previous work—and in most research that relies on regression model—the analytic focus is on individual regression coefficients and the effect of single covariates of interest.
 To more fully explore the relationships between different organizational- and individual-level attributes, we turn to simulation methods that allow us to examine the impact of multiple covariates at simultaneously
@@
 We also generate 24 simulated organizations that vary by issue area, relationship with host government, and source of funding (see @tbl:organization-attributes).
-This combination of personas and organizations yields 768 hypothetical scenarios where potential donors can interact with different organizations.
 
@@
 Relying on simulation methods offers useful analytic benefits.
-Rather than interpret individual marginal effects from a regression model, we can explore multiple moving parts from the same model simultaneously to understand how characteristics interact with each other.
+Rather than interpret individual marginal effects from a regression model, we can explore multiple moving parts from the same model simultaneously to understand how individual characteristics interact with each other.
 This allows us to more fully explore our key research questions and see which kinds of donors are more or less likely to consider specific organizational attributes when deciding to donate, and which donor characteristics are associated with the propensity to donate.
@@
 Our analysis uses the characteristics of our sample to model the effects of various salient attributes while holding others constant, and thus allows us to explore multiple attributes at once.
+
 Also importantly, our findings are not causal.
@@
 
-Figures @fig:issue-social, @fig:relationship-social, and @fig:funding-social show the results of the market simulation across these three dimensions of persona characteristics, varying public affairs knowledge, political ideology, and social trust.
+@fig:issue-social, @fig:relationship-social, and @fig:funding-social show the results of the market simulation across these three dimensions of persona characteristics, varying public affairs knowledge, political ideology, and social trust.
 Personas respond differently to organizational issue areas.
@@
 Both conservative and liberal personas tend to follow similar patterns of preference across NGO issue.
+
 Social trust plays a substantial role in determining simulated market share, however.
@@
 
-Figure @fig:relationship-social shows how personas respond to different NGO–host government relationships.
+@fig:relationship-social shows how personas respond to different NGO–host government relationships.
 Public affairs knowledge and experience has little effect on donor preferences, as the average market shares are roughly identical across the two columns of the figure.
@@
 Once the organization faces criticism or crackdown, however, support deteriorates rapidly, since such a crackdown could be perceived as a violation of the persona's trust in the charity—that is, the organization must be doing something wrong to deserve criticism.
-Personas with low levels of trust, on the other hand, are eschew friendly organizations entirely and are far more willing to donate to organizations facing criticism and crackdown, likely because they do not assume that charities must always be above reproach.
+Personas with low levels of trust, on the other hand, eschew friendly organizations entirely and are far more willing to donate to organizations facing criticism and crackdown, likely because they do not assume that charities must always be above reproach.
 The global crackdown on NGOs could thus counterintuitively sour NGOs' most trusting donors.
@@
 
+## Concerns about inference and generalizability
+
+While the survey seeks to uncover donor profiles of those who are influenced by legal crackdowns on NGOs in their decision to donate, it may be possible that results are based on respondents' prior beliefs about Amnesty, Oxfam, Greenpeace, and Red Cross.
+This may particularly be the case after an Oxfam scandal in Feburary 2018—scandals that may potentially strength the narrative that the nonprofit sector suffers from governance failures [@SurlockEtal2020].
+Analyzing a smaple of Twitter data to studythe daily gap between the positive and negative sentiments expressed towards INGOs embroiled in scandals, @SurlockEtal2020 find that while sentiments towards Oxfam did not completely recover even 6 months after the scandal, Save the Children's reputation recovered fairly quickly.
+Moreover, the recovery of their reputation was aided specifically by celebrity endorsements as well as be focusing public attention on the organizations' achievements.
+While reputational damage can lead to decline in donations and grants, their research lays provides important foundational evidence demonstrating both, "short-term fragility and longer-term durability of organizations' reputations" [SurlockEtal2020, p.
+104].
+
+However, given that the above analysis is not representative of the general population, we also sought out other surveys that could provide an insight into donors' prior beliefs and their possible impact on donation preferences.
+Contrary to media sentiment, we found that trust and confidence in NGOs specifically in the UK did not waver [@citemehere].
+We also failed to find evidence that these impacted public opinion among likely individual donors in the US - who were the main respondents in our survey [@CITE].
+Rather, any lack of trust towards overseas NGOs, particularly aid and developmental agencies often results due to donors perceiving INGOs as having low personal relevance [@FaulknerTruongRomanuik2015].
+Many individual donors have a preference to donate locally and they lack sufficient knowledge to make an informed decision about donating internationally.
+Overall, the literature suggests that lack of awareness is a much bigger issue for INGO fundraising, rather than specific scandals that would reduce the average individual donors' trust and confidence in these NGOs.
+
+The study was also conducted on a random sample of U.S.
+respondents with a prior history of charitable giving which raises questions about external validity.
+Public expectations about the role of public and private sectors differ across the U.S.
+and European countries.
+In the U.S., CSOs are typically seen as a counterweight to the government, whereas in some European countries like Germany, states are seen as supporting CSOs.
+Further, when we consider large INGOs such as Amnesty International and MSF - both receive very little support from their home governments (Stroup 2012).
+This may imply that donors in UK and France may have very different preferences when choosing to donate to government or privately-funded organizations.
+As such, more comparative research is needed to see if these results would also replicate across a variety of European countries
+
+There is also notable variation in terms of the targets of donations across various contexts.
+Though charitable-giving amounts are highest in the U.S, such donations are overwhelmingly towards local and religious causes.
+However, this pattern does not hold for many European countries.
+In the UK, international aid is often the largest component of giving (26%) while in Germany, Belgium, and Switzerland, international and humanitarian aid is considered a priority with 74%, 61% and 43% of donations are directed towards these causes in these countries, respectively.
+Thus, if crackdown on nonprofits abroad can elicit the results demonstrated in this paper among US respondents, then they provide reasons for optimism for pursuing individual philanthropy in Europe as well.
+However, more comparative research is required in order to confirm these trends.
+
 # Implications and conclusion
 
-With the turn towards private philanthropy in the face of the global crackdown on civil society and declining official aid and official development assistance, INGOs need to be aware of the dynamics of individual donor preferences.
-Based on our simulated market of 24 organizations and 32 persona profiles, we find several important trends.
-On average, human rights organizations tend to attract personas who are wealthier, follow national and international news, and travel abroad, while donors who are less wealthy, follow the news less often, and do not travel are more attracted to organizations working on  less contentious like emergency response and refugee relief.
-More importantly, we found that trust in political institutions and in charitable organizations in general matters substantially in shaping donor preferences.
+The global crackdown on civil society and the consequent declining official aid and official development assistance has made the role of philanthropy in sustaining CSOs abroad clear.
+INGOs need access to diverse and multiple sources of fundings and the value of individual-level philanthropy is still relatively under-explored.
+While existing research has examined the impact of organizational-level factors on individual giving, in this paper, we specifically look at demographic traits of those who are likely to donate to INGOs facing hostile environments abroad.
+Based on our simulated market of a nationally representative sample of individuals from the U.S., we find several important trends.
+On average, human rights organizations tend to attract personas who are wealthier, follow national and international news, and travel abroad.
+Donors who are less wealthy, follow the news less often, and do not travel are more attracted to organizations working on less contentious like emergency response and refugee relief.
+
+More importantly, we found that trust in political institutions and in charitable organizations matters substantially in shaping donor preferences.
 Personas with high levels of social and charitable trust prefer donating to human rights organizations that have friendly relationships with their host governments, while personas with low trust are drawn more to NGOs emergency response and refugee relief organizations with unfriendly relationships with their host governments.
@@
 
-TODO: All this conclusionary stuff + so what/implications?
+This survey was conducted on a random sample of US respondents.
+More comparative research is needed to understand the extent to which these results can be replicated across other countries.
+Future research should also determine the extent to which these preferences translate into behavior.
 
-??Individuals may also be more likely to donate to causes seen as vital to ongoing public services in countries across the Global South - such as health and education, rather than donate to more "contentious" causes such as corruption, advocacy, media freedoms and human rights.
-This has the potential to leave organizations focusing on the latter without adequate funding to continue their operations.??
+Surveys across a range of countries show that levels of giving are lowest for refugee and asylum organizations, as well as for overseas and development organizations.
+Rather, donors giving to international causes tend to support international disaster relief and religious groups [@RobsonHart2020].
+However, the former are precisely the organizations facing crackdown.
+More research is needed to answer how can these organizations appeal to broader array of potential foreign donors to increase levels of charitable-giving towards them?
+To be clear, research on international giving by individuals, especially in the era of closing civic space, is not meant to find answers that can be substitutes for strategic policy responses, especially by official aid donors and foundations.
+However, many NGOs are under immediate threat, and individual-level philanthropy can help support these organizations.
+Existing initiatives such as the Lifeline Embattled CSO Assistance Funds provide models for channeling such funds.
+To be sustainable in the era of closing civic space, CSOs need access to diverse and multiple sources of funding and this paper highlights one such source.
 
-Finally, it is important to acknowledge the role played by civil society organizations in dealing with health, poverty, and disaster - social needs that are tremendously important during the COVID-19 pandemic.
-This survey was conducted in June 2019 - can we expect insights from this survey to hold even during this time period, even as the world sees an economic recession?
-We argue that this is the case for two main reasons.
-First, prior research demonstrates that altruism and prosocial behavior are more common during and after disasters (cite?).
-Second, the most recent instance of the 2008 recession did not uniformly impact all demographic groups in the U.S.
-- individuals with lower levels of education, income, or wealth showed a statistically significant decline in charitable-giving.
-However, philanthropic patterns were not significantly different for other income brackets.
+\newpage
 
-Thus, while giving to international causes is likely to be sensitive to economic changes and disaster, this may not substantively amount to a huge difference given that while 5% of US households support international causes, more than double - 11% of US high net worth households donated to international causes between 2016-18.
-[^highnetworth].
-(TODO IU July 2019 - where is this paper?) In terms of overall giving, individuals with graduate degrees gave largest percentage of income both before and after the recession.
+# Appendix: Survey experiment
+
+```{r child = "experiment.md"}
+```
+
+\newpage
+
+[^NGOdef]: Broadly speaking, NGOs are any not-for-profit, voluntary group organizations at the local, national, or international level.
+They can either be domestic i.e.
+an NGO that operates entirely in a single state, or they can be international, more commonly known as INGOs.
+The latter are composed of members from two or more countries and are organized to advance their members' international goals and provide services to citizens of other states through routine transactions with states, private actors, and international institutions [@Tarrow:2001, 12].
 
@@
 [^highnetworth]: High-net worth households are defined as having greater than \$200,000 in annual household income and/or with more than \$1,000,000 in assets, excluding primary residence.
+
+[^phildef]: We use philanthropy to connote voluntary giving by an individual or group to promote the common good.
+While it can include grants given by foundations and corporations to nonprofit organizations, our focus here is on individual giving.
 

### 2020-09-25 manuscript/manuscript.Rmd
More Suparna edits

@@
   email: aheiss@gsu.edu
-date: "June 8, 2020"
+date: "September 24, 2020"
 published: Working paper.
@@
 abstract: >-
-  Over the past two decades, international nonprofit organizations (INGOs) have faced increasing legal scrutiny abroad, which has negatively impacted public funding flows.
-Consequently, INGOs may feel the need to fundraise from individuals.
+  Over the past two decades, international non-governmental organizations (INGOs) have faced increasing legal scrutiny and repression abroad.
+As a result, official aid to INGOs in repressive countries has reduced.
+NGOs thus need access to a diverse array of funds and may need to increase fundraising from private donors.
 Which demographic and experiential factors influence the decision of individuals to donate to legally besieged NGOs?
@@
 In contrast, donor profiles with lower levels of social trust prefer to donate to organizations that do face criticism or crackdown abroad.
-Our findings have practical implications for INGOs that hope to raise funds from the general public amid closing civic space.
+Our findings have practical implications for INGOs that aim to raise funds from the general public amid closing civic space.
 reference-section-title: References
@@
 
-In Human Rights Watch's 2016 annual report, Executive Director Kenneth Roth argued that civil society was under more aggressive attack than at any time in recent memory.
-Over the past few decades, governments across the globe have been cracking down on civil society organizations (CSOs) and non-governmental organizations (NGOs)—a phenomenon known as "closing civic space" in the policy arena [@CarothersBrechenmacher:2014; @CIVICUS:2017].[^NGOdef] As part of this phenomenon, CSOs, particularly NGOs, face increasing obstacles to their work, including legal restrictions and threats to their freedom of association, expression and speech.
-Legal restrictions-a core part of these efforts-create barriers to entry, funding, and advocacy for NGOs in an effort to control, obstruct or repress these organizations-what we refer to as legal crackdowns in this paper.
+In its 2016 annual report, Human Rights Watch claimed that civil society was under more aggressive attack than at any time in recent memory.
+Governments across the globe have cracked down on civil society organizations (CSOs) and non-governmental organizations (NGOs)—a phenomenon known as "closing civic space" [@CarothersBrechenmacher:2014; @CIVICUS:2017].[^NGOdef] As part of this phenomenon, NGOs face strong legal and bureaucratic obstacles to their work.
+Legal restrictions, or what we refer to as legal crackdowns, are a core part of these efforts.
+These crackdowns create barriers to entry, funding, and advocacy for NGOs in an effort to control, obstruct, and repress these organizations.
 
-As a result of these legal crackdowns, official aid flows to NGOs have decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
-While this has negatively impacted funding flows from public organizations like USAID, DFID, and other OECD funding agencies, philanthropy from private donors, in particular, foundations, appears to not be as adversely affected [@McGill:2018].
-Given this trend of closing civic space, NGOs need access to multiple sources of funding and individual-level giving can serve as one such source of funds.
-What individual donor characteristics and attributes are most salient for INGOs interested in maximizing philanthropy towards their operations abroad?
+As a result of these legal crackdowns, foreign aid channeled through NGOs has decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
+While this has negatively impacted funding flows from public organizations like United States Agency for International Development (USAID) and Organisation for Economic Cooperation and Development (OECD) funding agencies, philanthropy from private donors, in particular, foundations, appears to not be as adversely affected [@McGill:2018].
+Given this trend of closing civic space, INGOs need to maintain access to multiple sources of funding, including individual donors.
+
+Individual private donations are a critical source of INGO funding.
+Total private philanthropy in the United States has grown substantially over time, reaching more than \$400 billion in 2018 (@fig:giving-aggregate).
+In 2018, private giving to NGOs working specifically in international affairs reached \$22.08 billion, and international affairs-focused organizations are one of only two categories of organizations that have continued experiencing substantial growth in giving [@givingusa:2019].[^intlaffairs] Most of this growth is driven by individuals making small-scale or micro-donations.[^smalldonors] In 2017, 70% of donations to international affairs NGOs came from individuals, rising to 86% in 2018.
+But relying on individual donors means that NGOs must consider individual preferences when fundraising.
+Which individual donor characteristics and attributes are most salient for INGOs interested in maximizing philanthropy at a time when they are facing increasingly hostile environments abroad?
+What kinds of donors are more or less likely to consider an INGO's host country political environment when making the decision to donate?
+
+![Aggregate philanthropic giving in the United States, 1977–2017. Source: Giving USA.](output/figures/giving_aggregate.pdf){#fig:giving-aggregate}
 
 Existing scholarship on the determinants of individual-level philanthropy to domestic causes is robust across a variety of contexts.
-But the dynamics of *international* giving to NGOs are under-examined in the literature on individual donor attributes and preferences.[^exceptions] Research on the determinants of philanthropy towards international causes—particularly for organizations working in challenging environments—is still in its infancy due to the absence of expansive and high-quality data [@greenhill2013].
-Understanding why individuals donate to international causes is essential as it can be harder to motivate as the number of recipients are large and far removed from the donor [@CasaleBaumann:2015, 100].
+But the dynamics of *international* giving to NGOs are under-examined in the literature on individual donor attributes and preferences.[^exceptions] Motivating individuals to donate to international causes is hard as the number of recipients are large and far removed from the donor [@CasaleBaumann:2015, 100].
+And research on the determinants of philanthropy for international causes—particularly towards organizations working in challenging environments—is still in its infancy due to the absence of expansive and high-quality data [@greenhill2013].
+While previous work has looked at how organizational attributes of nonprofits affect donors' willingness to donate internationally [@todo:CITEOURPAPERTODIFFERENTIATE), we have yet to uncover demographic traits and experiences that motivate or deter individuals to donate during shrinking civic space.
 
-Individual giving is also important to understand because the amount of money donated by private individuals to CSOs working abroad has steadily increased over time.
-Total aggregate philanthropy in the United States has grown substantially over time, reaching more than \$400 billion in 2018 (@fig:giving-aggregate).
-In 2018, total private giving to CSOs working specifically in international affairs reached \$22.08 billion.
-Moreover, organizations working in the area of international affairs are one of the only two types of recipient organizations that have continued experiencing substantial growth in giving [@givingusa:2019].[^intlaffairs] Most of this is driven by individuals making small-scale or micro-donations.[^small donors] In 2017, individuals gave \$286.7 billion, or approximately 70% of total giving to organizations working in international affairs.
-This further increased to \$427.71 billion in 2018, 85.7% of which was through individuals [@givingusa:2019].
-However, we lack a systematic understanding of which individual donors may be further motivated or deterred to donate under an increasingly restricted civic space abroad.
-What is the optimal mix of individual-level donor attributes for international NGOs working in restricted political environments interested in maximizing donations?
-What kinds of individual donors are more or less likely to consider an NGO's host country political environment when making the decision to donate?
-
-![Aggregate philanthopic giving in the United States, 1977–2017. Source: Giving USA.](output/figures/giving_aggregate.pdf){#fig:giving-aggregate}
-
-We explore these questions using a simulated market for philanthropic donations, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity.
+We explore this question using a simulated market for philanthropic donations, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity.
 We adapt methods used in marketing research to generate dozens of distinct simulated personas that represent typical donor profiles, and we vary these personas along different dimensions of demographic, political, and social attributes.
@@
 
-This study contributes to both to scholarship and practice in public policy, nonprofits and charitable-giving.
-Individual-level philanthropic giving abroad can help bridge socioeconomic disparities worldwide, especially given the stark inequality in global distribution of income.
+This study contributes to both to scholarship and practice in public policy, nonprofits, and philanthropy.
+Individual giving abroad can help bridge socioeconomic disparities worldwide, especially given the stark inequality in global distribution of income.
 Knowledge of demographic traits and its impact on funding can help nonprofits craft more effective and targeted marketing strategies [@Rajan:2009, 414].
 Most NGOs working internationally have previously relied on government and foundation funding.
-But in the era of closing civic space, these groups may need to readjust their fundraising strategies to cater to individuals.
-Framing is important in this regard—how people process information affects their willingness to donate.[^framing] However, we lack systematic studies of which frames may be effective when making appeals to individual donors considering international philanthropy.
-Since our study looks at multiple organizational-level factors, it can help these CSOs frame their appeals.
+But with shrinking civic space, these groups may need to readjust their fundraising strategies towards individuals.
+Framing is important in this regard—how people process information affects their willingness to donate.[^framing] However, existing research is unclear about which frames are effective when making appeals to individual donors considering international philanthropy.
+Since our study looks at multiple organizational and host country factors, our results can help NGOs frame their appeals.
 
-More broadly, while research in public policy and nonprofit studies has focused on giving to NGOs, philanthropy is not seen as relevant by international relations as a discipline [@youde2019].
-However, philanthropy—particularly donations received by international nongovernmental organizations (INGOs)—can help us understand changes in the dynamics of global governance.
+More broadly, while research in public policy examines giving to NGOs, philanthropy is not seen as relevant by international relations as a discipline [@youde2019].
+However, philanthropy—particularly donations received by INGOs—can help us understand changes in the dynamics of global governance.
 Private individuals exercise power and influence in unique ways that differ from other non-state actors.
 As @youde2019 [p.
-44] points out, it changes our conceptions of individuals being passive recipients to active entities that are not merely objects of governance, thus shedding light on the changing logic of global governance.
+44] points out, it changes our conceptions of individuals being passive recipients to active entities that are not merely objects of governance.
+Thus, it can shed light on the changing logic of global governance.
 
-Below, we first examine the state of the existing literature on the key drivers of individual charitable giving, as understanding what motivates private donations is crucial to more effective NGO fundraising.
+Below, we first examine the state of the existing literature on the key drivers of individual giving.
 We then describe our survey experiment and simulation methods and explore the results.
@@
 Foreign aid to civil society—and NGOs in particular—has steadily increased over time.
-Many government and foundation donors perceive that NGOs have a superior ability to achieve intended outcomes.
-Therefore, in countries with weak institutions and poor governance, where direct aid transfers to governments raise issues of misuse and bureaucratic inefficiency, donors specifically seek out NGOs for projects [@Dietrich2013].
-These groups provide services to large parts of the population in the Global South, especially where governments are unable to do so on a consistent basis.
+Many government and foundation donors perceive NGOs as nimbler and less bureaucratic than governments.
+In countries with weak institutions and poor governance, where direct aid transfers to governments raise issues of misuse and bureaucratic inefficiency, donors specifically seek out NGOs for projects [@Dietrich2013].
 
@@
 Thousands of INGOs in the Global South receive funds from a variety of public and private sources each year.
-Public funds (more commonly known as traditional donor aid) channel money from official aid agencies through a variety of bilateral and multilateral institutions.
+Public funds—or traditional donor aid—channel money from official aid agencies through a variety of bilateral and multilateral institutions.
 Private sources include foundations, private corporations, and individuals.
-While INGOs have not been passive in responding to the crackdown on civil society, they face increasing obstacles especially from a funding perspective.
-Official aid donors have reduced the amount of aid channeled to countries with legal restrictions @DupuyPrakash:2018].
-In addition, official donors have also redirected funds within restrictive countries, decreasing funds for politically sensitive causes in favor of tamer issues that are more compatible with the governments of other countries [@ChaudhryHeiss:2018].
-However, it is notable that private funding towards international nonprofits has not been as adversely affected.
-Many foundations have continued channeling funds to countries with hostile legal environments [@FoundationCenter2018].
+While INGOs have not been passive in responding to the crackdown on civil society, they face increasing obstacles from a funding perspective.
+Official donors have reduced the amount of aid channeled to countries with legal restrictions [@DupuyPrakash:2018] and have redirected funds within restrictive countries, decreasing funds for politically sensitive causes in favor of tamer issues that are more compatible with the governments of those countries [@ChaudhryHeiss:2018].
+However, private funding towards international nonprofits has not been as adversely affected.
+Many foundations have continued channeling funds to countries with hostile legal environments [@NeedlesWolcheckSato:2018].
 
 The advent of funding restrictions on NGOs globally and a subsequent decline in government and foundation funding has made the role and value of individual philanthropy in sustaining NGOs even clearer.[^phildef] NGOs need access to a diverse array of funds and individual donations to international affairs organizations have steadily increased over the past two decades.
-Between 2014-2016, giving to organizations working in international affairs increased by 14.1% [@givingusa2017report].
-Moreover, at least in the U.S.
-context, donations from individuals far outstripped foundation and corporate giving.
-In 2018, individual donations amounted to \$292.09 billion, compared to \$75.86 billion from foundations and \$20.05 billion from corporations [Source from NVSQ].
-Given that a majority of research is restricted to elite high net-worth donors [@USTrust2014], these figures show that it is imperative to understand motivations and attributes of small-scale donors as well.
-In this paper, we therefore look at which kinds of individual donors—beyond high-net worth donors—are most likely to give abroad.[^highnetworth]
+Moreover, in the United States donations from individuals have far outstripped foundation and corporate giving.
+In 2018, individual donations amounted to \$292 billion, compared to \$76 billion from foundations and \$20 billion from corporations [@NPT].
+Given that a majority of research is restricted to elite high net-worth donors[^highnetworth] [@USTrust2014], these figures show that it is imperative to understand motivations and attributes of small-scale donors as well.
 
@@
 
-A vast literature on philanthropy looks at organizational-level factors that motivate individuals to donate [@BilodeauSlivinski:1997; @TBPrakash:2017].
-However, donation decisions are not determined solely by an organization's characteristics.
+A vast literature on philanthropy looks at organizational-level factors that motivate individuals to donate [@TBPrakash:2017].
+However, donation decisions are not determined solely by a recipient organization's characteristics.
 Donors have personality traits, preferences, and experiences that make them more or less likely to engage in philanthropy.
-A robust literature in nonprofit studies has looked at individual donor behavior and characteristics for giving to local—rather than international—causes.
-This literature focuses on the importance of five main attributes: (1) social capital; (2) the role of higher education; (3) levels of religiosity; (4) wealth; and (5) national group attachment.
+Substantial research has looked at the determinants of donating to local—rather than international—causes, including four main attributes: social capital, the role of higher education, levels of religiosity, wealth, and national group attachment.
 
-One major area of inquiry in philanthropic studies examines the role of social capital, particularly associational capital, or "the networks of formal and informal relationships to which people are associated." [@havens2007, 240].
-Research finds that those who participate in a variety of associations are more likely to make larger donations [@hossainlamb2017].
-Further, those who volunteer their time (compared to those who did not) were both more likely to make charitable donations and make bigger donations.
+Social capital, particularly associational capital, or "the networks of formal and informal relationships to which people are associated," is often considered an important indicator of giving [@havens2007, 240].
 Volunteering exposes individuals to the need for donations, making them feel more compelled to donate [@hossainlamb2012].
+Those who participate in a variety of associations are both more likely to donate as well as make larger donations [@hossainlamb2017].
 
-Higher education can also play an important role in charitable-giving decisions as it fosters prosocial motivations.
-It also brings people into particular social networks that entail a higher level of solicitations, which is vital in giving to international causes [@BekkersWiepking:2011].
+Higher education also influences charitable-giving decisions as it fosters prosocial motivations.
+Education brings people into social networks that entail a higher level of solicitations, which is vital in giving to international causes [@BekkersWiepking:2011].
+Education also helps determine the kinds of causes that people donate to globally.
 @Micklewright:2009 show that higher education matters more for donating to international relief organizations than donating to domestic organizations.
 
-Higher education also helps determine the kinds of causes that people donate to globally.
-A number of NGOs facing crackdowns abroad work on issues that may be seen as "contentious," including human rights, elections, corruption, advocacy, media freedom—issues that may have a harder time attracting funds due to their non-essential nature when compared to causes like health, education, sanitation, and social services.
-However, additional education has been shown to increase abstract thinking [@wiepkingmaas, 1978], which may be necessary to donate to causes that do not have quantifiable goals, which is particularly important for organizations with more "contentious" causes as part of their missions [@Bush:2015].
+A number of NGOs facing crackdowns abroad also work on issues that may be seen as "contentious," including human rights, elections, corruption, advocacy, media freedom—issues that may have a harder time attracting funds due to their non-essential nature when compared to causes like health, education, sanitation, and social services.
+However, additional education has been shown to increase abstract thinking [@wiepkingmaas, 1978], which may be necessary to donate to causes that do not have quantifiable goals.
+This is particularly important for organizations with more "contentious" causes as part of their missions [@Bush:2015].
 
-Levels of religiosity are also a significant predictor of the likelihood and level of giving.
-People who regularly attention religious services are more likely to have prosocial values, face a stronger norm of charitable giving, and may feel pressure to conform that group and community standard [@wiepking2010].
+Religiosity is also a significant predictor of the likelihood and level of giving.
+People who regularly attend religious services are more likely to have prosocial values, face a stronger norm of charitable giving, and may feel pressure to conform that group and community standard [@wiepking2010].
 Regular attendance may also strengthen individuals' beliefs in organizations' missions.
@@
 Looking at UK respondents, @hartrobson2019 find that whereas nationalists have a preference for domestic charities, they are not necessarily averse to donating to international causes, whereas internationalists have a strong preference for donating to causes and groups working abroad.
-More specifically, immigrant households are more likely to contribute to international aid organizations [@OktenOsili:2007], and that immigrants can find value in donating to both home and host cultures, especially if their family members still reside in the home country [@burgoyne2005].
 
+Which of these characteristics matter when deciding to donate to an INGO, particularly when an organization faces legal crackdown abroad?
 Overall, individuals with higher levels of income, education, and greater religious proclivities are not only more likely to give internationally, but also give higher amounts [@Rajan:2009; @CasaleBaumann:2015].
-While we expect these determinants to be reflected in our survey experiment, we do not lay out specific hypotheses.
-Because there is so little research about international donations during legal crackdown by host governments, our analysis and results are exploratory and descriptive.
-Our innovative experimental approach, however, provides rich quantitative details of individual and organizational characteristics simultaneously and reveals unique insights into donor motivations that both confirm and expand previous research.
+Additionally, we posit that other related characteristics such as civic and associational engagement and social trust also influence the decision to donate.
+
+We explore this question using a conjoint survey experiment conducted with a nationally representative sample in the U.S.
+Importantly, because there is so little research about international donations during legal crackdown by host governments, our analysis and results are exploratory and descriptive.
+Accordingly, we do not test specific hypotheses or theories.
+However, we do talk about causal effects given the that we conduct an experiment that varies organizational characteristics in order to elicit opinions from respondents (i.e.
+specific attributes and features cause different aggregate effects).
+Instead, we structure our analysis around broader themes from the existing literature and investigate how donors' (1) demographic characteristics, (2) public affairs knowledge and experience, and (3) levels of trust in government, charitable work, and associational life change their donation preferences across different organizational issue areas, relationships with host governments, and funding sources.
+Our innovative experimental approach provides rich quantitative details of individual and organizational characteristics simultaneously and reveals unique insights into donor motivations that both confirm and expand previous research.
 
@@
 We use a conjoint survey experiment to simultaneously study the effects of organizational characteristics and individual attributes on individuals' preferences to donate to a nonprofit organization.
-Conjoint analysis methods are well suited for the questions we explore, as they allow us to elicit donor preferences without forcing respondents to explicitly state their exact preferences.
-Conjoint analysis is commonly used in marketing research to reveal consumer preferences for different mixes of products.
-It has also been increasingly used in political science and public policy to assess citizen perceptions of political communication [@Helfer:2016; @Mummolo:2016; @KnudsenJohannesson:2019].
+Conjoint analysis allow us to elicit donor preferences without forcing respondents to explicitly state their exact preferences.
+This kind of analysis is commonly used in marketing research to reveal consumer preferences for different mixes of products, and has become increasingly popular in political science and public policy [@KnudsenJohannesson:2019].
 Because we are interested in exploring the complexity behind the decision to donate, we apply conjoint methods to the study of nonprofits and philanthropy.
 
-After collecting baseline information on respondent demographics and attitudes toward charity and voluntarism, we presented respondents with four randomly selected international nonprofit organizations with four randomly assigned features.^[See the appendix for a copy of the survey.] We included organizations that are associated with a range of contentious and noncontentious issues: Amnesty International, Greenpeace, Oxfam, and the International Committee of the Red Cross.
-These organizations are commonly used in surveys on TODO TODO, in addition to other organizations such as MSF, World Vision (LOOK UP SAVED PAPERS - I THINK NVSQ).
-We then displayed various combinations of features, including one of four issue areas (emergency response, environmental advocacy, human rights advocacy, and refugee relief), one of two organizational practices (financial transparency and third-party accountability audits), one of three funding sources (many small private donations, a handful of wealthy private donors, and government grants), and one of three relationships with host governments (friendly, criticized by the government, and under government crackdown).
-We presented twelve sets of four hypothetical combinations of organizational features, and because our partial fractional factorial design resulted in 288 (4 × 4 × 2 × 3 × 3) possible combinations of organizations and features, no single respondent was offered every combination.
+In our experiment, we presented respondents with four randomly selected international nonprofit organizations with four randomly assigned features.^[See the appendix for a copy of the survey.] We included organizations that are associated with a range of contentious and noncontentious issues: Amnesty International, Greenpeace, Oxfam, and the International Committee of the Red Cross.
+Because of their strong name recognition, these organizations (and others like World Vision, the World Wildlife Fund, and Médecins Sans Frontières) are commonly used in experimental surveys on philanthropy [@FaulknerTruongRomaniuk:2015].
+
+```{r child = "output/tables/tbl-organization-attributes-full.md"}
+```
+
+We then displayed four hypothetical organizations based on random combinations of features , including one of four issue areas, one of two organizational practices, one of three funding sources, and one of three relationships with host governments (see @tbl:organization-attributes-full; see also Q3.1 in the survey text in the appendix).
+Respondents saw twelve sets of four hypothetical combinations of organizational features, and because our partial fractional factorial design resulted in 288 (4 × 4 × 2 × 3 × 3) possible combinations of organizations and features, no single respondent was offered every combination.
+Not every combination necessarily reflected reality—for instance, a respondent might have been asked to compare a fictional Amesty International that focuses on environmental issues and that is funded by private donations with a Greenpeace that focuses on human rights and that is funded by government grants.
+It is not important that these features align with true organizational characteristics, since the goal of these repeated hypothetical questions is to identify which attributes are the most salient for donors.
 
@@
 
-In this paper, we look at which kinds of donors are more or less likely to consider an NGO's issue area, funding sources, and host country politics when deciding to donate.
+In this paper, we look at which kinds of donors are more or less likely to consider an NGO's issue area, funding sources, and relationships with host governments when deciding to donate.
 Disentangling the effect of every individual level-characteristics measured in the survey on every combination of organizational characteristics presented in the conjoint experiment is unwieldy and near impossible.
 Given the organizational attributes presented in our experiment, and the possible individual characteristics that respondents could select, there are billions of possible combinations and iterations of organizational and individual attributes—many of which rarely occur in the actual population of potential donors.
-To more fully explore the relationships between different organizational- and individual-level attributes, we turn to simulation methods that allow us to examine the impact of multiple covariates at simultaneously
-
-We use market segmentation methods to construct simulated personas that interact with simulated organizations in a market for charitable contributions.
-To simplify the many possible combinations of individual characteristics, we generate 32 distinct personas with attributes that vary along different dimensions of demographics, politics and public affairs experience, and social attitudes (see @tbl:persona-attributes).
+To more fully explore the relationships between different organizational- and individual-level attributes, we turn to simulation methods that allow us to examine the impact of multiple covariates at simultaneously.
+To simplify the possible combinations of individual characteristics, we generate 32 distinct personas with attributes that vary along different dimensions of demographics, politics and public affairs experience, and social attitudes (see @tbl:persona-attributes).
 We also generate 24 simulated organizations that vary by issue area, relationship with host government, and source of funding (see @tbl:organization-attributes).
@@
 Importantly, each persona is an artificial construct.
-While some survey respondents might match an exact persona profile, most do not.
-This is acceptable in simulations, and each combination of persona characteristics is plausible in the real world.
-Our analysis uses the characteristics of our sample to model the effects of various salient attributes while holding others constant, and thus allows us to explore multiple attributes at once.
-
-Also importantly, our findings are not causal.
-Rather, they are the descriptive results of simulated data from a nationally representative sample of people who regularly donate to charity.
-The insights from this simulation, however, still reveal interesting patterns of donor preferences when faced with organizations focusing on a variety of issues, funding sources, and legal restrictions abroad.
+While some survey respondents might match an exact persona profile, others may not.
+This is acceptable in simulations as each combination of persona characteristics is plausible in the real world.
 
@@
 
+These simulated findings are more abstract than the results from an ordinary survey sample.
+But by using simulations, we can discover interesting patterns of donor preferences when faced with organizations focusing on a variety of issues, funding sources, and legal restrictions abroad.
 Our market simulation reveals which combination of organizational features each persona is most likely to express a preference for donation to.
@@
 The three panels of @fig:demographics shows the average predicted market share for different organizational issue areas, relationships with governments, and funding sources.
-Though we varied gender across the different personas, gender has no significant effect on any of the simulated outcomes—males and females follow nearly identical patterns across all organizational and individual characteristics.
+Though we varied gender across the different personas, gender has no significant effect on any of the simulated outcomes—men and women follow nearly identical patterns across all organizational and individual characteristics.
 As such, in @fig:demographics, we only vary income.
@@
 
-*(Note: We also plan on examining religiosity and education in the very near future)*
+*(TODO: I'll need ≈150 words to describe education and religiosity results)*
 
@@
 
-We also combine these dimensions with an additional set of donor characteristics that vary a persona's level of social trust.
-Personas with high levels of trust have high trust in political institutions and charities, thinks people should be more charitable, frequently volunteers, donates to charity once a month, has a history of political activism, and is a member of an association.
-Personas with low levels of trust have the opposite characteristics: they do not trust political institutions or charities, rarely donate or volunteer, and are not members or other associations.
+We combine these dimensions with an additional set of donor characteristics that vary a persona's level of social trust.
+Personas with high levels of trust have high trust in political institutions and charities, think people should be more charitable, frequently volunteer, donate to charity once a month, have a history of political activism, and are members of an association.
+Personas with low levels of trust have the opposite characteristics: they do not trust political institutions or charities, rarely donate or volunteer, and are not members of associations.
 
@@
 Public affairs knowledge and experience has little effect on donor preferences, as the average market shares are roughly identical across the two columns of the figure.
-Similarly, there are no ideological differences across the rows of the figure.
 Persona preferences toward friendly, criticized, and legally suppressed organizations do not change much across different ideological views.
@@
 
-![Average predicted donation market shares across all personas, segmented by persona public affairs knowledge, political ideology, and social trust across different forms of NGO funding](output/figures/funding-social.pdf){#fig:funding-social}
-
-Finally, @fig:funding-social shows the average share of persona market shares across different forms of NGO funding.
-There are only insignificant differences in donor preferences across public affairs knowledge and experience, political ideology, and social trust.
-On average, it appears that the source of NGO funding does not play an important role in a donor's preference for the organization.
-Other organizational factors—in particular issue area and host government relationship—have a much larger influence in shaping donor preferences.
-
 ## Concerns about inference and generalizability
 
-While the survey seeks to uncover donor profiles of those who are influenced by legal crackdowns on NGOs in their decision to donate, it may be possible that results are based on respondents' prior beliefs about Amnesty, Oxfam, Greenpeace, and Red Cross.
-This may particularly be the case after an Oxfam scandal in Feburary 2018—scandals that may potentially strength the narrative that the nonprofit sector suffers from governance failures [@SurlockEtal2020].
-Analyzing a smaple of Twitter data to studythe daily gap between the positive and negative sentiments expressed towards INGOs embroiled in scandals, @SurlockEtal2020 find that while sentiments towards Oxfam did not completely recover even 6 months after the scandal, Save the Children's reputation recovered fairly quickly.
-Moreover, the recovery of their reputation was aided specifically by celebrity endorsements as well as be focusing public attention on the organizations' achievements.
-While reputational damage can lead to decline in donations and grants, their research lays provides important foundational evidence demonstrating both, "short-term fragility and longer-term durability of organizations' reputations" [SurlockEtal2020, p.
-104].
+Given the nature of conjoint experiments, the randomly presented organizations may have influenced respondent choices.
+All four organizations are well known, and it is likely that participant responses reflect prior beliefs and news coverage about Amnesty, Oxfam, Greenpeace, and the Red Cross.
+For instance, in February 2018, news broke about sexual abuse and misconduct at Oxfam and several other well known organizations, including Amnesty International and Save the Children.
+This potentially strengthened a narrative that the nonprofit sector suffers from governance failures [@Phillips:2019].
+As such, it could be argued that respondents may be less likely to select Oxfam or Amnesty because of these scandals.
 
-However, given that the above analysis is not representative of the general population, we also sought out other surveys that could provide an insight into donors' prior beliefs and their possible impact on donation preferences.
-Contrary to media sentiment, we found that trust and confidence in NGOs specifically in the UK did not waver [@citemehere].
-We also failed to find evidence that these impacted public opinion among likely individual donors in the US - who were the main respondents in our survey [@CITE].
-Rather, any lack of trust towards overseas NGOs, particularly aid and developmental agencies often results due to donors perceiving INGOs as having low personal relevance [@FaulknerTruongRomanuik2015].
+However, we remain doubtful that the above news would impact our U.S.
+respondents' beliefs about these four organizations, as evidence about the effect of these scandals is mixed.
+Using data from Twitter, @ScurlockDolsakPrakash:2020 find that while Oxfam's reputation suffered for at least six months after the scandal (but has since recovered), other NGOs facing scandals, such as Save the Children, were able to recover more quickly.
+More broadly, the effect of scandals was mixed—while reputational damage can lead to decline in donations and grants, organizations can become more resilient and durable after a public relations recovery.
+
+Additionally, we remain skeptical that this scandal affected U.S.
+donors, given Oxfam is based in the UK and lack of awareness about INGOs is well-documented (CITE).
+Rather, lack of trust towards overseas NGOs, particularly aid and developmental agencies often results due to donors perceiving INGOs as having low personal relevance [@FaulknerTruongRomaniuk:2015].
+We failed to find any systematic evidence that the Oxfam scandal influenced perceptions of the nonprofit sector, likely because the story had far less news coverage in the U.S.
 Many individual donors have a preference to donate locally and they lack sufficient knowledge to make an informed decision about donating internationally.
-Overall, the literature suggests that lack of awareness is a much bigger issue for INGO fundraising, rather than specific scandals that would reduce the average individual donors' trust and confidence in these NGOs.
+Overall, the literature suggests that for INGO fundraising, lack of awareness is a much larger issue than specific scandals or other knowledge of specific organizational characteristics that might reduce donor trust and confidence.
 
-The study was also conducted on a random sample of U.S.
-respondents with a prior history of charitable giving which raises questions about external validity.
-Public expectations about the role of public and private sectors differ across the U.S.
-and European countries.
-In the U.S., CSOs are typically seen as a counterweight to the government, whereas in some European countries like Germany, states are seen as supporting CSOs.
-Further, when we consider large INGOs such as Amnesty International and MSF - both receive very little support from their home governments (Stroup 2012).
-This may imply that donors in UK and France may have very different preferences when choosing to donate to government or privately-funded organizations.
-As such, more comparative research is needed to see if these results would also replicate across a variety of European countries
+The survey conducted among a random sample of U.S.
+residents with a prior history of charitable giving, also raises questions about generalizability external validity.
+Public expectations about the role of the public, private, and nonprofit sectors differ by country.
+In the U.S., for instance, NGOs often receive substantial funding through government grants, while those in the UK and France, such as Amnesty International and Médecins Sans Frontières, receive minimal government funding [@Stroup:2012].
+This could imply that donors in UK and France may have very different preferences when choosing to donate to government or privately-funded organizations.
+As such, more comparative research is needed to see if our results would also replicate cross-nationally.
 
-There is also notable variation in terms of the targets of donations across various contexts.
-Though charitable-giving amounts are highest in the U.S, such donations are overwhelmingly towards local and religious causes.
-However, this pattern does not hold for many European countries.
-In the UK, international aid is often the largest component of giving (26%) while in Germany, Belgium, and Switzerland, international and humanitarian aid is considered a priority with 74%, 61% and 43% of donations are directed towards these causes in these countries, respectively.
-Thus, if crackdown on nonprofits abroad can elicit the results demonstrated in this paper among US respondents, then they provide reasons for optimism for pursuing individual philanthropy in Europe as well.
+There is also notable country-based variation in general patterns of philanthropy.
+Though charitable giving is highest in the U.S, such donations are overwhelmingly directed at local and religious causes.
+This pattern does not hold for many European countries.
+In the UK, international aid is one of the largest targets of giving (26%).
+Other countries prioritize international philanthopy even more, such as Germany (74%), Belgium (61%), and Switzerland (43%) [@Milner:2017].
+Thus, if crackdown on INGOs abroad can elicit the effects found in this paper among U.S.
+respondents, the results provide much reason for optimism for pursuing individual philanthropy towards INGOs in Europe as well.
 However, more comparative research is required in order to confirm these trends.
@@
 
-The global crackdown on civil society and the consequent declining official aid and official development assistance has made the role of philanthropy in sustaining CSOs abroad clear.
-INGOs need access to diverse and multiple sources of fundings and the value of individual-level philanthropy is still relatively under-explored.
-While existing research has examined the impact of organizational-level factors on individual giving, in this paper, we specifically look at demographic traits of those who are likely to donate to INGOs facing hostile environments abroad.
-Based on our simulated market of a nationally representative sample of individuals from the U.S., we find several important trends.
+The global crackdown on civil society and the consequent decline of official development assistance has made the role of philanthropy in sustaining INGOs clear.
+INGOs need access to multiple sources of funding, and the value of individual-level philanthropy is still relatively under-explored.
+While existing research has examined the impact of organizational-level factors on individual giving as well as giving to local causes, in this paper, we specifically look at the demographic traits of those who are likely to donate to INGOs facing hostile environments abroad.
+We find several important trends from our simulated market for philanthropy.
 On average, human rights organizations tend to attract personas who are wealthier, follow national and international news, and travel abroad.
@@
 
-More importantly, we found that trust in political institutions and in charitable organizations matters substantially in shaping donor preferences.
-Personas with high levels of social and charitable trust prefer donating to human rights organizations that have friendly relationships with their host governments, while personas with low trust are drawn more to NGOs emergency response and refugee relief organizations with unfriendly relationships with their host governments.
+More importantly, we find that trust in political institutions and in charitable organizations matters substantially in shaping donor preferences.
+Personas with high levels of social and charitable trust prefer donating to human rights organizations that have friendly relationships with their host governments, while personas with low trust are drawn more to emergency response and refugee relief organizations with unfriendly relationships with their host governments.
 Personas with low social trust rarely prefer to donate to any type of organization with friendly host-country relationships, while personas with high social trust tend to avoid organizations with unfriendly relationships.
@@
 
-This survey was conducted on a random sample of US respondents.
-More comparative research is needed to understand the extent to which these results can be replicated across other countries.
-Future research should also determine the extent to which these preferences translate into behavior.
+The above results have important implications for NGOs as they navigate a shriking civic space and consider the use of different frames to tailor their fundraising appeals to individual donors.
+Our survey finds that at least for some kinds of individuals, NGOs may benefit from publicizing when they are targets of government crackdown, including that information in their fundraising appeals.
+However, the bigger challenge may be addressing concerns of donors with low levels of trust.
+More broadly, studies from a range of countries show that levels of giving are lowest for refugee and asylum organizations, as well as for overseas and development organizations.
+Rather, donors giving to international causes tend to support international disaster relief and religious groups [@RobsonHart:2020].
+However, the former are precisely the organizations facing crackdown.
+More research is needed to answer how these organizations can appeal to broader array of potential foreign donors to increase levels of charitable-giving towards them.
 
-Surveys across a range of countries show that levels of giving are lowest for refugee and asylum organizations, as well as for overseas and development organizations.
-Rather, donors giving to international causes tend to support international disaster relief and religious groups [@RobsonHart2020].
-However, the former are precisely the organizations facing crackdown.
-More research is needed to answer how can these organizations appeal to broader array of potential foreign donors to increase levels of charitable-giving towards them?
-To be clear, research on international giving by individuals, especially in the era of closing civic space, is not meant to find answers that can be substitutes for strategic policy responses, especially by official aid donors and foundations.
+To be clear, research on international giving by individuals, especially in the era of closing civic space, is not meant to find answers that can act as substitutes for strategic policy responses, especially by official aid donors and foundations.
 However, many NGOs are under immediate threat, and individual-level philanthropy can help support these organizations.
 Existing initiatives such as the Lifeline Embattled CSO Assistance Funds provide models for channeling such funds.
-To be sustainable in the era of closing civic space, CSOs need access to diverse and multiple sources of funding and this paper highlights one such source.
+In the face of legal crackdowns abroad, individual doations are an important additional funding source for besieged NGOs.
 
@@
 
-[^NGOdef]: Broadly speaking, NGOs are any not-for-profit, voluntary group organizations at the local, national, or international level.
-They can either be domestic i.e.
-an NGO that operates entirely in a single state, or they can be international, more commonly known as INGOs.
-The latter are composed of members from two or more countries and are organized to advance their members' international goals and provide services to citizens of other states through routine transactions with states, private actors, and international institutions [@Tarrow:2001, 12].
+[^smalldonors]: Micro-donations refer to donations between $0.25–$10; small donors are individuals who donate up to $50 [@SaxtonWang:2014].
 
-[^exceptions]: For exceptions, see @Micklewright:2009 on the UK, @Rajan:2009 on Canada, @wiepking2010 on Netherlands, @CasaleBaumann:2015 on the USA.
+[^NGOdef]: Broadly speaking, NGOs are any local, national, or international not-for-profit, voluntary organization.
+They can be domestic (i.e.
+an NGO that operates entirely in a single state), or international (INGOs).
+INGOs are composed of members from two or more countries and are organized to advance their members' international goals and provide services to citizens of other states through routine transactions with states, private actors, and international institutions [@Tarrow:2001, 12].
 
-[^highnetworth]: High-net worth households are defined as having greater than \$200,000 in annual household income and/or with more than \$1,000,000 in assets, excluding primary residence.
+[^exceptions]: For exceptions, see @Micklewright:2009 on the UK; @Rajan:2009 on Canada; @wiepking2010 on the Netherlands; @CasaleBaumann:2015 on the U.S.
+
+[^highnetworth]: High-net worth households are have greater than \$200,000 in annual household income and/or have more than \$1,000,000 in assets, excluding primary residence.
 

### 2020-09-29 manuscript/manuscript.Rmd
Marc edits

@@
 Which demographic and experiential factors influence the decision of individuals to donate to legally besieged NGOs?
-We investigate this question using a market simulation based on a nationally representative conjoint survey experiment conducted on individuals with a history of charitable giving.
+We investigate this question using a market simulation based on a nationally representative conjoint experiment conducted on individuals with a history of charitable giving.
 We find that trust in political institutions and charities is enormously influential in shaping donor preferences.
@@
 As a result of these legal crackdowns, foreign aid channeled through NGOs has decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
-While this has negatively impacted funding flows from public organizations like United States Agency for International Development (USAID) and Organisation for Economic Cooperation and Development (OECD) funding agencies, philanthropy from private donors, in particular, foundations, appears to not be as adversely affected [@McGill:2018].
+While this has negatively impacted funding flows from public organizations like United States Agency for International Development (USAID) and Organisation for Economic Cooperation and Development (OECD) philanthropy from private donors and foundations appears to not be as adversely affected [@McGill:2018].
 Given this trend of closing civic space, INGOs need to maintain access to multiple sources of funding, including individual donors.
@@
 We explore this question using a simulated market for philanthropic donations, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity.
-We adapt methods used in marketing research to generate dozens of distinct simulated personas that represent typical donor profiles, and we vary these personas along different dimensions of demographic, political, and social attributes.
+We adapt methods used in marketing to generate dozens of distinct simulated personas that represent typical donor profiles, and we vary these personas along different dimensions of demographic, political, and social attributes.
 We find that specific individual characteristics help shape donor preferences for donating to international NGOs, and that an INGO's target issue area and its relationship with host government interact strongly with these characteristics.
@@
 
-A number of NGOs facing crackdowns abroad also work on issues that may be seen as "contentious," including human rights, elections, corruption, advocacy, media freedom—issues that may have a harder time attracting funds due to their non-essential nature when compared to causes like health, education, sanitation, and social services.
+A number of NGOs facing crackdowns abroad also work on issues that may be seen as "contentious," including human rights, elections, corruption, advocacy, and media freedom—issues that may have a harder time attracting funds due to their non-essential nature when compared to causes like health, education, sanitation, and social services.
 However, additional education has been shown to increase abstract thinking [@wiepkingmaas, 1978], which may be necessary to donate to causes that do not have quantifiable goals.
@@
 Religiosity is also a significant predictor of the likelihood and level of giving.
-People who regularly attend religious services are more likely to have prosocial values, face a stronger norm of charitable giving, and may feel pressure to conform that group and community standard [@wiepking2010].
+People who regularly attend religious services are more likely to have prosocial values, face a stronger norm of charitable giving, and may feel pressure to conform to group and community standards [@wiepking2010].
 Regular attendance may also strengthen individuals' beliefs in organizations' missions.
@@
 
-We explore this question using a conjoint survey experiment conducted with a nationally representative sample in the U.S.
+We explore this question using a conjoint experiment conducted with a nationally representative sample in the U.S.
 Importantly, because there is so little research about international donations during legal crackdown by host governments, our analysis and results are exploratory and descriptive.
 Accordingly, we do not test specific hypotheses or theories.
-However, we do talk about causal effects given the that we conduct an experiment that varies organizational characteristics in order to elicit opinions from respondents (i.e.
+However, we do talk about causal effects given that we conduct an experiment that varies organizational characteristics in order to elicit opinions from respondents (i.e.
 specific attributes and features cause different aggregate effects).
@@
 
-## Conjoint survey experiment
+## Conjoint experiment
 
-We use a conjoint survey experiment to simultaneously study the effects of organizational characteristics and individual attributes on individuals' preferences to donate to a nonprofit organization.
-Conjoint analysis allow us to elicit donor preferences without forcing respondents to explicitly state their exact preferences.
-This kind of analysis is commonly used in marketing research to reveal consumer preferences for different mixes of products, and has become increasingly popular in political science and public policy [@KnudsenJohannesson:2019].
+We use a conjoint experiment to simultaneously study the effects of organizational characteristics and individual attributes on individuals' preferences to donate to a nonprofit organization.
+Conjoint analysis allow us to elicit donor preferences without respondents explicitly stating their exact preferences.
+This kind of analysis is commonly used in marketing to reveal consumer preferences for hypothetical products, and has become increasingly popular in political science and public policy [@KnudsenJohannesson:2019].
 Because we are interested in exploring the complexity behind the decision to donate, we apply conjoint methods to the study of nonprofits and philanthropy.
@@
 
-We then displayed four hypothetical organizations based on random combinations of features , including one of four issue areas, one of two organizational practices, one of three funding sources, and one of three relationships with host governments (see @tbl:organization-attributes-full; see also Q3.1 in the survey text in the appendix).
-Respondents saw twelve sets of four hypothetical combinations of organizational features, and because our partial fractional factorial design resulted in 288 (4 × 4 × 2 × 3 × 3) possible combinations of organizations and features, no single respondent was offered every combination.
-Not every combination necessarily reflected reality—for instance, a respondent might have been asked to compare a fictional Amesty International that focuses on environmental issues and that is funded by private donations with a Greenpeace that focuses on human rights and that is funded by government grants.
-It is not important that these features align with true organizational characteristics, since the goal of these repeated hypothetical questions is to identify which attributes are the most salient for donors.
+The hypothetical organizations are based on random combinations of features, including one of four issue areas, the presence or absence of two organizational practices, one of three funding sources, and one of three relationships with host governments (see @tbl:organization-attributes-full; see also Q3.1 in the survey text in the appendix).
+Respondents saw twelve sets of four hypothetical organizations out of 288 (4 × 4 × 2 × 3 × 3) possible combinations, meaning no single respondent was offered every combination.
+While not every combination necessarily reflected reality—for instance, a respondent might have been asked to compare a fictional Amnesty International that focuses on environmental issues and that is funded by private donations with a Greenpeace that focuses on human rights and that is funded by government grants—it is not important that these features align with true organizational characteristics, since the goal of these repeated hypothetical questions is to identify which attributes are the most salient for donors.
 
-In June 2019, we recruited survey respondents through Centiment, a commercial provider of high quality non-probability opt-in survey panels.
-Centiment ensures panel quality by actively recruiting representative samples of the US population and rewards participants with monetary incentives.
+In June 2019, we recruited survey respondents through Centiment, a commercial provider of high-quality, non-probability opt-in survey panels.
+Centiment ensures panel quality by actively recruiting and paying representative samples of the U.S.
+population.
 To participate in the study, respondents were first screened based on their charitable activities.
@@
 
-We analyze the effect of different combinations of organizational features and individual respondent attributes with a two-stage hierarchical Bayesian multinomial logit model.[^model-details] Simply put, the first level of the model predicts individual donor preferences for various combinations of features (e.g.
-the combination of human rights issues, financial transparency, government funding, and government crackdown), while the second level of the model uses these fitted preferences to predict the ultimate choice of donation.
+We analyze the effect of different combinations of organizational features and individual respondent attributes with a two-level hierarchical Bayesian multinomial logit model.[^model-details] Simply put, the first level of the model predicts individual donor preferences for various combinations of features (e.g.
+the combination of human rights issues, financial transparency, government funding, and government crackdown), while the second level predicts the heterogeneity of these fitted preferences as a function of individual donor characteristics.
 
@@
 Given the organizational attributes presented in our experiment, and the possible individual characteristics that respondents could select, there are billions of possible combinations and iterations of organizational and individual attributes—many of which rarely occur in the actual population of potential donors.
-To more fully explore the relationships between different organizational- and individual-level attributes, we turn to simulation methods that allow us to examine the impact of multiple covariates at simultaneously.
+To more fully explore the relationships between different organizational- and individual-level attributes, we turn to simulation methods that allow us to examine the impact of multiple covariates simultaneously.
 To simplify the possible combinations of individual characteristics, we generate 32 distinct personas with attributes that vary along different dimensions of demographics, politics and public affairs experience, and social attitudes (see @tbl:persona-attributes).
@@
 But by using simulations, we can discover interesting patterns of donor preferences when faced with organizations focusing on a variety of issues, funding sources, and legal restrictions abroad.
-Our market simulation reveals which combination of organizational features each persona is most likely to express a preference for donation to.
+Our market simulation reveals which combination of organizational features each persona is most likely to express a preference for donating to.
 We examine the results of the simulation in three stages, looking at how personas with different (1) demographic characteristics, (2) public affairs knowledge and experience, and (3) levels of trust in government, charitable work, and associational life change their donation preferences across different organizational issue areas, relationships with host governments, and funding sources.
@@
 Wealthier donors are more likely to prefer donating to organizations that are criticized by their host governments.
-This falls in line with their preference for human rights organizations which have more contentious missions and are more likely to receive government criticism.
+This falls in line with their preference for human rights organizations, which have more contentious missions and are more likely to receive government criticism.
 This support, however, appears to evaporate as civil society crackdown intensifies.
@@
 We next look at how differences in public affairs knowledge, experience, and political ideology influence a persona's propensity to donate to an organization.
-We vary personas along two dimensions: (1) political ideology, with semi liberal and semi conservative political leanings (2 and 5 on a 7-point scale), and (2) knowledge and experience with public affairs and the news, with personas that either follow national and international news and that have travelled abroad or personas that do not follow the news or travel.
+We vary personas along two dimensions: (1) political ideology, with semi-liberal and semi-conservative political leanings (2 and 5 on a 7-point scale), and (2) knowledge and experience with public affairs and the news, with personas that either follow national and international news and that have travelled abroad or personas that do not follow the news or travel.
 
@@
 This stark difference in attitudes towards friendly NGOs likely reflects the underlying levels of trust in the model.
-For those who trust charities to do the right thing and have a positive influence on society, a friendly relationship with a host government is a manifestation of that belief and a sign that the organization is living up to its idea.
+For those who trust charities to do the right thing and have a positive influence on society, a friendly relationship with a host government is a manifestation of that belief and a sign that the organization is living up to its ideal.
 Once the organization faces criticism or crackdown, however, support deteriorates rapidly, since such a crackdown could be perceived as a violation of the persona's trust in the charity—that is, the organization must be doing something wrong to deserve criticism.
@@
 In the UK, international aid is one of the largest targets of giving (26%).
-Other countries prioritize international philanthopy even more, such as Germany (74%), Belgium (61%), and Switzerland (43%) [@Milner:2017].
+Other countries prioritize international philanthropy even more, such as Germany (74%), Belgium (61%), and Switzerland (43%) [@Milner:2017].
 Thus, if crackdown on INGOs abroad can elicit the effects found in this paper among U.S.
@@
 
-The above results have important implications for NGOs as they navigate a shriking civic space and consider the use of different frames to tailor their fundraising appeals to individual donors.
+The above results have important implications for NGOs as they navigate a shrinking civic space and consider the use of different frames to tailor their fundraising appeals to individual donors.
 Our survey finds that at least for some kinds of individuals, NGOs may benefit from publicizing when they are targets of government crackdown, including that information in their fundraising appeals.
@@
 Existing initiatives such as the Lifeline Embattled CSO Assistance Funds provide models for channeling such funds.
-In the face of legal crackdowns abroad, individual doations are an important additional funding source for besieged NGOs.
+In the face of legal crackdowns abroad, individual donations are an important additional funding source for besieged NGOs.
 
@@
 
-[^highnetworth]: High-net worth households are have greater than \$200,000 in annual household income and/or have more than \$1,000,000 in assets, excluding primary residence.
+[^highnetworth]: High-net worth households have greater than \$200,000 in annual household income and/or have more than \$1,000,000 in assets, excluding primary residence.
 

### 2020-09-29 manuscript/manuscript.Rmd
Updates with new simulation results

@@
 We find that trust in political institutions and charities is enormously influential in shaping donor preferences.
-Donor profiles with high levels of social trust are likely to donate to human rights INGOs with friendly relationships with host governments, but that support evaporates if INGOs face criticism or crackdown.
-In contrast, donor profiles with lower levels of social trust prefer to donate to organizations that do face criticism or crackdown abroad.
+Donor profiles with high levels of social trust are likely to donate to human rights INGOs with friendly relationships with host governments, and that support hold steady if INGOs face criticism or crackdown.
+In contrast, donor profiles with lower levels of social trust prefer to donate to organizations that do not face criticism or crackdown abroad.
 Our findings have practical implications for INGOs that aim to raise funds from the general public amid closing civic space.
@@
 And research on the determinants of philanthropy for international causes—particularly towards organizations working in challenging environments—is still in its infancy due to the absence of expansive and high-quality data [@greenhill2013].
-While previous work has looked at how organizational attributes of nonprofits affect donors' willingness to donate internationally [@todo:CITEOURPAPERTODIFFERENTIATE), we have yet to uncover demographic traits and experiences that motivate or deter individuals to donate during shrinking civic space.
+While previous work has looked at how organizational attributes of nonprofits affect donors' willingness to donate internationally [@ChaudhryHeiss:2020], we have yet to uncover demographic traits and experiences that motivate or deter individuals to donate during shrinking civic space.
 
@@
 We begin by looking at differences in donation preferences across a range of basic demographic characteristics.
-The three panels of @fig:demographics shows the average predicted market share for different organizational issue areas, relationships with governments, and funding sources.
-Though we varied gender across the different personas, gender has no significant effect on any of the simulated outcomes—men and women follow nearly identical patterns across all organizational and individual characteristics.
-As such, in @fig:demographics, we only vary income.
-Personas with high income earn \$100,000 a year, while those with less income earn \$50,000 annually.
+The four panels of @fig:income show the average predicted market share for different organizational issue areas, funding sources, and relationships with host governments across different levels of persona income, with two different cutpoints for high and low income.
 
-![Average predicted donation market shares across all personas, segmented by individual persona income and organizational issue area, relationship with host government, and funding sources](output/figures/income-all.pdf){#fig:demographics}
+![Average predicted donation market shares across all personas, segmented by individual persona income and organizational issue area, relationship with host government, and funding sources](output/figures/income-all.pdf){#fig:income}
 
-Wealthier personas respond better to human rights organizations over refugee assistance and environmental advocacy organizations, while personas that earn less money tend to prefer donating to refugee and environmental organizations.
+In general, personas respond better to human rights and refugee assistance organizations and environmental advocacy organizations across both levels of income, though wealthier personas show a slight preference towards human rights and refugee organizations.
 As we explore below, this is likely because income correlates with interest in public affairs and political activity—individuals who are wealthier arguably have more time and resources to follow the news and be continuously engaged in their communities and in other activist causes.
+There are no sizable differences in donation preferences by income across different forms of NGO funding—both levels of income tend to prefer organizations funded by government grants over small donors.
 
-There are also sizable income-based differences across different NGO host-country relationships.
-Wealthier donors are more likely to prefer donating to organizations that are criticized by their host governments.
+An organization's relationship with its host government does influence market shares across levels of income, but the size of this difference depends on the magnitude of income.
+When splitting income based on the US median income (\$61,372), there is no difference between income levels.
+In general, personas prefer to donate to organizations with friendly relationships with their host governments and avoid those that are criticized or under crackdown.
+However, instead of looking at personas with below- and above-median incomes, we can simulate a subset of wealthier donors that earn at least \$100,000 annually.
+These personas are more likely to prefer donating to organizations that are criticized by their host governments.
 This falls in line with their preference for human rights organizations, which have more contentious missions and are more likely to receive government criticism.
@@
 Their lower income counterparts, on the other hand, are generally unfazed by NGOs' relationships with government, maintaining the same average market share across all three types of host country relationships.
-Finally, as seen in the right panel of @fig:demographics, there are no sizable differences in donation preferences by income across different forms of NGO funding.
-Income thus appears to influence preferences particularly for NGOs facing criticism and crackdown abroad—wealthier donors are perhaps fair-weather friends that are more likely to pull their support when an organization's work becomes more difficult.
+Patterns in preferences for issue area and funding sources remain constant across both methods of categorizing income—crackdown only has an effect on very high income personas.
+Income thus appears to influence preferences particularly for NGOs facing criticism and crackdown abroad—wealthy donors are perhaps fair-weather friends that are more likely to pull their support when an organization's work becomes more difficult.
 
-*(TODO: I'll need ≈150 words to describe education and religiosity results)*
+While education and religiosity are both important drivers of individual philanthropy, neither are associated with any sizable differences in persona donation patterns.
+In general, both high school and college graduates *and* personas who rarely attend and who often attend religious services follow the same patterns in preferences shown in @fig:income: personas prefer human rights and refugee relief organizations, organizations funded by government grants, and organizations with friendly relaitonships with their host governments (see @fig:education and @fig:religiosity in the appendix.)
 
@@
 
-@fig:issue-social, @fig:relationship-social, and @fig:funding-social show the results of the market simulation across these three dimensions of persona characteristics, varying public affairs knowledge, political ideology, and social trust.
+@fig:issue-social and @fig:relationship-social show the results of the market simulation across these three dimensions of persona characteristics, varying public affairs knowledge, political ideology, and social trust.
 Personas respond differently to organizational issue areas.
@@
 The strongest, most overriding factor in determining donor preferences when considering an organization's relationship with its host country is social trust.
-Personas with high levels of social trust are overwhelmingly most likely to donate to organizations with friendly relationships with their host governments, while those with low levels of trust avoid friendly NGOs almost entirely.
 
-This stark difference in attitudes towards friendly NGOs likely reflects the underlying levels of trust in the model.
-For those who trust charities to do the right thing and have a positive influence on society, a friendly relationship with a host government is a manifestation of that belief and a sign that the organization is living up to its ideal.
-Once the organization faces criticism or crackdown, however, support deteriorates rapidly, since such a crackdown could be perceived as a violation of the persona's trust in the charity—that is, the organization must be doing something wrong to deserve criticism.
-Personas with low levels of trust, on the other hand, eschew friendly organizations entirely and are far more willing to donate to organizations facing criticism and crackdown, likely because they do not assume that charities must always be above reproach.
-The global crackdown on NGOs could thus counterintuitively sour NGOs' most trusting donors.
+Personas across both levels of social trust are most likely to donate to donate to organizations with friendly relationships with their host governments.
+However, those with higher trust are less likely to be deterred by poor host-country relationships, while those with low trust tend to not donate to organizations facing criticism or crackdown abroad.
+A friendly relationship with a host government is a manifestation of a belief that charities behave properly and exert a positive influence on society.
+Once an organization faces criticism or crackdown, however, support deteriorates rapidly among personas with low social trust, since such a crackdown could be perceived as a violation of the persona's trust in the charity—that is, the organization must be doing something wrong to deserve criticism.
+Personas with high levels of trust, on the other hand, seem to stick with legally besieged organizations and show them the benefit of the doubt.
+The global crackdown on NGOs thus sours NGOs' least trusting donors.
 
@@
 Personas with high levels of social and charitable trust prefer donating to human rights organizations that have friendly relationships with their host governments, while personas with low trust are drawn more to emergency response and refugee relief organizations with unfriendly relationships with their host governments.
-Personas with low social trust rarely prefer to donate to any type of organization with friendly host-country relationships, while personas with high social trust tend to avoid organizations with unfriendly relationships.
-This could imply that donors that are the most trusting and involved might be fair-weather friends that drop their support when charities face government criticism and crackdown.
+Personas with low social trust tend to be scared off by negative host-country relationships and strongly prefer to donate to organizations that are friendly with their host governments, while personas with high social trust are more willing to stick with legally besieged organizations.
+This could imply that donors that are the most trusting and involved could remain supportive when charities face government criticism and crackdown.
 
@@
 Our survey finds that at least for some kinds of individuals, NGOs may benefit from publicizing when they are targets of government crackdown, including that information in their fundraising appeals.
-However, the bigger challenge may be addressing concerns of donors with low levels of trust.
+**TODO THIS IS DIFFERENT NOW** However, the bigger challenge may be addressing concerns of donors with low levels of trust.
 More broadly, studies from a range of countries show that levels of giving are lowest for refugee and asylum organizations, as well as for overseas and development organizations.
@@
 
-[^model-details]:	Specifically,
-
-    $$
-    \begin{aligned}
-    \beta &\sim \operatorname{Multivariate} \mathcal{N}(Z \Gamma, \xi) \\
-    y &\sim \operatorname{Multinomial\ logit}(X \beta, \varepsilon)
-    \end{aligned}
-    $$
-
-    where $y$ = which alternative the respondent chooses to donate to, $X$ = design matrix of attribute levels (i.e.
-organizations, issue areas, organizational practices, funding sources, and government relations), $\beta$ = latent individual preferences for the attribute levels, $Z$ = matrix of individual-level covariates (i.e.
-demographics, political knowledge, attitudes towards charity, etc.), $\Gamma$ = matrix of coefficients mapping individual-level covariates onto the latent individual-level preferences, and $\varepsilon$ and $\xi$ = errors.
+[^model-details]: See the appendix for technical details about the model and simulation.

### 2020-09-29 manuscript/manuscript.Rmd
More slight changes because of new results

@@
 Personas with high levels of trust in political and charitable institutions and who are actively engaged in charity and volunteerism prefer donating to human rights organizations that have friendly relationships with their host governments.
-In contrast, personas with low levels of social trust eschew both human rights organizations *and* any type of NGO with friendly relationships with host governments, preferring instead to donate to NGOs facing more restrictions and working on less contentious issues like emergency response and refugee relief.
-This may indicate that donors with high trust and support for NGOs could be fair-weather friends that drop their support when their preferred organizations meet resistance abroad.
+In contrast, personas with low levels of social trust eschew both human rights organizations *and* any type of NGO with more contentious relationships with host governments, preferring instead to donate to NGOs with friendly host-country relationships and working on less contentious issues like emergency response and refugee relief.
+Personas with higher trust are more comfortable donating to legall besieged INGOs.
 
@@
 To more fully explore the relationships between different organizational- and individual-level attributes, we turn to simulation methods that allow us to examine the impact of multiple covariates simultaneously.
-To simplify the possible combinations of individual characteristics, we generate 32 distinct personas with attributes that vary along different dimensions of demographics, politics and public affairs experience, and social attitudes (see @tbl:persona-attributes).
+To simplify the possible combinations of individual characteristics, we generate 64 distinct personas with attributes that vary along different dimensions of demographics, politics and public affairs experience, and social attitudes (see @tbl:persona-attributes).
 We also generate 24 simulated organizations that vary by issue area, relationship with host government, and source of funding (see @tbl:organization-attributes).

### 2020-09-29 analysis/01_clean-generate-data.Rmd
Finally add Rmd website-based analysis

---
title: "Generate and clean simulated data"
author: "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: show
    pandoc_args:
      - "--default-image-extension=png"
editor_options: 
  chunk_output_type: console
---

```{r load-packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(fastDummies)
library(scales)
library(readxl)
library(here)

# Turn off grouping message
options(dplyr.summarise.inform = FALSE)

# Project-specific functions
source(here("R", "graphics.R"))

# General settings
source(here("analysis", "options.R"))

# Make all the randomness reproducible
set.seed(1234)
```

```{r simpler-excel-based-model, message=FALSE}
sim_raw <- read_excel(here("data", "raw_data", "Market Simulator Version 01.xlsx"),
                      sheet = "Results", range = "O3:AU27")

orgs_raw <- read_excel(here("data", "raw_data", "Market Simulator Version 01.xlsx"),
                       sheet = "Results", range = "N4:O27", 
                       col_names = c("organization", "org_details"))

orgs_clean <- orgs_raw %>% 
  separate(org_details, into = c("org_issue", "org_funding", "org_relationship"), sep = ", ")

personas_raw <- read_excel(here("data", "raw_data", "Market Simulator Version 01.xlsx"),
                           sheet = "Results", range = "P2:AU3") %>% 
  pivot_longer(everything(), names_to = "persona", values_to = "persona_details")

personas_clean <- personas_raw %>% 
  separate(persona_details, into = c("demographics", "actions", "persona_trust"), sep = ", ") %>% 
  separate(demographics, into = c("persona_income", "persona_gender"), sep = " Income ") %>% 
  separate(actions, into = c("persona_ideology", "persona_experience"), sep = " that ")

sim_long <- sim_raw %>% 
  rename(org_details = `...1`) %>% 
  pivot_longer(cols = -org_details, names_to = "persona_details", values_to = "share")

sim_excel_clean <- sim_long %>% 
  left_join(orgs_raw, by = "org_details") %>% 
  left_join(personas_raw, by = "persona_details") %>% 
  separate(org_details, into = c("org_issue", "org_funding", "org_relationship"), sep = ", ") %>% 
  separate(persona_details, into = c("demographics", "actions", "persona_trust"), sep = ", ") %>% 
  separate(demographics, into = c("persona_income", "persona_gender"), sep = " Income ") %>% 
  separate(actions, into = c("persona_ideology", "persona_experience"), sep = " that ") %>% 
  mutate(org_issue = recode(org_issue, "Refugess Relief" = "Refugee Relief"),
         org_funding = recode(org_funding, "Grants" = "Mostly funded by government grants",
                              "Small Donors" = "Mostly funded by small donors"),
         persona_income = paste(persona_income, "income"),
         persona_income = factor(persona_income, levels = c("Lower income", "Higher income"), ordered = TRUE),
         persona_trust = recode(persona_trust,
                                "Doesn't Trust or Donate" = "Less trusting; donates and volunteers less often",
                                "Trusts and Donates" = "More trusting; donates and volunteers often"),
         persona_experience = recode(persona_experience,
                                     "Doesn't Read or Travel" = "Doesn't follow news; has not travelled abroad",
                                     "Reads and Travels" = "Follows the news; has travelled abroad")) %>% 
  mutate_at(vars(organization, persona), ~fct_inorder(.))
```

```{r load-data, message=FALSE}
# Gammas of the "everything" model
gammas <- read_rds(
  here('data', 'raw_data', 'posterior_draws', 'public_political_social_charity_demo.rds')
  ) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i) %>% 
  t()
```

```{r possible-organizations}
organization_columns <- c("organization", "issue.area", "transparency", 
                          "accountability", "funding", "relationship")

organization_possibilities <- expand_grid(
  issue.area = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  relationship = c("Friendly", "Criticized", "Under crackdown"),
  funding = c("Small private donations", "Government grants")
) %>% 
  mutate(org_id = paste0("org", 1:n()))

organizations <- organization_possibilities %>% 
  mutate(
    organization = "Red Cross",
    transparency = "Yes",
    accountability = "Yes"
  ) %>% 
  select(org_id, all_of(organization_columns)) %>% 
  mutate(organization = factor(organization, 
                               levels = c("Amnesty International", "Greenpeace", 
                                          "Oxfam", "Red Cross")),
         issue.area = factor(issue.area, 
                            levels = c("Emergency response", "Environment", 
                                       "Human rights", "Refugee relief")),
         transparency = factor(transparency, levels = c("No", "Yes")),
         accountability = factor(accountability, levels = c("No", "Yes")),
         funding = factor(funding, levels = c("Small private donations", 
                                              "Handful of wealthy private donors", 
                                              "Government grants")),
         relationship = factor(relationship, levels = c("Friendly", "Criticized", 
                                                        "Under crackdown")))

org_table <- organizations %>% 
  dummy_columns(select_columns = organization_columns,
                remove_selected_columns = TRUE) %>% 
  pivot_longer(cols = -org_id, names_to = "name", ) %>% 
  pivot_wider(names_from = org_id, values_from = value) %>% 
  separate(name, into = c("attribute", "option"), sep = "_") %>% 
  filter(!(option %in% c("Emergency response", "No", "Small private donations", "Friendly")))
```

```{r possible-personas}
persona_columns <- c("national.news", "international.news", "medium.follow.tv", 
                     "medium.follow.print", "medium.follow.online", "medium.follow.social", 
                     "medium.follow.radio", "medium.follow.email", "medium.follow.app", 
                     "follow.govt", "travel", "ideology", "trust.institutions", 
                     "should.be.charitable", "religious.attendance", "religion.importance", 
                     "religion", "trust.charity.importance", "trust.charities", 
                     "donation.frequency", "donated.last.year", "volunteered", 
                     "volunteer.frequency", "history.activism.personal", "history.activism.family",
                     "membership.church", "membership.sport", "membership.art", "membership.union", 
                     "membership.party", "membership.environment", "membership.professional", 
                     "membership.charitable", "membership.consumer", "membership.other", 
                     "gender", "marital", "education", "income", "race", "age")

persona_demographics <- expand_grid(
  income = c("Less than median", "More than median"),
  education = c("High school graduate", "4 year degree"),
  religious.attendance = c("Rarely", "At least once a month")
) %>% 
  mutate(demographics_id = 1:n())

persona_politics <- tribble(
  ~ideology, ~national.news, ~international.news, ~travel,
  "Extremely liberal", "At least once a day",  "Always", "Yes",
  "Extremely conservative", "At least once a day", "Always", "Yes",
  "Extremely liberal", "Rarely", "Never", "No",
  "Extremely conservative", "Rarely", "Never", "No"
) %>% 
  mutate(politics_id = 1:n())

persona_social <- tibble(
  social_id = 1:2,
  trust.institutions = c("Complete trust", "No trust"),
  should.be.charitable = c("Strongly agree", "Strongly disagree"),
  trust.charities = c("Complete trust", "No trust"),
  volunteer.frequency = c("At least once a month", "Rarely"),
  donation.frequency = c("At least once a month", 
                         "More than once a month, less than once a year"),
  history.activism.personal = c("Involved", "Not involved"),
  membership.party = c("Active member", "Don't belong"),
  membership.charitable = c("Active member", "Don't belong")
)

persona_possibilities <- expand_grid(
  demographics_id = persona_demographics$demographics_id,
  politics_id = persona_politics$politics_id,
  social_id = persona_social$social_id
) %>% 
  left_join(persona_demographics, by = "demographics_id") %>% 
  left_join(persona_politics, by = "politics_id") %>% 
  left_join(persona_social, by = "social_id") %>% 
  select(-ends_with("_id")) %>% 
  mutate(persona_id = paste0("persona", 1:n()))

# Columns that should be held constant
# persona_columns %>% .[!(. %in% colnames(persona_possibilities))] %>% cat(sep = "\n")

personas <- persona_possibilities %>% 
  mutate(
    medium.follow.tv = "Follow",
    medium.follow.print = "Follow",
    medium.follow.online = "Don't follow",
    medium.follow.social = "Follow",
    medium.follow.radio = "Don't follow",
    medium.follow.email = "Don't follow",
    medium.follow.app = "Don't follow",
    follow.govt = "Often",
    religion.importance = "Important",
    religion = "Protestant",
    trust.charity.importance = "Somewhat important",
    donated.last.year = "$100-$499",
    volunteered = "No",
    history.activism.family = "Not involved",
    membership.church = "Don't belong",
    membership.sport = "Don't belong",
    membership.art = "Don't belong",
    membership.union = "Don't belong",
    membership.environment = "Don't belong",
    membership.professional = "Don't belong",
    membership.consumer = "Don't belong",
    membership.other = "Don't belong",
    gender = "Male",
    marital = "Married",
    race = "White",
    age = "Less than median"
  ) %>% 
  select(persona_id, all_of(persona_columns)) %>% 
  mutate(
    national.news = factor(national.news, levels = c("Rarely", "Once a week", "At least once a day")),
    international.news = factor(international.news, levels = c("Never", "Sometimes", "Always")),
    medium.follow.tv = factor(medium.follow.tv, levels = c("Don't follow", "Follow")),
    medium.follow.print = factor(medium.follow.print, levels = c("Don't follow", "Follow")),
    medium.follow.online = factor(medium.follow.online, levels = c("Don't follow", "Follow")),
    medium.follow.social = factor(medium.follow.social, levels = c("Don't follow", "Follow")),
    medium.follow.radio = factor(medium.follow.radio, levels = c("Don't follow", "Follow")),
    medium.follow.email = factor(medium.follow.email, levels = c("Don't follow", "Follow")),
    medium.follow.app = factor(medium.follow.app, levels = c("Don't follow", "Follow")),
    follow.govt = factor(follow.govt, levels = c("Not often", "Often")),
    travel = factor(travel, levels = c("No", "Yes")),
    ideology = factor(ideology, 
                      levels = c("Extremely liberal", "Somewhat liberal", 
                                 "Slightly liberal", "Moderate", "Slightly conservative", 
                                 "Somewhat conservative", "Extremely conservative")),
    trust.institutions = factor(trust.institutions,
                                levels = c("No trust", "Very little trust", "Little trust", 
                                           "Neutral", "Some trust", "A lot of trust", "Complete trust")),
    should.be.charitable = factor(should.be.charitable,
                                  levels = c("Strongly disagree", "Disagree", "Somewhat disagree", 
                                             "Neutral", "Somewhat agree", "Agree", "Strongly agree")),
    religious.attendance = factor(religious.attendance,
                                  levels = c("Not sure", "Rarely", "At least once a month")),
    religion.importance = factor(religion.importance,
                                 levels = c("Not important", "Important")),
    religion = factor(religion, 
                      levels = c("Catholic", "Protestant", "Christian Orthodox", "Jewish", 
                                 "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")),
    trust.charity.importance = factor(trust.charity.importance,
                                      levels = c("Not important", "Very unimportant", 
                                                 "Somewhat unimportant", "Neutral", 
                                                 "Somewhat important", "Very important", "Essential")),
    trust.charities = factor(trust.charities,
                             levels = c("No trust", "Very little trust", "Little trust", 
                                        "Neutral", "Some trust", "A lot of trust", "Complete trust")),
    donation.frequency = factor(donation.frequency,
                                levels = c("More than once a month, less than once a year", "At least once a month")),
    donated.last.year = factor(donated.last.year,
                               levels = c("$1-$49", "$50-$99", "$100-$499", "$500-$999", 
                                          "$1000-$4,999", "$5000-$9,999", "$10,000+")),
    volunteered = factor(volunteered, levels = c("No", "Yes")),
    volunteer.frequency = factor(volunteer.frequency,
                                 levels = c("Haven't volunteered in past 12 months", "Rarely", 
                                            "More than once a month, less than once a year", 
                                            "At least once a month")),
    history.activism.personal = factor(history.activism.personal,
                                       levels = c("Not involved", "Involved")),
    history.activism.family = factor(history.activism.family,
                                     levels = c("Not involved", "Involved")),
    membership.church = factor(membership.church,
                               levels  = c("Don't belong", "Inactive member", "Active member")),
    membership.sport = factor(membership.sport,
                              levels = c("Don't belong", "Inactive member", "Active member")),
    membership.art = factor(membership.art,
                            levels = c("Don't belong", "Inactive member", "Active member")),
    membership.union = factor(membership.union,
                              levels = c("Don't belong", "Inactive member", "Active member")),
    membership.party = factor(membership.party,
                              levels = c("Don't belong", "Inactive member", "Active member")),
    membership.environment = factor(membership.environment,
                                    levels = c("Don't belong", "Inactive member", "Active member")),
    membership.professional = factor(membership.professional,
                                     levels  = c("Don't belong", "Inactive member", "Active member")),
    membership.charitable = factor(membership.charitable,
                                   levels  = c("Don't belong", "Inactive member", "Active member")),
    membership.consumer = factor(membership.consumer,
                                 levels  = c("Don't belong", "Inactive member", "Active member")),
    membership.other = factor(membership.other,
                              levels = c("Don't belong", "Inactive member", "Active member")),
    gender = factor(gender,
                    levels = c("Male", "Female", "Transgender", "Prefer not to say", "Other")),
    marital = factor(marital,
                     levels = c("Married", "Widowed", "Divorced", "Separated", "Never married")),
    education = factor(education,
                       levels = c("Less than high school", "High school graduate", "Some college", 
                                  "2 year degree", "4 year degree", "Graduate or professional degree", "Doctorate")),
    income = factor(income,
                    levels = c("Less than median", "More than median")),
    race = factor(race,
                  levels = c("White", "Black or African American", "American Indian or Alaska Native", 
                             "Asian", "Native Hawaiian or Pacific Islander", "Other")),
    age = factor(age,
                 levels = c("Less than median", "More than median"))
  )

persona_base_cases <- c(
  "national.news_Rarely",
  "international.news_Never",
  "follow.govt_Not often",
  "travel_No",
  "ideology_Extremely liberal",
  "trust.institutions_No trust",
  "should.be.charitable_Strongly disagree",
  "religious.attendance_Not sure",
  "religion.importance_Not important",
  "religion_Catholic",
  "trust.charity.importance_Not important",
  "trust.charities_No trust",
  "donation.frequency_More than once a month, less than once a year",
  "donated.last.year_$1-$49",
  "volunteered_No",
  "volunteer.frequency_Haven't volunteered in past 12 months",
  "history.activism.personal_Not involved",
  "history.activism.family_Not involved",
  "gender_Male",
  "marital_Married",
  "education_Less than high school",
  "income_Less than median",
  "age_Less than median"
)

persona_table <- personas %>% 
  dummy_columns(select_columns = persona_columns,
                remove_selected_columns = TRUE) %>% 
  pivot_longer(cols = -persona_id, names_to = "name", ) %>% 
  pivot_wider(names_from = persona_id, values_from = value) %>% 
  # Get rid of base cases
  filter(!(name %in% persona_base_cases)) %>% 
  filter(!str_detect(name, "Don't follow"),
         !str_detect(name, "Don't belong")) %>% 
  separate(name, into = c("attribute", "option"), sep = "_") %>% 
  # Add intercept
  add_row(attribute = "Intercept", option = "Intercept", .before = 1) %>% 
  mutate(across(everything(), ~replace_na(., 1)))
```

```{r predicted-market-shares}
predicted_betas <- persona_table %>% 
  summarize(across(starts_with("persona"), ~as.matrix(gammas) %*% as.matrix(.)))

expected_utilities <- exp(t(org_table[,3:ncol(org_table)]) %*% 
                            as.matrix(predicted_betas[,1:ncol(predicted_betas)])) %>% 
  as_tibble(rownames = "org")

prop_expected_utilities <- expected_utilities %>% 
  mutate(across(starts_with("persona"), ~. / sum(.)))
```

```{r finalize-data}
org_details <- organizations %>% 
  mutate(organization = str_replace(org_id, "org", "Org "),
         funding = fct_recode(funding, 
                              "Mostly funded by small donors" = "Small private donations",
                              "Mostly funded by government grants" = "Government grants"),
         relationship = fct_rev(relationship)) %>%
  select(org_id, organization, org_issue = issue.area, 
         org_funding = funding, org_relationship = relationship)

persona_details <- personas %>% 
  mutate(persona_income = fct_recode(income, 
                                     "Lower income" = "Less than median", 
                                     "Higher income" = "More than median"),
         persona_education = fct_recode(education, "College graduate" = "4 year degree"),
         persona_religion = fct_recode(religious.attendance, 
                                       "Rarely attends religious services" = "Rarely",
                                       "Attends at least monthly" = "At least once a month"),
         persona_ideology = fct_recode(ideology, 
                                       "Conservative" = "Extremely conservative",
                                       "Liberal" = "Extremely liberal"),
         persona_experience = ifelse(travel == "Yes", 
                                     "Follows the news; has travelled abroad", 
                                     "Doesn't follow news; has not travelled abroad"),
         persona_trust = ifelse(trust.charities == "Complete trust", 
                                "More trusting; donates and volunteers often", 
                                "Less trusting; donates and volunteers less often")) %>% 
  mutate(persona = str_replace(persona_id, "persona", "Persona ")) %>% 
  select(persona, starts_with("persona"))

sim_clean <- prop_expected_utilities %>% 
  pivot_longer(cols = -org, names_to = "persona_id", values_to = "share") %>% 
  left_join(org_details, by = c("org" = "org_id")) %>% 
  left_join(persona_details, by = "persona_id")
```

```{r save-clean-data}
write_rds(sim_excel_clean, here("data", "derived_data", "sim_excel_final.rds"))
write_rds(sim_clean, here("data", "derived_data", "sim_final.rds"))
```

\

# Original computing environment

<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>

<div id="sessioninfo" class="collapse">

```{r show-session-info, echo=TRUE, width=100}
devtools::session_info()

writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))
```

</div>

### 2020-09-29 analysis/02_tables.Rmd
Finally add Rmd website-based analysis

---
title: "Tables"
author: "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
    pandoc_args:
      - "--default-image-extension=png"
editor_options: 
  chunk_output_type: console
---

```{r packages, warning=FALSE, message=FALSE, include=FALSE}
library(tidyverse)
library(pander)
library(magrittr)
library(glue)
library(scales)
library(janitor)
library(here)
```

```{r load-data}
sim_clean <- read_rds(here("data", "derived_data", "sim_final.rds"))
results <- read_rds(here("data", "raw_data", "final_data.rds"))

org_attributes <- tribble(
  ~`Issue area`, ~`Relationship with government`, ~`Funding`, ~`Funding sources`, ~`Organizational practices`, ~`Organization`,
  "Emergency response", "Friendly", "Small private donors", "Small private donors", "Financial transparency", "Amnesty International",
  "Environment", "Criticized", "Government grants", "Wealthy donors", "Accountability", "Greenpeace",
  "Human rights", "Crackdown", "", "Government grants", "", "Oxfam",
  "Refugee relief", "", "", "", "", "Red Cross"
)

persona_attributes <- tribble(
  ~`Demographics`, ~`Politics and public affairs`, ~`Social views`,
  "Higher income (> US median ($61,372)), high school graduate, frequent religious attendance", "Liberal (1), follows national and international news often, has traveled internationally", "High social trust: Trusts political institutions, trusts charities, thinks people should be more charitable, frequently volunteers, donates once a month, has a history of personal activism, is a member of an association",
  "Lower income (< US median), high school graduate, frequent religious attendance", "Conservative (7), follows news, has traveled", "Low social trust: Does not trust political institutions or charities, thinks people should be less charitable, does not volunteer or donate often, has no history of personal activism, is not a member of an association",
  "Higher income, college graduate, frequent religious attendance", "Liberal, does not follow news, has not traveled", "",
  "Lower income, college graduate, frequent religious attendance", "Conservative, does not follow news, has not traveled", "",
  "Higher income, high school graduate, rare religious attendance", "", "",
  "Lower income, high school graduate, rare religious attendance", "", "",
  "Higher income, college graduate, rare religious attendance", "", "",
  "Lower income, college graduate, rare religious attendance", "", ""
)
```

# Organization attributes

## All possible conjoint attributes

```{r results="asis"}
org_attributes %>% 
  select(Organization, `Issue area`, `Organizational practices`, `Funding sources`, `Relationship with government`) %>% 
  pandoc.table.return(caption = 'Organization attributes varied in the experiment {#tbl:organization-attributes-full}',
                      justify = "lllll", split.tables = Inf) %T>%
  cat() %>%
  cat(file = here("analysis", "output", "tables", "tbl-organization-attributes-full.md"))
```

## Attributes varied in simulation

```{r results="asis"}
org_attributes %>% 
  select(`Issue area`, `Relationship with government`, `Funding`) %>% 
  pandoc.table.return(caption = 'Organization attributes varied in the simulation, resulting in 24 hypothetical organizations {#tbl:organization-attributes}',
                      justify = "lll") %T>%
  cat() %>%
  cat(file = here("analysis", "output", "tables", "tbl-organization-attributes.md"))
```

# Persona attributes

## Attributes varied in simulation

```{r results="asis"}
persona_attributes %>% 
  pandoc.table.return(caption = 'Individual attributes varied in the simulation, resulting in 64 persona profiles {#tbl:persona-attributes}',
                      justify = "lll", split.tables = Inf) %T>%
  cat() %>%
  cat(file = here("analysis", "output", "tables", "tbl-persona-attributes.md"))
```

# Example simulation output

```{r results="asis"}
example_personas <- c("persona2", "persona63")

example_persona_details <- sim_clean %>%
  filter(persona_id %in% example_personas) %>% 
  select(starts_with("persona")) %>% 
  slice(1:2)

example_persona_details %>% 
  select(-persona_id) %>% 
  pivot_longer(cols = !persona) %>% 
  pivot_wider(names_from = "persona", values_from = "value") %>% 
  select(-name) %>% 
  pandoc.table(justify = "ll")
```

```{r results="asis"}
example_persona_results <- sim_clean %>% 
  filter(persona_id %in% example_personas) %>% 
  mutate(org_funding = str_to_sentence(str_remove(org_funding, "Mostly funded by "))) %>% 
  mutate(org_clean = glue("{organization}: {org_issue}, {org_funding}, {org_relationship}")) %>% 
  mutate(persona_desc = recode(
    persona_id,
    "persona2" = "Lower income high school graduate who rarely attends religious services; liberal who reads and travels; doesn't trust or donate",
    "persona63" = "Higher income college graduate who attends religious services; conservative who doesn't read or travel; trusts and donates")
  ) %>%
  mutate(persona_clean = glue("{persona}: {persona_desc}")) %>% 
  select(persona_clean, share, org_clean) %>% 
  pivot_wider(names_from = "persona_clean", values_from = "share") %>% 
  adorn_totals(where = "row", name = "**Total**")

example_persona_results_small <- example_persona_results %>% 
  slice(c(1, 2, 3, 7, 8, 9, 16, 17, 25)) %>% 
  mutate(across(where(is.numeric), ~ percent_format(accuracy = 0.1)(.))) %>% 
  add_row(org_clean = "…", .after = 3) %>% 
  add_row(org_clean = "…", .after = 7) %>% 
  add_row(org_clean = "…", .after = 10) %>% 
  mutate(across(everything(), ~replace_na(., "…"))) %>% 
  rename(Organization = org_clean)

example_persona_results_small %>% 
  pandoc.table.return(caption = 'Sample simulation output {#tbl:sim-output}',
                      justify = "lcc", split.tables = Inf) %T>%
  cat() %>%
  cat(file = here("analysis", "output", "tables", "tbl-sim-output.md"))
```

# Sample details

```{r}
vars_to_summarize <- tribble(
  ~category, ~variable, ~clean_name,
  "Demographics", "Q5.12", "Gender",
  "Demographics", "Q5.17", "Age",
  "Demographics", "Q5.13", "Marital status",
  "Demographics", "Q5.14", "Education",
  "Demographics", "Q5.15", "Income",
  "Attitudes toward charity", "Q2.5", "Frequency of donating to charity",
  "Attitudes toward charity", "Q2.6", "Amount of donations to charity last year",
  "Attitudes toward charity", "Q2.7_f", "Importance of trusting charities",
  "Attitudes toward charity", "Q2.8_f", "Level of trust in charities",
  "Attitudes toward charity", "Q2.10", "Frequency of volunteering",
  "Politics, ideology, and religion", "Q2.1", "Frequency of following national news",
  "Politics, ideology, and religion", "Q5.7", "Traveled to a developing country",
  "Politics, ideology, and religion", "Q5.1", "Voted in last election",
  "Politics, ideology, and religion", "Q5.6_f", "Trust in political institutions and the state",
  "Politics, ideology, and religion", "Q5.2_f", "Political ideology",
  "Politics, ideology, and religion", "Q5.4", "Involvement in activist causes",
  "Politics, ideology, and religion", "Q5.8", "Frequency of attending religious services",
  "Politics, ideology, and religion", "Q5.9", "Importance of religion"
)

summarize_factor <- function(x) {
  output <- table(x) %>% 
    as_tibble() %>% 
    magrittr::set_colnames(., c("level", "count")) %>% 
    mutate(level = factor(level, levels = levels(x))) %>%
    mutate(prop = count / sum(count),
           nice_prop = scales::percent(prop))

  return(list(output))
}

participant_summary <- results %>% 
  select(one_of(vars_to_summarize$variable)) %>% 
  summarize_all(summarize_factor) %>% 
  pivot_longer(cols = everything(), names_to = "variable", values_to = "details") %>% 
  left_join(vars_to_summarize, by = "variable") %>% 
  unnest(details) %>% 
  mutate(level = as.character(level)) %>% 
  mutate(level = case_when(
    variable == "Q2.7_f" & level == "1" ~ "1 (not important)",
    variable == "Q2.7_f" & level == "7" ~ "7 (important)",
    variable == "Q2.8_f" & level == "1" ~ "1 (no trust)",
    variable == "Q2.8_f" & level == "7" ~ "7 (complete trust)",
    variable == "Q5.6_f" & level == "1" ~ "1 (no trust)",
    variable == "Q5.6_f" & level == "7" ~ "7 (complete trust)",
    variable == "Q5.2_f" & level == "1" ~ "1 (extremely liberal)",
    variable == "Q5.2_f" & level == "7" ~ "7 (extremely conservative)",
    variable == "Q5.15" & level == "Less than median" ~ "Less than 2017 national median ($61,372)",
    variable == "Q5.17" & level == "Less than median" ~ "Less than 2017 national median (36)",
    TRUE ~ level
  )) %>% 
  mutate(clean_name_shrunk = ifelse(clean_name == lag(clean_name), "", clean_name),
         clean_name_shrunk = ifelse(is.na(clean_name_shrunk), 
                                    clean_name[1], 
                                    clean_name_shrunk),
         category_shrunk = ifelse(category == lag(category), "", category),
         category_shrunk = ifelse(is.na(category_shrunk), 
                                    category[1], 
                                    category_shrunk))
```

```{r results="asis"}
participant_summary %>% 
  select("Category" = category_shrunk, "Question" = clean_name_shrunk, 
         "Response" = level, "N" = count, "%" = nice_prop) %>% 
  pandoc.table.return(caption = 'Summary of individual respondent characteristics {#tbl:sample-details}',
                      justify = "lllcc", split.tables = Inf) %T>%
  cat() %>%
  cat(file = here("analysis", "output", "tables", "tbl-sample-details.md"))
```

\

# Original computing environment

<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>

<div id="sessioninfo" class="collapse">

```{r show-session-info, echo=TRUE, width=100}
devtools::session_info()

writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))
```

</div>

### 2020-09-29 analysis/03_analysis.Rmd
Finally add Rmd website-based analysis

---
title: "Analysis and figures"
author: "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
    pandoc_args:
      - "--default-image-extension=png"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.retina = 3, fig.align = "center")
```

```{r load-packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(fastDummies)
library(scales)
library(patchwork)
library(ggstance)
library(here)

# Turn off grouping message
options(dplyr.summarise.inform = FALSE)

# Project-specific functions
source(here("R", "graphics.R"))

# General settings
source(here("analysis", "options.R"))

# Make all the randomness reproducible
set.seed(1234)
```

```{r load-data}
sim_excel_clean <- read_rds(here("data", "derived_data", "sim_excel_final.rds"))
sim_clean <- read_rds(here("data", "derived_data", "sim_final.rds"))
```

# General trends in private philanthropy

Based on data from [Giving USA](https://theconversation.com/fewer-americans-are-giving-money-to-charity-but-total-donations-are-at-record-levels-anyway-98291), philanthropy in the United states continues to increase, both in aggregate and per capita.

```{r giving-usa-data, message=FALSE}
giving_aggregate_raw <- read_csv(here("data", "raw_data", "data-FTjUv.csv"))

giving_aggregate <- giving_aggregate_raw %>% 
  mutate(total = `Total donations` * 1000000000)

giving_per_capita_raw <- read_csv(here("data", "raw_data", "data-xextT.csv"))

giving_per_capita <- giving_per_capita_raw
```

## Total giving

```{r plot-total-giving, fig.width=4, fig.height=2.4}
ggplot(giving_aggregate, aes(x = Year, y = `Total donations`)) +
  geom_line(size = 1, color = clrs$maroon) +
  scale_x_continuous(breaks = seq(1980, 2015, 5)) +
  scale_y_continuous(labels = dollar, breaks = seq(100, 450, 50)) + 
  coord_cartesian(ylim = c(100, 450)) +
  labs(x = NULL, y = "Billions of dollars") + 
  theme_ngo(9)

ggsave(here("analysis", "output", "figures", "giving_aggregate.pdf"), 
       width = 4, height = 2.4, units = "in", device = cairo_pdf)
ggsave(here("analysis", "output", "figures", "giving_aggregate.png"), 
       width = 4, height = 2.4, units = "in", type = "cairo", dpi = 300)
```

## Average per capita giving

```{r plot-per-capita-giving, fig.width=6, fig.height=3.6}
ggplot(giving_per_capita, aes(x = Year, y = `Average giving`)) +
  geom_line(size = 1, color = clrs$green) +
  scale_x_continuous(breaks = seq(2000, 2014, 2)) +
  scale_y_continuous(labels = dollar, breaks = seq(1750, 2750, 250)) + 
  coord_cartesian(ylim = c(1750, 2750)) +
  labs(x = NULL, y = "Average annual donation") + 
  theme_ngo()

ggsave(here("analysis", "output", "figures", "giving_per_capita.pdf"), 
       width = 6, height = 3.6, units = "in", device = cairo_pdf)
ggsave(here("analysis", "output", "figures", "giving_per_capita.png"), 
       width = 6, height = 3.6, units = "in", type = "cairo", dpi = 300)
```

# Simulations

## Income across issue area, funding, and relationship

```{r income-issue-funding-relationship, fig.width=6.5, fig.height=4.75}
plot_income_issue <- sim_clean %>% 
  group_by(org_issue, persona_income) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Issue area") %>% 
  ggplot(aes(y = fct_rev(org_issue), x = avg_share, color = fct_rev(persona_income))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002)),
                     breaks = seq(0, 0.06, 0.02)) +
  scale_color_manual(values = c(clrs$green, clrs$blue), guide = FALSE) +
  coord_cartesian(xlim = c(0, 0.06)) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_income_funding <- sim_clean %>% 
  group_by(org_funding, persona_income) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Funding sources") %>% 
  ggplot(aes(y = str_wrap(fct_rev(org_funding), 10), 
             x = avg_share, color = fct_rev(persona_income))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.06)) +
  scale_color_manual(values = c(clrs$green, clrs$blue), guide = FALSE) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_income_relationship <- sim_clean %>% 
  mutate(persona_income = fct_recode(persona_income,
                                     "< $61,372/year" = "Lower income",
                                     "> $61,372/year" = "Higher income")) %>% 
  group_by(org_relationship, persona_income) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Relationship with host government") %>% 
  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = fct_rev(persona_income))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) +
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.003))) +
  coord_cartesian(xlim = c(0, 0.1)) +
  scale_color_manual(values = c(clrs$green, clrs$blue), 
                     guide = guide_legend(reverse = TRUE, nrow = 1)) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(str_wrap(facet, 50))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_income_relationship_extreme <- sim_excel_clean %>% 
  mutate(persona_income = fct_recode(persona_income,
                                     "$50,000/year" = "Lower income",
                                     "$100,000/year" = "Higher income"),
         org_relationship = fct_recode(org_relationship,
                                       "Under crackdown" = "Crackdown")) %>% 
  group_by(org_relationship, persona_income) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Relationship with host government") %>% 
  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = fct_rev(persona_income))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.1)) +
  scale_color_manual(values = c(colorspace::darken(clrs$green, 0.4), 
                                colorspace::darken(clrs$blue, 0.6)), 
                     guide = guide_legend(reverse = TRUE, nrow = 1)) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(str_wrap(facet, 50))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_income <- plot_income_issue + plot_income_funding + 
  plot_income_relationship + plot_income_relationship_extreme +
  plot_layout(nrow = 2)

plot_income
ggsave(plot_income, filename = here("analysis", "output", "figures", "income-all.pdf"),
       width = 6.5, height = 4.75, units = "in", device = cairo_pdf)
ggsave(plot_income, filename = here("analysis", "output", "figures", "income-all.png"),
       width = 6.5, height = 4.75, units = "in", type = "cairo", dpi = 300)
```

## Education across issue area, funding, and relationship

```{r edu-issue-funding-relationship, fig.width=5, fig.height=4.25}
plot_education_issue <- sim_clean %>% 
  group_by(org_issue, persona_education) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Issue area") %>% 
  ggplot(aes(y = fct_rev(org_issue), x = avg_share, color = fct_rev(persona_education))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.06)) +
  scale_color_manual(values = c(clrs$orange, clrs$purple), guide = FALSE) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_education_funding <- sim_clean %>% 
  group_by(org_funding, persona_education) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Funding sources") %>% 
  ggplot(aes(y = str_wrap(fct_rev(org_funding), 10), 
             x = avg_share, color = fct_rev(persona_education))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.06)) +
  scale_color_manual(values = c(clrs$orange, clrs$purple), guide = FALSE) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_education_relationship <- sim_clean %>% 
  group_by(org_relationship, persona_education) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Relationship with host government") %>% 
  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = fct_rev(persona_education))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.1)) +
  scale_color_manual(values = c(clrs$orange, clrs$purple), 
                     guide = guide_legend(reverse = TRUE, ncol = 1)) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(str_wrap(facet, 20))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_education <- plot_education_issue + plot_education_funding + 
  plot_education_relationship + guide_area() + 
  plot_layout(guides = "collect", ncol = 2)
plot_education

ggsave(plot_education, filename = here("analysis", "output", "figures", "education-all.pdf"),
       width = 5, height = 4.25, units = "in", device = cairo_pdf)
ggsave(plot_education, filename = here("analysis", "output", "figures", "education-all.png"),
       width = 5, height = 4.25, units = "in", type = "cairo", dpi = 300)
```

## Religiosity across issue area, funding, and relationship

```{r religion-issue-funding-relationship, fig.width=5, fig.height=4.25}
plot_religion_issue <- sim_clean %>% 
  group_by(org_issue, persona_religion) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Issue area") %>% 
  ggplot(aes(y = fct_rev(org_issue), x = avg_share, color = fct_rev(persona_religion))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.06)) +
  scale_color_manual(values = c(clrs$red, clrs$navy), guide = FALSE) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_religion_funding <- sim_clean %>% 
  group_by(org_funding, persona_religion) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Funding sources") %>% 
  ggplot(aes(y = str_wrap(fct_rev(org_funding), 10), 
             x = avg_share, color = fct_rev(persona_religion))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.06)) +
  scale_color_manual(values = c(clrs$red, clrs$navy), guide = FALSE) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_religion_relationship <- sim_clean %>% 
  group_by(org_relationship, persona_religion) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Relationship with host government") %>% 
  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = fct_rev(persona_religion))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.1)) +
  scale_color_manual(values = c(clrs$red, clrs$navy), 
                     guide = guide_legend(reverse = TRUE, ncol = 1)) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(str_wrap(facet, 20))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_religion <- plot_religion_issue + plot_religion_funding + 
  plot_religion_relationship + guide_area() + 
  plot_layout(guides = "collect", ncol = 2)
plot_religion

ggsave(plot_religion, filename = here("analysis", "output", "figures", "religion-all.pdf"),
       width = 5, height = 4.25, units = "in", device = cairo_pdf)
ggsave(plot_religion, filename = here("analysis", "output", "figures", "religion-all.png"),
       width = 5, height = 4.25, units = "in", type = "cairo", dpi = 300)
```

## Social trust across issue area

```{r trust-issues}
plot_issue_social <- sim_clean %>% 
  group_by(org_issue, persona_trust, persona_ideology, persona_experience) %>% 
  summarize(avg_share = mean(share)) %>% 
  ggplot(aes(y = fct_rev(org_issue), x = avg_share, color = persona_trust)) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent) +
  scale_color_manual(values = c(clrs$orange, clrs$navy), guide = guide_legend(reverse = TRUE)) +
  labs(x = "Average share of donations", y = NULL, color = NULL) +
  facet_grid(rows = vars(persona_ideology), cols = vars(str_wrap(persona_experience, 100))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_issue_social
ggsave(plot_issue_social, filename = here("analysis", "output", "figures", "issue-social.pdf"),
       width = 6, height = 4.2, units = "in", device = cairo_pdf)
ggsave(plot_issue_social, filename = here("analysis", "output", "figures", "issue-social.png"),
       width = 6, height = 4.2, units = "in", type = "cairo", dpi = 300)
```

## Social trust across relationship

```{r trust-relationship}
plot_relationship_social <- sim_clean %>% 
  group_by(org_relationship, persona_trust, persona_ideology, persona_experience) %>% 
  summarize(avg_share = mean(share)) %>% 
  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = persona_trust)) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent) +
  scale_color_manual(values = c(clrs$orange, clrs$navy), guide = guide_legend(reverse = TRUE)) +
  labs(x = "Average share of donations", y = NULL, color = NULL) +
  facet_grid(rows = vars(persona_ideology), cols = vars(str_wrap(persona_experience, 100))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_relationship_social
ggsave(plot_relationship_social, filename = here("analysis", "output", "figures", "relationship-social.pdf"),
       width = 6, height = 4.2, units = "in", device = cairo_pdf)
ggsave(plot_relationship_social, filename = here("analysis", "output", "figures", "relationship-social.png"),
       width = 6, height = 4.2, units = "in", type = "cairo", dpi = 300)
```

## Social trust across funding

```{r trust-funding}
plot_funding_social <- sim_clean %>% 
  group_by(org_funding, persona_trust, persona_ideology, persona_experience) %>% 
  summarize(avg_share = mean(share)) %>% 
  ggplot(aes(y = str_wrap(fct_rev(org_funding), 20), x = avg_share, color = persona_trust)) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent) +
  scale_color_manual(values = c(clrs$orange, clrs$navy), guide = guide_legend(reverse = TRUE)) +
  labs(x = "Average share of donations", y = NULL, color = NULL) +
  facet_grid(rows = vars(persona_ideology), cols = vars(str_wrap(persona_experience, 100))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_funding_social
ggsave(plot_funding_social, filename = here("analysis", "output", "figures", "funding-social.pdf"),
       width = 6, height = 4.2, units = "in", device = cairo_pdf)
ggsave(plot_funding_social, filename = here("analysis", "output", "figures", "funding-social.png"),
       width = 6, height = 4.2, units = "in", type = "cairo", dpi = 300)
```

\

# Original computing environment

<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>

<div id="sessioninfo" class="collapse">

```{r show-session-info, echo=TRUE, width=100}
devtools::session_info()

writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))
```

</div>

### 2020-09-29 analysis/index.Rmd
Finally add Rmd website-based analysis

--- 2020-09-29 manuscript/manuscript.Rmd
@@
 title: "Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy"
-short-title: "Who Cares About Crackdowns?"
-author:
-- name: Suparna Chaudhry
-  affiliation: Lewis & Clark College
-  url: http://www.suparnachaudhry.com/
-  email: schaudhry@lclark.edu
-- name: Marc Dotson
-  affiliation: Brigham Young University
-  url: https://marriottschool.byu.edu/directory/details?id=50683
-  email: marc_dotson@byu.edu
-- name: Andrew Heiss
-  affiliation: Georgia State University
-  url: https://www.andrewheiss.com/
-  email: aheiss@gsu.edu
-date: "September 24, 2020"
-published: Working paper.
-git-repo: https://example.com
-abstract: >-
+author: "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
+date: "Last run: `r format(Sys.time(), '%F')`"
+---
+
+## Abstract
+
 Over the past two decades, international non-governmental organizations (INGOs) have faced increasing legal scrutiny and repression abroad.
@@
 Our findings have practical implications for INGOs that aim to raise funds from the general public amid closing civic space.
-reference-section-title: References
-toc: false
-mainfont: Lora
-sansfont: IBM Plex Sans
----
-
-<!-- manuscript.md is generated from manuscript.Rmd. Only edit the .Rmd file, *not* the .md file. -->
-
-In its 2016 annual report, Human Rights Watch claimed that civil society was under more aggressive attack than at any time in recent memory.
-Governments across the globe have cracked down on civil society organizations (CSOs) and non-governmental organizations (NGOs)—a phenomenon known as "closing civic space" [@CarothersBrechenmacher:2014; @CIVICUS:2017].[^NGOdef] As part of this phenomenon, NGOs face strong legal and bureaucratic obstacles to their work.
-Legal restrictions, or what we refer to as legal crackdowns, are a core part of these efforts.
-These crackdowns create barriers to entry, funding, and advocacy for NGOs in an effort to control, obstruct, and repress these organizations.
-
-As a result of these legal crackdowns, foreign aid channeled through NGOs has decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
-While this has negatively impacted funding flows from public organizations like United States Agency for International Development (USAID) and Organisation for Economic Cooperation and Development (OECD) philanthropy from private donors and foundations appears to not be as adversely affected [@McGill:2018].
-Given this trend of closing civic space, INGOs need to maintain access to multiple sources of funding, including individual donors.
-
-Individual private donations are a critical source of INGO funding.
-Total private philanthropy in the United States has grown substantially over time, reaching more than \$400 billion in 2018 (@fig:giving-aggregate).
-In 2018, private giving to NGOs working specifically in international affairs reached \$22.08 billion, and international affairs-focused organizations are one of only two categories of organizations that have continued experiencing substantial growth in giving [@givingusa:2019].[^intlaffairs] Most of this growth is driven by individuals making small-scale or micro-donations.[^smalldonors] In 2017, 70% of donations to international affairs NGOs came from individuals, rising to 86% in 2018.
-But relying on individual donors means that NGOs must consider individual preferences when fundraising.
-Which individual donor characteristics and attributes are most salient for INGOs interested in maximizing philanthropy at a time when they are facing increasingly hostile environments abroad?
-What kinds of donors are more or less likely to consider an INGO's host country political environment when making the decision to donate?
-
-![Aggregate philanthropic giving in the United States, 1977–2017. Source: Giving USA.](output/figures/giving_aggregate.pdf){#fig:giving-aggregate}
-
-Existing scholarship on the determinants of individual-level philanthropy to domestic causes is robust across a variety of contexts.
-But the dynamics of *international* giving to NGOs are under-examined in the literature on individual donor attributes and preferences.[^exceptions] Motivating individuals to donate to international causes is hard as the number of recipients are large and far removed from the donor [@CasaleBaumann:2015, 100].
-And research on the determinants of philanthropy for international causes—particularly towards organizations working in challenging environments—is still in its infancy due to the absence of expansive and high-quality data [@greenhill2013].
-While previous work has looked at how organizational attributes of nonprofits affect donors' willingness to donate internationally [@ChaudhryHeiss:2020], we have yet to uncover demographic traits and experiences that motivate or deter individuals to donate during shrinking civic space.
-
-We explore this question using a simulated market for philanthropic donations, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity.
-We adapt methods used in marketing to generate dozens of distinct simulated personas that represent typical donor profiles, and we vary these personas along different dimensions of demographic, political, and social attributes.
-We find that specific individual characteristics help shape donor preferences for donating to international NGOs, and that an INGO's target issue area and its relationship with host government interact strongly with these characteristics.
-Personas with high levels of trust in political and charitable institutions and who are actively engaged in charity and volunteerism prefer donating to human rights organizations that have friendly relationships with their host governments.
-In contrast, personas with low levels of social trust eschew both human rights organizations *and* any type of NGO with more contentious relationships with host governments, preferring instead to donate to NGOs with friendly host-country relationships and working on less contentious issues like emergency response and refugee relief.
-Personas with higher trust are more comfortable donating to legall besieged INGOs.
-
-This study contributes to both to scholarship and practice in public policy, nonprofits, and philanthropy.
-Individual giving abroad can help bridge socioeconomic disparities worldwide, especially given the stark inequality in global distribution of income.
-Knowledge of demographic traits and its impact on funding can help nonprofits craft more effective and targeted marketing strategies [@Rajan:2009, 414].
-Most NGOs working internationally have previously relied on government and foundation funding.
-But with shrinking civic space, these groups may need to readjust their fundraising strategies towards individuals.
-Framing is important in this regard—how people process information affects their willingness to donate.[^framing] However, existing research is unclear about which frames are effective when making appeals to individual donors considering international philanthropy.
-Since our study looks at multiple organizational and host country factors, our results can help NGOs frame their appeals.
-
-More broadly, while research in public policy examines giving to NGOs, philanthropy is not seen as relevant by international relations as a discipline [@youde2019].
-However, philanthropy—particularly donations received by INGOs—can help us understand changes in the dynamics of global governance.
-Private individuals exercise power and influence in unique ways that differ from other non-state actors.
-As @youde2019 [p.
-44] points out, it changes our conceptions of individuals being passive recipients to active entities that are not merely objects of governance.
-Thus, it can shed light on the changing logic of global governance.
-
-Below, we first examine the state of the existing literature on the key drivers of individual giving.
-We then describe our survey experiment and simulation methods and explore the results.
-We conclude with a discussion of the implications our findings have on general INGO funding in the age of constrained civil society space.
-
-# Sustaining civil society organizations abroad
-
-Foreign aid to civil society—and NGOs in particular—has steadily increased over time.
-Many government and foundation donors perceive NGOs as nimbler and less bureaucratic than governments.
-In countries with weak institutions and poor governance, where direct aid transfers to governments raise issues of misuse and bureaucratic inefficiency, donors specifically seek out NGOs for projects [@Dietrich2013].
-
-## Sources of funding
-
-Thousands of INGOs in the Global South receive funds from a variety of public and private sources each year.
-Public funds—or traditional donor aid—channel money from official aid agencies through a variety of bilateral and multilateral institutions.
-Private sources include foundations, private corporations, and individuals.
-While INGOs have not been passive in responding to the crackdown on civil society, they face increasing obstacles from a funding perspective.
-Official donors have reduced the amount of aid channeled to countries with legal restrictions [@DupuyPrakash:2018] and have redirected funds within restrictive countries, decreasing funds for politically sensitive causes in favor of tamer issues that are more compatible with the governments of those countries [@ChaudhryHeiss:2018].
-However, private funding towards international nonprofits has not been as adversely affected.
-Many foundations have continued channeling funds to countries with hostile legal environments [@NeedlesWolcheckSato:2018].
-
-The advent of funding restrictions on NGOs globally and a subsequent decline in government and foundation funding has made the role and value of individual philanthropy in sustaining NGOs even clearer.[^phildef] NGOs need access to a diverse array of funds and individual donations to international affairs organizations have steadily increased over the past two decades.
-Moreover, in the United States donations from individuals have far outstripped foundation and corporate giving.
-In 2018, individual donations amounted to \$292 billion, compared to \$76 billion from foundations and \$20 billion from corporations [@NPT].
-Given that a majority of research is restricted to elite high net-worth donors[^highnetworth] [@USTrust2014], these figures show that it is imperative to understand motivations and attributes of small-scale donors as well.
-
-## Key drivers of individual-level philanthropy
-
-A vast literature on philanthropy looks at organizational-level factors that motivate individuals to donate [@TBPrakash:2017].
-However, donation decisions are not determined solely by a recipient organization's characteristics.
-Donors have personality traits, preferences, and experiences that make them more or less likely to engage in philanthropy.
-Substantial research has looked at the determinants of donating to local—rather than international—causes, including four main attributes: social capital, the role of higher education, levels of religiosity, wealth, and national group attachment.
-
-Social capital, particularly associational capital, or "the networks of formal and informal relationships to which people are associated," is often considered an important indicator of giving [@havens2007, 240].
-Volunteering exposes individuals to the need for donations, making them feel more compelled to donate [@hossainlamb2012].
-Those who participate in a variety of associations are both more likely to donate as well as make larger donations [@hossainlamb2017].
-
-Higher education also influences charitable-giving decisions as it fosters prosocial motivations.
-Education brings people into social networks that entail a higher level of solicitations, which is vital in giving to international causes [@BekkersWiepking:2011].
-Education also helps determine the kinds of causes that people donate to globally.
-@Micklewright:2009 show that higher education matters more for donating to international relief organizations than donating to domestic organizations.
-
-A number of NGOs facing crackdowns abroad also work on issues that may be seen as "contentious," including human rights, elections, corruption, advocacy, and media freedom—issues that may have a harder time attracting funds due to their non-essential nature when compared to causes like health, education, sanitation, and social services.
-However, additional education has been shown to increase abstract thinking [@wiepkingmaas, 1978], which may be necessary to donate to causes that do not have quantifiable goals.
-This is particularly important for organizations with more "contentious" causes as part of their missions [@Bush:2015].
-
-Religiosity is also a significant predictor of the likelihood and level of giving.
-People who regularly attend religious services are more likely to have prosocial values, face a stronger norm of charitable giving, and may feel pressure to conform to group and community standards [@wiepking2010].
-Regular attendance may also strengthen individuals' beliefs in organizations' missions.
-
-Finally, recent research looks at how a sense of ethnonationalism and national group attachment affects the decision to donate to domestic and international charities.
-Looking at UK respondents, @hartrobson2019 find that whereas nationalists have a preference for domestic charities, they are not necessarily averse to donating to international causes, whereas internationalists have a strong preference for donating to causes and groups working abroad.
-
-Which of these characteristics matter when deciding to donate to an INGO, particularly when an organization faces legal crackdown abroad?
-Overall, individuals with higher levels of income, education, and greater religious proclivities are not only more likely to give internationally, but also give higher amounts [@Rajan:2009; @CasaleBaumann:2015].
-Additionally, we posit that other related characteristics such as civic and associational engagement and social trust also influence the decision to donate.
-
-We explore this question using a conjoint experiment conducted with a nationally representative sample in the U.S.
-Importantly, because there is so little research about international donations during legal crackdown by host governments, our analysis and results are exploratory and descriptive.
-Accordingly, we do not test specific hypotheses or theories.
-However, we do talk about causal effects given that we conduct an experiment that varies organizational characteristics in order to elicit opinions from respondents (i.e.
-specific attributes and features cause different aggregate effects).
-Instead, we structure our analysis around broader themes from the existing literature and investigate how donors' (1) demographic characteristics, (2) public affairs knowledge and experience, and (3) levels of trust in government, charitable work, and associational life change their donation preferences across different organizational issue areas, relationships with host governments, and funding sources.
-Our innovative experimental approach provides rich quantitative details of individual and organizational characteristics simultaneously and reveals unique insights into donor motivations that both confirm and expand previous research.
-
-# Data and methods
-
-## Conjoint experiment
-
-We use a conjoint experiment to simultaneously study the effects of organizational characteristics and individual attributes on individuals' preferences to donate to a nonprofit organization.
-Conjoint analysis allow us to elicit donor preferences without respondents explicitly stating their exact preferences.
-This kind of analysis is commonly used in marketing to reveal consumer preferences for hypothetical products, and has become increasingly popular in political science and public policy [@KnudsenJohannesson:2019].
-Because we are interested in exploring the complexity behind the decision to donate, we apply conjoint methods to the study of nonprofits and philanthropy.
-
-In our experiment, we presented respondents with four randomly selected international nonprofit organizations with four randomly assigned features.^[See the appendix for a copy of the survey.] We included organizations that are associated with a range of contentious and noncontentious issues: Amnesty International, Greenpeace, Oxfam, and the International Committee of the Red Cross.
-Because of their strong name recognition, these organizations (and others like World Vision, the World Wildlife Fund, and Médecins Sans Frontières) are commonly used in experimental surveys on philanthropy [@FaulknerTruongRomaniuk:2015].
-
-```{r child = "output/tables/tbl-organization-attributes-full.md"}
-```
-
-The hypothetical organizations are based on random combinations of features, including one of four issue areas, the presence or absence of two organizational practices, one of three funding sources, and one of three relationships with host governments (see @tbl:organization-attributes-full; see also Q3.1 in the survey text in the appendix).
-Respondents saw twelve sets of four hypothetical organizations out of 288 (4 × 4 × 2 × 3 × 3) possible combinations, meaning no single respondent was offered every combination.
-While not every combination necessarily reflected reality—for instance, a respondent might have been asked to compare a fictional Amnesty International that focuses on environmental issues and that is funded by private donations with a Greenpeace that focuses on human rights and that is funded by government grants—it is not important that these features align with true organizational characteristics, since the goal of these repeated hypothetical questions is to identify which attributes are the most salient for donors.
-
-In June 2019, we recruited survey respondents through Centiment, a commercial provider of high-quality, non-probability opt-in survey panels.
-Centiment ensures panel quality by actively recruiting and paying representative samples of the U.S.
-population.
-To participate in the study, respondents were first screened based on their charitable activities.
-Those who indicated that they gave to charity once every few years or never were disqualified.
-After screening, we collected a sample of 1,016 respondents, which is sufficient for model estimation.[^sample-size]
-
-\newpage
-
-```{r child = "output/tables/tbl-sample-details.md"}
-```
-
-@tbl:sample-details provides a summary of the individual characteristics of survey respondents.
-Because we limited the sample to people who regularly make charitable contributions, most respondents have a favorable opinion of nonprofits and charities, with more than half reporting a 5 or greater level of trust in charities (on a 7-point scale).
-Moreover, nearly 90% indicated that it is important to trust charities.
-Additionally, the majority of respondents volunteer at least once a year, donate to charity at least once a year, and give between \$1–\$999 annually.
-Most rarely attend church, but feel that religion is important.
-Respondents are also civically engaged (three quarters voted in the last election) and follow national news closely (70% follow the news daily).
-Respondents are fairly balanced ideologically, with the majority reporting a 3, 4, or 5 on a 7-point scale of liberal–conservative political ideology.
-
-We analyze the effect of different combinations of organizational features and individual respondent attributes with a two-level hierarchical Bayesian multinomial logit model.[^model-details] Simply put, the first level of the model predicts individual donor preferences for various combinations of features (e.g.
-the combination of human rights issues, financial transparency, government funding, and government crackdown), while the second level predicts the heterogeneity of these fitted preferences as a function of individual donor characteristics.
-
-## Simulated philanthropy market
-
-In this paper, we look at which kinds of donors are more or less likely to consider an NGO's issue area, funding sources, and relationships with host governments when deciding to donate.
-Disentangling the effect of every individual level-characteristics measured in the survey on every combination of organizational characteristics presented in the conjoint experiment is unwieldy and near impossible.
-Given the organizational attributes presented in our experiment, and the possible individual characteristics that respondents could select, there are billions of possible combinations and iterations of organizational and individual attributes—many of which rarely occur in the actual population of potential donors.
-To more fully explore the relationships between different organizational- and individual-level attributes, we turn to simulation methods that allow us to examine the impact of multiple covariates simultaneously.
-To simplify the possible combinations of individual characteristics, we generate 64 distinct personas with attributes that vary along different dimensions of demographics, politics and public affairs experience, and social attitudes (see @tbl:persona-attributes).
-We also generate 24 simulated organizations that vary by issue area, relationship with host government, and source of funding (see @tbl:organization-attributes).
-
-```{r child = "output/tables/tbl-persona-attributes.md"}
-```
-
-```{r child = "output/tables/tbl-organization-attributes.md"}
-```
-
-We then combine these different scenarios of donor and organization attributes with the coefficients from a multinomial multilevel regression model to calculate the probability that each simulated persona has of giving to specific combinations of organizational attributes.
-Any individual characteristics that we do not explicitly vary in @tbl:persona-attributes are held at their means or modal values from the survey sample.
-@tbl:sim-output provides an example of the simulation output, showing how two different personas are predicted to allocate donations to organizations with various characteristics.
-The proportion of donations from each persona sums to 100%, as every persona is guaranteed to make a donation.
-
-```{r child = "output/tables/tbl-sim-output.md"}
-```
-
-Relying on simulation methods offers useful analytic benefits.
-Rather than interpret individual marginal effects from a regression model, we can explore multiple moving parts from the same model simultaneously to understand how individual characteristics interact with each other.
-This allows us to more fully explore our key research questions and see which kinds of donors are more or less likely to consider specific organizational attributes when deciding to donate, and which donor characteristics are associated with the propensity to donate.
-Importantly, each persona is an artificial construct.
-While some survey respondents might match an exact persona profile, others may not.
-This is acceptable in simulations as each combination of persona characteristics is plausible in the real world.
-
-# Results
-
-These simulated findings are more abstract than the results from an ordinary survey sample.
-But by using simulations, we can discover interesting patterns of donor preferences when faced with organizations focusing on a variety of issues, funding sources, and legal restrictions abroad.
-Our market simulation reveals which combination of organizational features each persona is most likely to express a preference for donating to.
-We examine the results of the simulation in three stages, looking at how personas with different (1) demographic characteristics, (2) public affairs knowledge and experience, and (3) levels of trust in government, charitable work, and associational life change their donation preferences across different organizational issue areas, relationships with host governments, and funding sources.
-
-## Demographics
-
-We begin by looking at differences in donation preferences across a range of basic demographic characteristics.
-The four panels of @fig:income show the average predicted market share for different organizational issue areas, funding sources, and relationships with host governments across different levels of persona income, with two different cutpoints for high and low income.
-
-![Average predicted donation market shares across all personas, segmented by individual persona income and organizational issue area, relationship with host government, and funding sources](output/figures/income-all.pdf){#fig:income}
-
-In general, personas respond better to human rights and refugee assistance organizations and environmental advocacy organizations across both levels of income, though wealthier personas show a slight preference towards human rights and refugee organizations.
-As we explore below, this is likely because income correlates with interest in public affairs and political activity—individuals who are wealthier arguably have more time and resources to follow the news and be continuously engaged in their communities and in other activist causes.
-There are no sizable differences in donation preferences by income across different forms of NGO funding—both levels of income tend to prefer organizations funded by government grants over small donors.
-
-An organization's relationship with its host government does influence market shares across levels of income, but the size of this difference depends on the magnitude of income.
-When splitting income based on the US median income (\$61,372), there is no difference between income levels.
-In general, personas prefer to donate to organizations with friendly relationships with their host governments and avoid those that are criticized or under crackdown.
-However, instead of looking at personas with below- and above-median incomes, we can simulate a subset of wealthier donors that earn at least \$100,000 annually.
-These personas are more likely to prefer donating to organizations that are criticized by their host governments.
-This falls in line with their preference for human rights organizations, which have more contentious missions and are more likely to receive government criticism.
-This support, however, appears to evaporate as civil society crackdown intensifies.
-High income personas are the least likely demographic to prefer donating to NGOs under crackdown.
-Their lower income counterparts, on the other hand, are generally unfazed by NGOs' relationships with government, maintaining the same average market share across all three types of host country relationships.
-Patterns in preferences for issue area and funding sources remain constant across both methods of categorizing income—crackdown only has an effect on very high income personas.
-Income thus appears to influence preferences particularly for NGOs facing criticism and crackdown abroad—wealthy donors are perhaps fair-weather friends that are more likely to pull their support when an organization's work becomes more difficult.
-
-While education and religiosity are both important drivers of individual philanthropy, neither are associated with any sizable differences in persona donation patterns.
-In general, both high school and college graduates *and* personas who rarely attend and who often attend religious services follow the same patterns in preferences shown in @fig:income: personas prefer human rights and refugee relief organizations, organizations funded by government grants, and organizations with friendly relaitonships with their host governments (see @fig:education and @fig:religiosity in the appendix.)
-
-## Public affairs knowledge, experience, and social trust
-
-We next look at how differences in public affairs knowledge, experience, and political ideology influence a persona's propensity to donate to an organization.
-We vary personas along two dimensions: (1) political ideology, with semi-liberal and semi-conservative political leanings (2 and 5 on a 7-point scale), and (2) knowledge and experience with public affairs and the news, with personas that either follow national and international news and that have travelled abroad or personas that do not follow the news or travel.
-
-We combine these dimensions with an additional set of donor characteristics that vary a persona's level of social trust.
-Personas with high levels of trust have high trust in political institutions and charities, think people should be more charitable, frequently volunteer, donate to charity once a month, have a history of political activism, and are members of an association.
-Personas with low levels of trust have the opposite characteristics: they do not trust political institutions or charities, rarely donate or volunteer, and are not members of associations.
-
-![Average predicted donation market shares across all personas, segmented by persona public affairs knowledge, political ideology, and social trust across different NGO issue areas](output/figures/issue-social.pdf){#fig:issue-social}
-
-@fig:issue-social and @fig:relationship-social show the results of the market simulation across these three dimensions of persona characteristics, varying public affairs knowledge, political ideology, and social trust.
-Personas respond differently to organizational issue areas.
-In @fig:issue-social, those who follow the news and travel abroad are more likely to prefer donating to human rights organizations than their less knowledgeable and less traveled counterparts.
-Personas who do not follow the news or travel show a greater preference for emergency response and refugee relief organization, similar to the income effects seen previously.
-There are no strong ideological effects across issue areas.
-Both conservative and liberal personas tend to follow similar patterns of preference across NGO issue.
-
-Social trust plays a substantial role in determining simulated market share, however.
-Those who trust social and charitable institutions are very likely to prefer donating to human rights organizations, regardless of their public affairs knowledge or political leanings.
-In all circumstances, those with high levels of trust have between a 7–10% chance of donating to a human rights organization, on average.
-Personas with low levels of trust, on the other hand, strongly avoid human rights organizations and prefer instead to donate to refugee and emergency response NGOs.
-The difference is substantial—a liberal persona with high levels of public affairs knowledge and experience will give to a human rights organization 10% of the time, on average if they have high levels of trust, but less than 3% of the time if they are less trusting.
-Trust in charities and institutions is a key factor in deciding to donate to more contentious human rights organizations.
-
-![Average predicted donation market shares across all personas, segmented by persona public affairs knowledge, political ideology, and social trust across different NGO–host government relationships](output/figures/relationship-social.pdf){#fig:relationship-social}
-
-@fig:relationship-social shows how personas respond to different NGO–host government relationships.
-Public affairs knowledge and experience has little effect on donor preferences, as the average market shares are roughly identical across the two columns of the figure.
-Persona preferences toward friendly, criticized, and legally suppressed organizations do not change much across different ideological views.
-The strongest, most overriding factor in determining donor preferences when considering an organization's relationship with its host country is social trust.
-
-Personas across both levels of social trust are most likely to donate to donate to organizations with friendly relationships with their host governments.
-However, those with higher trust are less likely to be deterred by poor host-country relationships, while those with low trust tend to not donate to organizations facing criticism or crackdown abroad.
-A friendly relationship with a host government is a manifestation of a belief that charities behave properly and exert a positive influence on society.
-Once an organization faces criticism or crackdown, however, support deteriorates rapidly among personas with low social trust, since such a crackdown could be perceived as a violation of the persona's trust in the charity—that is, the organization must be doing something wrong to deserve criticism.
-Personas with high levels of trust, on the other hand, seem to stick with legally besieged organizations and show them the benefit of the doubt.
-The global crackdown on NGOs thus sours NGOs' least trusting donors.
-
-## Concerns about inference and generalizability
-
-Given the nature of conjoint experiments, the randomly presented organizations may have influenced respondent choices.
-All four organizations are well known, and it is likely that participant responses reflect prior beliefs and news coverage about Amnesty, Oxfam, Greenpeace, and the Red Cross.
-For instance, in February 2018, news broke about sexual abuse and misconduct at Oxfam and several other well known organizations, including Amnesty International and Save the Children.
-This potentially strengthened a narrative that the nonprofit sector suffers from governance failures [@Phillips:2019].
-As such, it could be argued that respondents may be less likely to select Oxfam or Amnesty because of these scandals.
-
-However, we remain doubtful that the above news would impact our U.S.
-respondents' beliefs about these four organizations, as evidence about the effect of these scandals is mixed.
-Using data from Twitter, @ScurlockDolsakPrakash:2020 find that while Oxfam's reputation suffered for at least six months after the scandal (but has since recovered), other NGOs facing scandals, such as Save the Children, were able to recover more quickly.
-More broadly, the effect of scandals was mixed—while reputational damage can lead to decline in donations and grants, organizations can become more resilient and durable after a public relations recovery.
-
-Additionally, we remain skeptical that this scandal affected U.S.
-donors, given Oxfam is based in the UK and lack of awareness about INGOs is well-documented (CITE).
-Rather, lack of trust towards overseas NGOs, particularly aid and developmental agencies often results due to donors perceiving INGOs as having low personal relevance [@FaulknerTruongRomaniuk:2015].
-We failed to find any systematic evidence that the Oxfam scandal influenced perceptions of the nonprofit sector, likely because the story had far less news coverage in the U.S.
-Many individual donors have a preference to donate locally and they lack sufficient knowledge to make an informed decision about donating internationally.
-Overall, the literature suggests that for INGO fundraising, lack of awareness is a much larger issue than specific scandals or other knowledge of specific organizational characteristics that might reduce donor trust and confidence.
-
-The survey conducted among a random sample of U.S.
-residents with a prior history of charitable giving, also raises questions about generalizability external validity.
-Public expectations about the role of the public, private, and nonprofit sectors differ by country.
-In the U.S., for instance, NGOs often receive substantial funding through government grants, while those in the UK and France, such as Amnesty International and Médecins Sans Frontières, receive minimal government funding [@Stroup:2012].
-This could imply that donors in UK and France may have very different preferences when choosing to donate to government or privately-funded organizations.
-As such, more comparative research is needed to see if our results would also replicate cross-nationally.
-
-There is also notable country-based variation in general patterns of philanthropy.
-Though charitable giving is highest in the U.S, such donations are overwhelmingly directed at local and religious causes.
-This pattern does not hold for many European countries.
-In the UK, international aid is one of the largest targets of giving (26%).
-Other countries prioritize international philanthropy even more, such as Germany (74%), Belgium (61%), and Switzerland (43%) [@Milner:2017].
-Thus, if crackdown on INGOs abroad can elicit the effects found in this paper among U.S.
-respondents, the results provide much reason for optimism for pursuing individual philanthropy towards INGOs in Europe as well.
-However, more comparative research is required in order to confirm these trends.
-
-# Implications and conclusion
-
-The global crackdown on civil society and the consequent decline of official development assistance has made the role of philanthropy in sustaining INGOs clear.
-INGOs need access to multiple sources of funding, and the value of individual-level philanthropy is still relatively under-explored.
-While existing research has examined the impact of organizational-level factors on individual giving as well as giving to local causes, in this paper, we specifically look at the demographic traits of those who are likely to donate to INGOs facing hostile environments abroad.
-We find several important trends from our simulated market for philanthropy.
-On average, human rights organizations tend to attract personas who are wealthier, follow national and international news, and travel abroad.
-Donors who are less wealthy, follow the news less often, and do not travel are more attracted to organizations working on less contentious like emergency response and refugee relief.
-
-More importantly, we find that trust in political institutions and in charitable organizations matters substantially in shaping donor preferences.
-Personas with high levels of social and charitable trust prefer donating to human rights organizations that have friendly relationships with their host governments, while personas with low trust are drawn more to emergency response and refugee relief organizations with unfriendly relationships with their host governments.
-Personas with low social trust tend to be scared off by negative host-country relationships and strongly prefer to donate to organizations that are friendly with their host governments, while personas with high social trust are more willing to stick with legally besieged organizations.
-This could imply that donors that are the most trusting and involved could remain supportive when charities face government criticism and crackdown.
-
-The above results have important implications for NGOs as they navigate a shrinking civic space and consider the use of different frames to tailor their fundraising appeals to individual donors.
-Our survey finds that at least for some kinds of individuals, NGOs may benefit from publicizing when they are targets of government crackdown, including that information in their fundraising appeals.
-**TODO THIS IS DIFFERENT NOW** However, the bigger challenge may be addressing concerns of donors with low levels of trust.
-More broadly, studies from a range of countries show that levels of giving are lowest for refugee and asylum organizations, as well as for overseas and development organizations.
-Rather, donors giving to international causes tend to support international disaster relief and religious groups [@RobsonHart:2020].
-However, the former are precisely the organizations facing crackdown.
-More research is needed to answer how these organizations can appeal to broader array of potential foreign donors to increase levels of charitable-giving towards them.
-
-To be clear, research on international giving by individuals, especially in the era of closing civic space, is not meant to find answers that can act as substitutes for strategic policy responses, especially by official aid donors and foundations.
-However, many NGOs are under immediate threat, and individual-level philanthropy can help support these organizations.
-Existing initiatives such as the Lifeline Embattled CSO Assistance Funds provide models for channeling such funds.
-In the face of legal crackdowns abroad, individual donations are an important additional funding source for besieged NGOs.
-
-\newpage
-
-# Appendix: Survey experiment
-
-```{r child = "experiment.md"}
-```
-
-\newpage
-
-[^smalldonors]: Micro-donations refer to donations between $0.25–$10; small donors are individuals who donate up to $50 [@SaxtonWang:2014].
-
-[^NGOdef]: Broadly speaking, NGOs are any local, national, or international not-for-profit, voluntary organization.
-They can be domestic (i.e.
-an NGO that operates entirely in a single state), or international (INGOs).
-INGOs are composed of members from two or more countries and are organized to advance their members' international goals and provide services to citizens of other states through routine transactions with states, private actors, and international institutions [@Tarrow:2001, 12].
-
-[^exceptions]: For exceptions, see @Micklewright:2009 on the UK; @Rajan:2009 on Canada; @wiepking2010 on the Netherlands; @CasaleBaumann:2015 on the U.S.
-
-[^highnetworth]: High-net worth households have greater than \$200,000 in annual household income and/or have more than \$1,000,000 in assets, excluding primary residence.
-
-[^phildef]: We use philanthropy to connote voluntary giving by an individual or group to promote the common good.
-While it can include grants given by foundations and corporations to nonprofit organizations, our focus here is on individual giving.
-
-[^framing]: Framing is the process through which actors present information to influence perceptions or behavior.
-Previous research has shown that which frames are employed can have a significant effect on individuals' attitudes and behaviors [@BenfordSnow:2000; @ChongDruckman:2007].
-
-[^intlaffairs]: Giving USA defines the sector of international affairs to include any nonprofit organization working in international development, international relief services, disaster relief, international human rights, international peace and security, foreign policy research and analysis, and international exchange programs.
-
-[^sample-size]: A sample size of at least 500 respondents is typical when using conjoint data in a hierarchical Bayesian model.
-We doubled this amount because we are interested in analyzing subpopulations of respondents, which requires a larger sample.
-
-[^model-details]: See the appendix for technical details about the model and simulation.

### 2020-09-29 analysis/options.R

@@ -1,0 +1,52 @@
+# Universal pandoc options ------------------------------------------------
+
+pander::panderOptions("table.split.table", Inf)
+pander::panderOptions("table.split.cells", Inf)
+pander::panderOptions("missing", "")
+pander::panderOptions("big.mark", ",")
+pander::panderOptions("digits", 3)
+pander::panderOptions("round", 3)
+pander::panderOptions("table.alignment.default", "left")
+
+
+# Colors ------------------------------------------------------------------
+
+# Colors via http://clrs.cc/
+clrs <- list(
+  navy = "#001F3F",
+  blue = "#0074D9",
+  aqua = "#7FDBFF",
+  teal = "#39CCCC",
+  olive = "#3D9970",
+  green = "#2ECC40",
+  lime = "#01FF70",
+  yellow = "#FFDC00",
+  orange = "#FF851B",
+  red = "#FF4136",
+  fuchsia = "#F012BE",
+  purple = "#B10DC9",
+  maroon = "#85144B",
+  white = "#FFFFFF",
+  silver = "#DDDDDD",
+  gray = "#AAAAAA",
+  black = "#111111"
+)
+
+
+# Bayes options -----------------------------------------------------------
+
+CHAINS <- 4
+ITER <- 4000
+WARMUP <- 2000
+BAYES_SEED <- 1234
+options(mc.cores = parallel::detectCores())
+
+
+# Ordered factor modeling setup -------------------------------------------
+
+# By default, R uses polynomial contrasts for ordered factors in linear models
+# options("contrasts")
+# So make ordered factors use treatment contrasts instead
+options(contrasts = rep("contr.treatment", 2))
+# Or do it on a single variable:
+# contrasts(df$x) <- "contr.treatment"

### 2020-09-29 R/graphics.R
Make legend text a little smaller

@@ -35,7 +35,8 @@ theme_ngo <- function(base_size = 9, base_family = "IBM Plex Sans Condensed") {
           axis.title.x = element_text(margin = margin(t = 5)),
           axis.text = element_text(family = "IBM Plex Sans Condensed Light", face = "plain"),
           legend.key = element_blank(),
-          legend.text = element_text(size = rel(1), family = "IBM Plex Sans Condensed Light", face = "plain"),
+          legend.text = element_text(size = rel(0.75), 
+                                     family = "IBM Plex Sans Condensed Light", face = "plain"),
           legend.spacing = unit(0.1, "lines"),
           legend.box.margin = margin(t = -0.5, unit = "lines"),
           legend.margin = margin(t = 0),

### 2020-09-29 README.Rmd
Add README

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

Title <- "Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy"
Authors <- "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
Year <- "2020"
```

# `r Title`

[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Department of International Affairs • Christopher Newport University  
[Marc Dotson](https://marriottschool.byu.edu/directory/details?id=50683) • Marriott School of Business • Brigham Young University  
[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University

---

## Abstract

Over the past two decades, international non-governmental organizations (INGOs) have faced increasing legal scrutiny and repression abroad. As a result, official aid to INGOs in repressive countries has reduced. NGOs thus need access to a diverse array of funds and may need to increase fundraising from private donors. Which demographic and experiential factors influence the decision of individuals to donate to legally besieged NGOs? We investigate this question using a market simulation based on a nationally representative conjoint experiment conducted on individuals with a history of charitable giving. We find that trust in political institutions and charities is enormously influential in shaping donor preferences. Donor profiles with high levels of social trust are likely to donate to human rights INGOs with friendly relationships with host governments, and that support hold steady if INGOs face criticism or crackdown. In contrast, donor profiles with lower levels of social trust prefer to donate to organizations that do not face criticism or crackdown abroad. Our findings have practical implications for INGOs that aim to raise funds from the general public amid closing civic space.

---

This repository contains the data and code for our paper. Our pre-print is online here:

> `r Authors`. (`r Year`). *`r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <dx.doi.org>

## How to cite

Please cite this compendium as:

> `r Authors`. (`r format(Sys.Date(), "%Y")`). *Compendium of R code and data for `r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <dx.doi.org>

## How to download and replicate

You can either [download the compendium as a ZIP file](/archive/master.zip) or use GitHub to clone or fork the compendium repository (see the green "Clone or download" button at the top of the GitHub page).

TODO: More instructions

## Data

This project includes the following data files:

TODO: List of data

## Licenses

**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/))

**Code:** All code is dual-licensed under the [MIT License](LICENSE.md)

## Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

### 2020-09-30 README.Rmd
Update Suparna affiliation

@@
 
-[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Department of International Affairs • Christopher Newport University  
+[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Department of International Affairs • Lewis & Clark College  
 [Marc Dotson](https://marriottschool.byu.edu/directory/details?id=50683) • Marriott School of Business • Brigham Young University  

### 2020-09-30 manuscript/manuscript.Rmd
Add survey text
Suparna edits

@@
   email: aheiss@gsu.edu
-date: "September 24, 2020"
+date: "September 29, 2020"
 published: Working paper.
@@
 NGOs thus need access to a diverse array of funds and may need to increase fundraising from private donors.
+However, research on the determinants of philanthropy towards international causes—particularly towards organizations working in challenging environments—is still in its infancy.
 Which demographic and experiential factors influence the decision of individuals to donate to legally besieged NGOs?
-We investigate this question using a market simulation based on a nationally representative conjoint experiment conducted on individuals with a history of charitable giving.
+We investigate this question using a market simulation based on a nationally representative conjoint experiment conducted on individuals across the U.S.
+with a history of charitable giving.
 We find that trust in political institutions and charities is enormously influential in shaping donor preferences.
-Donor profiles with high levels of social trust are likely to donate to human rights INGOs with friendly relationships with host governments, and that support hold steady if INGOs face criticism or crackdown.
+Donor profiles with high levels of social trust are likely to donate to human rights INGOs with friendly relationships with host governments, and that support holds steady if INGOs face criticism or crackdown.
 In contrast, donor profiles with lower levels of social trust prefer to donate to organizations that do not face criticism or crackdown abroad.
-Our findings have practical implications for INGOs that aim to raise funds from the general public amid closing civic space.
+Our findings have practical implications for INGOs raising funds from individuals amid closing civic space.
 reference-section-title: References
@@
 As a result of these legal crackdowns, foreign aid channeled through NGOs has decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
-While this has negatively impacted funding flows from public organizations like United States Agency for International Development (USAID) and Organisation for Economic Cooperation and Development (OECD) philanthropy from private donors and foundations appears to not be as adversely affected [@McGill:2018].
+While this has negatively impacted funding flows from public organizations like the United States Agency for International Development (USAID) and the Organisation for Economic Cooperation and Development (OECD), philanthropy from private donors and foundations is not as adversely affected [@McGill:2018].
 Given this trend of closing civic space, INGOs need to maintain access to multiple sources of funding, including individual donors.
@@
 Total private philanthropy in the United States has grown substantially over time, reaching more than \$400 billion in 2018 (@fig:giving-aggregate).
-In 2018, private giving to NGOs working specifically in international affairs reached \$22.08 billion, and international affairs-focused organizations are one of only two categories of organizations that have continued experiencing substantial growth in giving [@givingusa:2019].[^intlaffairs] Most of this growth is driven by individuals making small-scale or micro-donations.[^smalldonors] In 2017, 70% of donations to international affairs NGOs came from individuals, rising to 86% in 2018.
+In 2018, private giving to NGOs working in international affairs reached \$22.08 billion, and international affairs-focused organizations are one of only two categories of organizations that have continued experiencing substantial growth in giving [@givingusa:2019].[^intlaffairs] Most of this growth is driven by individuals making small-scale or micro-donations.[^smalldonors] In 2017, 70% of donations to international affairs NGOs came from individuals, rising to 86% in 2018 [@givingusa:2019].
 But relying on individual donors means that NGOs must consider individual preferences when fundraising.
 Which individual donor characteristics and attributes are most salient for INGOs interested in maximizing philanthropy at a time when they are facing increasingly hostile environments abroad?
-What kinds of donors are more or less likely to consider an INGO's host country political environment when making the decision to donate?
+What kinds of donors consider an INGO's host country political environment when making the decision to donate?
 
@@
 
-Existing scholarship on the determinants of individual-level philanthropy to domestic causes is robust across a variety of contexts.
+There exists a robust scholarship on the determinants of individual-level philanthropy to domestic causes.
 But the dynamics of *international* giving to NGOs are under-examined in the literature on individual donor attributes and preferences.[^exceptions] Motivating individuals to donate to international causes is hard as the number of recipients are large and far removed from the donor [@CasaleBaumann:2015, 100].
@@
 We adapt methods used in marketing to generate dozens of distinct simulated personas that represent typical donor profiles, and we vary these personas along different dimensions of demographic, political, and social attributes.
-We find that specific individual characteristics help shape donor preferences for donating to international NGOs, and that an INGO's target issue area and its relationship with host government interact strongly with these characteristics.
+We find that specific individual characteristics help shape donor preferences for donating to INGOs, and that an organization's target issue area and its relationship with its host government interact strongly with these characteristics.
 Personas with high levels of trust in political and charitable institutions and who are actively engaged in charity and volunteerism prefer donating to human rights organizations that have friendly relationships with their host governments.
 In contrast, personas with low levels of social trust eschew both human rights organizations *and* any type of NGO with more contentious relationships with host governments, preferring instead to donate to NGOs with friendly host-country relationships and working on less contentious issues like emergency response and refugee relief.
-Personas with higher trust are more comfortable donating to legall besieged INGOs.
+Personas with higher trust are more comfortable donating to legally besieged INGOs.
 
-This study contributes to both to scholarship and practice in public policy, nonprofits, and philanthropy.
-Individual giving abroad can help bridge socioeconomic disparities worldwide, especially given the stark inequality in global distribution of income.
+This study contributes both to scholarship and practice in public policy, nonprofits, and philanthropy.
+Individual giving abroad can help bridge socioeconomic disparities worldwide, especially given the stark inequality in the global distribution of income.
 Knowledge of demographic traits and its impact on funding can help nonprofits craft more effective and targeted marketing strategies [@Rajan:2009, 414].
@@
 We then describe our survey experiment and simulation methods and explore the results.
-We conclude with a discussion of the implications our findings have on general INGO funding in the age of constrained civil society space.
+We conclude by discussing the implications of our findings for INGOs facing constrained space for civil society.
 
@@
 In countries with weak institutions and poor governance, where direct aid transfers to governments raise issues of misuse and bureaucratic inefficiency, donors specifically seek out NGOs for projects [@Dietrich2013].
+However, a restricted NGO environment merits examination of the diverse array of funds available to these organizations.
 
@@
 The advent of funding restrictions on NGOs globally and a subsequent decline in government and foundation funding has made the role and value of individual philanthropy in sustaining NGOs even clearer.[^phildef] NGOs need access to a diverse array of funds and individual donations to international affairs organizations have steadily increased over the past two decades.
-Moreover, in the United States donations from individuals have far outstripped foundation and corporate giving.
+Moreover, in the United States, donations from individuals have far outstripped foundation and corporate giving.
 In 2018, individual donations amounted to \$292 billion, compared to \$76 billion from foundations and \$20 billion from corporations [@NPT].
@@
 Donors have personality traits, preferences, and experiences that make them more or less likely to engage in philanthropy.
-Substantial research has looked at the determinants of donating to local—rather than international—causes, including four main attributes: social capital, the role of higher education, levels of religiosity, wealth, and national group attachment.
+Substantial research has looked at the determinants of donating to local—rather than international—causes, including four main attributes: social capital, the role of higher education, levels of religiosity, and national group attachment.
 
@@
 Higher education also influences charitable-giving decisions as it fosters prosocial motivations.
-Education brings people into social networks that entail a higher level of solicitations, which is vital in giving to international causes [@BekkersWiepking:2011].
+Education brings people into social networks that entail a higher level of solicitation, which is vital in giving to international causes [@BekkersWiepking:2011].
 Education also helps determine the kinds of causes that people donate to globally.
@@
 
-A number of NGOs facing crackdowns abroad also work on issues that may be seen as "contentious," including human rights, elections, corruption, advocacy, and media freedom—issues that may have a harder time attracting funds due to their non-essential nature when compared to causes like health, education, sanitation, and social services.
-However, additional education has been shown to increase abstract thinking [@wiepkingmaas, 1978], which may be necessary to donate to causes that do not have quantifiable goals.
-This is particularly important for organizations with more "contentious" causes as part of their missions [@Bush:2015].
+A number of NGOs facing crackdowns abroad also work on issues that may be seen as "contentious," including human rights, elections, corruption, advocacy, and media freedom—issues that may have a harder time attracting funds due to their non-essential nature when compared to causes like health, education, sanitation, and social services [@Bush:2015].
+However, additional education has been shown to increase abstract thinking [@wiepkingmaas, 1978], which may be necessary to donate to causes that do not have quantifiable goals, including politically sensitive or contentious causes mentioned above.
 
@@
 Finally, recent research looks at how a sense of ethnonationalism and national group attachment affects the decision to donate to domestic and international charities.
-Looking at UK respondents, @hartrobson2019 find that whereas nationalists have a preference for domestic charities, they are not necessarily averse to donating to international causes, whereas internationalists have a strong preference for donating to causes and groups working abroad.
+Looking at UK respondents, @hartrobson2019 find that whereas nationalists have a preference for domestic charities, they are not necessarily averse to donating to international causes, whereas internationalists have a strong preference for donating to groups working abroad.
 
@@
 Accordingly, we do not test specific hypotheses or theories.
-However, we do talk about causal effects given that we conduct an experiment that varies organizational characteristics in order to elicit opinions from respondents (i.e.
-specific attributes and features cause different aggregate effects).
-Instead, we structure our analysis around broader themes from the existing literature and investigate how donors' (1) demographic characteristics, (2) public affairs knowledge and experience, and (3) levels of trust in government, charitable work, and associational life change their donation preferences across different organizational issue areas, relationships with host governments, and funding sources.
+However, we do talk about causal effects given that we conduct an experiment that varies a number of factors in order to elicit opinions from respondents.
+Instead, we structure our analysis around broader themes from the existing literature and investigate how donors' (1) demographic characteristics, (2) public affairs knowledge and experience, and (3) levels of trust in government, charitable work, and associational life change individual donation preferences across different organizational issue areas, relationships with host governments, and funding sources.
 Our innovative experimental approach provides rich quantitative details of individual and organizational characteristics simultaneously and reveals unique insights into donor motivations that both confirm and expand previous research.
@@
 
-We use a conjoint experiment to simultaneously study the effects of organizational characteristics and individual attributes on individuals' preferences to donate to a nonprofit organization.
-Conjoint analysis allow us to elicit donor preferences without respondents explicitly stating their exact preferences.
+We use a conjoint experiment to study the simultaneous effects of organizational characteristics and individual attributes on individuals' preferences to donate to a nonprofit organization.
+Conjoint analysis allows us to elicit donor preferences without respondents explicitly stating their exact preferences.
 This kind of analysis is commonly used in marketing to reveal consumer preferences for hypothetical products, and has become increasingly popular in political science and public policy [@KnudsenJohannesson:2019].
@@
 Moreover, nearly 90% indicated that it is important to trust charities.
-Additionally, the majority of respondents volunteer at least once a year, donate to charity at least once a year, and give between \$1–\$999 annually.
+Additionally, the majority of respondents volunteer and donate to charity at least once a year and give between \$1–\$999 annually.
 Most rarely attend church, but feel that religion is important.
@@
 In this paper, we look at which kinds of donors are more or less likely to consider an NGO's issue area, funding sources, and relationships with host governments when deciding to donate.
-Disentangling the effect of every individual level-characteristics measured in the survey on every combination of organizational characteristics presented in the conjoint experiment is unwieldy and near impossible.
+Disentangling the effect of every individual level-characteristic measured in the survey on every combination of organizational characteristics presented in the conjoint experiment is unwieldy and near impossible.
 Given the organizational attributes presented in our experiment, and the possible individual characteristics that respondents could select, there are billions of possible combinations and iterations of organizational and individual attributes—many of which rarely occur in the actual population of potential donors.
@@
 
-In general, personas respond better to human rights and refugee assistance organizations and environmental advocacy organizations across both levels of income, though wealthier personas show a slight preference towards human rights and refugee organizations.
+In general, regardless of income, personas respond better to human rights and refugee assistance organizations and environmental advocacy organizations, followed by emergency response organizations—though wealthier personas show a slight preference towards human rights and refugee organizations.
 As we explore below, this is likely because income correlates with interest in public affairs and political activity—individuals who are wealthier arguably have more time and resources to follow the news and be continuously engaged in their communities and in other activist causes.
@@
 While education and religiosity are both important drivers of individual philanthropy, neither are associated with any sizable differences in persona donation patterns.
-In general, both high school and college graduates *and* personas who rarely attend and who often attend religious services follow the same patterns in preferences shown in @fig:income: personas prefer human rights and refugee relief organizations, organizations funded by government grants, and organizations with friendly relaitonships with their host governments (see @fig:education and @fig:religiosity in the appendix.)
+In general, both high school and college graduates *and* personas who both rarely and often attend religious services follow the same patterns in preferences shown in @fig:income: personas prefer human rights and refugee relief organizations, organizations funded by government grants, and organizations with friendly relationships with their host governments (see @fig:education and @fig:religiosity in the appendix.)
 
@@
 In @fig:issue-social, those who follow the news and travel abroad are more likely to prefer donating to human rights organizations than their less knowledgeable and less traveled counterparts.
-Personas who do not follow the news or travel show a greater preference for emergency response and refugee relief organization, similar to the income effects seen previously.
+Personas who do not follow the news or travel show a greater preference for emergency response and refugee relief organizations.
 There are no strong ideological effects across issue areas.
@@
 
-Personas across both levels of social trust are most likely to donate to donate to organizations with friendly relationships with their host governments.
+Personas across both levels of social trust are most likely to donate to organizations with friendly relationships with their host governments.
 However, those with higher trust are less likely to be deterred by poor host-country relationships, while those with low trust tend to not donate to organizations facing criticism or crackdown abroad.
-A friendly relationship with a host government is a manifestation of a belief that charities behave properly and exert a positive influence on society.
+A friendly relationship with a host government may be a manifestation of a belief that charities behave properly and exert a positive influence on society.
 Once an organization faces criticism or crackdown, however, support deteriorates rapidly among personas with low social trust, since such a crackdown could be perceived as a violation of the persona's trust in the charity—that is, the organization must be doing something wrong to deserve criticism.
 Personas with high levels of trust, on the other hand, seem to stick with legally besieged organizations and show them the benefit of the doubt.
-The global crackdown on NGOs thus sours NGOs' least trusting donors.
+The global crackdown on NGOs thus sours NGOs' least trusting individual donors.
 
@@
 Given the nature of conjoint experiments, the randomly presented organizations may have influenced respondent choices.
-All four organizations are well known, and it is likely that participant responses reflect prior beliefs and news coverage about Amnesty, Oxfam, Greenpeace, and the Red Cross.
-For instance, in February 2018, news broke about sexual abuse and misconduct at Oxfam and several other well known organizations, including Amnesty International and Save the Children.
+All four organizations are well-known, and it is likely that participant responses reflect prior beliefs and news coverage about Amnesty, Oxfam, Greenpeace, and the Red Cross.
+For instance, in February 2018, news broke out about sexual abuse and misconduct at Oxfam and several other prominent organizations, including Amnesty International and Save the Children.
 This potentially strengthened a narrative that the nonprofit sector suffers from governance failures [@Phillips:2019].
-As such, it could be argued that respondents may be less likely to select Oxfam or Amnesty because of these scandals.
+As such, it could be argued that respondents may be less likely to donate to Oxfam or Amnesty because of these scandals.
 
@@
 Using data from Twitter, @ScurlockDolsakPrakash:2020 find that while Oxfam's reputation suffered for at least six months after the scandal (but has since recovered), other NGOs facing scandals, such as Save the Children, were able to recover more quickly.
-More broadly, the effect of scandals was mixed—while reputational damage can lead to decline in donations and grants, organizations can become more resilient and durable after a public relations recovery.
+More broadly, the effect of scandals was mixed—while reputational damage can lead to a decline in donations and grants, organizations can become more resilient and durable after a public relations recovery.
 
 Additionally, we remain skeptical that this scandal affected U.S.
-donors, given Oxfam is based in the UK and lack of awareness about INGOs is well-documented (CITE).
+donors, given Oxfam is based in the UK, and "media narratives are often not as unsupportive as often assumed" [@BanksSchulpenBrockington:2020, 703].
 Rather, lack of trust towards overseas NGOs, particularly aid and developmental agencies often results due to donors perceiving INGOs as having low personal relevance [@FaulknerTruongRomaniuk:2015].
-We failed to find any systematic evidence that the Oxfam scandal influenced perceptions of the nonprofit sector, likely because the story had far less news coverage in the U.S.
+We failed to find any systematic evidence that the Oxfam scandal influenced perceptions of the nonprofit sector in the U.S., likely because the story had far less news coverage in the U.S.
 Many individual donors have a preference to donate locally and they lack sufficient knowledge to make an informed decision about donating internationally.
@@
 The survey conducted among a random sample of U.S.
-residents with a prior history of charitable giving, also raises questions about generalizability external validity.
-Public expectations about the role of the public, private, and nonprofit sectors differ by country.
+residents with a prior history of charitable giving also raises questions about generalizability and external validity.
+Public expectations about the role of government and private funding of the nonprofit sectors differ by country.
 In the U.S., for instance, NGOs often receive substantial funding through government grants, while those in the UK and France, such as Amnesty International and Médecins Sans Frontières, receive minimal government funding [@Stroup:2012].
 This could imply that donors in UK and France may have very different preferences when choosing to donate to government or privately-funded organizations.
-As such, more comparative research is needed to see if our results would also replicate cross-nationally.
+More comparative research is needed to see if our results would also replicate cross-nationally.
 
@@
 respondents, the results provide much reason for optimism for pursuing individual philanthropy towards INGOs in Europe as well.
-However, more comparative research is required in order to confirm these trends.
+However, more comparative research is required to confirm these trends.
 
@@
 Personas with high levels of social and charitable trust prefer donating to human rights organizations that have friendly relationships with their host governments, while personas with low trust are drawn more to emergency response and refugee relief organizations with unfriendly relationships with their host governments.
-Personas with low social trust tend to be scared off by negative host-country relationships and strongly prefer to donate to organizations that are friendly with their host governments, while personas with high social trust are more willing to stick with legally besieged organizations.
+Personas with low social trust tend to be wary of negative host-country relationships and strongly prefer to donate to organizations that are friendly with their host governments, while personas with high social trust are more willing to stick with legally besieged organizations.
 This could imply that donors that are the most trusting and involved could remain supportive when charities face government criticism and crackdown.
+The global crackdown on NGOs may also possibly sour NGOs' least trusting individual donors.
 
@@
 Our survey finds that at least for some kinds of individuals, NGOs may benefit from publicizing when they are targets of government crackdown, including that information in their fundraising appeals.
-**TODO THIS IS DIFFERENT NOW** However, the bigger challenge may be addressing concerns of donors with low levels of trust.
+However, the larger challenge may be addressing concerns of donors with low levels of trust who are the least likely to donate organizations facing criticism and crackdown abroad.
 More broadly, studies from a range of countries show that levels of giving are lowest for refugee and asylum organizations, as well as for overseas and development organizations.
@@
 In the face of legal crackdowns abroad, individual donations are an important additional funding source for besieged NGOs.
-
-\newpage
-
-# Appendix: Survey experiment
-
-```{r child = "experiment.md"}
-```
 
@@
 
-[^model-details]: See the appendix for technical details about the model and simulation.
+[^model-details]: Specifically,
+
+    $$
+    \begin{aligned}
+    \beta &\sim \operatorname{Multivariate} \mathcal{N}(Z \Gamma, \xi) \\
+    y &\sim \operatorname{Multinomial\ logit}(X \beta, \varepsilon)
+    \end{aligned}
+    $$
+
+    where $y$ = which alternative the respondent chooses to donate to, $X$ = design matrix of attribute levels (i.e.
+organizations, issue areas, organizational practices, funding sources, and government relations), $\beta$ = latent individual preferences for the attribute levels, $Z$ = matrix of individual-level covariates (i.e.
+demographics, political knowledge, attitudes towards charity, etc.), $\Gamma$ = matrix of coefficients mapping individual-level covariates onto the latent individual-level preferences, and $\varepsilon$ and $\xi$ = errors.

### 2020-09-30 manuscript/manuscript.Rmd
Add actual link to github

@@
 published: Working paper.
-git-repo: https://example.com
+git-repo: https://github.com/andrewheiss/who-cares-about-crackdown
 abstract: >-

### 2020-10-01 analysis/03_analysis.Rmd
Consistent figure colors and dimensions

@@
 library(tidyverse)
-library(fastDummies)
 library(scales)
@@
 library(here)
+
+# Wrap factor levels
+# via Hadley: https://github.com/tidyverse/stringr/issues/107#issuecomment-233723948
+str_wrap_factor <- function(x, ...) {
+  levels(x) <- str_wrap(levels(x), ...)
+  x
+}
 
@@
 
-```{r plot-total-giving, fig.width=4, fig.height=2.4}
+```{r plot-total-giving, fig.width=4, fig.height=2.4, out.width="80%"}
 ggplot(giving_aggregate, aes(x = Year, y = `Total donations`)) +
-  geom_line(size = 1, color = clrs$maroon) +
+  geom_line(size = 1, color = clrs_ngo$vi_blue_dark) +
   scale_x_continuous(breaks = seq(1980, 2015, 5)) +
@@
   labs(x = NULL, y = "Billions of dollars") + 
-  theme_ngo(9)
+  theme_ngo()
 
@@
 
-```{r plot-per-capita-giving, fig.width=6, fig.height=3.6}
+```{r plot-per-capita-giving, fig.width=4, fig.height=2.4, out.width="80%"}
 ggplot(giving_per_capita, aes(x = Year, y = `Average giving`)) +
-  geom_line(size = 1, color = clrs$green) +
+  geom_line(size = 1, color = clrs_ngo$vi_blue_dark) +
   scale_x_continuous(breaks = seq(2000, 2014, 2)) +
@@
   theme_ngo()
-
-ggsave(here("analysis", "output", "figures", "giving_per_capita.pdf"), 
-       width = 6, height = 3.6, units = "in", device = cairo_pdf)
-ggsave(here("analysis", "output", "figures", "giving_per_capita.png"), 
-       width = 6, height = 3.6, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
-```{r income-issue-funding-relationship, fig.width=6.5, fig.height=4.75}
+```{r income-issue-funding-relationship, fig.width=6, fig.height=4.5, out.width="100%"}
 plot_income_issue <- sim_clean %>% 
@@
   mutate(facet = "Issue area") %>% 
-  ggplot(aes(y = fct_rev(org_issue), x = avg_share, color = fct_rev(persona_income))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)),
+             x = avg_share, color = fct_rev(persona_income))) +
+  geom_pointrangeh(size = 0.75, fatten = 1.5,
+                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002)),
                      breaks = seq(0, 0.06, 0.02)) +
-  scale_color_manual(values = c(clrs$green, clrs$blue), guide = FALSE) +
+  scale_color_manual(values = c(clrs_ngo$vi_turquoise, clrs_ngo$vi_purple), guide = FALSE) +
   coord_cartesian(xlim = c(0, 0.06)) +
@@
   mutate(facet = "Funding sources") %>% 
-  ggplot(aes(y = str_wrap(fct_rev(org_funding), 10), 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_funding, 10)), 
              x = avg_share, color = fct_rev(persona_income))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  geom_pointrangeh(size = 0.75, fatten = 1.5,
+                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
   coord_cartesian(xlim = c(0, 0.06)) +
-  scale_color_manual(values = c(clrs$green, clrs$blue), guide = FALSE) +
+  scale_color_manual(values = c(clrs_ngo$vi_turquoise, clrs_ngo$vi_purple), guide = FALSE) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
   mutate(facet = "Relationship with host government") %>% 
-  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = fct_rev(persona_income))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) +
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
+             x = avg_share, color = fct_rev(persona_income))) +
+  geom_pointrangeh(size = 0.75, fatten = 1.5, 
+                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) +
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.003))) +
   coord_cartesian(xlim = c(0, 0.1)) +
-  scale_color_manual(values = c(clrs$green, clrs$blue), 
-                     guide = guide_legend(reverse = TRUE, nrow = 1)) +
+  scale_color_manual(values = c(clrs_ngo$vi_turquoise, clrs_ngo$vi_purple), 
+                     guide = guide_legend(reverse = TRUE, nrow = 1,
+                                          override.aes = list(size = 0.25))) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
   mutate(facet = "Relationship with host government") %>% 
-  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = fct_rev(persona_income))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
+             x = avg_share, color = fct_rev(persona_income))) +
+  geom_pointrangeh(size = 0.75, fatten = 1.5,
+                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
   coord_cartesian(xlim = c(0, 0.1)) +
-  scale_color_manual(values = c(colorspace::darken(clrs$green, 0.4), 
-                                colorspace::darken(clrs$blue, 0.6)), 
-                     guide = guide_legend(reverse = TRUE, nrow = 1)) +
+  scale_color_manual(values = c(clrs_ngo$pl_yellow, clrs_ngo$pl_purple_light), 
+                     guide = guide_legend(reverse = TRUE, nrow = 1,
+                                          override.aes = list(size = 0.25))) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
 
-plot_income <- plot_income_issue + plot_income_funding + 
-  plot_income_relationship + plot_income_relationship_extreme +
-  plot_layout(nrow = 2)
+plot_income <- ((plot_income_issue + labs(x = NULL)) + 
+  (plot_income_funding + labs(x = NULL))) / 
+  (plot_income_relationship + plot_income_relationship_extreme)
 
@@
 ggsave(plot_income, filename = here("analysis", "output", "figures", "income-all.pdf"),
-       width = 6.5, height = 4.75, units = "in", device = cairo_pdf)
+       width = 6, height = 4.5, units = "in", device = cairo_pdf)
 ggsave(plot_income, filename = here("analysis", "output", "figures", "income-all.png"),
-       width = 6.5, height = 4.75, units = "in", type = "cairo", dpi = 300)
+       width = 6, height = 4.5, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
-```{r edu-issue-funding-relationship, fig.width=5, fig.height=4.25}
+```{r edu-issue-funding-relationship, fig.width=8, fig.height=2.75, out.width="100%"}
 plot_education_issue <- sim_clean %>% 
@@
   mutate(facet = "Issue area") %>% 
-  ggplot(aes(y = fct_rev(org_issue), x = avg_share, color = fct_rev(persona_education))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)), 
+             x = avg_share, color = fct_rev(persona_education))) +
+  geom_pointrangeh(size = 0.75, fatten = 1.5,
+                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
   coord_cartesian(xlim = c(0, 0.06)) +
-  scale_color_manual(values = c(clrs$orange, clrs$purple), guide = FALSE) +
+  scale_color_manual(values = c(clrs_ngo$pl_purple_dark, clrs_ngo$pl_orange), guide = FALSE) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
   mutate(facet = "Funding sources") %>% 
-  ggplot(aes(y = str_wrap(fct_rev(org_funding), 10), 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_funding, 10)), 
              x = avg_share, color = fct_rev(persona_education))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  geom_pointrangeh(size = 0.75, fatten = 1.5,
+                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
   coord_cartesian(xlim = c(0, 0.06)) +
-  scale_color_manual(values = c(clrs$orange, clrs$purple), guide = FALSE) +
+  scale_color_manual(values = c(clrs_ngo$pl_purple_dark, clrs_ngo$pl_orange), guide = FALSE) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
   mutate(facet = "Relationship with host government") %>% 
-  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = fct_rev(persona_education))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)),
+             x = avg_share, color = fct_rev(persona_education))) +
+  geom_pointrangeh(size = 0.75, fatten = 1.5,
+                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
   coord_cartesian(xlim = c(0, 0.1)) +
-  scale_color_manual(values = c(clrs$orange, clrs$purple), 
-                     guide = guide_legend(reverse = TRUE, ncol = 1)) +
+  scale_color_manual(values = c(clrs_ngo$pl_purple_dark, clrs_ngo$pl_orange), 
+                     guide = guide_legend(reverse = TRUE, ncol = 1,
+                                          override.aes = list(size = 0.25)),
+                     labels = label_wrap(15)) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
   plot_education_relationship + guide_area() +
-  plot_layout(guides = "collect", ncol = 2)
+  plot_layout(guides = "collect", ncol = 4)
 plot_education
-
-ggsave(plot_education, filename = here("analysis", "output", "figures", "education-all.pdf"),
-       width = 5, height = 4.25, units = "in", device = cairo_pdf)
-ggsave(plot_education, filename = here("analysis", "output", "figures", "education-all.png"),
-       width = 5, height = 4.25, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
-```{r religion-issue-funding-relationship, fig.width=5, fig.height=4.25}
+```{r religion-issue-funding-relationship, fig.width=8, fig.height=2.75, out.width="100%"}
 plot_religion_issue <- sim_clean %>% 
@@
   mutate(facet = "Issue area") %>% 
-  ggplot(aes(y = fct_rev(org_issue), x = avg_share, color = fct_rev(persona_religion))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)), 
+             x = avg_share, color = fct_rev(persona_religion))) +
+  geom_pointrangeh(size = 0.75, fatten = 1.5, 
+                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
   coord_cartesian(xlim = c(0, 0.06)) +
-  scale_color_manual(values = c(clrs$red, clrs$navy), guide = FALSE) +
+  scale_color_manual(values = c(clrs_ngo$vi_blue_light, clrs_ngo$vi_yellow), guide = FALSE) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
   mutate(facet = "Funding sources") %>% 
-  ggplot(aes(y = str_wrap(fct_rev(org_funding), 10), 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_funding, 10)), 
              x = avg_share, color = fct_rev(persona_religion))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  geom_pointrangeh(size = 0.75, fatten = 1.5,
+                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
   coord_cartesian(xlim = c(0, 0.06)) +
-  scale_color_manual(values = c(clrs$red, clrs$navy), guide = FALSE) +
+  scale_color_manual(values = c(clrs_ngo$vi_blue_light, clrs_ngo$vi_yellow), guide = FALSE) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
   mutate(facet = "Relationship with host government") %>% 
-  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = fct_rev(persona_religion))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
+             x = avg_share, color = fct_rev(persona_religion))) +
+  geom_pointrangeh(size = 0.75, fatten = 1.5,
+                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
   coord_cartesian(xlim = c(0, 0.1)) +
-  scale_color_manual(values = c(clrs$red, clrs$navy), 
-                     guide = guide_legend(reverse = TRUE, ncol = 1)) +
+  scale_color_manual(values = c(clrs_ngo$vi_blue_light, clrs_ngo$vi_yellow), 
+                     guide = guide_legend(reverse = TRUE, ncol = 1,
+                                          override.aes = list(size = 0.25)),
+                     labels = label_wrap(20)) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
   plot_religion_relationship + guide_area() +
-  plot_layout(guides = "collect", ncol = 2)
+  plot_layout(guides = "collect", ncol = 4)
 plot_religion
+```
 
-ggsave(plot_religion, filename = here("analysis", "output", "figures", "religion-all.pdf"),
-       width = 5, height = 4.25, units = "in", device = cairo_pdf)
-ggsave(plot_religion, filename = here("analysis", "output", "figures", "religion-all.png"),
-       width = 5, height = 4.25, units = "in", type = "cairo", dpi = 300)
+## Education and religion across issue area, funding, and relationship
+
+```{r education-religion-issue-funding-relationship, fig.width=6, fig.height=4.5, out.width="100%"}
+plot_education_religion <- (plot_education_issue + labs(x = NULL)) + 
+  (plot_education_funding + labs(x = NULL)) + 
+  (plot_education_relationship + labs(x = NULL)) + 
+  guide_area() +
+  plot_religion_issue + 
+  plot_religion_funding + 
+  plot_religion_relationship +
+  plot_layout(guides = "collect", ncol = 4)
+
+plot_education_religion
+ggsave(plot_education_religion, 
+       filename = here("analysis", "output", "figures", "education-religion-all.pdf"),
+       width = 6.5, height = 4.5, units = "in", device = cairo_pdf)
+ggsave(plot_education_religion, 
+       filename = here("analysis", "output", "figures", "education-religion-all.png"),
+       width = 6.5, height = 4.5, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
-```{r trust-issues}
+```{r trust-issues, fig.width=6, fig.height=4, out.width="100%"}
 plot_issue_social <- sim_clean %>% 
@@
   summarize(avg_share = mean(share)) %>% 
-  ggplot(aes(y = fct_rev(org_issue), x = avg_share, color = persona_trust)) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
-  scale_x_continuous(labels = percent) +
-  scale_color_manual(values = c(clrs$orange, clrs$navy), guide = guide_legend(reverse = TRUE)) +
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)), 
+             x = avg_share, color = persona_trust)) +
+  geom_pointrangeh(size = 0.75, fatten = 1.5, 
+                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+  scale_color_manual(values = c(clrs_ngo$pl_blue, clrs_ngo$pl_pink), 
+                     guide = guide_legend(reverse = TRUE,
+                                          override.aes = list(size = 0.25))) +
   labs(x = "Average share of donations", y = NULL, color = NULL) +
@@
 ggsave(plot_issue_social, filename = here("analysis", "output", "figures", "issue-social.pdf"),
-       width = 6, height = 4.2, units = "in", device = cairo_pdf)
+       width = 6, height = 4, units = "in", device = cairo_pdf)
 ggsave(plot_issue_social, filename = here("analysis", "output", "figures", "issue-social.png"),
-       width = 6, height = 4.2, units = "in", type = "cairo", dpi = 300)
+       width = 6, height = 4, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
-```{r trust-relationship}
+```{r trust-relationship, fig.width=6, fig.height=4, out.width="100%"}
 plot_relationship_social <- sim_clean %>% 
@@
   summarize(avg_share = mean(share)) %>% 
-  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = persona_trust)) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
-  scale_x_continuous(labels = percent) +
-  scale_color_manual(values = c(clrs$orange, clrs$navy), guide = guide_legend(reverse = TRUE)) +
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
+             x = avg_share, color = persona_trust)) +
+  geom_pointrangeh(size = 0.75, fatten = 1.5,
+                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+  scale_color_manual(values = c(clrs_ngo$pl_blue, clrs_ngo$pl_pink), 
+                     guide = guide_legend(reverse = TRUE,
+                                          override.aes = list(size = 0.25))) +
   labs(x = "Average share of donations", y = NULL, color = NULL) +
@@
 ggsave(plot_relationship_social, filename = here("analysis", "output", "figures", "relationship-social.pdf"),
-       width = 6, height = 4.2, units = "in", device = cairo_pdf)
+       width = 6, height = 4, units = "in", device = cairo_pdf)
 ggsave(plot_relationship_social, filename = here("analysis", "output", "figures", "relationship-social.png"),
-       width = 6, height = 4.2, units = "in", type = "cairo", dpi = 300)
+       width = 6, height = 4, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
-```{r trust-funding}
+```{r trust-funding, fig.width=6, fig.height=4, out.width="100%"}
 plot_funding_social <- sim_clean %>% 
@@
   summarize(avg_share = mean(share)) %>% 
-  ggplot(aes(y = str_wrap(fct_rev(org_funding), 20), x = avg_share, color = persona_trust)) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
-  scale_x_continuous(labels = percent) +
-  scale_color_manual(values = c(clrs$orange, clrs$navy), guide = guide_legend(reverse = TRUE)) +
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_funding, 15)), 
+             x = avg_share, color = persona_trust)) +
+  geom_pointrangeh(size = 0.75, fatten = 1.5,
+                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+  scale_color_manual(values = c(clrs_ngo$pl_blue, clrs_ngo$pl_pink), 
+                     guide = guide_legend(reverse = TRUE,
+                                          override.aes = list(size = 0.25))) +
   labs(x = "Average share of donations", y = NULL, color = NULL) +
@@
 ggsave(plot_funding_social, filename = here("analysis", "output", "figures", "funding-social.pdf"),
-       width = 6, height = 4.2, units = "in", device = cairo_pdf)
+       width = 6, height = 4, units = "in", device = cairo_pdf)
 ggsave(plot_funding_social, filename = here("analysis", "output", "figures", "funding-social.png"),
-       width = 6, height = 4.2, units = "in", type = "cairo", dpi = 300)
+       width = 6, height = 4, units = "in", type = "cairo", dpi = 300)
 ```

### 2020-10-01 R/graphics.R

@@ -31,7 +31,8 @@ theme_ngo <- function(base_size = 9, base_family = "IBM Plex Sans Condensed") {
                                     family = "IBM Plex Sans Condensed", face = "bold"),
           strip.background = element_rect(fill = "#ffffff", colour = NA),
           axis.ticks = element_blank(),
-          axis.title = element_text(family = "IBM Plex Sans Condensed SemiBold", face = "plain"),
+          axis.title = element_text(family = "IBM Plex Sans Condensed SemiBold", face = "plain", 
+                                    size = rel(0.8)),
           axis.title.x = element_text(margin = margin(t = 5)),
           axis.text = element_text(family = "IBM Plex Sans Condensed Light", face = "plain"),
           legend.key = element_blank(),
@@ -46,24 +47,39 @@ theme_ngo <- function(base_size = 9, base_family = "IBM Plex Sans Condensed") {
 }
 
 
-# Conversion and formatting help ------------------------------------------
+# Colors ------------------------------------------------------------------
 
-#' Convert mms to pts
-#'
-#' Convert units specified in millimeters to typographic points. This is especially helpful when working with ggplot geoms that use size parameters
-#'
-#' @param x a numeric value (in millimeters)
-#'
-#' @return A numeric value (in points)
-#' @export
-#'
-#' @examples
-#' library(ggplot2)
-#'
-#' ggplot(mtcars, aes(x = mpg, y = wt)) +
-#'   geom_point() +
-#'   annotate(geom = "text", x = 20, y = 4,
-#'            label = "Here's a label", size = pts(11))
-pts <- function(x) {
-  as.numeric(grid::convertUnit(grid::unit(x, "pt"), "mm"))
-}
+# colors_plasma <- viridisLite::plasma(6, begin = 0, end = 0.85)
+# colors_plasma %>% scales::show_col()
+# 
+# colors_viridis <- viridisLite::viridis(6, begin = 0, end = 0.97)
+# colors_viridis %>% scales::show_col()
+
+clrs_ngo <- as.list(c(viridisLite::plasma(6, begin = 0, end = 0.85), 
+                      viridisLite::viridis(6, begin = 0, end = 0.94)))
+# unlist(clrs_ngo) %>% scales::show_col()
[…]

### 2020-10-01 analysis/options.R

@@ -7,46 +7,3 @@ pander::panderOptions("big.mark", ",")
 pander::panderOptions("digits", 3)
 pander::panderOptions("round", 3)
 pander::panderOptions("table.alignment.default", "left")
-
-
-# Colors ------------------------------------------------------------------
-
-# Colors via http://clrs.cc/
-clrs <- list(
-  navy = "#001F3F",
-  blue = "#0074D9",
-  aqua = "#7FDBFF",
-  teal = "#39CCCC",
-  olive = "#3D9970",
-  green = "#2ECC40",
-  lime = "#01FF70",
-  yellow = "#FFDC00",
-  orange = "#FF851B",
-  red = "#FF4136",
-  fuchsia = "#F012BE",
-  purple = "#B10DC9",
-  maroon = "#85144B",
-  white = "#FFFFFF",
-  silver = "#DDDDDD",
-  gray = "#AAAAAA",
-  black = "#111111"
-)
-
-
-# Bayes options -----------------------------------------------------------
-
-CHAINS <- 4
-ITER <- 4000
-WARMUP <- 2000
-BAYES_SEED <- 1234
-options(mc.cores = parallel::detectCores())
-
-
-# Ordered factor modeling setup -------------------------------------------
-
-# By default, R uses polynomial contrasts for ordered factors in linear models
-# options("contrasts")
-# So make ordered factors use treatment contrasts instead
-options(contrasts = rep("contr.treatment", 2))
-# Or do it on a single variable:
-# contrasts(df$x) <- "contr.treatment"

### 2020-10-01 manuscript/manuscript.Rmd
Move lonely footnote with the others

@@
 
-In our experiment, we presented respondents with four randomly selected international nonprofit organizations with four randomly assigned features.^[See the appendix for a copy of the survey.] We included organizations that are associated with a range of contentious and noncontentious issues: Amnesty International, Greenpeace, Oxfam, and the International Committee of the Red Cross.
+In our experiment, we presented respondents with four randomly selected international nonprofit organizations with four randomly assigned features.[^appendix-survey] We included organizations that are associated with a range of contentious and noncontentious issues: Amnesty International, Greenpeace, Oxfam, and the International Committee of the Red Cross.
 Because of their strong name recognition, these organizations (and others like World Vision, the World Wildlife Fund, and Médecins Sans Frontières) are commonly used in experimental surveys on philanthropy [@FaulknerTruongRomaniuk:2015].
@@
 An organization's relationship with its host government does influence market shares across levels of income, but the size of this difference depends on the magnitude of income.
-When splitting income based on the US median income (\$61,372), there is no difference between income levels.
+When splitting income based on the 2017 US median income (\$61,372), there is no difference between income levels.
 In general, personas prefer to donate to organizations with friendly relationships with their host governments and avoid those that are criticized or under crackdown.
@@
 
+[^appendix-survey]: See the appendix for the full text of the survey.
+
 [^model-details]: Specifically,

### 2020-10-01 manuscript/manuscript.Rmd
Expand findings section since we have space

@@
   email: aheiss@gsu.edu
-date: "September 29, 2020"
+date: "September 30, 2020"
 published: Working paper.
@@
 The four panels of @fig:income show the average predicted market share for different organizational issue areas, funding sources, and relationships with host governments across different levels of persona income, with two different cutpoints for high and low income.
+To ease with modeling and interpretation, we split high and low income personas based on the 2017 U.S.
+median income (\$61,372), showing personas with incomes higher and lower than the national median.
+Because there is wide variation in donor incomes in the U.S., we also show the results from a simulation model with a more extreme split in income, holding annual persona income at \$50,000 and \$100,000+.
+The difference in the division of high and low income makes no difference in the market shares across issue areas and funding sources, but there are substantial income-based differences across different relationships with host governments.
 
-![Average predicted donation market shares across all personas, segmented by individual persona income and organizational issue area, relationship with host government, and funding sources](output/figures/income-all.pdf){#fig:income}
+![Average predicted donation market shares across all personas, segmented by persona income across organizational issue area, relationship with host government, and funding sources](output/figures/income-all.pdf){#fig:income}
 
-In general, regardless of income, personas respond better to human rights and refugee assistance organizations and environmental advocacy organizations, followed by emergency response organizations—though wealthier personas show a slight preference towards human rights and refugee organizations.
-As we explore below, this is likely because income correlates with interest in public affairs and political activity—individuals who are wealthier arguably have more time and resources to follow the news and be continuously engaged in their communities and in other activist causes.
+In general, regardless of income, personas respond better to human rights and refugee assistance organizations, followed closely by emergency response organizations.
+Environmental NGOs have the lowest market share across both levels of incomes.
+There are negligible differences across income levels—wealthier personas show a slight preference towards human rights and refugee organizations.
+As we explore below, this is possibly because income correlates with interest in public affairs and political activity—individuals who are wealthier arguably have more time and resources to follow the news and be continuously engaged in their communities and in other activist causes.
 There are no sizable differences in donation preferences by income across different forms of NGO funding—both levels of income tend to prefer organizations funded by government grants over small donors.
@@
 An organization's relationship with its host government does influence market shares across levels of income, but the size of this difference depends on the magnitude of income.
-When splitting income based on the 2017 US median income (\$61,372), there is no difference between income levels.
+When splitting income based on income, there is no difference between income levels.
 In general, personas prefer to donate to organizations with friendly relationships with their host governments and avoid those that are criticized or under crackdown.
-However, instead of looking at personas with below- and above-median incomes, we can simulate a subset of wealthier donors that earn at least \$100,000 annually.
+However, instead of looking at personas with below- and above-median incomes, we can simulate a subset of wealthier donors.
 These personas are more likely to prefer donating to organizations that are criticized by their host governments.
@@
 
+![Average predicted donation market shares across all personas, segmented by persona education and religiosity across organizational issue area, relationship with host government, and funding sources](output/figures/education-religion-all.pdf){#fig:edu-religion}
+
 While education and religiosity are both important drivers of individual philanthropy, neither are associated with any sizable differences in persona donation patterns.
-In general, both high school and college graduates *and* personas who both rarely and often attend religious services follow the same patterns in preferences shown in @fig:income: personas prefer human rights and refugee relief organizations, organizations funded by government grants, and organizations with friendly relationships with their host governments (see @fig:education and @fig:religiosity in the appendix.)
+As seen in @fig:edu-religion, preferences for issue areas are constant across both persona characteristics, with human rights and refugee relief organizations the most preferred, followed closely by emergency response organizations.
+regardless of levels of education or religiosity.
+Human rights issues attract a slightly larger market share of personas who are college graduates or who attend religious services at least monthly, while refugee issues are more likely to attract less religious personas, but these differences are minor.
+Preferences are consistent for different sources of funding as well—personas generally prefer organizations funded mostly by government grants.
+Persona preferences across different organizational relationships with host governments are also consisten across education and religiosity, with most personas preferring to donate to NGOs that enjoy friendly relations abroad.
+College graduate personas are slightly more willing to donate to organizations facing crackdown, but the difference is roughly half a percentage point.
 

### 2020-10-01 analysis/experiment.Rmd
Add experiment text

---
title: "Experiment"
author: "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
    pandoc_args:
      - "--default-image-extension=png"
editor_options: 
  chunk_output_type: console
---

# Description

This survey was hosted on [Qualtrics](https://www.qualtrics.com) and participants were recruited through [Centiment](https://www.centiment.co/).

# Survey experiment {.survey}

```{r child = "text/experiment.md"}
```

### 2020-10-03 manuscript/manuscript.Rmd
Final Suparna edits

@@
   email: aheiss@gsu.edu
-date: "September 30, 2020"
+date: "October 2, 2020"
 published: Working paper.
@@
 However, research on the determinants of philanthropy towards international causes—particularly towards organizations working in challenging environments—is still in its infancy.
-Which demographic and experiential factors influence the decision of individuals to donate to legally besieged NGOs?
+Which demographic and experiential factors influence the decisions of individuals to donate to legally besieged NGOs?
 We investigate this question using a market simulation based on a nationally representative conjoint experiment conducted on individuals across the U.S.
@@
 
-In its 2016 annual report, Human Rights Watch claimed that civil society was under more aggressive attack than at any time in recent memory.
-Governments across the globe have cracked down on civil society organizations (CSOs) and non-governmental organizations (NGOs)—a phenomenon known as "closing civic space" [@CarothersBrechenmacher:2014; @CIVICUS:2017].[^NGOdef] As part of this phenomenon, NGOs face strong legal and bureaucratic obstacles to their work.
+In 2016, Human Rights Watch claimed that civil society was under more aggressive attack than at any time in recent memory [@Roth:2016].
+Governments across the globe have cracked down on civil society organizations (CSOs) and non-governmental organizations (NGOs)—a phenomenon known as "closing civic space" [@CarothersBrechenmacher:2014; @CIVICUS:2017; @DPR:2015; @DPR:2016].[^NGOdef] As part of this phenomenon, NGOs face strong legal and bureaucratic obstacles to their work.
 Legal restrictions, or what we refer to as legal crackdowns, are a core part of these efforts.
@@
 In 2018, private giving to NGOs working in international affairs reached \$22.08 billion, and international affairs-focused organizations are one of only two categories of organizations that have continued experiencing substantial growth in giving [@givingusa:2019].[^intlaffairs] Most of this growth is driven by individuals making small-scale or micro-donations.[^smalldonors] In 2017, 70% of donations to international affairs NGOs came from individuals, rising to 86% in 2018 [@givingusa:2019].
-But relying on individual donors means that NGOs must consider individual preferences when fundraising.
+But relying on individual donors means that NGOs must consider their preferences when fundraising.
 Which individual donor characteristics and attributes are most salient for INGOs interested in maximizing philanthropy at a time when they are facing increasingly hostile environments abroad?
@@
 Personas with high levels of trust in political and charitable institutions and who are actively engaged in charity and volunteerism prefer donating to human rights organizations that have friendly relationships with their host governments.
-In contrast, personas with low levels of social trust eschew both human rights organizations *and* any type of NGO with more contentious relationships with host governments, preferring instead to donate to NGOs with friendly host-country relationships and working on less contentious issues like emergency response and refugee relief.
+In contrast, personas with low levels of social trust eschew both human rights organizations *and* any type of NGO with more contentious relationships with host governments.
+Instead, they prefer donating to NGOs with friendly host-country relationships and working on less contentious issues like emergency response and refugee relief.
 Personas with higher trust are more comfortable donating to legally besieged INGOs.
@@
 Conjoint analysis allows us to elicit donor preferences without respondents explicitly stating their exact preferences.
-This kind of analysis is commonly used in marketing to reveal consumer preferences for hypothetical products, and has become increasingly popular in political science and public policy [@KnudsenJohannesson:2019].
+This kind of analysis is commonly used in marketing to reveal consumer preferences for hypothetical products, and has become increasingly popular in political science and public policy [@Helfer:206; @Mummolo:2016; @KnudsenJohannesson:2019].
 Because we are interested in exploring the complexity behind the decision to donate, we apply conjoint methods to the study of nonprofits and philanthropy.
@@
 The four panels of @fig:income show the average predicted market share for different organizational issue areas, funding sources, and relationships with host governments across different levels of persona income, with two different cutpoints for high and low income.
-To ease with modeling and interpretation, we split high and low income personas based on the 2017 U.S.
+To ease with modeling and interpretation, we split high- and low-income personas based on the 2017 U.S.
 median income (\$61,372), showing personas with incomes higher and lower than the national median.
@@
 This support, however, appears to evaporate as civil society crackdown intensifies.
-High income personas are the least likely demographic to prefer donating to NGOs under crackdown.
+High-income personas are the least likely demographic to prefer donating to NGOs under crackdown.
 Their lower income counterparts, on the other hand, are generally unfazed by NGOs' relationships with government, maintaining the same average market share across all three types of host country relationships.
-Patterns in preferences for issue area and funding sources remain constant across both methods of categorizing income—crackdown only has an effect on very high income personas.
+Patterns in preferences for issue area and funding sources remain constant across both methods of categorizing income—crackdown only has an effect on very high-income personas.
 Income thus appears to influence preferences particularly for NGOs facing criticism and crackdown abroad—wealthy donors are perhaps fair-weather friends that are more likely to pull their support when an organization's work becomes more difficult.
@@
 While education and religiosity are both important drivers of individual philanthropy, neither are associated with any sizable differences in persona donation patterns.
-As seen in @fig:edu-religion, preferences for issue areas are constant across both persona characteristics, with human rights and refugee relief organizations the most preferred, followed closely by emergency response organizations.
-regardless of levels of education or religiosity.
+As seen in @fig:edu-religion, preferences for issue areas are constant across both persona characteristics, with human rights and refugee relief organizations the most preferred, followed closely by emergency response organizations, regardless of levels of education or religiosity.
 Human rights issues attract a slightly larger market share of personas who are college graduates or who attend religious services at least monthly, while refugee issues are more likely to attract less religious personas, but these differences are minor.
 Preferences are consistent for different sources of funding as well—personas generally prefer organizations funded mostly by government grants.
-Persona preferences across different organizational relationships with host governments are also consisten across education and religiosity, with most personas preferring to donate to NGOs that enjoy friendly relations abroad.
+Persona preferences across different organizational relationships with host governments are also consistent across education and religiosity, with most personas preferring to donate to NGOs that enjoy friendly relations abroad.
 College graduate personas are slightly more willing to donate to organizations facing crackdown, but the difference is roughly half a percentage point.
@@
 
+The conjoint experiment conducted among a nationally representative sample of U.S.
+respondents with a prior history of charitable giving raises two main concerns for inference.
+It may be the case that respondent answers—and the corresponding beahavior of simulated personas—could potentially be driven by their priors towards these organizations.
+In addition, there are also important questions about the generalizability of these results outside the American context.
+We explore both below.
+
 Given the nature of conjoint experiments, the randomly presented organizations may have influenced respondent choices.
@@
 For instance, in February 2018, news broke out about sexual abuse and misconduct at Oxfam and several other prominent organizations, including Amnesty International and Save the Children.
-This potentially strengthened a narrative that the nonprofit sector suffers from governance failures [@Phillips:2019].
+This may have potentially strengthened a narrative that the nonprofit sector suffers from governance failures [@Phillips:2019].
+In a competitive NGO environment [@Cooley:2002], maintaining positive perceptions is important as donors who perceive these organizations as untrustworthy may simply take their resources elsewhere.
 As such, it could be argued that respondents may be less likely to donate to Oxfam or Amnesty because of these scandals.
@@
 donors, given Oxfam is based in the UK, and "media narratives are often not as unsupportive as often assumed" [@BanksSchulpenBrockington:2020, 703].
+Moreover, research shows that when donors feel solidarity or an ideological connection with an NGO – especially because of the cause espoused by them – they are likely to consider the organization to be trustworthy, despite the lack of full transparency and oversight [@KeatingThrandardottir:2017].
+Even watchdog organizations such as Charity Navigator and Better Business Bureau Giving Alliance have been found to not significantly impact individuals’ trust in nonprofit organizations.
+Rather, trust is more likely fostered through local networks and personal scrutiny [@TBPrakash:2017, 643].
+
+We also failed to find any systematic evidence that the Oxfam scandal influenced perceptions of the nonprofit sector in the U.S., likely because the story had far less news coverage in the U.S.
+Many individual donors have a preference to donate locally and they lack sufficient knowledge to make an informed decision about donating internationally.
+@KnowlesSullivan:2017, conducting a field experiment in New Zealand, found that only a small number of participants in the study stated that not giving internationally was driven by mistrust.
 Rather, lack of trust towards overseas NGOs, particularly aid and developmental agencies often results due to donors perceiving INGOs as having low personal relevance [@FaulknerTruongRomaniuk:2015].
-We failed to find any systematic evidence that the Oxfam scandal influenced perceptions of the nonprofit sector in the U.S., likely because the story had far less news coverage in the U.S.
-Many individual donors have a preference to donate locally and they lack sufficient knowledge to make an informed decision about donating internationally.
 Overall, the literature suggests that for INGO fundraising, lack of awareness is a much larger issue than specific scandals or other knowledge of specific organizational characteristics that might reduce donor trust and confidence.
@@
 On average, human rights organizations tend to attract personas who are wealthier, follow national and international news, and travel abroad.
-Donors who are less wealthy, follow the news less often, and do not travel are more attracted to organizations working on less contentious like emergency response and refugee relief.
+Donors who are less wealthy, follow the news less often, and do not travel, are more attracted to organizations working on less contentious like emergency response and refugee relief.
 
@@
 Personas with low social trust tend to be wary of negative host-country relationships and strongly prefer to donate to organizations that are friendly with their host governments, while personas with high social trust are more willing to stick with legally besieged organizations.
-This could imply that donors that are the most trusting and involved could remain supportive when charities face government criticism and crackdown.
+This could imply who donors that are the most trusting and involved could remain supportive when charities face government criticism and crackdown.
 The global crackdown on NGOs may also possibly sour NGOs' least trusting individual donors.
@@
 The above results have important implications for NGOs as they navigate a shrinking civic space and consider the use of different frames to tailor their fundraising appeals to individual donors.
-Our survey finds that at least for some kinds of individuals, NGOs may benefit from publicizing when they are targets of government crackdown, including that information in their fundraising appeals.
-However, the larger challenge may be addressing concerns of donors with low levels of trust who are the least likely to donate organizations facing criticism and crackdown abroad.
+Our simulation finds that at least for some kinds of personas, NGOs may benefit from publicizing when they are targets of government crackdown, including that information in their fundraising appeals.
+However, the larger challenge may be addressing the concerns of donors with low levels of trust, as they are the least likely to donate organizations facing criticism and crackdown abroad.
 More broadly, studies from a range of countries show that levels of giving are lowest for refugee and asylum organizations, as well as for overseas and development organizations.
 Rather, donors giving to international causes tend to support international disaster relief and religious groups [@RobsonHart:2020].
-However, the former are precisely the organizations facing crackdown.
+However, some of the former are precisely the organizations facing crackdown.
 More research is needed to answer how these organizations can appeal to broader array of potential foreign donors to increase levels of charitable-giving towards them.

### 2020-10-03 manuscript/appendix.Rmd
Add separate appendix

---
title: 'Online appendix for "Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy"'
short-title: 'Online appendix for "Who Cares About Crackdowns?"'
author:
- name: Suparna Chaudhry
  affiliation: Lewis & Clark College
  url: http://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
- name: Marc Dotson
  affiliation: Brigham Young University
  url: https://marriottschool.byu.edu/directory/details?id=50683
  email: marc_dotson@byu.edu
- name: Andrew Heiss
  affiliation: Georgia State University
  url: https://www.andrewheiss.com/
  email: aheiss@gsu.edu
date: "October 2, 2020"
title-page: false
published: 
git-repo: https://github.com/andrewheiss/who-cares-about-crackdown
reference-section-title: References
toc: true
appendix: true
---

<!-- supplement.md is generated from supplement.Rmd. Only edit the .Rmd file, *not* the .md file. -->

# Survey experiment

```{r child = "../analysis/text/experiment_anonymized.md"}
```

### 2020-10-03 manuscript/manuscript.Rmd
Minor typos

@@
 Conjoint analysis allows us to elicit donor preferences without respondents explicitly stating their exact preferences.
-This kind of analysis is commonly used in marketing to reveal consumer preferences for hypothetical products, and has become increasingly popular in political science and public policy [@Helfer:206; @Mummolo:2016; @KnudsenJohannesson:2019].
+This kind of analysis is commonly used in marketing to reveal consumer preferences for hypothetical products, and has become increasingly popular in political science and public policy [@Helfer:2016; @Mummolo:2016; @KnudsenJohannesson:2019].
 Because we are interested in exploring the complexity behind the decision to donate, we apply conjoint methods to the study of nonprofits and philanthropy.
@@
 Personas with low social trust tend to be wary of negative host-country relationships and strongly prefer to donate to organizations that are friendly with their host governments, while personas with high social trust are more willing to stick with legally besieged organizations.
-This could imply who donors that are the most trusting and involved could remain supportive when charities face government criticism and crackdown.
+This could imply who donors who are the most trusting and involved could remain supportive when charities face government criticism and crackdown.
 The global crackdown on NGOs may also possibly sour NGOs' least trusting individual donors.

### 2020-10-03 manuscript/manuscript.Rmd
Add publication-related metadata

@@
 toc: false
+title-page: true
+word-count: "7,562"
+keywords: international NGOs, donor behavior, philanthropy, human rights, repression, international giving, donor choice
+thanks: >-
+  The data that support the findings of this study, as well as the code to reproduce the findings, are openly available at <https://github.com/andrewheiss/who-cares-about-crackdown> and <https://osf.io/sm5ew/>.
+This experiment received approval by the human subjects research committees at Christopher Newport University (1436622-1), Brigham Young University (E19135), and Georgia State University (H19644).
+As part of a larger project, we preregistered hypotheses and our research design at the Open Science Framework, and our preregistration protocol is available at <https://osf.io/hsbyd/>.
+This study covers the third research question of our preregistered design.
+author-note: >-
+  Suparna Chaudhry, PhD, Assistant Professor of International Affairs, Department of International Affairs, Lewis \& Clark College; Marc Dotson, PhD, Assistant Professor of Marketing, Marriott School of Business, Brigham Young University; Andrew Heiss, PhD, Assistant Professor of Public Management, Andrew Young School of Policy Studies, Georgia State University.
+correspondence: >-
+  Correspondence concerning this article should be addressed to Andrew Heiss, PhD, Department of Public Management and Policy, Andrew Young School of Policy Studies, Georgia State University, 14 Marietta Street NW, Suite 357, Atlanta, GA 30303.
+Contact: aheiss@gsu.edu
 mainfont: Lora
 sansfont: IBM Plex Sans
+policy-implications: >-
+  In the wake of the global crackdown on civil society, international NGOs (INGOs) need to maintain access to multiple sources of funding, including individual donors.
+
+  It is critical for INGOs to understand what motivates individuals to donate, especially if INGOs face legal crackdown in their host countries.
+
+  Trust in political institutions and in charitable organizations matters substantially in shaping donor preferences.
+
+  We find that potential donors with low social trust tend to be wary of negative host-country relationships and prefer to donate to INGOs that are friendly with their host governments, while potential donors with high social trust are more willing to stick with legally besieged INGOs.
+
+  Donors that are the most trusting and involved may remain supportive when charities face government criticism and crackdown.
+The global crackdown on NGOs may also possibly sour NGOs' least trusting individual donors.
 ---

### 2021-04-16 manuscript/manuscript.Rmd
Add explicit singlespacing for tables for manuscript template
Suparna's initial R&R additions

@@
 These crackdowns create barriers to entry, funding, and advocacy for NGOs in an effort to control, obstruct, and repress these organizations.
+Barriers to funding are especially pervasive and restrict the ability of NGOs to secure financial resources.
+Restrictive states may prevent the transfer of foreign funds to NGOs based on the origin of these funds and which issues these funds can be used towards.
 
-As a result of these legal crackdowns, foreign aid channeled through NGOs has decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
-While this has negatively impacted funding flows from public organizations like the United States Agency for International Development (USAID) and the Organisation for Economic Cooperation and Development (OECD), philanthropy from private donors and foundations is not as adversely affected [@McGill:2018].
-Given this trend of closing civic space, INGOs need to maintain access to multiple sources of funding, including individual donors.
+As a result of these laws, foreign aid (also referred to as public or official aid) channeled through NGOs has decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
+Aid from public organizations like the United States Agency for International Development (USAID) and the Organisation for Economic Cooperation and Development (OECD) has decreased following the passage and implementation of these laws.
+However, philanthropy from private donors and foundations is not as adversely affected [@McGill:2018].
+Many foundations have continued channeling funds to countries with hostile legal environments [@NeedlesWolcheckSato:2018].
+Given this trend of reduced public aid following restricted legal environments for NGOs abroad, many INGOs may need to devote more resources to fundraise from individual donors.
 
 Individual private donations are a critical source of INGO funding.
-Total private philanthropy in the United States has grown substantially over time, reaching more than \$400 billion in 2018 (@fig:giving-aggregate).
-In 2018, private giving to NGOs working in international affairs reached \$22.08 billion, and international affairs-focused organizations are one of only two categories of organizations that have continued experiencing substantial growth in giving [@givingusa:2019].[^intlaffairs] Most of this growth is driven by individuals making small-scale or micro-donations.[^smalldonors] In 2017, 70% of donations to international affairs NGOs came from individuals, rising to 86% in 2018 [@givingusa:2019].
+While total private philanthropy[^phildef] in the United States has grown substantially over time, particularly notable is the fact that private giving to NGOs working in international affairs  and international affairs-focused organizations are one of only two categories of organizations that have continued experiencing substantial growth in giving and reached \$22.08 billion in 2018 [@givingusa:2019].[^intlaffairs] Most of this growth is driven by individuals making small-scale or micro-donations.[^smalldonors] In 2017, 70% of donations to international affairs NGOs came from individuals, rising to 86% in 2018 [@givingusa:2019].
 But relying on individual donors means that NGOs must consider their preferences when fundraising.
@@
 
-![Aggregate philanthropic giving in the United States, 1977–2017. Source: Giving USA.](output/figures/giving_aggregate.pdf){#fig:giving-aggregate}
-
 There exists a robust scholarship on the determinants of individual-level philanthropy to domestic causes.
 But the dynamics of *international* giving to NGOs are under-examined in the literature on individual donor attributes and preferences.[^exceptions] Motivating individuals to donate to international causes is hard as the number of recipients are large and far removed from the donor [@CasaleBaumann:2015, 100].
-And research on the determinants of philanthropy for international causes—particularly towards organizations working in challenging environments—is still in its infancy due to the absence of expansive and high-quality data [@greenhill2013].
-While previous work has looked at how organizational attributes of nonprofits affect donors' willingness to donate internationally [@ChaudhryHeiss:2020], we have yet to uncover demographic traits and experiences that motivate or deter individuals to donate during shrinking civic space.
+Trust is an essential component for INGO sustainability and for many nonprofits, trust often translates into grants and donations [@coombs2007].
+Geography often impedes donors' direct evaluation of their work and trust is one of the most influential criteria that private donors use when deciding which nonprofits to support [@prakash2010trust; @bekkers2003trust].
+A lack of trust could be further fueled by legal trouble with the NGO host government—a dynamic that individuals may not wish to enter with their dollars.
+How does trust in NGOs influence individuals' preferences to donate, especially when groups face crackdown?
 
-We explore this question using a simulated market for philanthropic donations, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity.
+We explore this question using a simulated market for philanthropic donations towards INGOs, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity.
 We adapt methods used in marketing to generate dozens of distinct simulated personas that represent typical donor profiles, and we vary these personas along different dimensions of demographic, political, and social attributes.
@@
 Personas with higher trust are more comfortable donating to legally besieged INGOs.
+Our findings imply that individual donors with high trust would continue remaining supportive of INGOs when they face criticism and crackdown from foreign governments.
+On the other hand, government crackdown, and more broadly, closing civic space, may further sour NGOs least trusting individual donors.
 
-This study contributes both to scholarship and practice in public policy, nonprofits, and philanthropy.
-Individual giving abroad can help bridge socioeconomic disparities worldwide, especially given the stark inequality in the global distribution of income.
-Knowledge of demographic traits and its impact on funding can help nonprofits craft more effective and targeted marketing strategies [@Rajan:2009, 414].
+This study contributes both to scholarship and practice in public policy, nonprofits, and philanthropy in three important ways.
+The paper helps us understand how the international community and NGOs might respond to the phenomenon of closing civic space, which does not appear to be receding.
 Most NGOs working internationally have previously relied on government and foundation funding.
-But with shrinking civic space, these groups may need to readjust their fundraising strategies towards individuals.
-Framing is important in this regard—how people process information affects their willingness to donate.[^framing] However, existing research is unclear about which frames are effective when making appeals to individual donors considering international philanthropy.
+But in the face of decreasing funds from official donors, our results show that INGOs can rely on individual donors, specifically, their most trusting donors, when groups face a hostile environment abroad.
+These findings lend support to previous literature arguing that trust matters only when individuals donate to organizations acting under great uncertainty or working towards difficult goals [@Wiepking:2010].
+
+Second, knowledge of demographic traits and its impact on funding can help nonprofits craft more effective and targeted marketing strategies [@Rajan:2009, 414].
+Our paper shows that in readjusting their fundraising strategies towards individuals, framing, or the process through which actors present information to influence perceptions, is particularly important [@chong2007framing].
+Framing affects their willingness to donate.
+However, existing research is unclear about which frames are effective when making appeals to individual donors considering international philanthropy.
 Since our study looks at multiple organizational and host country factors, our results can help NGOs frame their appeals.
+In particular, our results show that NGOs may benefit from publicizing crackdown at least towards their most trusting donors.
 
-More broadly, while research in public policy examines giving to NGOs, philanthropy is not seen as relevant by international relations as a discipline [@youde2019].
+Finally, while research in public policy examines giving to NGOs, philanthropy is not seen as relevant by international relations as a discipline [@youde2019].
 However, philanthropy—particularly donations received by INGOs—can help us understand changes in the dynamics of global governance.
@@
 
-# Sustaining civil society organizations abroad
+# Closing civic space and its impact on INGOs
 
@@
 In countries with weak institutions and poor governance, where direct aid transfers to governments raise issues of misuse and bureaucratic inefficiency, donors specifically seek out NGOs for projects [@Dietrich2013].
-However, a restricted NGO environment merits examination of the diverse array of funds available to these organizations.
+However, NGO-state relationships have evolved over time—in the 1950s and 60s, international assistance channeled through NGOs aimed at producing socio-economic change rather than political progress.
+But in the aftermath of the dissolution of the Soviet Union, many NGOs had the explicit goal of promoting democracy and bringing down authoritarian governments.
+Subsequently, many states perceive them as threatening and have sought to repress them.
 
-## Sources of funding
+LINE ABOUT EXTENT.
+This phenomenon can have three main impacts on INGOs.
+First, it has led to a reduction in resources and grants available to INGOs.
+Second, restrictive NGO laws can affect INGO programming by preventing organizations from working in certain issue areas, or at least by making it more burdensome to do so.
+To deal with this, some groups have adapted by changing the nature of their programming to appear less threatening to the repressive countries.
+Finally, in the worst-case scenario, this phenomenon can also lead to a loss in INGOs access to target countries—often also associated with the use of violence against INGOs and their employees.
+In this paper, we exlusively focus on the first dilemma—the reduction in INGO funding and possible responses to it.
+
+## Changes in INGO funding
 
@@
 While INGOs have not been passive in responding to the crackdown on civil society, they face increasing obstacles from a funding perspective.
-Official donors have reduced the amount of aid channeled to countries with legal restrictions [@DupuyPrakash:2018] and have redirected funds within restrictive countries, decreasing funds for politically sensitive causes in favor of tamer issues that are more compatible with the governments of those countries [@ChaudhryHeiss:2018].
-However, private funding towards international nonprofits has not been as adversely affected.
-Many foundations have continued channeling funds to countries with hostile legal environments [@NeedlesWolcheckSato:2018].
 
-The advent of funding restrictions on NGOs globally and a subsequent decline in government and foundation funding has made the role and value of individual philanthropy in sustaining NGOs even clearer.[^phildef] NGOs need access to a diverse array of funds and individual donations to international affairs organizations have steadily increased over the past two decades.
-Moreover, in the United States, donations from individuals have far outstripped foundation and corporate giving.
-In 2018, individual donations amounted to \$292 billion, compared to \$76 billion from foundations and \$20 billion from corporations [@NPT].
-Given that a majority of research is restricted to elite high net-worth donors[^highnetworth] [@USTrust2014], these figures show that it is imperative to understand motivations and attributes of small-scale donors as well.
+Closing civic space not just resulted in net losses of income to INGOs, particularly through official bilateral and multilateral aid [@DupuyPrakash:2018], it has also affected how and where funds are allocated.
+Following the passage of anti-NGO laws, official donors move funds away from contentious causes such as human rights, media, corruption, advocacy, among others, towards tamer and more regime-compatible causes such as health, education [@ChaudhryHeiss:2018].
+The latter trend has also been exacerbated by a preference among donors working in official aid and the democracy promotion establishment to gradually increase funding directed towards tame causes, at the expense of more contentious causes.
+This is because many tame causes can have easily quantifiable, measurable outputs, which makes it clear to show a program’s effectiveness over time (Bush 2015).
 
-## Key drivers of individual-level philanthropy
+We argue that individual private donors can help fill in an important gap.
+Previous research has shown that individual donors do not use the same performance-based metrics as official donors [@desaikharas].
+Rather, individual donors often use heuristics to simply their decision-making, making cursory judgments about an organization’s issue area, mission, vision, and values and seek out supplementary information from friends family, and acquaintances [@CrosonShang:2011a; @TBPrakash:2017; @SzperPrakash:2011].
+Due to these differences, we argue that individual donors can help address some of the challenges arising from reduced public funding available to INGOs.
+To be clear, we are not arguing that giving by individual donors would be a perfect substitute for NGOs net loss of income or income for certain programs, but rather, an important supplement to reduced funding from foreign sources.
+Moreover, it would also be a supplement to private funding from foundations towards international nonprofits which has not been as adversely affected, with foundations continue to channel funds to countries with hostile legal environments [@NeedlesWolcheckSato:2018].
 
-A vast literature on philanthropy looks at organizational-level factors that motivate individuals to donate [@TBPrakash:2017].
-However, donation decisions are not determined solely by a recipient organization's characteristics.
-Donors have personality traits, preferences, and experiences that make them more or less likely to engage in philanthropy.
-Substantial research has looked at the determinants of donating to local—rather than international—causes, including four main attributes: social capital, the role of higher education, levels of religiosity, and national group attachment.
+However, research on the determinants of individual-level philanthropy for international causes—particularly towards organizations working in challenging environments—is still in its infancy due to the absence of expansive and high-quality data [@greenhill2013].
+Moreover, a majority of research on giving to international groups is restricted to elite high net-worth donors[^highnetworth] [@USTrust2014].
+We still know little about demographic traits and experiences that motivate or deter individuals to donate during shrinking civic space.
+Below, we look at key drivers of individual-level philanthropy and show how the importance of trust in donating during civic crackdowns.
+
+ the role of higher education, levels of religiosity, and trust.
 
@@
 Religiosity is also a significant predictor of the likelihood and level of giving.
-People who regularly attend religious services are more likely to have prosocial values, face a stronger norm of charitable giving, and may feel pressure to conform to group and community standards [@wiepking2010].
+People who regularly attend religious services are more likely to have prosocial values, face a stronger norm of charitable giving, and may feel pressure to conform to group and community standards [@WiepkingBekkers:2010].
 Regular attendance may also strengthen individuals' beliefs in organizations' missions.
 
-Finally, recent research looks at how a sense of ethnonationalism and national group attachment affects the decision to donate to domestic and international charities.
-Looking at UK respondents, @hartrobson2019 find that whereas nationalists have a preference for domestic charities, they are not necessarily averse to donating to international causes, whereas internationalists have a strong preference for donating to groups working abroad.
+Finally, an individual's disposition to trust, or the general tendency to trust others, including individuals groups or institutions has been shown to have an impact on both intention to donate as well as actual donation behavior.
+Trusting people are not only more likely to give to charitable causes, but also donate more [@BrownFerris2007].
 
@@
 Overall, individuals with higher levels of income, education, and greater religious proclivities are not only more likely to give internationally, but also give higher amounts [@Rajan:2009; @CasaleBaumann:2015].
-Additionally, we posit that other related characteristics such as civic and associational engagement and social trust also influence the decision to donate.
+Additionally, we posit that social trust can play an important role in the decision to donate, as individuals who trust NGOs are less likely than others to halt their monetary support in the face of difficulties [@dwyer1987].
 
@@
 
+\stgroup
+
+\singlespacing
+
 ```{r child = "output/tables/tbl-organization-attributes-full.md"}
 ```
+
+\fingroup
 
@@
 
-\newpage
+\stgroup
+
+\singlespacing
 
@@
 ```
+
+\fingroup
 
@@
 
+\stgroup
+
+\singlespacing
+
 ```{r child = "output/tables/tbl-persona-attributes.md"}
@@
 
+\fingroup
+
 We then combine these different scenarios of donor and organization attributes with the coefficients from a multinomial multilevel regression model to calculate the probability that each simulated persona has of giving to specific combinations of organizational attributes.
@@
 
+\stgroup
+
+\singlespacing
+
 ```{r child = "output/tables/tbl-sim-output.md"}
 ```
+
+\fingroup
 
@@
 Once an organization faces criticism or crackdown, however, support deteriorates rapidly among personas with low social trust, since such a crackdown could be perceived as a violation of the persona's trust in the charity—that is, the organization must be doing something wrong to deserve criticism.
-Personas with high levels of trust, on the other hand, seem to stick with legally besieged organizations and show them the benefit of the doubt.
+When the risk of a certain action is higher, people need higher levels of confidence or trust to engage in that action [@coleman1990].
+When NGOs have goals that are harder to accomplish (as is the case under shrinking civic space), there is greater uncertainty that the donated money will meaningfully contribute to the intended cause.
+
+Personas with high levels of trust, on the other hand, seem to stick with legally besieged organizations and show targeted groups the benefit of the doubt.
 The global crackdown on NGOs thus sours NGOs' least trusting individual donors.
+Overall, our results support research that donors with high levels of trust are more active in giving than those with low levels of trust [@sargeant2008] and that trust especially matters when individuals donate to organizations working under great uncertainty and towards difficult goals [@Wiepking:2010].
 
@@
 The global crackdown on civil society and the consequent decline of official development assistance has made the role of philanthropy in sustaining INGOs clear.
-INGOs need access to multiple sources of funding, and the value of individual-level philanthropy is still relatively under-explored.
-While existing research has examined the impact of organizational-level factors on individual giving as well as giving to local causes, in this paper, we specifically look at the demographic traits of those who are likely to donate to INGOs facing hostile environments abroad.
-We find several important trends from our simulated market for philanthropy.
-On average, human rights organizations tend to attract personas who are wealthier, follow national and international news, and travel abroad.
-Donors who are less wealthy, follow the news less often, and do not travel, are more attracted to organizations working on less contentious like emergency response and refugee relief.
+INGOs need access to multiple sources of funding, and the value of individual-level philanthropy in sustaining the operations of groups working in challenging environments is still relatively under-explored.
+While trust is a difficult construct to define, the nonprofit literature conceptualizes trust as a key driver of commitment, which is shown to impact both intention to donate as well as actual donation behavior.
+When considering repressive environments and NGOs working on more difficult goals, a lack of trust could be further fueled by legal trouble with the NGO host government—a dynamic that individuals may not wish to enter with their dollars.
+How does trust in NGOs influence individuals' preferences to donate, especially when groups face crackdown?
 
-More importantly, we find that trust in political institutions and in charitable organizations matters substantially in shaping donor preferences.
+Using a simulated market for philanthropic donations towards INGOs, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity, we find several important trends.
+Trust in political institutions and in charitable organizations matters substantially in shaping donor preferences.
 Personas with high levels of social and charitable trust prefer donating to human rights organizations that have friendly relationships with their host governments, while personas with low trust are drawn more to emergency response and refugee relief organizations with unfriendly relationships with their host governments.
@@
 The global crackdown on NGOs may also possibly sour NGOs' least trusting individual donors.
+Our findings lend support to research showing that individuals who trust NGOs are more likely to continue their monetary support of NGOs in the face of difficulties and under great uncertainty [@dwyer1987; @Wiepking:2010].
+
+In addition, we find that on average, human rights organizations tend to attract personas who are wealthier, follow national and international news, and travel abroad.
+Donors who are less wealthy, follow the news less often, and do not travel, are more attracted to organizations working on less contentious like emergency response and refugee relief.
 
@@
 
-[^exceptions]: For exceptions, see @Micklewright:2009 on the UK; @Rajan:2009 on Canada; @wiepking2010 on the Netherlands; @CasaleBaumann:2015 on the U.S.
+[^exceptions]: For exceptions, see @Micklewright:2009 on the UK; @Rajan:2009 on Canada; @WiepkingBekkers:2010 on the Netherlands; @CasaleBaumann:2015 on the U.S.
 
@@
 While it can include grants given by foundations and corporations to nonprofit organizations, our focus here is on individual giving.
-
-[^framing]: Framing is the process through which actors present information to influence perceptions or behavior.
-Previous research has shown that which frames are employed can have a significant effect on individuals' attitudes and behaviors [@BenfordSnow:2000; @ChongDruckman:2007].
+Some perspectives see philanthropy as more of a strategic long-term practice that seeks to address the root causes of issues, and charity as a more short-term practice focused on providing immediate relief.
+But many scholars see philanthropy as essentially synonymous with charitable donations, as the latter can also address longer-term or strategic isssues [@Castle:2004].
+As such, despite these subtle differences, we use the terms inter-changeably here both because previous literature does so, and because in the case of philanthropic or charitable-giving to NGOs during crackdown, individuals could be giving to nonprofits both for immediate relief as well as long-term strategic purposes.
 

### 2021-04-17 manuscript/manuscript.Rmd
More Suparna edits

@@
 abstract: >-
-  Over the past two decades, international non-governmental organizations (INGOs) have faced increasing legal scrutiny and repression abroad.
-As a result, official aid to INGOs in repressive countries has reduced.
-NGOs thus need access to a diverse array of funds and may need to increase fundraising from private donors.
-However, research on the determinants of philanthropy towards international causes—particularly towards organizations working in challenging environments—is still in its infancy.
-Which demographic and experiential factors influence the decisions of individuals to donate to legally besieged NGOs?
-We investigate this question using a market simulation based on a nationally representative conjoint experiment conducted on individuals across the U.S.
-with a history of charitable giving.
-We find that trust in political institutions and charities is enormously influential in shaping donor preferences.
-Donor profiles with high levels of social trust are likely to donate to human rights INGOs with friendly relationships with host governments, and that support holds steady if INGOs face criticism or crackdown.
+  The phenomenon of closing civic space has adversely impacted the operations of INGOs.
+It has not just resulted in net losses of income to INGOs, but also how and where funds are allocated.
+We argue that individual private donors can be important in sustaining the operations of INGOs working in repressive contexts.
+Individual donors do not use the same performance-based metrics as official aid donors, and trust has shown to be an important component of support for nonprofits working towards difficult goals.
+How does trust in charitable organizations influence individuals’ preferences to donate, especially when these groups face crackdown?
+Using a simulated market for philanthropic donations towards INGOs, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity, we find that trust in charitable organizations matters substantially in shaping donor preferences.
+Donor profiles with high levels of social trust are likely to donate to INGOs with friendly relationships with host governments.
+This support holds steady if INGOs face criticism or crackdown.
 In contrast, donor profiles with lower levels of social trust prefer to donate to organizations that do not face criticism or crackdown abroad.
+The global crackdown on NGOs may thus possibly sour NGOs' least trusting individual donors.
 Our findings have practical implications for INGOs raising funds from individuals amid closing civic space.
@@
 In 2016, Human Rights Watch claimed that civil society was under more aggressive attack than at any time in recent memory [@Roth:2016].
-Governments across the globe have cracked down on civil society organizations (CSOs) and non-governmental organizations (NGOs)—a phenomenon known as "closing civic space" [@CarothersBrechenmacher:2014; @CIVICUS:2017; @DPR:2015; @DPR:2016].[^NGOdef] As part of this phenomenon, NGOs face strong legal and bureaucratic obstacles to their work.
-Legal restrictions, or what we refer to as legal crackdowns, are a core part of these efforts.
+Governments across the globe have cracked down on civil society organizations (CSOs) and non-governmental organizations (NGOs)—a phenomenon known as "closing civic space" [@CarothersBrechenmacher:2014; @CIVICUS:2017; @DPR:2015; @DPR:2016].[^NGOdef] Legal restrictions, or what we refer to as legal crackdowns, are a core part of these efforts.
 These crackdowns create barriers to entry, funding, and advocacy for NGOs in an effort to control, obstruct, and repress these organizations.
@@
 As a result of these laws, foreign aid (also referred to as public or official aid) channeled through NGOs has decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
-Aid from public organizations like the United States Agency for International Development (USAID) and the Organisation for Economic Cooperation and Development (OECD) has decreased following the passage and implementation of these laws.
 However, philanthropy from private donors and foundations is not as adversely affected [@McGill:2018].
 Many foundations have continued channeling funds to countries with hostile legal environments [@NeedlesWolcheckSato:2018].
-Given this trend of reduced public aid following restricted legal environments for NGOs abroad, many INGOs may need to devote more resources to fundraise from individual donors.
+Given this trend of reduced public aid following restricted legal environments for NGOs abroad, INGOs may need to devote more resources to fundraise from individual donors.
 
 Individual private donations are a critical source of INGO funding.
-While total private philanthropy[^phildef] in the United States has grown substantially over time, particularly notable is the fact that private giving to NGOs working in international affairs  and international affairs-focused organizations are one of only two categories of organizations that have continued experiencing substantial growth in giving and reached \$22.08 billion in 2018 [@givingusa:2019].[^intlaffairs] Most of this growth is driven by individuals making small-scale or micro-donations.[^smalldonors] In 2017, 70% of donations to international affairs NGOs came from individuals, rising to 86% in 2018 [@givingusa:2019].
+While total private philanthropy[^phildef] in the United States has grown substantially over time, it is notable that private giving to NGOs working in international affairs  and international affairs-focused organizations are one of only two categories of organizations that have continued experiencing substantial growth in giving and reached \$22.08 billion in 2018 [@givingusa:2019].[^intlaffairs] Most of this growth is driven by individuals making small-scale or micro-donations.[^smalldonors] In 2017, 70% of donations to international affairs NGOs came from individuals, rising to 86% in 2018 [@givingusa:2019].
 But relying on individual donors means that NGOs must consider their preferences when fundraising.
 Which individual donor characteristics and attributes are most salient for INGOs interested in maximizing philanthropy at a time when they are facing increasingly hostile environments abroad?
-What kinds of donors consider an INGO's host country political environment when making the decision to donate?
 
@@
 
-We explore this question using a simulated market for philanthropic donations towards INGOs, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity.
+We explore this using a simulated market for philanthropic donations towards INGOs, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity.
 We adapt methods used in marketing to generate dozens of distinct simulated personas that represent typical donor profiles, and we vary these personas along different dimensions of demographic, political, and social attributes.
-We find that specific individual characteristics help shape donor preferences for donating to INGOs, and that an organization's target issue area and its relationship with its host government interact strongly with these characteristics.
+We find that an organization's target issue area and its relationship with its host government interact strongly with individuals' characteristics.
 Personas with high levels of trust in political and charitable institutions and who are actively engaged in charity and volunteerism prefer donating to human rights organizations that have friendly relationships with their host governments.
@@
 Our findings imply that individual donors with high trust would continue remaining supportive of INGOs when they face criticism and crackdown from foreign governments.
-On the other hand, government crackdown, and more broadly, closing civic space, may further sour NGOs least trusting individual donors.
+On the other hand, government crackdown may further sour NGOs least trusting individual donors.
 
 This study contributes both to scholarship and practice in public policy, nonprofits, and philanthropy in three important ways.
-The paper helps us understand how the international community and NGOs might respond to the phenomenon of closing civic space, which does not appear to be receding.
+It helps us understand how the international community and NGOs might respond to the phenomenon of closing civic space, which does not appear to be receding.
 Most NGOs working internationally have previously relied on government and foundation funding.
 But in the face of decreasing funds from official donors, our results show that INGOs can rely on individual donors, specifically, their most trusting donors, when groups face a hostile environment abroad.
-These findings lend support to previous literature arguing that trust matters only when individuals donate to organizations acting under great uncertainty or working towards difficult goals [@Wiepking:2010].
+These findings lend support to previous literature arguing that trust matters  when individuals donate to organizations acting under great uncertainty or working towards difficult goals [@Wiepking:2010].
 
@@
 
-LINE ABOUT EXTENT.
-This phenomenon can have three main impacts on INGOs.
+Mre than 100 countries have proposed or enacted 244 measures restricting, repressing, or shutting down civil society since 2013 (ICNL 2021 CITATION FROM ISA PAPER).
+This has had a three-hold impact on INGOs.
 First, it has led to a reduction in resources and grants available to INGOs.
-Second, restrictive NGO laws can affect INGO programming by preventing organizations from working in certain issue areas, or at least by making it more burdensome to do so.
+Second, restrictive NGO laws can affect INGO programming by preventing organizations from working in certain (contentious) issue areas.
 To deal with this, some groups have adapted by changing the nature of their programming to appear less threatening to the repressive countries.
-Finally, in the worst-case scenario, this phenomenon can also lead to a loss in INGOs access to target countries—often also associated with the use of violence against INGOs and their employees.
+Finally, in the worst-case scenario, this has led to a loss in INGOs' access to target countries—often also associated with the use of violence against INGOs and their employees.
 In this paper, we exlusively focus on the first dilemma—the reduction in INGO funding and possible responses to it.
@@
 
-Thousands of INGOs in the Global South receive funds from a variety of public and private sources each year.
+Many INGOs in the Global South receive funds from a variety of public and private sources each year.
 Public funds—or traditional donor aid—channel money from official aid agencies through a variety of bilateral and multilateral institutions.
@@
 We argue that individual private donors can help fill in an important gap.
-Previous research has shown that individual donors do not use the same performance-based metrics as official donors [@desaikharas].
-Rather, individual donors often use heuristics to simply their decision-making, making cursory judgments about an organization’s issue area, mission, vision, and values and seek out supplementary information from friends family, and acquaintances [@CrosonShang:2011a; @TBPrakash:2017; @SzperPrakash:2011].
-Due to these differences, we argue that individual donors can help address some of the challenges arising from reduced public funding available to INGOs.
+Individual donors do not use the same performance-based metrics as official donors [@desaikharas].
+Rather, individual donors often use heuristics to simply their decision-making, making cursory judgments about an organization’s issue area, mission, vision, and values and seek out supplementary information from friends, family, and acquaintances [@TBPrakash:2017; @SzperPrakash:2011].
+Due to these differences, individual donors can help address some of the challenges arising from reduced public funding available to INGOs.
 To be clear, we are not arguing that giving by individual donors would be a perfect substitute for NGOs net loss of income or income for certain programs, but rather, an important supplement to reduced funding from foreign sources.
@@
 
- the role of higher education, levels of religiosity, and trust.
+## Key drivers of individual-level philanthropy
+
+Substantial research has looked at the individual-level determinants of donating to local, rather than international causes, including four main attributes: social capital, the role of higher education, levels of religiosity, and trust.
 
@@
 Accordingly, we do not test specific hypotheses or theories.
+
+TODO: Fix final point - connect testing stuff with existing theories - we don't have a list of things to test
+
 However, we do talk about causal effects given that we conduct an experiment that varies a number of factors in order to elicit opinions from respondents.
@@
 
-In general, regardless of income, personas respond better to human rights and refugee assistance organizations, followed closely by emergency response organizations.
+Regardless of income, personas respond better to human rights and refugee assistance organizations, followed closely by emergency response organizations.
 Environmental NGOs have the lowest market share across both levels of incomes.
 There are negligible differences across income levels—wealthier personas show a slight preference towards human rights and refugee organizations.
-As we explore below, this is possibly because income correlates with interest in public affairs and political activity—individuals who are wealthier arguably have more time and resources to follow the news and be continuously engaged in their communities and in other activist causes.
+This is possibly because income correlates with interest in public affairs and political activity—individuals who are wealthier arguably have more time and resources to follow the news and be continuously engaged in their communities and in other activist causes.
 There are no sizable differences in donation preferences by income across different forms of NGO funding—both levels of income tend to prefer organizations funded by government grants over small donors.
@@
 An organization's relationship with its host government does influence market shares across levels of income, but the size of this difference depends on the magnitude of income.
-When splitting income based on income, there is no difference between income levels.
-In general, personas prefer to donate to organizations with friendly relationships with their host governments and avoid those that are criticized or under crackdown.
-However, instead of looking at personas with below- and above-median incomes, we can simulate a subset of wealthier donors.
-These personas are more likely to prefer donating to organizations that are criticized by their host governments.
-This falls in line with their preference for human rights organizations, which have more contentious missions and are more likely to receive government criticism.
-This support, however, appears to evaporate as civil society crackdown intensifies.
+In general, personas prefer to donate to organizations with friendly relationships with their host governments and avoid those under crackdown.
+Wealthier donor personas are more likely to prefer donating to organizations that are criticized by their host governments.
+This falls in line with their preference for human rights organizations, which have more contentious missions and are more likely to be targeted.
+This support, however, evaporates as crackdown intensifies.
 High-income personas are the least likely demographic to prefer donating to NGOs under crackdown.
@@
 Patterns in preferences for issue area and funding sources remain constant across both methods of categorizing income—crackdown only has an effect on very high-income personas.
-Income thus appears to influence preferences particularly for NGOs facing criticism and crackdown abroad—wealthy donors are perhaps fair-weather friends that are more likely to pull their support when an organization's work becomes more difficult.
+Income thus appears to influence preferences particularly for NGOs facing crackdown abroad—wealthy donors are perhaps fair-weather friends that are more likely to pull their support when an organization's work becomes more difficult.
 
@@
 
-While education and religiosity are both important drivers of individual philanthropy, neither are associated with any sizable differences in persona donation patterns.
-As seen in @fig:edu-religion, preferences for issue areas are constant across both persona characteristics, with human rights and refugee relief organizations the most preferred, followed closely by emergency response organizations, regardless of levels of education or religiosity.
+While education and religiosity are both important drivers of individual philanthropy, neither are associated with any sizable differences in persona donation patterns (as seen in @fig:edu-religion).
 Human rights issues attract a slightly larger market share of personas who are college graduates or who attend religious services at least monthly, while refugee issues are more likely to attract less religious personas, but these differences are minor.
@@
 Persona preferences across different organizational relationships with host governments are also consistent across education and religiosity, with most personas preferring to donate to NGOs that enjoy friendly relations abroad.
-College graduate personas are slightly more willing to donate to organizations facing crackdown, but the difference is roughly half a percentage point.
 
@@
 
-The global crackdown on civil society and the consequent decline of official development assistance has made the role of philanthropy in sustaining INGOs clear.
-INGOs need access to multiple sources of funding, and the value of individual-level philanthropy in sustaining the operations of groups working in challenging environments is still relatively under-explored.
+The global crackdown on civil society has adversely impacted the operations of NGOs.
+It has not just resulted in net losses of income from official sources to INGOs, it has also affected how and where funds are allocated.
+We argue that individual donors can be useful in sustaining the operations of groups working in challenging environments.
+Individual donors do not use the same perfomance-based metrics as official aid donors and use heuristics to smiplify their decision-making.
+The role of trust may be important in understanding donations preferences towards INGOs working in challenging contexts.
 While trust is a difficult construct to define, the nonprofit literature conceptualizes trust as a key driver of commitment, which is shown to impact both intention to donate as well as actual donation behavior.
-When considering repressive environments and NGOs working on more difficult goals, a lack of trust could be further fueled by legal trouble with the NGO host government—a dynamic that individuals may not wish to enter with their dollars.
+With repressive environments and NGOs working on more difficult goals, a lack of trust could be further fueled by legal trouble with the NGO host government—a dynamic that individuals may not wish to enter with their dollars.
 How does trust in NGOs influence individuals' preferences to donate, especially when groups face crackdown?
@@
 Personas with low social trust tend to be wary of negative host-country relationships and strongly prefer to donate to organizations that are friendly with their host governments, while personas with high social trust are more willing to stick with legally besieged organizations.
-This could imply who donors who are the most trusting and involved could remain supportive when charities face government criticism and crackdown.
+This implies that donors who are the most trusting could remain supportive when nonprofits face government criticism and crackdown.
 The global crackdown on NGOs may also possibly sour NGOs' least trusting individual donors.
@@
 
-In addition, we find that on average, human rights organizations tend to attract personas who are wealthier, follow national and international news, and travel abroad.
-Donors who are less wealthy, follow the news less often, and do not travel, are more attracted to organizations working on less contentious like emergency response and refugee relief.
-
-The above results have important implications for NGOs as they navigate a shrinking civic space and consider the use of different frames to tailor their fundraising appeals to individual donors.
+Our results have important implications for NGOs as they navigate a shrinking civic space and consider the use of different frames to tailor their fundraising appeals to individual donors.
 Our simulation finds that at least for some kinds of personas, NGOs may benefit from publicizing when they are targets of government crackdown, including that information in their fundraising appeals.
 However, the larger challenge may be addressing the concerns of donors with low levels of trust, as they are the least likely to donate organizations facing criticism and crackdown abroad.
-More broadly, studies from a range of countries show that levels of giving are lowest for refugee and asylum organizations, as well as for overseas and development organizations.
+As @TBPrakash:2017 argue, "trust in the charity sector cannot be assumed: the sector has to demonstrate that the trust it receives is justified." (643).
+
+When considering INGOs working in different issue areas, studies from a range of countries show that levels of giving are lowest for refugee and asylum organizations.
 Rather, donors giving to international causes tend to support international disaster relief and religious groups [@RobsonHart:2020].
 However, some of the former are precisely the organizations facing crackdown.
-More research is needed to answer how these organizations can appeal to broader array of potential foreign donors to increase levels of charitable-giving towards them.
+More research is needed to answer how contentious or advocacy organizations (as opposed to service nonprofits) can appeal to broader array of potential foreign donors to increase levels of charitable-giving towards them.
 
@@
 an NGO that operates entirely in a single state), or international (INGOs).
-INGOs are composed of members from two or more countries and are organized to advance their members' international goals and provide services to citizens of other states through routine transactions with states, private actors, and international institutions [@Tarrow:2001, 12].
+INGOs are composed of members from two or more countries and are organized to advance their members' international goals and provide services to citizens of other states through transactions with states, private actors, and international institutions [@Tarrow:2001, 12].
 
@@
 
-[^phildef]: We use philanthropy to connote voluntary giving by an individual or group to promote the common good.
-While it can include grants given by foundations and corporations to nonprofit organizations, our focus here is on individual giving.
-Some perspectives see philanthropy as more of a strategic long-term practice that seeks to address the root causes of issues, and charity as a more short-term practice focused on providing immediate relief.
+[^phildef]: We use philanthropy to connote voluntary giving to promote the common good.
+While it can include grants given by foundations and corporations to nonprofit organizations, our focus is on individual giving.
+Some perspectives see philanthropy as more of a strategic long-term practice addressing the root causes of issues, and charity as a more short-term practice focused on providing immediate relief.
 But many scholars see philanthropy as essentially synonymous with charitable donations, as the latter can also address longer-term or strategic isssues [@Castle:2004].
-As such, despite these subtle differences, we use the terms inter-changeably here both because previous literature does so, and because in the case of philanthropic or charitable-giving to NGOs during crackdown, individuals could be giving to nonprofits both for immediate relief as well as long-term strategic purposes.
+Despite these subtle differences, we use the terms inter-changeably here both because previous literature does so, and because in the case of giving to NGOs during crackdown, individuals could be giving to nonprofits both for immediate relief as well as long-term strategic purposes.
 

### 2021-04-17 analysis/01_clean-generate-data.Rmd
Use targets now!

@@
   html_document:
-    code_folding: show
-    pandoc_args:
-      - "--default-image-extension=png"
+    code_folding: hide
 editor_options: 
@@
 
-```{r load-packages, warning=FALSE, message=FALSE}
-library(tidyverse)
-library(fastDummies)
-library(scales)
-library(readxl)
-library(here)
+# `targets` pipeline
 
-# Turn off grouping message
-options(dplyr.summarise.inform = FALSE)
+Here's the general process for building and running this analysis.
+This is all done with [the magical **`targets`** package](https://docs.ropensci.org/targets/), which orchestrates all the dependencies automatically.
 
-# Project-specific functions
-source(here("R", "graphics.R"))
-
-# General settings
-source(here("analysis", "options.R"))
-
-# Make all the randomness reproducible
-set.seed(1234)
+```{r show-targets-pipeline, echo=FALSE}
+withr::with_dir(here::here(), {
+  targets::tar_glimpse()
+})
 ```
 
-```{r simpler-excel-based-model, message=FALSE}
-sim_raw <- read_excel(here("data", "raw_data", "Market Simulator Version 01.xlsx"),
-                      sheet = "Results", range = "O3:AU27")
+\
 
-orgs_raw <- read_excel(here("data", "raw_data", "Market Simulator Version 01.xlsx"),
-                       sheet = "Results", range = "N4:O27", 
-                       col_names = c("organization", "org_details"))
+# Actual code
 
-orgs_clean <- orgs_raw %>% 
-  separate(org_details, into = c("org_issue", "org_funding", "org_relationship"), sep = ", ")
+All the simulation and data processing is handled with dataset-specific functions that live in `R/funs_data-generation.R`, which **`targets`** then runs as needed.
+For the sake of transparency, here's that code:
 
-personas_raw <- read_excel(here("data", "raw_data", "Market Simulator Version 01.xlsx"),
-                           sheet = "Results", range = "P2:AU3") %>% 
-  pivot_longer(everything(), names_to = "persona", values_to = "persona_details")
-
-personas_clean <- personas_raw %>% 
-  separate(persona_details, into = c("demographics", "actions", "persona_trust"), sep = ", ") %>% 
-  separate(demographics, into = c("persona_income", "persona_gender"), sep = " Income ") %>% 
-  separate(actions, into = c("persona_ideology", "persona_experience"), sep = " that ")
-
-sim_long <- sim_raw %>% 
-  rename(org_details = `...1`) %>% 
-  pivot_longer(cols = -org_details, names_to = "persona_details", values_to = "share")
-
-sim_excel_clean <- sim_long %>% 
-  left_join(orgs_raw, by = "org_details") %>% 
-  left_join(personas_raw, by = "persona_details") %>% 
-  separate(org_details, into = c("org_issue", "org_funding", "org_relationship"), sep = ", ") %>% 
-  separate(persona_details, into = c("demographics", "actions", "persona_trust"), sep = ", ") %>% 
-  separate(demographics, into = c("persona_income", "persona_gender"), sep = " Income ") %>% 
-  separate(actions, into = c("persona_ideology", "persona_experience"), sep = " that ") %>% 
-  mutate(org_issue = recode(org_issue, "Refugess Relief" = "Refugee Relief"),
-         org_funding = recode(org_funding, "Grants" = "Mostly funded by government grants",
-                              "Small Donors" = "Mostly funded by small donors"),
-         persona_income = paste(persona_income, "income"),
-         persona_income = factor(persona_income, levels = c("Lower income", "Higher income"), ordered = TRUE),
-         persona_trust = recode(persona_trust,
-                                "Doesn't Trust or Donate" = "Less trusting; donates and volunteers less often",
-                                "Trusts and Donates" = "More trusting; donates and volunteers often"),
-         persona_experience = recode(persona_experience,
-                                     "Doesn't Read or Travel" = "Doesn't follow news; has not travelled abroad",
-                                     "Reads and Travels" = "Follows the news; has travelled abroad")) %>% 
-  mutate_at(vars(organization, persona), ~fct_inorder(.))
-```
-
-```{r load-data, message=FALSE}
-# Gammas of the "everything" model
-gammas <- read_rds(
-  here('data', 'raw_data', 'posterior_draws', 'public_political_social_charity_demo.rds')
-  ) %>% 
-  group_by(i, j) %>% 
-  summarize(gamma_mean = mean(Gamma)) %>% 
-  ungroup() %>% 
-  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
-  select(-i) %>% 
-  t()
-```
-
-```{r possible-organizations}
-organization_columns <- c("organization", "issue.area", "transparency", 
-                          "accountability", "funding", "relationship")
-
-organization_possibilities <- expand_grid(
-  issue.area = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
-  relationship = c("Friendly", "Criticized", "Under crackdown"),
-  funding = c("Small private donations", "Government grants")
-) %>% 
-  mutate(org_id = paste0("org", 1:n()))
-
-organizations <- organization_possibilities %>% 
-  mutate(
-    organization = "Red Cross",
-    transparency = "Yes",
-    accountability = "Yes"
-  ) %>% 
-  select(org_id, all_of(organization_columns)) %>% 
-  mutate(organization = factor(organization, 
-                               levels = c("Amnesty International", "Greenpeace", 
-                                          "Oxfam", "Red Cross")),
-         issue.area = factor(issue.area, 
-                            levels = c("Emergency response", "Environment", 
-                                       "Human rights", "Refugee relief")),
-         transparency = factor(transparency, levels = c("No", "Yes")),
-         accountability = factor(accountability, levels = c("No", "Yes")),
-         funding = factor(funding, levels = c("Small private donations", 
-                                              "Handful of wealthy private donors", 
-                                              "Government grants")),
-         relationship = factor(relationship, levels = c("Friendly", "Criticized", 
-                                                        "Under crackdown")))
-
-org_table <- organizations %>% 
-  dummy_columns(select_columns = organization_columns,
-                remove_selected_columns = TRUE) %>% 
-  pivot_longer(cols = -org_id, names_to = "name", ) %>% 
-  pivot_wider(names_from = org_id, values_from = value) %>% 
-  separate(name, into = c("attribute", "option"), sep = "_") %>% 
-  filter(!(option %in% c("Emergency response", "No", "Small private donations", "Friendly")))
-```
-
-```{r possible-personas}
-persona_columns <- c("national.news", "international.news", "medium.follow.tv", 
-                     "medium.follow.print", "medium.follow.online", "medium.follow.social", 
-                     "medium.follow.radio", "medium.follow.email", "medium.follow.app", 
-                     "follow.govt", "travel", "ideology", "trust.institutions", 
-                     "should.be.charitable", "religious.attendance", "religion.importance", 
-                     "religion", "trust.charity.importance", "trust.charities", 
-                     "donation.frequency", "donated.last.year", "volunteered", 
-                     "volunteer.frequency", "history.activism.personal", "history.activism.family",
-                     "membership.church", "membership.sport", "membership.art", "membership.union", 
-                     "membership.party", "membership.environment", "membership.professional", 
-                     "membership.charitable", "membership.consumer", "membership.other", 
-                     "gender", "marital", "education", "income", "race", "age")
-
-persona_demographics <- expand_grid(
-  income = c("Less than median", "More than median"),
-  education = c("High school graduate", "4 year degree"),
-  religious.attendance = c("Rarely", "At least once a month")
-) %>% 
-  mutate(demographics_id = 1:n())
-
-persona_politics <- tribble(
-  ~ideology, ~national.news, ~international.news, ~travel,
-  "Extremely liberal", "At least once a day",  "Always", "Yes",
-  "Extremely conservative", "At least once a day", "Always", "Yes",
-  "Extremely liberal", "Rarely", "Never", "No",
-  "Extremely conservative", "Rarely", "Never", "No"
-) %>% 
-  mutate(politics_id = 1:n())
-
-persona_social <- tibble(
-  social_id = 1:2,
-  trust.institutions = c("Complete trust", "No trust"),
-  should.be.charitable = c("Strongly agree", "Strongly disagree"),
-  trust.charities = c("Complete trust", "No trust"),
-  volunteer.frequency = c("At least once a month", "Rarely"),
-  donation.frequency = c("At least once a month", 
-                         "More than once a month, less than once a year"),
-  history.activism.personal = c("Involved", "Not involved"),
-  membership.party = c("Active member", "Don't belong"),
-  membership.charitable = c("Active member", "Don't belong")
-)
-
-persona_possibilities <- expand_grid(
-  demographics_id = persona_demographics$demographics_id,
-  politics_id = persona_politics$politics_id,
-  social_id = persona_social$social_id
-) %>% 
-  left_join(persona_demographics, by = "demographics_id") %>% 
-  left_join(persona_politics, by = "politics_id") %>% 
-  left_join(persona_social, by = "social_id") %>% 
-  select(-ends_with("_id")) %>% 
-  mutate(persona_id = paste0("persona", 1:n()))
-
-# Columns that should be held constant
-# persona_columns %>% .[!(. %in% colnames(persona_possibilities))] %>% cat(sep = "\n")
-
-personas <- persona_possibilities %>% 
-  mutate(
-    medium.follow.tv = "Follow",
-    medium.follow.print = "Follow",
-    medium.follow.online = "Don't follow",
-    medium.follow.social = "Follow",
-    medium.follow.radio = "Don't follow",
-    medium.follow.email = "Don't follow",
-    medium.follow.app = "Don't follow",
-    follow.govt = "Often",
-    religion.importance = "Important",
-    religion = "Protestant",
-    trust.charity.importance = "Somewhat important",
-    donated.last.year = "$100-$499",
-    volunteered = "No",
-    history.activism.family = "Not involved",
-    membership.church = "Don't belong",
-    membership.sport = "Don't belong",
-    membership.art = "Don't belong",
-    membership.union = "Don't belong",
-    membership.environment = "Don't belong",
-    membership.professional = "Don't belong",
-    membership.consumer = "Don't belong",
-    membership.other = "Don't belong",
-    gender = "Male",
-    marital = "Married",
-    race = "White",
-    age = "Less than median"
-  ) %>% 
-  select(persona_id, all_of(persona_columns)) %>% 
-  mutate(
-    national.news = factor(national.news, levels = c("Rarely", "Once a week", "At least once a day")),
-    international.news = factor(international.news, levels = c("Never", "Sometimes", "Always")),
-    medium.follow.tv = factor(medium.follow.tv, levels = c("Don't follow", "Follow")),
-    medium.follow.print = factor(medium.follow.print, levels = c("Don't follow", "Follow")),
-    medium.follow.online = factor(medium.follow.online, levels = c("Don't follow", "Follow")),
-    medium.follow.social = factor(medium.follow.social, levels = c("Don't follow", "Follow")),
-    medium.follow.radio = factor(medium.follow.radio, levels = c("Don't follow", "Follow")),
-    medium.follow.email = factor(medium.follow.email, levels = c("Don't follow", "Follow")),
-    medium.follow.app = factor(medium.follow.app, levels = c("Don't follow", "Follow")),
-    follow.govt = factor(follow.govt, levels = c("Not often", "Often")),
-    travel = factor(travel, levels = c("No", "Yes")),
-    ideology = factor(ideology, 
-                      levels = c("Extremely liberal", "Somewhat liberal", 
-                                 "Slightly liberal", "Moderate", "Slightly conservative", 
-                                 "Somewhat conservative", "Extremely conservative")),
-    trust.institutions = factor(trust.institutions,
-                                levels = c("No trust", "Very little trust", "Little trust", 
-                                           "Neutral", "Some trust", "A lot of trust", "Complete trust")),
-    should.be.charitable = factor(should.be.charitable,
-                                  levels = c("Strongly disagree", "Disagree", "Somewhat disagree", 
-                                             "Neutral", "Somewhat agree", "Agree", "Strongly agree")),
-    religious.attendance = factor(religious.attendance,
-                                  levels = c("Not sure", "Rarely", "At least once a month")),
-    religion.importance = factor(religion.importance,
-                                 levels = c("Not important", "Important")),
-    religion = factor(religion, 
-                      levels = c("Catholic", "Protestant", "Christian Orthodox", "Jewish", 
-                                 "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")),
-    trust.charity.importance = factor(trust.charity.importance,
-                                      levels = c("Not important", "Very unimportant", 
-                                                 "Somewhat unimportant", "Neutral", 
-                                                 "Somewhat important", "Very important", "Essential")),
-    trust.charities = factor(trust.charities,
-                             levels = c("No trust", "Very little trust", "Little trust", 
-                                        "Neutral", "Some trust", "A lot of trust", "Complete trust")),
-    donation.frequency = factor(donation.frequency,
-                                levels = c("More than once a month, less than once a year", "At least once a month")),
-    donated.last.year = factor(donated.last.year,
-                               levels = c("$1-$49", "$50-$99", "$100-$499", "$500-$999", 
-                                          "$1000-$4,999", "$5000-$9,999", "$10,000+")),
-    volunteered = factor(volunteered, levels = c("No", "Yes")),
-    volunteer.frequency = factor(volunteer.frequency,
-                                 levels = c("Haven't volunteered in past 12 months", "Rarely", 
-                                            "More than once a month, less than once a year", 
-                                            "At least once a month")),
-    history.activism.personal = factor(history.activism.personal,
-                                       levels = c("Not involved", "Involved")),
-    history.activism.family = factor(history.activism.family,
-                                     levels = c("Not involved", "Involved")),
-    membership.church = factor(membership.church,
-                               levels  = c("Don't belong", "Inactive member", "Active member")),
-    membership.sport = factor(membership.sport,
-                              levels = c("Don't belong", "Inactive member", "Active member")),
-    membership.art = factor(membership.art,
-                            levels = c("Don't belong", "Inactive member", "Active member")),
-    membership.union = factor(membership.union,
-                              levels = c("Don't belong", "Inactive member", "Active member")),
-    membership.party = factor(membership.party,
-                              levels = c("Don't belong", "Inactive member", "Active member")),
-    membership.environment = factor(membership.environment,
-                                    levels = c("Don't belong", "Inactive member", "Active member")),
-    membership.professional = factor(membership.professional,
-                                     levels  = c("Don't belong", "Inactive member", "Active member")),
-    membership.charitable = factor(membership.charitable,
-                                   levels  = c("Don't belong", "Inactive member", "Active member")),
-    membership.consumer = factor(membership.consumer,
-                                 levels  = c("Don't belong", "Inactive member", "Active member")),
-    membership.other = factor(membership.other,
-                              levels = c("Don't belong", "Inactive member", "Active member")),
-    gender = factor(gender,
-                    levels = c("Male", "Female", "Transgender", "Prefer not to say", "Other")),
-    marital = factor(marital,
-                     levels = c("Married", "Widowed", "Divorced", "Separated", "Never married")),
-    education = factor(education,
-                       levels = c("Less than high school", "High school graduate", "Some college", 
-                                  "2 year degree", "4 year degree", "Graduate or professional degree", "Doctorate")),
-    income = factor(income,
-                    levels = c("Less than median", "More than median")),
-    race = factor(race,
-                  levels = c("White", "Black or African American", "American Indian or Alaska Native", 
-                             "Asian", "Native Hawaiian or Pacific Islander", "Other")),
-    age = factor(age,
-                 levels = c("Less than median", "More than median"))
-  )
-
-persona_base_cases <- c(
-  "national.news_Rarely",
-  "international.news_Never",
-  "follow.govt_Not often",
-  "travel_No",
-  "ideology_Extremely liberal",
-  "trust.institutions_No trust",
-  "should.be.charitable_Strongly disagree",
-  "religious.attendance_Not sure",
-  "religion.importance_Not important",
-  "religion_Catholic",
-  "trust.charity.importance_Not important",
-  "trust.charities_No trust",
-  "donation.frequency_More than once a month, less than once a year",
-  "donated.last.year_$1-$49",
-  "volunteered_No",
-  "volunteer.frequency_Haven't volunteered in past 12 months",
-  "history.activism.personal_Not involved",
-  "history.activism.family_Not involved",
-  "gender_Male",
-  "marital_Married",
-  "education_Less than high school",
-  "income_Less than median",
-  "age_Less than median"
-)
-
-persona_table <- personas %>% 
-  dummy_columns(select_columns = persona_columns,
-                remove_selected_columns = TRUE) %>% 
-  pivot_longer(cols = -persona_id, names_to = "name", ) %>% 
-  pivot_wider(names_from = persona_id, values_from = value) %>% 
-  # Get rid of base cases
-  filter(!(name %in% persona_base_cases)) %>% 
-  filter(!str_detect(name, "Don't follow"),
-         !str_detect(name, "Don't belong")) %>% 
-  separate(name, into = c("attribute", "option"), sep = "_") %>% 
-  # Add intercept
-  add_row(attribute = "Intercept", option = "Intercept", .before = 1) %>% 
-  mutate(across(everything(), ~replace_na(., 1)))
-```
-
-```{r predicted-market-shares}
-predicted_betas <- persona_table %>% 
-  summarize(across(starts_with("persona"), ~as.matrix(gammas) %*% as.matrix(.)))
-
-expected_utilities <- exp(t(org_table[,3:ncol(org_table)]) %*% 
-                            as.matrix(predicted_betas[,1:ncol(predicted_betas)])) %>% 
-  as_tibble(rownames = "org")
-
-prop_expected_utilities <- expected_utilities %>% 
-  mutate(across(starts_with("persona"), ~. / sum(.)))
-```
-
-```{r finalize-data}
-org_details <- organizations %>% 
-  mutate(organization = str_replace(org_id, "org", "Org "),
-         funding = fct_recode(funding, 
-                              "Mostly funded by small donors" = "Small private donations",
-                              "Mostly funded by government grants" = "Government grants"),
-         relationship = fct_rev(relationship)) %>%
-  select(org_id, organization, org_issue = issue.area, 
-         org_funding = funding, org_relationship = relationship)
-
-persona_details <- personas %>% 
-  mutate(persona_income = fct_recode(income, 
-                                     "Lower income" = "Less than median", 
-                                     "Higher income" = "More than median"),
-         persona_education = fct_recode(education, "College graduate" = "4 year degree"),
-         persona_religion = fct_recode(religious.attendance, 
-                                       "Rarely attends religious services" = "Rarely",
-                                       "Attends at least monthly" = "At least once a month"),
-         persona_ideology = fct_recode(ideology, 
-                                       "Conservative" = "Extremely conservative",
-                                       "Liberal" = "Extremely liberal"),
-         persona_experience = ifelse(travel == "Yes", 
-                                     "Follows the news; has travelled abroad", 
-                                     "Doesn't follow news; has not travelled abroad"),
-         persona_trust = ifelse(trust.charities == "Complete trust", 
-                                "More trusting; donates and volunteers often", 
-                                "Less trusting; donates and volunteers less often")) %>% 
-  mutate(persona = str_replace(persona_id, "persona", "Persona ")) %>% 
-  select(persona, starts_with("persona"))
-
-sim_clean <- prop_expected_utilities %>% 
-  pivot_longer(cols = -org, names_to = "persona_id", values_to = "share") %>% 
-  left_join(org_details, by = c("org" = "org_id")) %>% 
-  left_join(persona_details, by = "persona_id")
-```
-
-```{r save-clean-data}
-write_rds(sim_excel_clean, here("data", "derived_data", "sim_excel_final.rds"))
-write_rds(sim_clean, here("data", "derived_data", "sim_final.rds"))
+```{r, code=xfun::read_utf8(here::here("R", "funs_data-generation.R")), eval=FALSE, class.source="fold-show"}
 ```

### 2021-04-17 analysis/02_tables.Rmd
Use targets now!

@@
     code_folding: hide
-    pandoc_args:
-      - "--default-image-extension=png"
 editor_options: 
@@
 
-```{r packages, warning=FALSE, message=FALSE, include=FALSE}
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(fig.retina = 3,
+                      tidy.opts = list(width.cutoff = 120),  # For code
+                      options(width = 90),  # For output
+                      fig.asp = 0.618, fig.width = 7, 
+                      fig.align = "center", out.width = "85%")
+
+options(dplyr.summarise.inform = FALSE,
+        knitr.kable.NA = "")
+```
+
+```{r load-libraries-data, message=FALSE, warning=FALSE}
 library(tidyverse)
-library(pander)
-library(magrittr)
+library(targets)
+library(kableExtra)
 library(glue)
@@
 library(here)
-```
 
-```{r load-data}
-sim_clean <- read_rds(here("data", "derived_data", "sim_final.rds"))
-results <- read_rds(here("data", "raw_data", "final_data.rds"))
+# Generated via random.org
+set.seed(8316)
 
-org_attributes <- tribble(
-  ~`Issue area`, ~`Relationship with government`, ~`Funding`, ~`Funding sources`, ~`Organizational practices`, ~`Organization`,
-  "Emergency response", "Friendly", "Small private donors", "Small private donors", "Financial transparency", "Amnesty International",
-  "Environment", "Criticized", "Government grants", "Wealthy donors", "Accountability", "Greenpeace",
-  "Human rights", "Crackdown", "", "Government grants", "", "Oxfam",
-  "Refugee relief", "", "", "", "", "Red Cross"
-)
-
-persona_attributes <- tribble(
-  ~`Demographics`, ~`Politics and public affairs`, ~`Social views`,
-  "Higher income (> US median ($61,372)), high school graduate, frequent religious attendance", "Liberal (1), follows national and international news often, has traveled internationally", "High social trust: Trusts political institutions, trusts charities, thinks people should be more charitable, frequently volunteers, donates once a month, has a history of personal activism, is a member of an association",
-  "Lower income (< US median), high school graduate, frequent religious attendance", "Conservative (7), follows news, has traveled", "Low social trust: Does not trust political institutions or charities, thinks people should be less charitable, does not volunteer or donate often, has no history of personal activism, is not a member of an association",
-  "Higher income, college graduate, frequent religious attendance", "Liberal, does not follow news, has not traveled", "",
-  "Lower income, college graduate, frequent religious attendance", "Conservative, does not follow news, has not traveled", "",
-  "Higher income, high school graduate, rare religious attendance", "", "",
-  "Lower income, high school graduate, rare religious attendance", "", "",
-  "Higher income, college graduate, rare religious attendance", "", "",
-  "Lower income, college graduate, rare religious attendance", "", ""
-)
+# Load data
+# Need to use this withr thing because tar_read() and tar_load() need to see the
+# _targets folder in the current directory, but this .Rmd file is in a subfolder
+withr::with_dir(here::here(), {
+  tar_load(personas)
+  tar_load(orgs)
+  tar_load(sim_final)
+  tar_load(survey_results)
+  tar_load(participant_summary)
+})
 ```
@@
 
-```{r results="asis"}
-org_attributes %>% 
+```{r organization-attributes-full}
+orgs$org_attributes %>% 
   select(Organization, `Issue area`, `Organizational practices`, `Funding sources`, `Relationship with government`) %>% 
-  pandoc.table.return(caption = 'Organization attributes varied in the experiment {#tbl:organization-attributes-full}',
-                      justify = "lllll", split.tables = Inf) %T>%
-  cat() %>%
-  cat(file = here("analysis", "output", "tables", "tbl-organization-attributes-full.md"))
+  kbl(align = "lllll",
+      caption = "Organization attributes varied in the experiment") %>% 
+  kable_styling()
 ```
@@
 
-```{r results="asis"}
-org_attributes %>% 
+```{r organization-attributes}
+orgs$org_attributes %>% 
   select(`Issue area`, `Relationship with government`, `Funding`) %>% 
-  pandoc.table.return(caption = 'Organization attributes varied in the simulation, resulting in 24 hypothetical organizations {#tbl:organization-attributes}',
-                      justify = "lll") %T>%
-  cat() %>%
-  cat(file = here("analysis", "output", "tables", "tbl-organization-attributes.md"))
+  kbl(align = "lll",
+      caption = "Organization attributes varied in the simulation, resulting in 24 hypothetical organizations") %>% 
+  kable_styling()
 ```
@@
 
-```{r results="asis"}
-persona_attributes %>% 
-  pandoc.table.return(caption = 'Individual attributes varied in the simulation, resulting in 64 persona profiles {#tbl:persona-attributes}',
-                      justify = "lll", split.tables = Inf) %T>%
-  cat() %>%
-  cat(file = here("analysis", "output", "tables", "tbl-persona-attributes.md"))
+```{r persona-attributes}
+personas$persona_attributes %>% 
+  kbl(align = "lll",
+      caption = "Individual attributes varied in the simulation, resulting in 64 persona profiles") %>% 
+  kable_styling()
 ```
@@
 
-```{r results="asis"}
+```{r example-personas}
 example_personas <- c("persona2", "persona63")
 
-example_persona_details <- sim_clean %>%
+example_persona_details <- sim_final %>%
   filter(persona_id %in% example_personas) %>% 
@@
   select(-name) %>% 
-  pandoc.table(justify = "ll")
+  kbl(align = "ll",
+      caption = "Example personas") %>% 
+  kable_styling()
 ```
 
-```{r results="asis"}
-example_persona_results <- sim_clean %>% 
+```{r sim-output}
+example_persona_results <- sim_final %>% 
   filter(persona_id %in% example_personas) %>% 
@@
   pivot_wider(names_from = "persona_clean", values_from = "share") %>% 
-  adorn_totals(where = "row", name = "**Total**")
+  adorn_totals(where = "row", name = "Total")
 
@@
 example_persona_results_small %>% 
-  pandoc.table.return(caption = 'Sample simulation output {#tbl:sim-output}',
-                      justify = "lcc", split.tables = Inf) %T>%
-  cat() %>%
-  cat(file = here("analysis", "output", "tables", "tbl-sim-output.md"))
+  mutate(Organization = text_spec(Organization, bold = Organization == "Total")) %>% 
+  kbl(align = "lcc",
+      caption = "Sample simulation output",
+      escape = FALSE) %>% 
+  kable_styling()
 ```
@@
 
-```{r}
-vars_to_summarize <- tribble(
-  ~category, ~variable, ~clean_name,
-  "Demographics", "Q5.12", "Gender",
-  "Demographics", "Q5.17", "Age",
-  "Demographics", "Q5.13", "Marital status",
-  "Demographics", "Q5.14", "Education",
-  "Demographics", "Q5.15", "Income",
-  "Attitudes toward charity", "Q2.5", "Frequency of donating to charity",
-  "Attitudes toward charity", "Q2.6", "Amount of donations to charity last year",
-  "Attitudes toward charity", "Q2.7_f", "Importance of trusting charities",
-  "Attitudes toward charity", "Q2.8_f", "Level of trust in charities",
-  "Attitudes toward charity", "Q2.10", "Frequency of volunteering",
-  "Politics, ideology, and religion", "Q2.1", "Frequency of following national news",
-  "Politics, ideology, and religion", "Q5.7", "Traveled to a developing country",
-  "Politics, ideology, and religion", "Q5.1", "Voted in last election",
-  "Politics, ideology, and religion", "Q5.6_f", "Trust in political institutions and the state",
-  "Politics, ideology, and religion", "Q5.2_f", "Political ideology",
-  "Politics, ideology, and religion", "Q5.4", "Involvement in activist causes",
-  "Politics, ideology, and religion", "Q5.8", "Frequency of attending religious services",
-  "Politics, ideology, and religion", "Q5.9", "Importance of religion"
-)
-
-summarize_factor <- function(x) {
-  output <- table(x) %>% 
-    as_tibble() %>% 
-    magrittr::set_colnames(., c("level", "count")) %>% 
-    mutate(level = factor(level, levels = levels(x))) %>%
-    mutate(prop = count / sum(count),
-           nice_prop = scales::percent(prop))
-
-  return(list(output))
-}
-
-participant_summary <- results %>% 
-  select(one_of(vars_to_summarize$variable)) %>% 
-  summarize_all(summarize_factor) %>% 
-  pivot_longer(cols = everything(), names_to = "variable", values_to = "details") %>% 
-  left_join(vars_to_summarize, by = "variable") %>% 
-  unnest(details) %>% 
-  mutate(level = as.character(level)) %>% 
-  mutate(level = case_when(
-    variable == "Q2.7_f" & level == "1" ~ "1 (not important)",
-    variable == "Q2.7_f" & level == "7" ~ "7 (important)",
-    variable == "Q2.8_f" & level == "1" ~ "1 (no trust)",
-    variable == "Q2.8_f" & level == "7" ~ "7 (complete trust)",
-    variable == "Q5.6_f" & level == "1" ~ "1 (no trust)",
-    variable == "Q5.6_f" & level == "7" ~ "7 (complete trust)",
-    variable == "Q5.2_f" & level == "1" ~ "1 (extremely liberal)",
-    variable == "Q5.2_f" & level == "7" ~ "7 (extremely conservative)",
-    variable == "Q5.15" & level == "Less than median" ~ "Less than 2017 national median ($61,372)",
-    variable == "Q5.17" & level == "Less than median" ~ "Less than 2017 national median (36)",
-    TRUE ~ level
-  )) %>% 
-  mutate(clean_name_shrunk = ifelse(clean_name == lag(clean_name), "", clean_name),
-         clean_name_shrunk = ifelse(is.na(clean_name_shrunk), 
-                                    clean_name[1], 
-                                    clean_name_shrunk),
-         category_shrunk = ifelse(category == lag(category), "", category),
-         category_shrunk = ifelse(is.na(category_shrunk), 
-                                    category[1], 
-                                    category_shrunk))
-```
-
-```{r results="asis"}
+```{r sample-details}
 participant_summary %>% 
-  select("Category" = category_shrunk, "Question" = clean_name_shrunk, 
-         "Response" = level, "N" = count, "%" = nice_prop) %>% 
-  pandoc.table.return(caption = 'Summary of individual respondent characteristics {#tbl:sample-details}',
-                      justify = "lllcc", split.tables = Inf) %T>%
-  cat() %>%
-  cat(file = here("analysis", "output", "tables", "tbl-sample-details.md"))
+  select(Question = clean_name,
+         Response = level,
+         N = count,
+         `%` = nice_prop) %>% 
+  kbl(align = "lllcc",
+      caption = "Summary of individual respondent characteristics") %>% 
+  pack_rows(index = table(fct_inorder(participant_summary$category))) %>%
+  collapse_rows(columns = 1, valign = "top") %>% 
+  kable_styling()
 ```

### 2021-04-17 analysis/03_analysis.Rmd
Use targets now!

--- 2020-09-29 analysis/03_analysis.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(fig.retina = 3, fig.align = "center")
+knitr::opts_chunk$set(fig.retina = 3,
+                      tidy.opts = list(width.cutoff = 120),  # For code
+                      options(width = 90),  # For output
+                      fig.asp = 0.618, fig.width = 7, 
+                      fig.align = "center", out.width = "85%")
+
+options(dplyr.summarise.inform = FALSE,
+        knitr.kable.NA = "")
 ```
 
-```{r load-packages, warning=FALSE, message=FALSE}
+```{r load-libraries-data, message=FALSE, warning=FALSE}
 library(tidyverse)
-library(fastDummies)
+library(targets)
 library(scales)
@@
 
-# Turn off grouping message
-options(dplyr.summarise.inform = FALSE)
+# Generated via random.org
+set.seed(8316)
 
-# Project-specific functions
-source(here("R", "graphics.R"))
+# Load data
+# Need to use this withr thing because tar_read() and tar_load() need to see the
+# _targets folder in the current directory, but this .Rmd file is in a subfolder
+withr::with_dir(here::here(), {
+  source(tar_read(plot_funs))
 
-# General settings
-source(here("analysis", "options.R"))
-
-# Make all the randomness reproducible
-set.seed(1234)
-```
-
-```{r load-data}
-sim_excel_clean <- read_rds(here("data", "derived_data", "sim_excel_final.rds"))
-sim_clean <- read_rds(here("data", "derived_data", "sim_final.rds"))
+  tar_load(sim_excel_final)
+  tar_load(sim_final)
+  tar_load(giving_aggregate)
+  tar_load(giving_per_capita)
+})
 ```
@@
 
-```{r giving-usa-data, message=FALSE}
-giving_aggregate_raw <- read_csv(here("data", "raw_data", "data-FTjUv.csv"))
-
-giving_aggregate <- giving_aggregate_raw %>% 
-  mutate(total = `Total donations` * 1000000000)
-
-giving_per_capita_raw <- read_csv(here("data", "raw_data", "data-xextT.csv"))
-
-giving_per_capita <- giving_per_capita_raw
-```
-
 ## Total giving
 
-```{r plot-total-giving, fig.width=4, fig.height=2.4}
+```{r plot-total-giving, fig.width=4, fig.height=2.4, fig.asp=NULL, out.width="60%"}
 ggplot(giving_aggregate, aes(x = Year, y = `Total donations`)) +
-  geom_line(size = 1, color = clrs$maroon) +
+  geom_line(size = 1, color = clrs_okabe_ito$orange) +
   scale_x_continuous(breaks = seq(1980, 2015, 5)) +
@@
   labs(x = NULL, y = "Billions of dollars") + 
-  theme_ngo(9)
-
-ggsave(here("analysis", "output", "figures", "giving_aggregate.pdf"), 
-       width = 4, height = 2.4, units = "in", device = cairo_pdf)
-ggsave(here("analysis", "output", "figures", "giving_aggregate.png"), 
-       width = 4, height = 2.4, units = "in", type = "cairo", dpi = 300)
+  theme_ngo()
 ```
@@
 
-```{r plot-per-capita-giving, fig.width=6, fig.height=3.6}
+```{r plot-per-capita-giving, fig.width=4, fig.height=2.4, fig.asp=NULL, out.width="60%"}
 ggplot(giving_per_capita, aes(x = Year, y = `Average giving`)) +
-  geom_line(size = 1, color = clrs$green) +
+  geom_line(size = 1, color = clrs_okabe_ito$sky_blue) +
   scale_x_continuous(breaks = seq(2000, 2014, 2)) +
@@
 
-```{r income-issue-funding-relationship, fig.width=6.5, fig.height=4.75}
-plot_income_issue <- sim_clean %>% 
+```{r income-issue-funding-relationship, fig.width=6, fig.height=4.5, fig.asp=NULL, out.width="100%"}
+plot_income_issue <- sim_final %>% 
   group_by(org_issue, persona_income) %>% 
@@
   mutate(facet = "Issue area") %>% 
-  ggplot(aes(y = fct_rev(org_issue), x = avg_share, color = fct_rev(persona_income))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)),
+             x = avg_share, color = fct_rev(persona_income))) +
+  geom_pointrange(size = 0.75, fatten = 1.5,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002)),
                      breaks = seq(0, 0.06, 0.02)) +
-  scale_color_manual(values = c(clrs$green, clrs$blue), guide = FALSE) +
+  scale_color_manual(values = clrs_ngo_pairs[[1]], guide = FALSE) +
   coord_cartesian(xlim = c(0, 0.06)) +
@@
 
-plot_income_funding <- sim_clean %>% 
+plot_income_funding <- sim_final %>% 
   group_by(org_funding, persona_income) %>% 
@@
   mutate(facet = "Funding sources") %>% 
-  ggplot(aes(y = str_wrap(fct_rev(org_funding), 10), 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_funding, 10)), 
              x = avg_share, color = fct_rev(persona_income))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  geom_pointrange(size = 0.75, fatten = 1.5,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
   coord_cartesian(xlim = c(0, 0.06)) +
-  scale_color_manual(values = c(clrs$green, clrs$blue), guide = FALSE) +
+  scale_color_manual(values = clrs_ngo_pairs[[1]], guide = FALSE) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
 
-plot_income_relationship <- sim_clean %>% 
+plot_income_relationship <- sim_final %>% 
   mutate(persona_income = fct_recode(persona_income,
@@
   mutate(facet = "Relationship with host government") %>% 
-  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = fct_rev(persona_income))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) +
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
+             x = avg_share, color = fct_rev(persona_income))) +
+  geom_pointrange(size = 0.75, fatten = 1.5, 
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) +
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.003))) +
   coord_cartesian(xlim = c(0, 0.1)) +
-  scale_color_manual(values = c(clrs$green, clrs$blue), 
-                     guide = guide_legend(reverse = TRUE, nrow = 1)) +
+  scale_color_manual(values = clrs_ngo_pairs[[1]], 
+                     guide = guide_legend(reverse = TRUE, nrow = 1,
+                                          override.aes = list(size = 0.25,
+                                                              linetype = 0))) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
   theme_ngo() +
-  theme(panel.grid.major.y = element_blank())
+  theme(panel.grid.major.y = element_blank(),
+        legend.key.width = unit(0.5, "lines"))
 
-plot_income_relationship_extreme <- sim_excel_clean %>% 
+plot_income_relationship_extreme <- sim_excel_final %>% 
   mutate(persona_income = fct_recode(persona_income,
@@
   mutate(facet = "Relationship with host government") %>% 
-  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = fct_rev(persona_income))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
+             x = avg_share, color = fct_rev(persona_income))) +
+  geom_pointrange(size = 0.75, fatten = 1.5, linetype = "21", pch = 2,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
   coord_cartesian(xlim = c(0, 0.1)) +
-  scale_color_manual(values = c(colorspace::darken(clrs$green, 0.4), 
-                                colorspace::darken(clrs$blue, 0.6)), 
-                     guide = guide_legend(reverse = TRUE, nrow = 1)) +
+  scale_color_manual(values = clrs_ngo_pairs[[1]], 
+                     guide = guide_legend(reverse = TRUE, nrow = 1,
+                                          override.aes = list(size = 0.25, 
+                                                              linetype = 0))) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
   theme_ngo() +
-  theme(panel.grid.major.y = element_blank())
+  theme(panel.grid.major.y = element_blank(),
+        legend.key.width = unit(0.5, "lines"))
 
-plot_income <- plot_income_issue + plot_income_funding + 
-  plot_income_relationship + plot_income_relationship_extreme +
-  plot_layout(nrow = 2)
+plot_income <- ((plot_income_issue + labs(x = NULL)) + 
+  (plot_income_funding + labs(x = NULL))) / 
+  (plot_income_relationship + plot_income_relationship_extreme)
 
 plot_income
-ggsave(plot_income, filename = here("analysis", "output", "figures", "income-all.pdf"),
-       width = 6.5, height = 4.75, units = "in", device = cairo_pdf)
-ggsave(plot_income, filename = here("analysis", "output", "figures", "income-all.png"),
-       width = 6.5, height = 4.75, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
-```{r edu-issue-funding-relationship, fig.width=5, fig.height=4.25}
-plot_education_issue <- sim_clean %>% 
+```{r edu-issue-funding-relationship, fig.width=8, fig.height=2.75, fig.asp=NULL, out.width="100%"}
+plot_education_issue <- sim_final %>% 
   group_by(org_issue, persona_education) %>% 
@@
   mutate(facet = "Issue area") %>% 
-  ggplot(aes(y = fct_rev(org_issue), x = avg_share, color = fct_rev(persona_education))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)), 
+             x = avg_share, color = fct_rev(persona_education))) +
+  geom_pointrange(size = 0.75, fatten = 1.5,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
   coord_cartesian(xlim = c(0, 0.06)) +
-  scale_color_manual(values = c(clrs$orange, clrs$purple), guide = FALSE) +
+  scale_color_manual(values = clrs_ngo_pairs[[2]], guide = FALSE) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
 
-plot_education_funding <- sim_clean %>% 
+plot_education_funding <- sim_final %>% 
   group_by(org_funding, persona_education) %>% 
@@
   mutate(facet = "Funding sources") %>% 
-  ggplot(aes(y = str_wrap(fct_rev(org_funding), 10), 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_funding, 10)), 
              x = avg_share, color = fct_rev(persona_education))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  geom_pointrange(size = 0.75, fatten = 1.5,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
   coord_cartesian(xlim = c(0, 0.06)) +
-  scale_color_manual(values = c(clrs$orange, clrs$purple), guide = FALSE) +
+  scale_color_manual(values = clrs_ngo_pairs[[2]], guide = FALSE) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
 
-plot_education_relationship <- sim_clean %>% 
+plot_education_relationship <- sim_final %>% 
   group_by(org_relationship, persona_education) %>% 
@@
   mutate(facet = "Relationship with host government") %>% 
-  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = fct_rev(persona_education))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)),
+             x = avg_share, color = fct_rev(persona_education))) +
+  geom_pointrange(size = 0.75, fatten = 1.5,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
   coord_cartesian(xlim = c(0, 0.1)) +
-  scale_color_manual(values = c(clrs$orange, clrs$purple), 
-                     guide = guide_legend(reverse = TRUE, ncol = 1)) +
+  scale_color_manual(values = clrs_ngo_pairs[[2]], 
+                     guide = guide_legend(reverse = TRUE, ncol = 1,
+                                          override.aes = list(size = 0.25,
+                                                              linetype = 0)),
+                     labels = label_wrap(15)) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
   theme_ngo() +
-  theme(panel.grid.major.y = element_blank())
+  theme(panel.grid.major.y = element_blank(),
+        legend.key.width = unit(0.5, "lines"))
 
@@
 
-```{r religion-issue-funding-relationship, fig.width=5, fig.height=4.25}
-plot_religion_issue <- sim_clean %>% 
+```{r religion-issue-funding-relationship, fig.width=8, fig.height=2.75, fig.asp=NULL, out.width="100%"}
+plot_religion_issue <- sim_final %>% 
   group_by(org_issue, persona_religion) %>% 
@@
   mutate(facet = "Issue area") %>% 
-  ggplot(aes(y = fct_rev(org_issue), x = avg_share, color = fct_rev(persona_religion))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)), 
+             x = avg_share, color = fct_rev(persona_religion))) +
+  geom_pointrange(size = 0.75, fatten = 1.5, pch = 17,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
   coord_cartesian(xlim = c(0, 0.06)) +
-  scale_color_manual(values = c(clrs$red, clrs$navy), guide = FALSE) +
+  scale_color_manual(values = clrs_ngo_pairs[[4]], guide = FALSE) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
 
-plot_religion_funding <- sim_clean %>% 
+plot_religion_funding <- sim_final %>% 
   group_by(org_funding, persona_religion) %>% 
@@
   mutate(facet = "Funding sources") %>% 
-  ggplot(aes(y = str_wrap(fct_rev(org_funding), 10), 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_funding, 10)), 
              x = avg_share, color = fct_rev(persona_religion))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  geom_pointrange(size = 0.75, fatten = 1.5, pch = 17,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
   coord_cartesian(xlim = c(0, 0.06)) +
-  scale_color_manual(values = c(clrs$red, clrs$navy), guide = FALSE) +
+  scale_color_manual(values = clrs_ngo_pairs[[4]], guide = FALSE) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
 
-plot_religion_relationship <- sim_clean %>% 
+plot_religion_relationship <- sim_final %>% 
   group_by(org_relationship, persona_religion) %>% 
@@
   mutate(facet = "Relationship with host government") %>% 
-  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = fct_rev(persona_religion))) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
+             x = avg_share, color = fct_rev(persona_religion))) +
+  geom_pointrange(size = 0.75, fatten = 1.5, pch = 17,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
   scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
   coord_cartesian(xlim = c(0, 0.1)) +
-  scale_color_manual(values = c(clrs$red, clrs$navy), 
-                     guide = guide_legend(reverse = TRUE, ncol = 1)) +
+  scale_color_manual(values = clrs_ngo_pairs[[4]], 
+                     guide = guide_legend(reverse = TRUE, ncol = 1,
+                                          override.aes = list(size = 0.25,
+                                                              linetype = 0)),
+                     labels = label_wrap(20)) +
   labs(x = "Average donation share", y = NULL, color = NULL) +
@@
   plot_religion_relationship + guide_area() +
-  plot_layout(guides = "collect", ncol = 2)
+  plot_layout(guides = "collect", ncol = 4)
 plot_religion
+```
 
-ggsave(plot_religion, filename = here("analysis", "output", "figures", "religion-all.pdf"),
-       width = 5, height = 4.25, units = "in", device = cairo_pdf)
-ggsave(plot_religion, filename = here("analysis", "output", "figures", "religion-all.png"),
-       width = 5, height = 4.25, units = "in", type = "cairo", dpi = 300)
+## Education and religion across issue area, funding, and relationship
+
+```{r education-religion-issue-funding-relationship, fig.width=6, fig.height=4.5, fig.asp=NULL, out.width="100%"}
+plot_education_religion <- (plot_education_issue + labs(x = NULL)) + 
+  (plot_education_funding + labs(x = NULL)) + 
+  (plot_education_relationship + labs(x = NULL)) + 
+  guide_area() +
+  plot_religion_issue + 
+  plot_religion_funding + 
+  plot_religion_relationship +
+  plot_layout(guides = "collect", ncol = 4)
+
+plot_education_religion
 ```
@@
 
-```{r trust-issues}
-plot_issue_social <- sim_clean %>% 
+```{r trust-issues, fig.width=6, fig.height=4, fig.asp=NULL, out.width="100%"}
+plot_issue_social <- sim_final %>% 
   group_by(org_issue, persona_trust, persona_ideology, persona_experience) %>% 
   summarize(avg_share = mean(share)) %>% 
-  ggplot(aes(y = fct_rev(org_issue), x = avg_share, color = persona_trust)) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
-  scale_x_continuous(labels = percent) +
-  scale_color_manual(values = c(clrs$orange, clrs$navy), guide = guide_legend(reverse = TRUE)) +
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)), 
+             x = avg_share, color = persona_trust)) +
+  geom_pointrange(size = 0.75, fatten = 1.5, 
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+  scale_color_manual(values = clrs_ngo_pairs[[3]], 
+                     guide = guide_legend(reverse = TRUE,
+                                          override.aes = list(size = 0.25,
+                                                              linetype = 0))) +
   labs(x = "Average share of donations", y = NULL, color = NULL) +
@@
   theme_ngo() +
-  theme(panel.grid.major.y = element_blank())
+  theme(panel.grid.major.y = element_blank(),
+        legend.key.width = unit(0.5, "lines"))
 
 plot_issue_social
-ggsave(plot_issue_social, filename = here("analysis", "output", "figures", "issue-social.pdf"),
-       width = 6, height = 4.2, units = "in", device = cairo_pdf)
-ggsave(plot_issue_social, filename = here("analysis", "output", "figures", "issue-social.png"),
-       width = 6, height = 4.2, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
-```{r trust-relationship}
-plot_relationship_social <- sim_clean %>% 
+```{r trust-relationship, fig.width=6, fig.height=4, fig.asp=NULL, out.width="100%"}
+plot_relationship_social <- sim_final %>% 
   group_by(org_relationship, persona_trust, persona_ideology, persona_experience) %>% 
   summarize(avg_share = mean(share)) %>% 
-  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = persona_trust)) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
-  scale_x_continuous(labels = percent) +
-  scale_color_manual(values = c(clrs$orange, clrs$navy), guide = guide_legend(reverse = TRUE)) +
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
+             x = avg_share, color = persona_trust)) +
+  geom_pointrange(size = 0.75, fatten = 1.5,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+  scale_color_manual(values = clrs_ngo_pairs[[3]], 
+                     guide = guide_legend(reverse = TRUE,
+                                          override.aes = list(size = 0.25,
+                                                              linetype = 0))) +
   labs(x = "Average share of donations", y = NULL, color = NULL) +
@@
   theme_ngo() +
-  theme(panel.grid.major.y = element_blank())
+  theme(panel.grid.major.y = element_blank(),
+        legend.key.width = unit(0.5, "lines"))
 
 plot_relationship_social
-ggsave(plot_relationship_social, filename = here("analysis", "output", "figures", "relationship-social.pdf"),
-       width = 6, height = 4.2, units = "in", device = cairo_pdf)
-ggsave(plot_relationship_social, filename = here("analysis", "output", "figures", "relationship-social.png"),
-       width = 6, height = 4.2, units = "in", type = "cairo", dpi = 300)
 ```
@@
 
-```{r trust-funding}
-plot_funding_social <- sim_clean %>% 
+```{r trust-funding, fig.width=6, fig.height=4, fig.asp=NULL, out.width="100%"}
+plot_funding_social <- sim_final %>% 
   group_by(org_funding, persona_trust, persona_ideology, persona_experience) %>% 
   summarize(avg_share = mean(share)) %>% 
-  ggplot(aes(y = str_wrap(fct_rev(org_funding), 20), x = avg_share, color = persona_trust)) +
-  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
-  scale_x_continuous(labels = percent) +
-  scale_color_manual(values = c(clrs$orange, clrs$navy), guide = guide_legend(reverse = TRUE)) +
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_funding, 15)), 
+             x = avg_share, color = persona_trust)) +
+  geom_pointrange(size = 0.75, fatten = 1.5,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+  scale_color_manual(values = clrs_ngo_pairs[[3]], 
+                     guide = guide_legend(reverse = TRUE,
+                                          override.aes = list(size = 0.25,
+                                                              linetype = 0))) +
   labs(x = "Average share of donations", y = NULL, color = NULL) +
@@
   theme_ngo() +
-  theme(panel.grid.major.y = element_blank())
+  theme(panel.grid.major.y = element_blank(),
+        legend.key.width = unit(0.5, "lines"))
 
 plot_funding_social
-ggsave(plot_funding_social, filename = here("analysis", "output", "figures", "funding-social.pdf"),
-       width = 6, height = 4.2, units = "in", device = cairo_pdf)
-ggsave(plot_funding_social, filename = here("analysis", "output", "figures", "funding-social.png"),
-       width = 6, height = 4.2, units = "in", type = "cairo", dpi = 300)
 ```

### 2021-04-17 R/funs_data-generation.R

@@ -1,0 +1,389 @@
+library(fastDummies)
+library(readxl)
+
+process_excel_simulation <- function(simulator_path) {
+  suppressMessages({
+    sim_raw <- read_excel(simulator_path,
+                          sheet = "Results", 
+                          range = "O3:AU27")
+  })
+  
+  orgs_raw <- read_excel(simulator_path,
+                         sheet = "Results", 
+                         range = "N4:O27", 
+                         col_names = c("organization", "org_details"))
+  
+  personas_raw <- read_excel(simulator_path,
+                             sheet = "Results", range = "P2:AU3") %>% 
+    pivot_longer(everything(), names_to = "persona", values_to = "persona_details")
+  
+  sim_long <- sim_raw %>% 
+    rename(org_details = `...1`) %>% 
+    pivot_longer(cols = -org_details, names_to = "persona_details", values_to = "share")
+  
+  sim_excel_clean <- sim_long %>% 
+    left_join(orgs_raw, by = "org_details") %>% 
+    left_join(personas_raw, by = "persona_details") %>% 
+    separate(org_details, into = c("org_issue", "org_funding", "org_relationship"), sep = ", ") %>% 
+    separate(persona_details, into = c("demographics", "actions", "persona_trust"), sep = ", ") %>% 
+    separate(demographics, into = c("persona_income", "persona_gender"), sep = " Income ") %>% 
+    separate(actions, into = c("persona_ideology", "persona_experience"), sep = " that ") %>% 
+    mutate(org_issue = recode(org_issue, "Refugess Relief" = "Refugee Relief"),
+           org_funding = recode(org_funding, "Grants" = "Mostly funded by government grants",
+                                "Small Donors" = "Mostly funded by small donors"),
+           persona_income = paste(persona_income, "income"),
+           persona_income = factor(persona_income, levels = c("Lower income", "Higher income"), ordered = TRUE),
+           persona_trust = recode(persona_trust,
+                                  "Doesn't Trust or Donate" = "Less trusting; donates and volunteers less often",
+                                  "Trusts and Donates" = "More trusting; donates and volunteers often"),
+           persona_experience = recode(persona_experience,
+                                       "Doesn't Read or Travel" = "Doesn't follow news; has not travelled abroad",
+                                       "Reads and Travels" = "Follows the news; has travelled abroad")) %>% 
+    mutate_at(vars(organization, persona), ~fct_inorder(.))
+  
+  return(sim_excel_clean)
+}
+
+load_gammas <- function(gamma_path) {
[…]

### 2021-04-17 R/funs_knitting.R

@@ -1,0 +1,215 @@
+library(bib2df)
+library(rvest)
+library(xml2)
+library(stringi)
+
+render_html <- function(input, output, csl, support_folder, ...) {
+  # Add CSS file as a dependency so it goes into the _files directory
+  dep <- htmltools::htmlDependency(
+    name = "ath",
+    version = "1.0.0",
+    "pandoc/css",
+    stylesheet = "ath-clean.css"
+  )
+  extra_dependencies <- list(dep)
+  
+  # IMPORTANT
+  # When knitting to docx, bookdown deletes the _files directory for whatever
+  # reason, so if you knit to HTML and then docx, you get a nice *_files
+  # directly that then disappears when the Word file is done. One way around
+  # this is to specify lib_dir here in rmarkdown::render()
+  
+  out <- rmarkdown::render(
+    input = input,
+    output_file = output,
+    bookdown::html_document2(
+      template = "pandoc/templates/html.html",
+      pandoc_args = c("--metadata", "link-citations=true",
+                      "--metadata", "linkReferences=true",
+                      paste0("--csl=", csl)),
+      md_extensions = "+raw_tex+smart-autolink_bare_uris+ascii_identifiers",
+      toc = TRUE,
+      number_sections = FALSE,
+      self_contained = FALSE,
+      theme = NULL,
+      extra_dependencies = extra_dependencies,
+      lib_dir = support_folder
+    ),
+    encoding = "UTF-8"
+  )
+  
+  return(fs::path_rel(out))
+}
+
+render_pdf <- function(input, output, bibstyle, ...) {
+  out <- rmarkdown::render(
+    input = input,
+    output_file = output,
+    bookdown::pdf_document2(
+      template = "pandoc/templates/xelatex.tex",
+      latex_engine = "xelatex",
+      dev = "cairo_pdf",
+      pandoc_args = c("--top-level-division=section",
+                      "--shift-heading-level-by=0",
+                      "-V", bibstyle,
+                      "-V", "chapterstyle=hikma-article"),
+      md_extensions = "+raw_tex+smart-autolink_bare_uris",
+      toc = FALSE,
+      keep_tex = FALSE,
+      citation_package = "biblatex"
+    ),
+    encoding = "UTF-8"
+  )
+  
+  return(fs::path_rel(out))
+}
+
+render_pdf_ms <- function(input, output, bibstyle, ...) {
+  out <- rmarkdown::render(
+    input = input,
+    output_file = output,
[…]

### 2021-04-17 R/funs_notebook.R

@@ -1,0 +1,84 @@
+# This is adapted from TJ Mahr's {notestar}
+# (https://github.com/tjmahr/notestar/blob/main/R/tar-notebook.R).
+#
+# He did all the hard work figuring out how to dynamically generate targets
+# based on a bunch of files, while also checking for targets dependencies with
+# tarchetypes::tar_knitr_deps(), based on this issue in {tarchetypes}:
+# https://github.com/ropensci/tarchetypes/issues/23
+#
+# I just adapted it for an R Markdown website
+
+notebook_rmd_collate <- function(dir_notebook = "analysis") {
+  index <- file.path(dir_notebook, "index.Rmd")
+  posts <- list.files(
+    path = dir_notebook,
+    pattern = ".*[^index].Rmd",
+    full.names = TRUE
+  )
+  c(index, posts)
+}
+
+rmd_to_html <- function(x) gsub("[.]Rmd$", ".html", x = x)
+html_to_rmd <- function(x) gsub("[.]html$", ".Rmd", x = x)
+
+lazy_list <- function(...) {
+  q <- rlang::enexprs(..., .named = TRUE, .check_assign = TRUE)
+  data <- list()
+  for (x in seq_along(q)) {
+    data[names(q[x])] <- list(rlang::eval_tidy(q[[x]], data = data))
+  }
+  data
+}
+
+knit_notebook_page <- function(rmd_in, html_out) {
+  rmarkdown::render_site(rmd_in, encoding = "UTF-8")
+  html_out
+}
+
+tar_notebook_pages <- function(
+  dir_notebook = "analysis",
+  dir_html = "analysis/_site",
+  yaml_config = "analysis/_site.yml"
+) {
+  
+  rmds <- notebook_rmd_collate(dir_notebook)
+  
+  values <- lazy_list(
+    rmd_file = !! rmds,
+    rmd_page = basename(.data$rmd_file),
+    sym_rmd_page = rlang::syms(.data$rmd_page),
+    rmd_deps = lapply(.data$rmd_file, tarchetypes::tar_knitr_deps_expr),
+    html_page = rmd_to_html(.data$rmd_page),
+    html_file = file.path(!! dir_html, .data$html_page)
+  )
+  
+  list(
+    # Add _site.yml as a dependency
+    # Have to use tar_target_raw() instead of tar_target() so that yaml_config is usable
+    tar_target_raw("site_yml", yaml_config, format = "file"),
+    
[…]

### 2021-04-17 R/funs_plots.R

@@ -1,0 +1,97 @@
+library(patchwork)
+library(scales)
+
+plot_income <- function(grey = FALSE) {
+  if (grey) {
+    color_pairs <- c("grey30", "grey80")
+  } else {
+    color_pairs <- clrs_ngo_pairs[[1]]
+  }
+  
+  plot_income_issue <- sim_final %>% 
+    group_by(org_issue, persona_income) %>% 
+    summarize(avg_share = mean(share)) %>% 
+    mutate(facet = "Issue area") %>% 
+    ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)),
+               x = avg_share, color = fct_rev(persona_income))) +
+    geom_pointrange(size = 0.75, fatten = 1.5,
+                    aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+    scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002)),
+                       breaks = seq(0, 0.06, 0.02)) +
+    scale_color_manual(values = color_pairs, guide = FALSE) +
+    coord_cartesian(xlim = c(0, 0.06)) +
+    labs(x = "Average donation share", y = NULL, color = NULL) +
+    facet_wrap(vars(facet)) +
+    theme_ngo() +
+    theme(panel.grid.major.y = element_blank())
+  
+  plot_income_funding <- sim_final %>% 
+    group_by(org_funding, persona_income) %>% 
+    summarize(avg_share = mean(share)) %>% 
+    mutate(facet = "Funding sources") %>% 
+    ggplot(aes(y = fct_rev(str_wrap_factor(org_funding, 10)), 
+               x = avg_share, color = fct_rev(persona_income))) +
+    geom_pointrange(size = 0.75, fatten = 1.5,
+                    aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+    scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+    coord_cartesian(xlim = c(0, 0.06)) +
+    scale_color_manual(values = color_pairs, guide = FALSE) +
+    labs(x = "Average donation share", y = NULL, color = NULL) +
+    facet_wrap(vars(facet)) +
+    theme_ngo() +
+    theme(panel.grid.major.y = element_blank())
+  
+  plot_income_relationship <- sim_final %>% 
+    mutate(persona_income = fct_recode(persona_income,
[…]

### 2021-04-17 R/funs_survey.R

@@ -1,0 +1,58 @@
+create_sample_summary <- function(survey_results) {
+  vars_to_summarize <- tribble(
+    ~category, ~variable, ~clean_name,
+    "Demographics", "Q5.12", "Gender",
+    "Demographics", "Q5.17", "Age",
+    "Demographics", "Q5.13", "Marital status",
+    "Demographics", "Q5.14", "Education",
+    "Demographics", "Q5.15", "Income",
+    "Attitudes toward charity", "Q2.5", "Frequency of donating to charity",
+    "Attitudes toward charity", "Q2.6", "Amount of donations to charity last year",
+    "Attitudes toward charity", "Q2.7_f", "Importance of trusting charities",
+    "Attitudes toward charity", "Q2.8_f", "Level of trust in charities",
+    "Attitudes toward charity", "Q2.10", "Frequency of volunteering",
+    "Politics, ideology, and religion", "Q2.1", "Frequency of following national news",
+    "Politics, ideology, and religion", "Q5.7", "Traveled to a developing country",
+    "Politics, ideology, and religion", "Q5.1", "Voted in last election",
+    "Politics, ideology, and religion", "Q5.6_f", "Trust in political institutions and the state",
+    "Politics, ideology, and religion", "Q5.2_f", "Political ideology",
+    "Politics, ideology, and religion", "Q5.4", "Involvement in activist causes",
+    "Politics, ideology, and religion", "Q5.8", "Frequency of attending religious services",
+    "Politics, ideology, and religion", "Q5.9", "Importance of religion"
+  )
+  
+  summarize_factor <- function(x) {
+    output <- table(x) %>% 
+      as_tibble() %>% 
+      magrittr::set_colnames(., c("level", "count")) %>% 
+      mutate(level = factor(level, levels = levels(x))) %>%
+      mutate(prop = count / sum(count),
+             nice_prop = scales::percent(prop))
+    
+    return(list(output))
+  }
+  
+  participant_summary <- survey_results %>% 
+    select(one_of(vars_to_summarize$variable)) %>% 
+    summarize(across(everything(), summarize_factor)) %>% 
+    pivot_longer(cols = everything(), names_to = "variable", values_to = "details") %>% 
+    left_join(vars_to_summarize, by = "variable") %>% 
+    unnest(details) %>% 
+    mutate(level = as.character(level)) %>% 
+    mutate(level = case_when(
[…]

### 2021-04-17 R/graphics.R

@@ -55,31 +55,30 @@ theme_ngo <- function(base_size = 9, base_family = "IBM Plex Sans Condensed") {
 # colors_viridis <- viridisLite::viridis(6, begin = 0, end = 0.97)
 # colors_viridis %>% scales::show_col()
 
-clrs_ngo <- as.list(c(viridisLite::plasma(6, begin = 0, end = 0.85), 
-                      viridisLite::viridis(6, begin = 0, end = 0.94)))
-# unlist(clrs_ngo) %>% scales::show_col()
-names(clrs_ngo) <- c("pl_blue", "pl_purple_dark", "pl_purple_light", 
-                     "pl_pink", "pl_orange", "pl_yellow",
-                     "vi_purple", "vi_blue_dark", "vi_blue_light", 
-                     "vi_turquoise", "vi_green", "vi_yellow")
+# colors_viridis <- viridisLite::viridis(4, option = "viridis")
 
-# Colors via http://clrs.cc/
-clrs <- list(
-  navy = "#001F3F",
-  blue = "#0074D9",
-  aqua = "#7FDBFF",
-  teal = "#39CCCC",
-  olive = "#3D9970",
-  green = "#2ECC40",
-  lime = "#01FF70",
-  yellow = "#FFDC00",
-  orange = "#FF851B",
-  red = "#FF4136",
-  fuchsia = "#F012BE",
-  purple = "#B10DC9",
-  maroon = "#85144B",
-  white = "#FFFFFF",
-  silver = "#DDDDDD",
-  gray = "#AAAAAA",
-  black = "#111111"
-)
+# Okabe and Ito (2008) colorblind-safe qualitative palette: https://jfly.uni-koeln.de/color/
+# See also https://clauswilke.com/dataviz/color-pitfalls.html
+clrs_okabe_ito <- list(orange = "#E69F00",
+                       sky_blue = "#56B4E9",
+                       bluish_green = "#009E73",
+                       yellow = "#F0E442",
+                       blue = "#0072B2",
+                       vermilion = "#D55E00",
+                       reddish_purple = "#CC79A7",
+                       black = "#000000")
+
+clrs_ngo_pairs <- list(c(clrs_okabe_ito[[1]], clrs_okabe_ito[[2]]),
+                       c(clrs_okabe_ito[[3]], clrs_okabe_ito[[4]]),
+                       c(clrs_okabe_ito[[5]], clrs_okabe_ito[[6]]),
[…]

### 2021-04-17 _targets.R

@@ -1,0 +1,120 @@
+library(targets)
+library(tarchetypes)
+library(tibble)
+
+# General variables
+csl <- "pandoc/csl/the-open-university-harvard.csl"
+bibstyle <- "bibstyle-chicago-authordate"
+
+options(tidyverse.quiet = TRUE,
+        dplyr.summarise.inform = FALSE)
+
+set.seed(1746)  # From random.org
+
+tar_option_set(packages = c("tidyverse", "here", "fs", "scales",
+                            "readxl", "haven", "sf", "lubridate", "scales",
+                            "janitor", "kableExtra", "huxtable", "modelsummary",
+                            "knitr", "withr", "flextable", "testthat", "DT",
+                            "brms", "tidybayes", "broom", "cmdstanr", "jsonlite"))
+
+source("R/funs_data-generation.R")
+source("R/funs_survey.R")
+source("R/funs_notebook.R")
+source("R/funs_knitting.R")
+
+# here::here() returns an absolute path, which then gets stored in tar_meta and
+# becomes computer-specific (i.e. /Users/andrew/Research/blah/thing.Rmd).
+# There's no way to get a relative path directly out of here::here(), but
+# fs::path_rel() works fine with it (see
+# https://github.com/r-lib/here/issues/36#issuecomment-530894167)
+here_rel <- function(...) {fs::path_rel(here::here(...))}
+
+# Pipeline
+list(
+  # Define raw data files
+  tar_target(excel_simulator_file,
+             here_rel("data", "raw_data", "Market Simulator Version 01.xlsx"),
+             format = "file"),
+  tar_target(gamma_draws_file,
+             here_rel("data", "raw_data", "posterior_draws", "public_political_social_charity_demo.rds"),
+             format = "file"),
+  tar_target(survey_results_file,
+             here_rel("data", "raw_data", "final_data.rds"),
+             format = "file"),
+  tar_target(giving_aggregate_file,
+             here_rel("data", "raw_data", "data-FTjUv.csv")),
+  tar_target(giving_per_capita_file,
+             here_rel("data", "raw_data", "data-xextT.csv")),
+  
+  # Define helper functions
+  tar_target(plot_funs, here_rel("R", "graphics.R"), format = "file"),
+  
+  # Process and clean data
+  tar_target(sim_excel_final, process_excel_simulation(excel_simulator_file)),
+  tar_target(gammas, load_gammas(gamma_draws_file)),
[…]

### 2021-04-17 analysis/options.R

@@ -1,9 +1,0 @@
-# Universal pandoc options ------------------------------------------------
-
-pander::panderOptions("table.split.table", Inf)
-pander::panderOptions("table.split.cells", Inf)
-pander::panderOptions("missing", "")
-pander::panderOptions("big.mark", ",")
-pander::panderOptions("digits", 3)
-pander::panderOptions("round", 3)
-pander::panderOptions("table.alignment.default", "left")

### 2021-04-17 manuscript/pandoc/bin/bib_extract.py

@@ -1,78 +1,0 @@
-#!/usr/bin/env python3
-
-# Find all pandoc-style citations in a Markdown file and extract their
-# corresponding BibTeX entries from a larger, master BibTeX file into a new
-# .bib file. Perfect for creating a clean bibliography file for distribution.
-#
-# Requires bibtool (http://www.gerd-# neugebauer.de/software/TeX/BibTool/index.en.html), 
-# which is easily installed on OS X with Homebrew (`brew install bib-tool`)
-#
-# Inspired and based on David Sanson's extract_bib.rb script: https://gist.github.com/dsanson/1383132
-#
-# Usage: bib_extract.py [-h] [--bibtex_file BIBTEX_FILE]
-#                       [--bibtools_resource BIBTOOLS_RESOURCE]
-#                       md_file output_file 
-#
-
-# Configure the three variables below for your system:
-default_bib_file = "/Users/andrew/Dropbox/Readings/Papers.bib"
-default_resource_file = "/Users/andrew/bin/bibtool.rsc"
-bibtool_path = "/usr/local/bin/bibtool"
-
-
-# Load libraries
-import argparse
-import re
-import os
-from subprocess import run, PIPE
-# import subprocess
-
-# Get command line information
-parser = argparse.ArgumentParser(description='Generate a BibTeX file containing citation entries in a given pandoc Markdown file.',
-                                 formatter_class=argparse.ArgumentDefaultsHelpFormatter)
-parser.add_argument('md_file', type=argparse.FileType('r'), 
-                    help='the path to a Markdown file')
-parser.add_argument('output_file', type=str, 
-                    help='the name of the new BibTeX file')
-parser.add_argument('--bibtex_file', type=str, 
-                    default=default_bib_file,
-                    help='the path to the existing master BibTeX file')
-parser.add_argument('--bibtools_resource', type=str, 
-                    default=default_resource_file,
-                    help='the path to the a custom resource file for bibtool')
-args = parser.parse_args()
-
-# Save arguments
-md_file = args.md_file
-output_file = os.path.abspath(args.output_file)
-bib_file = os.path.abspath(args.bibtex_file)
-
-# See http://www.gerd-neugebauer.de/software/TeX/BibTool/bibtool.pdf and
-# http://www.gerd-neugebauer.de/software/TeX/BibTool/ref_card.pdf for
-# documentation on resource files and command line options.
[…]

### 2021-04-17 manuscript/pandoc/bin/replace_pdfs.py

@@ -1,69 +1,0 @@
-#!/usr/bin/env python3
-
-# Replace any images that use PDFs with PNGs, since Word and HTML
-# struggle with displaying PDFs
-#
-# Usage: replace_pdfs [-h] [input_file] [output]
-#
-# Recommended usage: Send the Markdown output to stdout (default) and pipe
-# into pandoc for immediate processing:
-#
-#   replace_pdfs.py document.md | pandoc -f markdown -t docx -o document.docx
-#
-# TODO: Use subprocess instead of system - but doing that does weird stuff with the path
-
-# Load libraries
-import re
-import argparse
-import sys
-import subprocess
-from os import path, system
-
-# Get command line arguments
-parser = argparse.ArgumentParser(description='Replace image PDFs with PNGs')
-parser.add_argument('input_file', type=argparse.FileType('r'),
-                    nargs='?', default=sys.stdin,
-                    help='Markdown file to preprocess')
-parser.add_argument('output', type=argparse.FileType('w'),
-                    nargs='?', default=sys.stdout,
-                    help='the name of the output file (defaults to stdout)')
-parser.add_argument('--convert', dest='convert', action='store_true')
-parser.add_argument('--no-convert', dest='convert', action='store_false')
-parser.set_defaults(convert=False)
-args = parser.parse_args()
-
-# Save arguments
-input_file = args.input_file.read()
-output = args.output
-convert = args.convert
-
-# Find images
-# md_images = re.compile(r"!\[([^\[]*)\]\(([^\)]+)\)")
-md_images = re.compile(r"!\[(.*)\]\((.*)\)")
-
-
-# Convert a list of PDFs to PNGs
-def pdf2png(images):
-    for image in images:
-        file_name, file_extension = path.splitext(image)
-        command = 'sips -s format png "' + path.abspath(image) + '" --out "' + path.abspath(file_name) + '.png" > /dev/null 2>&1'
-        system(command)
-
-
-# Replace `.pdf` in the () part of the image syntax with `.png`
-def replace_extension(match):
-    converted_name = match.group(2).replace('.pdf', '.png')
-    return("![{0}]({1})".format(match.group(1), converted_name))
-
-
-# Find all PDFs and convert them
-if convert:
-    images = [image[1] for image in re.findall(md_images, input_file)]
-    pdf2png(images)
-
-# Replace calls to PDF images with PNGs
-result = re.sub(md_images, replace_extension, input_file)
-
-# Output results
-with output as f:
-    f.write(result)

### 2021-04-17 manuscript/pandoc/bin/word_count.R

@@ -1,71 +1,0 @@
-#!/usr/bin/Rscript
-
-# string::stri_count_words() counts, um, words. That's its whole job. But it
-# doesn't count them like Microsoft Word counts them, and academic publishing
-# portals tend to care about Word-like counts. For instance, Word considers
-# hyphenated words to be one word, while stringr counts them as two (and even
-# worse, stringi counts / as word boundaries, so URLs can severely inflate your
-# word count).
-#
-# Also, academic writing typically doesn't count the title, abstract, table
-# text, figure captions, or equations as words in the manuscript (and it
-# SHOULDN'T count bibliographies, but it always seems to ugh).
-#
-# This script parses the rendered manuscript HTML, removes extra elements,
-# adjusts the text so that stringi treats it more like Word, and then provides a
-# more accurate word count.
-
-suppressPackageStartupMessages(library(magrittr))
-suppressPackageStartupMessages(library(stringr))
-suppressPackageStartupMessages(library(purrr))
-suppressPackageStartupMessages(library(rvest))
-suppressPackageStartupMessages(library(stringi))
-
-args <- commandArgs(trailingOnly = TRUE)
-
-if (length(args) < 1) {
-  ms_file <- "paper.html"
-} else {
-  ms_file <- args[1]
-}
-
-# Read the HTML file
-ms_raw <- read_html(ms_file)
-
-# Extract just the article, ignoring title, abstract, etc.
-ms <- ms_raw %>%
-  html_nodes("article")
-
-# Get rid of figures, tables, and math
-xml_remove(ms %>% html_nodes("figure"))
-xml_remove(ms %>% html_nodes("table"))
-xml_remove(ms %>% html_nodes(".display"))  # Block math
-xml_replace(ms %>% html_nodes(".inline"), read_xml("<span>MATH</span>")) %>%
-  invisible()
-
-# Go through each child element in the article and extract it
-ms_cleaned_list <- map(html_children(ms), ~ {
-  .x %>%
-    html_text(trim = TRUE) %>%
-    # ICU counts hyphenated words as multiple words, so replace - with DASH
-    str_replace_all("\\-", "DASH") %>%
-    # ICU also counts / as multiple words, so URLs go crazy. Replace / with SLASH
-    str_replace_all("\\/", "SLASH") %>%
-    # ICU *also* counts [things] in bracketss multiple times, so kill those too
[…]

### 2021-04-17 manuscript/manuscript.Rmd
Make manuscript work with targets

@@
 Our findings have practical implications for INGOs raising funds from individuals amid closing civic space.
+toc: false
 reference-section-title: References
-toc: false
+bibliography: bibliography.bib
 title-page: true
@@
   In the wake of the global crackdown on civil society, international NGOs (INGOs) need to maintain access to multiple sources of funding, including individual donors. 
-
   It is critical for INGOs to understand what motivates individuals to donate, especially if INGOs face legal crackdown in their host countries.
@@
   Trust in political institutions and in charitable organizations matters substantially in shaping donor preferences.
-
   We find that potential donors with low social trust tend to be wary of negative host-country relationships and prefer to donate to INGOs that are friendly with their host governments, while potential donors with high social trust are more willing to stick with legally besieged INGOs.
-
   Donors that are the most trusting and involved may remain supportive when charities face government criticism and crackdown.
 The global crackdown on NGOs may also possibly sour NGOs' least trusting individual donors.
+editor_options: 
+  chunk_output_type: console
 ---
@@
 <!-- manuscript.md is generated from manuscript.Rmd. Only edit the .Rmd file, *not* the .md file. -->
+
+```{r setup, include=FALSE}
+# Figure out output format
+is_docx <- knitr::pandoc_to("docx") | knitr::pandoc_to("odt")
+is_latex <- knitr::pandoc_to("latex")
+is_html <- knitr::pandoc_to("html")
+
+# Word-specific things
+table_format <- ifelse(is_docx, "huxtable", "kableExtra")  # Huxtable tables
+conditional_dpi <- ifelse(is_docx, 300, 300)  # Higher DPI
+conditional_align <- ifelse(is_docx, "default", "center")  # Word doesn't support align
+
+# Knitr options
+knitr::opts_chunk$set(
+  echo = FALSE, warning = FALSE, message = FALSE,
+  tidy.opts = list(width.cutoff = 120),  # Code width
+  fig.retina = 3, dpi = conditional_dpi,
+  fig.width = 7, fig.asp = 0.618,
+  fig.align = conditional_align, out.width = "100%",
+  fig.path = "output/figures/",
+  cache.path = "output/_cache/",
+  fig.process = function(x) {  # Remove "-1" from figure names
+    x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
+    if (file.rename(x, x2)) x2 else x
+  }
+)
+
+# R options
+options(
+  width = 90,  # Output width
+  dplyr.summarise.inform = FALSE,  # Turn off dplyr's summarize() auto messages
+  knitr.kable.NA = "",  # Make NAs blank in kables
+  kableExtra.latex.load_packages = FALSE,  # Don't add LaTeX preamble stuff
+  modelsummary_default = table_format  # Set modelsummary backend
+)
+```
+
+```{r libraries-data, include=FALSE}
+library(tidyverse)
+library(targets)
+library(kableExtra)
+library(patchwork)
+library(scales)
+library(janitor)
+library(glue)
+library(here)
+
+withr::with_dir(here::here(), {
+  source(tar_read(plot_funs))
+
+  tar_load(personas)
+  tar_load(orgs)
+  tar_load(participant_summary)
+  tar_load(sim_final)
+  tar_load(sim_excel_final)
+})
+```
 
@@
 
-```{r child = "output/tables/tbl-organization-attributes-full.md"}
+```{r organization-attributes-full}
+orgs$org_attributes %>% 
+  select(Organization, `Issue area`, `Organizational practices`, 
+         `Funding sources`, `Relationship with government`) %>% 
+  kbl(align = "lllll",
+      caption = "Organization attributes varied in the experiment. Each participant saw repeated combinations of attributes, with one attribute randomly selected from each column.") %>% 
+  kable_styling()
 ```
@@
 
-The hypothetical organizations are based on random combinations of features, including one of four issue areas, the presence or absence of two organizational practices, one of three funding sources, and one of three relationships with host governments (see @tbl:organization-attributes-full; see also Q3.1 in the survey text in the appendix).
+The hypothetical organizations are based on random combinations of features, including one of four issue areas, the presence or absence of two organizational practices, one of three funding sources, and one of three relationships with host governments (see Table \@ref(tab:organization-attributes-full); see also Q3.1 in the survey text in the appendix).
 Respondents saw twelve sets of four hypothetical organizations out of 288 (4 × 4 × 2 × 3 × 3) possible combinations, meaning no single respondent was offered every combination.
@@
 
-```{r child = "output/tables/tbl-sample-details.md"}
+```{r sample-details}
+participant_summary %>% 
+  select(Question = clean_name,
+         Response = level,
+         N = count,
+         `%` = nice_prop) %>% 
+  kbl(align = "lllcc",
+      caption = "Summary of individual respondent characteristics") %>% 
+  pack_rows(index = table(fct_inorder(participant_summary$category))) %>%
+  collapse_rows(columns = 1, valign = "top") %>% 
+  kable_styling()
 ```
@@
 
-@tbl:sample-details provides a summary of the individual characteristics of survey respondents.
+Table \@ref(tab:sample-details) provides a summary of the individual characteristics of survey respondents.
 Because we limited the sample to people who regularly make charitable contributions, most respondents have a favorable opinion of nonprofits and charities, with more than half reporting a 5 or greater level of trust in charities (on a 7-point scale).
@@
 To more fully explore the relationships between different organizational- and individual-level attributes, we turn to simulation methods that allow us to examine the impact of multiple covariates simultaneously.
-To simplify the possible combinations of individual characteristics, we generate 64 distinct personas with attributes that vary along different dimensions of demographics, politics and public affairs experience, and social attitudes (see @tbl:persona-attributes).
-We also generate 24 simulated organizations that vary by issue area, relationship with host government, and source of funding (see @tbl:organization-attributes).
+To simplify the possible combinations of individual characteristics, we generate 64 distinct personas with attributes that vary along different dimensions of demographics, politics and public affairs experience, and social attitudes (see Table \@ref(tab:persona-attributes)).
+We also generate 24 simulated organizations that vary by issue area, relationship with host government, and source of funding (see Table \@ref(tab:organization-attributes)).
 
@@
 
-```{r child = "output/tables/tbl-persona-attributes.md"}
+```{r persona-attributes}
+personas$persona_attributes %>% 
+  kbl(align = "lll",
+      caption = "Individual attributes varied in the simulation, resulting in 64 persona profiles") %>% 
+  kable_styling()
 ```
 
-```{r child = "output/tables/tbl-organization-attributes.md"}
+```{r organization-attributes}
+orgs$org_attributes %>% 
+  select(`Issue area`, `Relationship with government`, `Funding`) %>% 
+  kbl(align = "lll",
+      caption = "Organization attributes varied in the simulation, resulting in 24 hypothetical organizations") %>% 
+  kable_styling()
 ```
@@
 We then combine these different scenarios of donor and organization attributes with the coefficients from a multinomial multilevel regression model to calculate the probability that each simulated persona has of giving to specific combinations of organizational attributes.
-Any individual characteristics that we do not explicitly vary in @tbl:persona-attributes are held at their means or modal values from the survey sample.
-@tbl:sim-output provides an example of the simulation output, showing how two different personas are predicted to allocate donations to organizations with various characteristics.
+Any individual characteristics that we do not explicitly vary in Table \@ref(tab:persona-attributes) are held at their means or modal values from the survey sample.
+Table \@ref(tab:sim-output) provides an example of the simulation output, showing how two different personas are predicted to allocate donations to organizations with various characteristics.
 The proportion of donations from each persona sums to 100%, as every persona is guaranteed to make a donation.
@@
 
-```{r child = "output/tables/tbl-sim-output.md"}
+```{r sim-output}
+example_personas <- c("persona2", "persona63")
+
+example_persona_results <- sim_final %>% 
+  filter(persona_id %in% example_personas) %>% 
+  mutate(org_funding = str_to_sentence(str_remove(org_funding, "Mostly funded by "))) %>% 
+  mutate(org_clean = glue("{organization}: {org_issue}, {org_funding}, {org_relationship}")) %>% 
+  mutate(persona_desc = recode(
+    persona_id,
+    "persona2" = "Lower income high school graduate who rarely attends religious services; liberal who reads and travels; doesn't trust or donate",
+    "persona63" = "Higher income college graduate who attends religious services; conservative who doesn't read or travel; trusts and donates")
+  ) %>%
+  mutate(persona_clean = glue("{persona}: {persona_desc}")) %>% 
+  select(persona_clean, share, org_clean) %>% 
+  pivot_wider(names_from = "persona_clean", values_from = "share") %>% 
+  adorn_totals(where = "row", name = "Total")
+
+example_persona_results_small <- example_persona_results %>% 
+  slice(c(1, 2, 3, 7, 8, 9, 16, 17, 25)) %>% 
+  mutate(across(where(is.numeric), ~ percent_format(accuracy = 0.1)(.))) %>% 
+  add_row(org_clean = "…", .after = 3) %>% 
+  add_row(org_clean = "…", .after = 7) %>% 
+  add_row(org_clean = "…", .after = 10) %>% 
+  mutate(across(everything(), ~replace_na(., "…"))) %>% 
+  rename(Organization = org_clean)
+
+example_persona_results_small %>% 
+  mutate(Organization = text_spec(Organization, bold = Organization == "Total")) %>% 
+  kbl(align = "lcc",
+      caption = "Sample simulation output",
+      escape = FALSE) %>% 
+  kable_styling()
 ```
@@
 
-## Demographics
+## Patterns across demographics
 
 We begin by looking at differences in donation preferences across a range of basic demographic characteristics.
-The four panels of @fig:income show the average predicted market share for different organizational issue areas, funding sources, and relationships with host governments across different levels of persona income, with two different cutpoints for high and low income.
+The four panels of Figure \@ref(fig:income) show the average predicted market share for different organizational issue areas, funding sources, and relationships with host governments across different levels of persona income, with two different cutpoints for high and low income.
 To ease with modeling and interpretation, we split high- and low-income personas based on the 2017 U.S.
@@
 
-![Average predicted donation market shares across all personas, segmented by persona income across organizational issue area, relationship with host government, and funding sources](output/figures/income-all.pdf){#fig:income}
+```{r income, fig.width=6, fig.height=4.5, fig.asp=NULL, out.width="100%", fig.cap="Average predicted donation market shares across all personas, segmented by persona income across organizational issue area, relationship with host government, and funding sources"}
+plot_income_issue <- sim_final %>% 
+  group_by(org_issue, persona_income) %>% 
+  summarize(avg_share = mean(share)) %>% 
+  mutate(facet = "Issue area") %>% 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)),
+             x = avg_share, color = fct_rev(persona_income))) +
+  geom_pointrange(size = 0.75, fatten = 1.5,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002)),
+                     breaks = seq(0, 0.06, 0.02)) +
+  scale_color_manual(values = clrs_ngo_pairs[[1]], guide = FALSE) +
+  coord_cartesian(xlim = c(0, 0.06)) +
+  labs(x = "Average donation share", y = NULL, color = NULL) +
+  facet_wrap(vars(facet)) +
+  theme_ngo() +
+  theme(panel.grid.major.y = element_blank())
+
+plot_income_funding <- sim_final %>% 
+  group_by(org_funding, persona_income) %>% 
+  summarize(avg_share = mean(share)) %>% 
+  mutate(facet = "Funding sources") %>% 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_funding, 10)), 
+             x = avg_share, color = fct_rev(persona_income))) +
+  geom_pointrange(size = 0.75, fatten = 1.5,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+  coord_cartesian(xlim = c(0, 0.06)) +
+  scale_color_manual(values = clrs_ngo_pairs[[1]], guide = FALSE) +
+  labs(x = "Average donation share", y = NULL, color = NULL) +
+  facet_wrap(vars(facet)) +
+  theme_ngo() +
+  theme(panel.grid.major.y = element_blank())
+
+plot_income_relationship <- sim_final %>% 
+  mutate(persona_income = fct_recode(persona_income,
+                                     "< $61,372/year" = "Lower income",
+                                     "> $61,372/year" = "Higher income")) %>% 
+  group_by(org_relationship, persona_income) %>% 
+  summarize(avg_share = mean(share)) %>% 
+  mutate(facet = "Relationship with host government") %>% 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
+             x = avg_share, color = fct_rev(persona_income))) +
+  geom_pointrange(size = 0.75, fatten = 1.5, 
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) +
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.003))) +
+  coord_cartesian(xlim = c(0, 0.1)) +
+  scale_color_manual(values = clrs_ngo_pairs[[1]], 
+                     guide = guide_legend(reverse = TRUE, nrow = 1,
+                                          override.aes = list(size = 0.25,
+                                                              linetype = 0))) +
+  labs(x = "Average donation share", y = NULL, color = NULL) +
+  facet_wrap(vars(str_wrap(facet, 50))) +
+  theme_ngo() +
+  theme(panel.grid.major.y = element_blank(),
+        legend.key.width = unit(0.5, "lines"))
+
+plot_income_relationship_extreme <- sim_excel_final %>% 
+  mutate(persona_income = fct_recode(persona_income,
+                                     "$50,000/year" = "Lower income",
+                                     "$100,000/year" = "Higher income"),
+         org_relationship = fct_recode(org_relationship,
+                                       "Under crackdown" = "Crackdown")) %>% 
+  group_by(org_relationship, persona_income) %>% 
+  summarize(avg_share = mean(share)) %>% 
+  mutate(facet = "Relationship with host government") %>% 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
+             x = avg_share, color = fct_rev(persona_income))) +
+  geom_pointrange(size = 0.75, fatten = 1.5, linetype = "21", pch = 2,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+  coord_cartesian(xlim = c(0, 0.1)) +
+  scale_color_manual(values = clrs_ngo_pairs[[1]], 
+                     guide = guide_legend(reverse = TRUE, nrow = 1,
+                                          override.aes = list(size = 0.25, 
+                                                              linetype = 0))) +
+  labs(x = "Average donation share", y = NULL, color = NULL) +
+  facet_wrap(vars(str_wrap(facet, 50))) +
+  theme_ngo() +
+  theme(panel.grid.major.y = element_blank(),
+        legend.key.width = unit(0.5, "lines"))
+
+plot_income <- ((plot_income_issue + labs(x = NULL)) + 
+  (plot_income_funding + labs(x = NULL))) / 
+  (plot_income_relationship + plot_income_relationship_extreme)
+
+plot_income
+```
 
@@
 
-![Average predicted donation market shares across all personas, segmented by persona education and religiosity across organizational issue area, relationship with host government, and funding sources](output/figures/education-religion-all.pdf){#fig:edu-religion}
+```{r edu-religion, fig.width=6, fig.height=4.5, fig.asp=NULL, out.width="100%", fig.cap="Average predicted donation market shares across all personas, segmented by persona education and religiosity across organizational issue area, relationship with host government, and funding sources"}
+# Education plots
+plot_education_issue <- sim_final %>% 
+  group_by(org_issue, persona_education) %>% 
+  summarize(avg_share = mean(share)) %>% 
+  mutate(facet = "Issue area") %>% 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)), 
+             x = avg_share, color = fct_rev(persona_education))) +
+  geom_pointrange(size = 0.75, fatten = 1.5,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+  coord_cartesian(xlim = c(0, 0.06)) +
+  scale_color_manual(values = clrs_ngo_pairs[[2]], guide = FALSE) +
+  labs(x = "Average donation share", y = NULL, color = NULL) +
+  facet_wrap(vars(facet)) +
+  theme_ngo() +
+  theme(panel.grid.major.y = element_blank())
 
-While education and religiosity are both important drivers of individual philanthropy, neither are associated with any sizable differences in persona donation patterns (as seen in @fig:edu-religion).
+plot_education_funding <- sim_final %>% 
+  group_by(org_funding, persona_education) %>% 
+  summarize(avg_share = mean(share)) %>% 
+  mutate(facet = "Funding sources") %>% 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_funding, 10)), 
+             x = avg_share, color = fct_rev(persona_education))) +
+  geom_pointrange(size = 0.75, fatten = 1.5,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+  coord_cartesian(xlim = c(0, 0.06)) +
+  scale_color_manual(values = clrs_ngo_pairs[[2]], guide = FALSE) +
+  labs(x = "Average donation share", y = NULL, color = NULL) +
+  facet_wrap(vars(facet)) +
+  theme_ngo() +
+  theme(panel.grid.major.y = element_blank())
+
+plot_education_relationship <- sim_final %>% 
+  group_by(org_relationship, persona_education) %>% 
+  summarize(avg_share = mean(share)) %>% 
+  mutate(facet = "Relationship with host government") %>% 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)),
+             x = avg_share, color = fct_rev(persona_education))) +
+  geom_pointrange(size = 0.75, fatten = 1.5,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+  coord_cartesian(xlim = c(0, 0.1)) +
+  scale_color_manual(values = clrs_ngo_pairs[[2]], 
+                     guide = guide_legend(reverse = TRUE, ncol = 1,
+                                          override.aes = list(size = 0.25,
+                                                              linetype = 0)),
+                     labels = label_wrap(15)) +
+  labs(x = "Average donation share", y = NULL, color = NULL) +
+  facet_wrap(vars(str_wrap(facet, 20))) +
+  theme_ngo() +
+  theme(panel.grid.major.y = element_blank(),
+        legend.key.width = unit(0.5, "lines"))
+
+# Religion plots
+plot_religion_issue <- sim_final %>% 
+  group_by(org_issue, persona_religion) %>% 
+  summarize(avg_share = mean(share)) %>% 
+  mutate(facet = "Issue area") %>% 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)), 
+             x = avg_share, color = fct_rev(persona_religion))) +
+  geom_pointrange(size = 0.75, fatten = 1.5, pch = 17,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+  coord_cartesian(xlim = c(0, 0.06)) +
+  scale_color_manual(values = clrs_ngo_pairs[[4]], guide = FALSE) +
+  labs(x = "Average donation share", y = NULL, color = NULL) +
+  facet_wrap(vars(facet)) +
+  theme_ngo() +
+  theme(panel.grid.major.y = element_blank())
+
+plot_religion_funding <- sim_final %>% 
+  group_by(org_funding, persona_religion) %>% 
+  summarize(avg_share = mean(share)) %>% 
+  mutate(facet = "Funding sources") %>% 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_funding, 10)), 
+             x = avg_share, color = fct_rev(persona_religion))) +
+  geom_pointrange(size = 0.75, fatten = 1.5, pch = 17,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+  coord_cartesian(xlim = c(0, 0.06)) +
+  scale_color_manual(values = clrs_ngo_pairs[[4]], guide = FALSE) +
+  labs(x = "Average donation share", y = NULL, color = NULL) +
+  facet_wrap(vars(facet)) +
+  theme_ngo() +
+  theme(panel.grid.major.y = element_blank())
+
+plot_religion_relationship <- sim_final %>% 
+  group_by(org_relationship, persona_religion) %>% 
+  summarize(avg_share = mean(share)) %>% 
+  mutate(facet = "Relationship with host government") %>% 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
+             x = avg_share, color = fct_rev(persona_religion))) +
+  geom_pointrange(size = 0.75, fatten = 1.5, pch = 17,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+  coord_cartesian(xlim = c(0, 0.1)) +
+  scale_color_manual(values = clrs_ngo_pairs[[4]], 
+                     guide = guide_legend(reverse = TRUE, ncol = 1,
+                                          override.aes = list(size = 0.25,
+                                                              linetype = 0)),
+                     labels = label_wrap(20)) +
+  labs(x = "Average donation share", y = NULL, color = NULL) +
+  facet_wrap(vars(str_wrap(facet, 20))) +
+  theme_ngo() +
+  theme(panel.grid.major.y = element_blank(),
+        legend.key.width = unit(0.5, "lines"))
+
+plot_education_religion <- (plot_education_issue + labs(x = NULL)) + 
+  (plot_education_funding + labs(x = NULL)) + 
+  (plot_education_relationship + labs(x = NULL)) + 
+  guide_area() +
+  plot_religion_issue + 
+  plot_religion_funding + 
+  plot_religion_relationship +
+  plot_layout(guides = "collect", ncol = 4)
+
+plot_education_religion
+```
+
+While education and religiosity are both important drivers of individual philanthropy, neither are associated with any sizable differences in persona donation patterns (as seen in Figure \@ref(fig:edu-religion)).
 Human rights issues attract a slightly larger market share of personas who are college graduates or who attend religious services at least monthly, while refugee issues are more likely to attract less religious personas, but these differences are minor.
@@
 
-## Public affairs knowledge, experience, and social trust
+## Patterns across public affairs knowledge, experience, and social trust
 
@@
 
-![Average predicted donation market shares across all personas, segmented by persona public affairs knowledge, political ideology, and social trust across different NGO issue areas](output/figures/issue-social.pdf){#fig:issue-social}
+```{r issue-social, fig.width=6, fig.height=4, fig.asp=NULL, out.width="100%", fig.cap="Average predicted donation market shares across all personas, segmented by persona public affairs knowledge, political ideology, and social trust across different NGO issue areas"}
+sim_final %>% 
+  group_by(org_issue, persona_trust, persona_ideology, persona_experience) %>% 
+  summarize(avg_share = mean(share)) %>% 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)), 
+             x = avg_share, color = persona_trust)) +
+  geom_pointrange(size = 0.75, fatten = 1.5, 
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+  scale_color_manual(values = clrs_ngo_pairs[[3]], 
+                     guide = guide_legend(reverse = TRUE,
+                                          override.aes = list(size = 0.25,
+                                                              linetype = 0))) +
+  labs(x = "Average share of donations", y = NULL, color = NULL) +
+  facet_grid(rows = vars(persona_ideology), cols = vars(str_wrap(persona_experience, 100))) +
+  theme_ngo() +
+  theme(panel.grid.major.y = element_blank(),
+        legend.key.width = unit(0.5, "lines"))
+```
 
-@fig:issue-social and @fig:relationship-social show the results of the market simulation across these three dimensions of persona characteristics, varying public affairs knowledge, political ideology, and social trust.
+Figures \@ref(fig:issue-social) and \@ref(fig:relationship-social) show the results of the market simulation across these three dimensions of persona characteristics, varying public affairs knowledge, political ideology, and social trust.
 Personas respond differently to organizational issue areas.
-In @fig:issue-social, those who follow the news and travel abroad are more likely to prefer donating to human rights organizations than their less knowledgeable and less traveled counterparts.
+In Figure \@ref(fig:issue-social), those who follow the news and travel abroad are more likely to prefer donating to human rights organizations than their less knowledgeable and less traveled counterparts.
 Personas who do not follow the news or travel show a greater preference for emergency response and refugee relief organizations.
@@
 
-![Average predicted donation market shares across all personas, segmented by persona public affairs knowledge, political ideology, and social trust across different NGO–host government relationships](output/figures/relationship-social.pdf){#fig:relationship-social}
+```{r relationship-social, fig.width=6, fig.height=4, fig.asp=NULL, out.width="100%", fig.cap="Average predicted donation market shares across all personas, segmented by persona public affairs knowledge, political ideology, and social trust across different NGO–host government relationships"}
+sim_final %>% 
+  group_by(org_relationship, persona_trust, persona_ideology, persona_experience) %>% 
+  summarize(avg_share = mean(share)) %>% 
+  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
+             x = avg_share, color = persona_trust)) +
+  geom_pointrange(size = 0.75, fatten = 1.5,
+                  aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
+  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
+  scale_color_manual(values = clrs_ngo_pairs[[3]], 
+                     guide = guide_legend(reverse = TRUE,
+                                          override.aes = list(size = 0.25,
+                                                              linetype = 0))) +
+  labs(x = "Average share of donations", y = NULL, color = NULL) +
+  facet_grid(rows = vars(persona_ideology), cols = vars(str_wrap(persona_experience, 100))) +
+  theme_ngo() +
+  theme(panel.grid.major.y = element_blank(),
+        legend.key.width = unit(0.5, "lines"))
+```
 
-@fig:relationship-social shows how personas respond to different NGO–host government relationships.
+Figure \@ref(fig:relationship-social) shows how personas respond to different NGO–host government relationships.
 Public affairs knowledge and experience has little effect on donor preferences, as the average market shares are roughly identical across the two columns of the figure.
@@
 Some perspectives see philanthropy as more of a strategic long-term practice addressing the root causes of issues, and charity as a more short-term practice focused on providing immediate relief.
-But many scholars see philanthropy as essentially synonymous with charitable donations, as the latter can also address longer-term or strategic isssues [@Castle:2004].
+But many scholars see philanthropy as essentially synonymous with charitable donations, as the latter can also address longer-term or strategic issues [@Castle:2004].
 Despite these subtle differences, we use the terms inter-changeably here both because previous literature does so, and because in the case of giving to NGOs during crackdown, individuals could be giving to nonprofits both for immediate relief as well as long-term strategic purposes.

### 2021-04-17 manuscript/appendix.Rmd
Make target for appendix

@@
   email: aheiss@gsu.edu
-date: "October 2, 2020"
+date: "April 17, 2021"
 title-page: false

### 2021-04-17 _targets.R

@@ -89,7 +89,7 @@ list(
                csl = csl,
                bib_file,
                support_folder = "output/html-support"),
-             format = "file")#,
+             format = "file"),#,
   # tar_target(pdf,
   #            render_pdf(
   #              input = main_manuscript,
@@ -117,4 +117,16 @@ list(
   #              input_bib = bib_file,
   #              output = here_rel("manuscript", "output", "extracted-citations.bib")),
   #            format = "file")
+  tar_target_raw("appendix", here_rel("manuscript", "appendix.Rmd"),
+                 format = "file",
+                 deps = c("bib_file",
+                          tar_knitr_deps(here_rel("manuscript", "appendix.Rmd")))),
+  tar_target(app_html,
+             render_html(
+               input = appendix,
+               output = here_rel("manuscript", "output", "appendix.html"),
+               csl = csl,
+               bib_file,
+               support_folder = "output/html-support"),
+             format = "file")
 )

### 2021-04-17 manuscript/manuscript.Rmd
Full support for all rmarkdown outputs

@@
 library(kableExtra)
+library(huxtable)
 library(patchwork)
@@
 The latter trend has also been exacerbated by a preference among donors working in official aid and the democracy promotion establishment to gradually increase funding directed towards tame causes, at the expense of more contentious causes.
-This is because many tame causes can have easily quantifiable, measurable outputs, which makes it clear to show a program’s effectiveness over time (Bush 2015).
+This is because many tame causes can have easily quantifiable, measurable outputs, which makes it clear to show a program's effectiveness over time [@Bush:2015].
 
@@
 Individual donors do not use the same performance-based metrics as official donors [@desaikharas].
-Rather, individual donors often use heuristics to simply their decision-making, making cursory judgments about an organization’s issue area, mission, vision, and values and seek out supplementary information from friends, family, and acquaintances [@TBPrakash:2017; @SzperPrakash:2011].
+Rather, individual donors often use heuristics to simply their decision-making, making cursory judgments about an organization's issue area, mission, vision, and values and seek out supplementary information from friends, family, and acquaintances [@TBPrakash:2017; @SzperPrakash:2011].
 Due to these differences, individual donors can help address some of the challenges arising from reduced public funding available to INGOs.
@@
 ```{r organization-attributes-full}
-orgs$org_attributes %>% 
+tbl_org_attributes_caption <- "Organization attributes varied in the experiment. Each participant saw repeated combinations of attributes, with one attribute randomly selected from each column."
+
+tbl_org_attributes <- orgs$org_attributes %>% 
   select(Organization, `Issue area`, `Organizational practices`, 
-         `Funding sources`, `Relationship with government`) %>% 
-  kbl(align = "lllll",
-      caption = "Organization attributes varied in the experiment. Each participant saw repeated combinations of attributes, with one attribute randomly selected from each column.") %>% 
-  kable_styling()
+         `Funding sources`, `Relationship with government`)
+
+if (!is_docx) {
+  tbl_org_attributes %>%
+    kbl(align = c("l", "l", "l", "l", "l"),
+        booktabs = TRUE, linesep = "\\addlinespace",
+        caption = tbl_org_attributes_caption) %>% 
+    kable_styling() %>% 
+    column_spec(1:5, width = "0.17\\\\textwidth")
+} else {
+  tbl_org_attributes %>% 
+    hux() %>% 
+    set_font_size(10) %>%
+    set_all_padding(3) %>% 
+    set_top_border(1, everywhere) %>%
+    set_bottom_border(c(1, 5), everywhere) %>%
+    set_width(1) %>% 
+    set_wrap(TRUE) %>% 
+    huxtable::set_caption(tbl_org_attributes_caption) %>% 
+    huxtable::as_flextable() %>% 
+    flextable::font(fontname = "Times New Roman")
+}
 ```
@@
 ```{r sample-details}
-participant_summary %>% 
+tbl_participant_summary_caption <- "Summary of individual respondent characteristics"
+
+tbl_participant_summary <- participant_summary %>% 
   select(Question = clean_name,
@@
          N = count,
-         `%` = nice_prop) %>% 
-  kbl(align = "lllcc",
-      caption = "Summary of individual respondent characteristics") %>% 
-  pack_rows(index = table(fct_inorder(participant_summary$category))) %>%
-  collapse_rows(columns = 1, valign = "top") %>% 
-  kable_styling()
+         `%` = nice_prop)
+
+if (!is_docx) {
+  tbl_participant_summary %>% 
+    kbl(align = c("l", "l", "c", "c"),
+        longtable = TRUE, booktabs = TRUE, linesep = "",
+        caption = tbl_participant_summary_caption) %>% 
+    pack_rows(index = table(fct_inorder(participant_summary$category)),
+              latex_gap_space = "1.5em", indent = FALSE) %>%
+    collapse_rows(columns = 1, valign = "top", latex_hline = "major") %>% 
+    kable_styling(latex_options = c("repeat_header"))
+} else {
+  tbl_participant_summary %>% 
+    hux() %>% 
+    set_font_size(10) %>%
+    set_all_padding(3) %>% 
+    set_align(everywhere, 1:2, "left") %>% 
+    set_align(everywhere, 3:4, "center") %>% 
+    merge_repeated_rows(col = 1) %>% 
+    insert_row("Demographics", "", "", "", after = 1) %>% 
+    insert_row("\nAttitudes toward charity", "", "", "", after = 23) %>% 
+    insert_row("\nPolitics, ideology, and religion", "", "", "", after = 51) %>%
+    merge_cells(2, 1:2) %>%
+    merge_cells(24, 1:2) %>%
+    merge_cells(52, 1:2) %>%
+    set_bold(1, everywhere) %>%
+    set_bold(c(2, 24, 52), everywhere) %>%
+    set_top_border(1, everywhere) %>%
+    set_bottom_border(1, everywhere) %>%
+    set_bottom_border(c(7, 9, 14, 21, 23,
+                        26, 33, 40, 47, 51,
+                        55, 57, 59, 66, 73, 75, 78, 80), 
+                      everywhere) %>% 
+    set_width(1) %>% 
+    set_col_width(1, 0.25) %>%
+    set_col_width(2, 0.4) %>%
+    set_col_width(3:4, 0.1) %>%
+    set_wrap(TRUE) %>% 
+    huxtable::set_caption(tbl_participant_summary_caption) %>% 
+    huxtable::as_flextable() %>% 
+    flextable::font(fontname = "Times New Roman")
+}
 ```
@@
 ```{r persona-attributes}
-personas$persona_attributes %>% 
-  kbl(align = "lll",
-      caption = "Individual attributes varied in the simulation, resulting in 64 persona profiles") %>% 
-  kable_styling()
+tbl_persona_attributes_caption <- "Individual attributes varied in the simulation, resulting in 64 persona profiles"
+
+tbl_persona_attributes <- personas$persona_attributes
+
+if (!is_docx) {
+  tbl_persona_attributes %>% 
+    kbl(align = c("l", "l", "l"),
+        booktabs = TRUE, linesep = "\\addlinespace",
+        caption = tbl_persona_attributes_caption) %>% 
+    kable_styling() %>% 
+    column_spec(1, width = "0.3\\\\textwidth") %>% 
+    column_spec(2, width = "0.3\\\\textwidth") %>% 
+    column_spec(3, width = "0.3\\\\textwidth")
+} else {
+  tbl_persona_attributes %>% 
+    hux() %>% 
+    set_font_size(10) %>%
+    set_all_padding(3) %>% 
+    set_align(everywhere, everywhere, "left") %>% 
+    set_top_border(1, everywhere) %>%
+    set_bottom_border(c(1, 9), everywhere) %>%
+    set_width(1) %>% 
+    set_wrap(TRUE) %>% 
+    huxtable::set_caption(tbl_persona_attributes_caption) %>% 
+    huxtable::as_flextable() %>% 
+    flextable::font(fontname = "Times New Roman")
+}
 ```
@@
 ```{r organization-attributes}
-orgs$org_attributes %>% 
-  select(`Issue area`, `Relationship with government`, `Funding`) %>% 
-  kbl(align = "lll",
-      caption = "Organization attributes varied in the simulation, resulting in 24 hypothetical organizations") %>% 
+tbl_org_attributes_caption <- "Organization attributes varied in the simulation, resulting in 24 hypothetical organizations"
+
+tbl_org_attributes <- orgs$org_attributes %>% 
+  select(`Issue area`, `Relationship with government`, `Funding`)
+
+if (!is_docx) {
+  tbl_org_attributes %>% 
+    kbl(align = c("l", "l", "l"),
+        booktabs = TRUE, linesep = "\\addlinespace",
+        caption = tbl_org_attributes_caption) %>% 
     kable_styling()
+} else {
+  tbl_persona_attributes %>% 
+    hux() %>% 
+    set_font_size(10) %>%
+    set_all_padding(3) %>% 
+    set_align(everywhere, everywhere, "left") %>% 
+    set_top_border(1, everywhere) %>%
+    set_bottom_border(c(1, 9), everywhere) %>%
+    set_width(1) %>% 
+    set_wrap(TRUE) %>% 
+    huxtable::set_caption(tbl_org_attributes_caption) %>% 
+    huxtable::as_flextable() %>% 
+    flextable::font(fontname = "Times New Roman")
+}
 ```
@@
 
+example_personal_results_caption <- "Sample simulation output"
+
+if (!is_docx) {
   example_persona_results_small %>% 
-  mutate(Organization = text_spec(Organization, bold = Organization == "Total")) %>% 
-  kbl(align = "lcc",
-      caption = "Sample simulation output",
-      escape = FALSE) %>% 
-  kable_styling()
+    # mutate(Organization = text_spec(Organization, bold = Organization == "Total")) %>% 
+    kbl(align = c("l", "c", "c"),
+        booktabs = TRUE, linesep = "\\addlinespace",
+        caption = example_personal_results_caption) %>% 
+    kable_styling() %>% 
+    column_spec(1, width = "0.2\\\\textwidth") %>% 
+    column_spec(2, width = "0.35\\\\textwidth") %>% 
+    column_spec(3, width = "0.35\\\\textwidth")
+} else {
+  example_persona_results_small %>% 
+    hux() %>% 
+    set_font_size(10) %>%
+    set_all_padding(3) %>% 
+    set_align(everywhere, 1, "left") %>% 
+    set_align(everywhere, 2:3, "center") %>% 
+    set_top_border(1, everywhere) %>%
+    set_bottom_border(c(1, 12, 13), everywhere) %>%
+    set_width(1) %>% 
+    set_wrap(TRUE) %>% 
+    huxtable::set_caption(example_personal_results_caption) %>% 
+    huxtable::as_flextable() %>% 
+    flextable::font(fontname = "Times New Roman")
+}
 ```

### 2021-04-17 _targets.R

@@ -89,34 +89,36 @@ list(
                csl = csl,
                bib_file,
                support_folder = "output/html-support"),
-             format = "file"),#,
-  # tar_target(pdf,
-  #            render_pdf(
-  #              input = main_manuscript,
-  #              output = here_rel("manuscript", "output/manuscript.pdf"),
-  #              bibstyle = bibstyle,
-  #              bib_file),
-  #            format = "file"),
-  # tar_target(ms_pdf,
-  #            render_pdf_ms(
-  #              input = main_manuscript,
-  #              output = here_rel("manuscript", "output/manuscript-ms.pdf"),
-  #              bibstyle = bibstyle,
-  #              bib_file),
-  #            format = "file"),
-  # tar_target(docx,
-  #            render_docx(
-  #              input = main_manuscript,
-  #              output = here_rel("manuscript", "output/manuscript.docx"),
-  #              csl = csl,
-  #              bib_file),
-  #            format = "file"),
-  # tar_target(bib,
-  #            extract_bib(
-  #              input_rmd = main_manuscript,
-  #              input_bib = bib_file,
-  #              output = here_rel("manuscript", "output", "extracted-citations.bib")),
-  #            format = "file")
+             format = "file"),
+  tar_target(pdf,
+             render_pdf(
+               input = main_manuscript,
+               output = here_rel("manuscript", "output", "manuscript.pdf"),
+               bibstyle = bibstyle,
+               bib_file),
+             format = "file"),
+  tar_target(ms_pdf,
+             render_pdf_ms(
+               input = main_manuscript,
+               output = here_rel("manuscript", "output", "manuscript-ms.pdf"),
+               bibstyle = bibstyle,
+               bib_file),
+             format = "file"),
+  tar_target(docx,
+             render_docx(
+               input = main_manuscript,
+               output = here_rel("manuscript", "output", "manuscript.docx"),
+               csl = csl,
+               bib_file),
+             format = "file"),
+  tar_target(bib,
+             extract_bib(
+               input_rmd = main_manuscript,
+               input_bib = bib_file,
+               output = here_rel("manuscript", "output", "extracted-citations.bib")),
+             format = "file"),
+  
+  # Appendix stuff
   tar_target_raw("appendix", here_rel("manuscript", "appendix.Rmd"),
                  format = "file",
                  deps = c("bib_file",
@@ -128,5 +130,26 @@ list(
                csl = csl,
                bib_file,
                support_folder = "output/html-support"),
[…]

### 2021-04-17 _packages.R
Use renv

@@ -1,0 +1,16 @@
+# Generated by targets::tar_renv(): do not edit by hand
+library(bs4Dash)
+library(clustermq)
+library(fs)
+library(future)
+library(gt)
+library(here)
+library(pingr)
+library(rstudioapi)
+library(scales)
+library(shiny)
+library(shinycssloaders)
+library(shinyWidgets)
+library(tidyverse)
+library(visNetwork)
+library(withr)

### 2021-04-17 _targets.R

@@ -11,11 +11,7 @@ options(tidyverse.quiet = TRUE,
 
 set.seed(1746)  # From random.org
 
-tar_option_set(packages = c("tidyverse", "here", "fs", "scales",
-                            "readxl", "haven", "sf", "lubridate", "scales",
-                            "janitor", "kableExtra", "huxtable", "modelsummary",
-                            "knitr", "withr", "flextable", "testthat", "DT",
-                            "brms", "tidybayes", "broom", "cmdstanr", "jsonlite"))
+tar_option_set(packages = c("tidyverse", "here", "fs", "scales", "withr"))
 
 source("R/funs_data-generation.R")
 source("R/funs_survey.R")

### 2021-04-17 analysis/03_analysis.Rmd
A bunch of edits

@@
 library(patchwork)
-library(ggstance)
 library(here)

### 2021-04-17 manuscript/manuscript.Rmd
A bunch of edits

@@
 Barriers to funding are especially pervasive and restrict the ability of NGOs to secure financial resources.
-Restrictive states may prevent the transfer of foreign funds to NGOs based on the origin of these funds and which issues these funds can be used towards.
+Restrictive states may prevent the transfer of foreign funds to NGOs based on the origin and purposes of these funds.
 
-As a result of these laws, foreign aid (also referred to as public or official aid) channeled through NGOs has decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
+As a result of these laws, public or official foreign aid channeled through international NGOs (INGOs) has decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
 However, philanthropy from private donors and foundations is not as adversely affected [@McGill:2018].
 Many foundations have continued channeling funds to countries with hostile legal environments [@NeedlesWolcheckSato:2018].
-Given this trend of reduced public aid following restricted legal environments for NGOs abroad, INGOs may need to devote more resources to fundraise from individual donors.
+Given the reduction of foreign aid following restricted legal environments abroad, INGOs may need to devote more resources to fundraise from individual donors.
 
 Individual private donations are a critical source of INGO funding.
-While total private philanthropy[^phildef] in the United States has grown substantially over time, it is notable that private giving to NGOs working in international affairs  and international affairs-focused organizations are one of only two categories of organizations that have continued experiencing substantial growth in giving and reached \$22.08 billion in 2018 [@givingusa:2019].[^intlaffairs] Most of this growth is driven by individuals making small-scale or micro-donations.[^smalldonors] In 2017, 70% of donations to international affairs NGOs came from individuals, rising to 86% in 2018 [@givingusa:2019].
+While total private philanthropy[^phildef] in the United States has grown over time, it is notable that private giving to NGOs working on international affairs-focused issues are one of only two categories of organizations that have continued experiencing substantial growth in giving, reaching \$22.08 billion in donations in 2018 [@givingusa:2019].[^intlaffairs] Most of this growth is driven by individuals making small-scale (up to \$50) or micro-donations (between \$0.25–\$10) [@SaxtonWang:2014].
+In 2017, 70% of donations to international affairs NGOs came from individuals, rising to 86% in 2018 [@givingusa:2019].
 But relying on individual donors means that NGOs must consider their preferences when fundraising.
@@
 
-There exists a robust scholarship on the determinants of individual-level philanthropy to domestic causes.
+A robust scholarship already examines the determinants of individual-level philanthropy to domestic causes.
 But the dynamics of *international* giving to NGOs are under-examined in the literature on individual donor attributes and preferences.[^exceptions] Motivating individuals to donate to international causes is hard as the number of recipients are large and far removed from the donor [@CasaleBaumann:2015, 100].
-Trust is an essential component for INGO sustainability and for many nonprofits, trust often translates into grants and donations [@coombs2007].
+Trust is an essential component for INGO sustainability—for many nonprofits, trust often translates into grants and donations [@coombs2007].
 Geography often impedes donors' direct evaluation of their work and trust is one of the most influential criteria that private donors use when deciding which nonprofits to support [@prakash2010trust; @bekkers2003trust].
-A lack of trust could be further fueled by legal trouble with the NGO host government—a dynamic that individuals may not wish to enter with their dollars.
-How does trust in NGOs influence individuals' preferences to donate, especially when groups face crackdown?
+A lack of trust could be further fueled by legal trouble with the INGO host government—a dynamic that individuals may not wish to enter with their dollars.
+How does trust in INGOs influence individuals' preferences to donate, especially when groups face crackdown?
 
@@
 Instead, they prefer donating to NGOs with friendly host-country relationships and working on less contentious issues like emergency response and refugee relief.
-Personas with higher trust are more comfortable donating to legally besieged INGOs.
-Our findings imply that individual donors with high trust would continue remaining supportive of INGOs when they face criticism and crackdown from foreign governments.
-On the other hand, government crackdown may further sour NGOs least trusting individual donors.
+Personas with higher trust are more comfortable donating to legally besieged organizations.
+Our findings imply that individual donors with high trust would remain supportive of INGOs when they face criticism and crackdown from foreign governments.
+On the other hand, government crackdown may further sour INGOs' least trusting donors.
 
 This study contributes both to scholarship and practice in public policy, nonprofits, and philanthropy in three important ways.
-It helps us understand how the international community and NGOs might respond to the phenomenon of closing civic space, which does not appear to be receding.
+It helps us understand how the international community and NGOs might respond to the phenomenon of closing civic space.
 Most NGOs working internationally have previously relied on government and foundation funding.
-But in the face of decreasing funds from official donors, our results show that INGOs can rely on individual donors, specifically, their most trusting donors, when groups face a hostile environment abroad.
+But in the face of decreasing funds from official donors, our results show that INGOs can rely on individual donors—particularly their most trusting donors—when organizations face a hostile environment abroad.
 These findings lend support to previous literature arguing that trust matters  when individuals donate to organizations acting under great uncertainty or working towards difficult goals [@Wiepking:2010].
@@
 However, existing research is unclear about which frames are effective when making appeals to individual donors considering international philanthropy.
-Since our study looks at multiple organizational and host country factors, our results can help NGOs frame their appeals.
-In particular, our results show that NGOs may benefit from publicizing crackdown at least towards their most trusting donors.
+Since our study looks at multiple organizational and host country factors, our results can help INGOs frame their appeals.
+In particular, our results show that INGOs may benefit from publicizing crackdown at least towards their most trusting donors.
 
-Finally, while research in public policy examines giving to NGOs, philanthropy is not seen as relevant by international relations as a discipline [@youde2019].
+Finally, while research in public policy examines giving to NGOs, the discipline of international relations tends to see philanthropy as less relevant [@youde2019].
 However, philanthropy—particularly donations received by INGOs—can help us understand changes in the dynamics of global governance.
@@
 As @youde2019 [p.
-44] points out, it changes our conceptions of individuals being passive recipients to active entities that are not merely objects of governance.
-Thus, it can shed light on the changing logic of global governance.
+44] points out, studying philanthropy changes our conceptions of individuals being passive recipients to active entities that are not merely objects of governance, and can thus shed light on the changing logic of global governance.
 
@@
 In countries with weak institutions and poor governance, where direct aid transfers to governments raise issues of misuse and bureaucratic inefficiency, donors specifically seek out NGOs for projects [@Dietrich2013].
-However, NGO-state relationships have evolved over time—in the 1950s and 60s, international assistance channeled through NGOs aimed at producing socio-economic change rather than political progress.
+However, NGO-state relationships have also evolved—in the 1950s and 60s, international assistance channeled through NGOs aimed at producing socioeconomic change rather than political progress.
 But in the aftermath of the dissolution of the Soviet Union, many NGOs had the explicit goal of promoting democracy and bringing down authoritarian governments.
-Subsequently, many states perceive them as threatening and have sought to repress them.
+Subsequently, many states see NGOs as a threat and seek to repress them.
 
-Mre than 100 countries have proposed or enacted 244 measures restricting, repressing, or shutting down civil society since 2013 (ICNL 2021 CITATION FROM ISA PAPER).
-This has had a three-hold impact on INGOs.
+More than 100 countries have proposed or enacted 244 measures restricting, repressing, or shutting down civil society since 2013 [@icnl:2021].
+This has had a threefold impact on INGOs.
 First, it has led to a reduction in resources and grants available to INGOs.
@@
 Finally, in the worst-case scenario, this has led to a loss in INGOs' access to target countries—often also associated with the use of violence against INGOs and their employees.
-In this paper, we exlusively focus on the first dilemma—the reduction in INGO funding and possible responses to it.
+We focus exclusively on the first dilemma—the reduction in INGO funding and possible responses to it.
 
@@
 
-Many INGOs in the Global South receive funds from a variety of public and private sources each year.
+INGOs receive funds from a variety of public and private sources.
 Public funds—or traditional donor aid—channel money from official aid agencies through a variety of bilateral and multilateral institutions.
 Private sources include foundations, private corporations, and individuals.
-While INGOs have not been passive in responding to the crackdown on civil society, they face increasing obstacles from a funding perspective.
+While INGOs have not been passive in responding to the crackdown on civil society, they face increasing obstacles in funding.
+Closing civic space has resulted in net losses of income to INGOs, particularly in official bilateral and multilateral aid [@DupuyPrakash:2018]
 
-Closing civic space not just resulted in net losses of income to INGOs, particularly through official bilateral and multilateral aid [@DupuyPrakash:2018], it has also affected how and where funds are allocated.
+Legal crackdown has also affected how and where funds are allocated.
 Following the passage of anti-NGO laws, official donors move funds away from contentious causes such as human rights, media, corruption, advocacy, among others, towards tamer and more regime-compatible causes such as health, education [@ChaudhryHeiss:2018].
 The latter trend has also been exacerbated by a preference among donors working in official aid and the democracy promotion establishment to gradually increase funding directed towards tame causes, at the expense of more contentious causes.
-This is because many tame causes can have easily quantifiable, measurable outputs, which makes it clear to show a program's effectiveness over time [@Bush:2015].
+This is because many tame causes can have easily quantifiable, measurable outputs, which makes it easier to show a program's effectiveness over time [@Bush:2015].
 
@@
 Individual donors do not use the same performance-based metrics as official donors [@desaikharas].
-Rather, individual donors often use heuristics to simply their decision-making, making cursory judgments about an organization's issue area, mission, vision, and values and seek out supplementary information from friends, family, and acquaintances [@TBPrakash:2017; @SzperPrakash:2011].
+Rather, individual donors often use heuristics to simply their decision-making, making cursory judgments about an organization's issue area, mission, vision, and values and seek out supplementary information from friends, family, and acquaintances [@ChaudhryHeiss:2021; @TBPrakash:2017; @SzperPrakash:2011].
 Due to these differences, individual donors can help address some of the challenges arising from reduced public funding available to INGOs.
-To be clear, we are not arguing that giving by individual donors would be a perfect substitute for NGOs net loss of income or income for certain programs, but rather, an important supplement to reduced funding from foreign sources.
-Moreover, it would also be a supplement to private funding from foundations towards international nonprofits which has not been as adversely affected, with foundations continue to channel funds to countries with hostile legal environments [@NeedlesWolcheckSato:2018].
+To be clear, we are not arguing that individual giving would be a perfect substitute for NGOs' net loss of income—rather, private donations can be an important supplement when facing reduced funding.
+Moreover, private philanthropy can also supplement foundation funding, which has been less adversely affected by hostile legal environments [@NeedlesWolcheckSato:2018].
 
-However, research on the determinants of individual-level philanthropy for international causes—particularly towards organizations working in challenging environments—is still in its infancy due to the absence of expansive and high-quality data [@greenhill2013].
-Moreover, a majority of research on giving to international groups is restricted to elite high net-worth donors[^highnetworth] [@USTrust2014].
-We still know little about demographic traits and experiences that motivate or deter individuals to donate during shrinking civic space.
-Below, we look at key drivers of individual-level philanthropy and show how the importance of trust in donating during civic crackdowns.
+Research on the determinants of individual-level philanthropy for international causes—particularly towards organizations working in challenging environments—is still in its infancy due to the absence of high-quality data [@greenhill2013].
+Moreover, a majority of research on giving to international groups is restricted to elite high net-worth donors who earn more than \$200,000 annually or have more than a \$1 million in assets [@USTrust2014].
+We know little about demographic traits and experiences that influence the choice to donate to organizations facing shrinking civic space.
+Below, we look at key drivers of individual-level philanthropy and highlight the importance of trust when donating during legal crackdowns.
 
@@
 
-Social capital, particularly associational capital, or "the networks of formal and informal relationships to which people are associated," is often considered an important indicator of giving [@havens2007, 240].
+Social capital, particularly associational capital, or "the networks of formal and informal relationships to which people are associated," is an important indicator of giving [@havens2007, 240].
 Volunteering exposes individuals to the need for donations, making them feel more compelled to donate [@hossainlamb2012].
@@
 
-Higher education also influences charitable-giving decisions as it fosters prosocial motivations.
+Higher education also influences philanthropic decisions as it fosters prosocial motivations.
 Education brings people into social networks that entail a higher level of solicitation, which is vital in giving to international causes [@BekkersWiepking:2011].
@@
 @Micklewright:2009 show that higher education matters more for donating to international relief organizations than donating to domestic organizations.
-
 A number of NGOs facing crackdowns abroad also work on issues that may be seen as "contentious," including human rights, elections, corruption, advocacy, and media freedom—issues that may have a harder time attracting funds due to their non-essential nature when compared to causes like health, education, sanitation, and social services [@Bush:2015].
-However, additional education has been shown to increase abstract thinking [@wiepkingmaas, 1978], which may be necessary to donate to causes that do not have quantifiable goals, including politically sensitive or contentious causes mentioned above.
+However, additional education has been shown to increase abstract thinking [@wiepkingmaas, 1978], which may be necessary to donate to more contentious causes without easily quantifiable goals.
 
@@
 
-We explore this question using a conjoint experiment conducted with a nationally representative sample in the U.S.
-Importantly, because there is so little research about international donations during legal crackdown by host governments, our analysis and results are exploratory and descriptive.
-Accordingly, we do not test specific hypotheses or theories.
-
-TODO: Fix final point - connect testing stuff with existing theories - we don't have a list of things to test
-
-However, we do talk about causal effects given that we conduct an experiment that varies a number of factors in order to elicit opinions from respondents.
-Instead, we structure our analysis around broader themes from the existing literature and investigate how donors' (1) demographic characteristics, (2) public affairs knowledge and experience, and (3) levels of trust in government, charitable work, and associational life change individual donation preferences across different organizational issue areas, relationships with host governments, and funding sources.
-Our innovative experimental approach provides rich quantitative details of individual and organizational characteristics simultaneously and reveals unique insights into donor motivations that both confirm and expand previous research.
+We structure our analysis around broader themes in previous research on individual determinants of philanthropy and we investigate how donors' (1) demographic characteristics, (2) public affairs knowledge and experience, and (3) levels of trust in government, charitable work, and associational life each shape individual donation preferences when simultaneously interacted with different organizational issue areas, relationships with host governments, and funding sources.
+Our experimental approach provides rich quantitative details of individual and organizational characteristics and reveals unique insights into private donor motivations.
 
@@
 
-We use a conjoint experiment to study the simultaneous effects of organizational characteristics and individual attributes on individuals' preferences to donate to a nonprofit organization.
+We explore the interaction between individual and organizational characteristics using a conjoint experiment conducted with a nationally representative sample in the U.S.
 Conjoint analysis allows us to elicit donor preferences without respondents explicitly stating their exact preferences.
-This kind of analysis is commonly used in marketing to reveal consumer preferences for hypothetical products, and has become increasingly popular in political science and public policy [@Helfer:2016; @Mummolo:2016; @KnudsenJohannesson:2019].
-Because we are interested in exploring the complexity behind the decision to donate, we apply conjoint methods to the study of nonprofits and philanthropy.
+This kind of experiment is commonly used in marketing to reveal consumer preferences for products and has become increasingly popular in political science and public policy [@KnudsenJohannesson:2019].
+Because we are interested in exploring the complexity behind the decision to donate, we apply conjoint methods to the study of nonprofits and philanthropy, where we can study the simultaneous effects of organizational characteristics and individual attributes on individuals' preferences to donate to an INGO.
 
-In our experiment, we presented respondents with four randomly selected international nonprofit organizations with four randomly assigned features.[^appendix-survey] We included organizations that are associated with a range of contentious and noncontentious issues: Amnesty International, Greenpeace, Oxfam, and the International Committee of the Red Cross.
+In our experiment, we presented respondents with four randomly selected international nonprofit organizations with four randomly assigned features.[^appendix-survey] We used organizations that are associated with a range of contentious and noncontentious issues: Amnesty International, Greenpeace, Oxfam, and the International Committee of the Red Cross.
 Because of their strong name recognition, these organizations (and others like World Vision, the World Wildlife Fund, and Médecins Sans Frontières) are commonly used in experimental surveys on philanthropy [@FaulknerTruongRomaniuk:2015].
@@
 ```{r organization-attributes-full}
-tbl_org_attributes_caption <- "Organization attributes varied in the experiment. Each participant saw repeated combinations of attributes, with one attribute randomly selected from each column."
+tbl_org_attributes_caption <- "Organization attributes varied in the experiment.
+Each participant saw twelve sets of four combinations of attributes, with one attribute randomly selected from each column."
 
@@
 
-The hypothetical organizations are based on random combinations of features, including one of four issue areas, the presence or absence of two organizational practices, one of three funding sources, and one of three relationships with host governments (see Table \@ref(tab:organization-attributes-full); see also Q3.1 in the survey text in the appendix).
-Respondents saw twelve sets of four hypothetical organizations out of 288 (4 × 4 × 2 × 3 × 3) possible combinations, meaning no single respondent was offered every combination.
-While not every combination necessarily reflected reality—for instance, a respondent might have been asked to compare a fictional Amnesty International that focuses on environmental issues and that is funded by private donations with a Greenpeace that focuses on human rights and that is funded by government grants—it is not important that these features align with true organizational characteristics, since the goal of these repeated hypothetical questions is to identify which attributes are the most salient for donors.
+After collecting information about demographics and attitudes towards charities, volunteering, and social interests, we presented respondents with twelve sets of four hypothetical organizations and asked them to select the one they would most likely donate to.
+Each organization was randomly generated with one feature from each of the columns in Table \@ref(tab:organization-attributes-full): issue area, organizational practices, funding sources, and relationship with host government.
+While not every one of the 288 (4 × 4 × 2 × 3 × 3) possible configurations necessarily reflects reality—for instance, a respondent might have been asked to compare a fictional Amnesty International that focuses on environmental issues and that is funded by private donations with a Greenpeace that focuses on human rights and that is funded by government grants—it is not important that these features align with true organizational characteristics, since the goal of these repeated hypothetical questions is to identify which attributes are the most salient for donors.
 
@@
 population.
-To participate in the study, respondents were first screened based on their charitable activities.
-Those who indicated that they gave to charity once every few years or never were disqualified.
+To participate in the study, respondents were first screened based on their charitable activities—those who indicated that they gave to charity once every few years or less were disqualified.
 After screening, we collected a sample of 1,016 respondents, which is sufficient for model estimation.[^sample-size]
@@
 
-We analyze the effect of different combinations of organizational features and individual respondent attributes with a two-level hierarchical Bayesian multinomial logit model.[^model-details] Simply put, the first level of the model predicts individual donor preferences for various combinations of features (e.g.
-the combination of human rights issues, financial transparency, government funding, and government crackdown), while the second level predicts the heterogeneity of these fitted preferences as a function of individual donor characteristics.
+We analyze the effect of different combinations of organizational features and individual respondent attributes with a two-level hierarchical Bayesian multinomial logit model.[^model-details] Simply put, the first level of the model predicts individual donor preferences for various combinations of organizational features (e.g.
+the combination of human rights issues, financial transparency, government funding, and government crackdown), while the second level predicts the heterogeneity of these fitted preferences as a function of individual donor characteristics (e.g.
+education, age, and attitudes towards charity, voluntarism, and religion).
 
@@
 
-We then combine these different scenarios of donor and organization attributes with the coefficients from a multinomial multilevel regression model to calculate the probability that each simulated persona has of giving to specific combinations of organizational attributes.
+We then combine these different scenarios of donor and organization attributes with the coefficients from the hierarchical regression model to calculate each persona's probability of donating to specific combinations of organizational attributes.
 Any individual characteristics that we do not explicitly vary in Table \@ref(tab:persona-attributes) are held at their means or modal values from the survey sample.
 Table \@ref(tab:sim-output) provides an example of the simulation output, showing how two different personas are predicted to allocate donations to organizations with various characteristics.
-The proportion of donations from each persona sums to 100%, as every persona is guaranteed to make a donation.
+The proportion of donations from each persona sums to 100%, as every simulated persona is guaranteed to make a donation.
 
@@
 
-Relying on simulation methods offers useful analytic benefits.
-Rather than interpret individual marginal effects from a regression model, we can explore multiple moving parts from the same model simultaneously to understand how individual characteristics interact with each other.
+Simulation methods offer useful analytic benefits.
+Instead of interpreting marginal coefficient effects from a regression model, we can explore multiple moving parts from the same model simultaneously to understand how individual characteristics interact with each other.
 This allows us to more fully explore our key research questions and see which kinds of donors are more or less likely to consider specific organizational attributes when deciding to donate, and which donor characteristics are associated with the propensity to donate.
 Importantly, each persona is an artificial construct.
-While some survey respondents might match an exact persona profile, others may not.
-This is acceptable in simulations as each combination of persona characteristics is plausible in the real world.
+While some survey respondents might match an exact persona profile, many do not.
+This is standard in simulations as each combination of persona characteristics is plausible in the real world.
+These simulated findings are more abstract than the results from an ordinary survey sample, but the simulation results allow us to explore the interaction between donor preferences and organization characteristics, including whether they face legal restrictions abroad.
+The results ultimately show which combination of organizational features each persona is most likely to prefer when choosing to donate.
 
@@
 
-These simulated findings are more abstract than the results from an ordinary survey sample.
-But by using simulations, we can discover interesting patterns of donor preferences when faced with organizations focusing on a variety of issues, funding sources, and legal restrictions abroad.
-Our market simulation reveals which combination of organizational features each persona is most likely to express a preference for donating to.
-We examine the results of the simulation in three stages, looking at how personas with different (1) demographic characteristics, (2) public affairs knowledge and experience, and (3) levels of trust in government, charitable work, and associational life change their donation preferences across different organizational issue areas, relationships with host governments, and funding sources.
+We examine the results of the simulation in three stages, varying persona (1) demographics, (2) views on politics and public affairs, and (3) social views (i.e.
+the three columns of Table \@ref(tab:persona-attributes)).
+Within these three broader categories, we explore the interaction of persona characteristics with different organizational configurations of issue areas, funding sources, and relationships with government (i.e.
+the three columns of Table \@ref(tab:organization-attributes)).
 
-## Patterns across demographics
-
-We begin by looking at differences in donation preferences across a range of basic demographic characteristics.
 The four panels of Figure \@ref(fig:income) show the average predicted market share for different organizational issue areas, funding sources, and relationships with host governments across different levels of persona income, with two different cutpoints for high and low income.
-To ease with modeling and interpretation, we split high- and low-income personas based on the 2017 U.S.
-median income (\$61,372), showing personas with incomes higher and lower than the national median.
-Because there is wide variation in donor incomes in the U.S., we also show the results from a simulation model with a more extreme split in income, holding annual persona income at \$50,000 and \$100,000+.
+To ease with modeling and interpretation, we split high- and low-income personas based on 2017 U.S.
+median income (\$61,372).
+Due to wide variation in donor incomes in the U.S., we also show the results from a simulation model with a more extreme split, holding annual persona income at \$50,000 and \$100,000+.
 The difference in the division of high and low income makes no difference in the market shares across issue areas and funding sources, but there are substantial income-based differences across different relationships with host governments.
@@
 
-## Patterns across public affairs knowledge, experience, and social trust
-
-We next look at how differences in public affairs knowledge, experience, and political ideology influence a persona's propensity to donate to an organization.
-We vary personas along two dimensions: (1) political ideology, with semi-liberal and semi-conservative political leanings (2 and 5 on a 7-point scale), and (2) knowledge and experience with public affairs and the news, with personas that either follow national and international news and that have travelled abroad or personas that do not follow the news or travel.
+Next, we next examine how differences in public affairs knowledge, experience, and political ideology influence a persona's propensity to donate to an organization.
+We vary personas along two dimensions: (1) political ideology, with semi-liberal and semi-conservative political leanings (2 and 5 on a 7-point scale), and (2) knowledge and experience with public affairs and the news, with personas that either follow national and international news and that have traveled abroad or personas that do not follow the news or travel.
 
 We combine these dimensions with an additional set of donor characteristics that vary a persona's level of social trust.
-Personas with high levels of trust have high trust in political institutions and charities, think people should be more charitable, frequently volunteer, donate to charity once a month, have a history of political activism, and are members of an association.
+Personas with high levels of trust support political institutions and charities, think people should be more charitable, frequently volunteer, donate to charity once a month, have a history of political activism, and are members of an association.
 Personas with low levels of trust have the opposite characteristics: they do not trust political institutions or charities, rarely donate or volunteer, and are not members of associations.
@@
 Personas with high levels of trust, on the other hand, seem to stick with legally besieged organizations and show targeted groups the benefit of the doubt.
-The global crackdown on NGOs thus sours NGOs' least trusting individual donors.
+The global crackdown on NGOs thus sours organizations' least trusting individual donors.
 Overall, our results support research that donors with high levels of trust are more active in giving than those with low levels of trust [@sargeant2008] and that trust especially matters when individuals donate to organizations working under great uncertainty and towards difficult goals [@Wiepking:2010].
@@
 
-The conjoint experiment conducted among a nationally representative sample of U.S.
-respondents with a prior history of charitable giving raises two main concerns for inference.
-It may be the case that respondent answers—and the corresponding beahavior of simulated personas—could potentially be driven by their priors towards these organizations.
-In addition, there are also important questions about the generalizability of these results outside the American context.
+Our conjoint experiment raises two main concerns for inference: (1) prior knowledge and opinions about these organizations could influence respondents' choices, and (2) there are questions about the generalizability of these results outside the American context.
 We explore both below.
 
-Given the nature of conjoint experiments, the randomly presented organizations may have influenced respondent choices.
-All four organizations are well-known, and it is likely that participant responses reflect prior beliefs and news coverage about Amnesty, Oxfam, Greenpeace, and the Red Cross.
+All four organizations from the experiment are well-known, and it is likely that participant responses reflect prior beliefs and news coverage about Amnesty, Oxfam, Greenpeace, and the Red Cross.
 For instance, in February 2018, news broke out about sexual abuse and misconduct at Oxfam and several other prominent organizations, including Amnesty International and Save the Children.
@@
 donors, given Oxfam is based in the UK, and "media narratives are often not as unsupportive as often assumed" [@BanksSchulpenBrockington:2020, 703].
-Moreover, research shows that when donors feel solidarity or an ideological connection with an NGO – especially because of the cause espoused by them – they are likely to consider the organization to be trustworthy, despite the lack of full transparency and oversight [@KeatingThrandardottir:2017].
-Even watchdog organizations such as Charity Navigator and Better Business Bureau Giving Alliance have been found to not significantly impact individuals’ trust in nonprofit organizations.
+Moreover, research shows that when donors feel solidarity or an ideological connection with an NGO, they are likely to consider the organization to be trustworthy, despite the lack of full transparency and oversight [@KeatingThrandardottir:2017].
+Even watchdog organizations such as Charity Navigator and Better Business Bureau Giving Alliance have been found to not significantly impact individuals' trust in nonprofit organizations.
 Rather, trust is more likely fostered through local networks and personal scrutiny [@TBPrakash:2017, 643].
@@
 
-The survey conducted among a random sample of U.S.
+The sample of U.S.
 residents with a prior history of charitable giving also raises questions about generalizability and external validity.
@@
 We argue that individual donors can be useful in sustaining the operations of groups working in challenging environments.
-Individual donors do not use the same perfomance-based metrics as official aid donors and use heuristics to smiplify their decision-making.
+Individual donors do not use the same performance-based metrics as official aid donors and use heuristics to simplify their decision-making.
 The role of trust may be important in understanding donations preferences towards INGOs working in challenging contexts.
@@
 However, the larger challenge may be addressing the concerns of donors with low levels of trust, as they are the least likely to donate organizations facing criticism and crackdown abroad.
-As @TBPrakash:2017 argue, "trust in the charity sector cannot be assumed: the sector has to demonstrate that the trust it receives is justified." (643).
+As @TBPrakash:2017 argue, "trust in the charity sector cannot be assumed: the sector has to demonstrate that the trust it receives is justified" (p.
+643).
 
@@
 However, some of the former are precisely the organizations facing crackdown.
-More research is needed to answer how contentious or advocacy organizations (as opposed to service nonprofits) can appeal to broader array of potential foreign donors to increase levels of charitable-giving towards them.
+More research is needed to answer how contentious or advocacy organizations can appeal to broader array of potential foreign donors to increase levels of charitable-giving towards them.
 
 To be clear, research on international giving by individuals, especially in the era of closing civic space, is not meant to find answers that can act as substitutes for strategic policy responses, especially by official aid donors and foundations.
-However, many NGOs are under immediate threat, and individual-level philanthropy can help support these organizations.
+However, many INGOs are under immediate threat, and individual-level philanthropy can help support these organizations.
 Existing initiatives such as the Lifeline Embattled CSO Assistance Funds provide models for channeling such funds.
@@
 \newpage
-
-[^smalldonors]: Micro-donations refer to donations between $0.25–$10; small donors are individuals who donate up to $50 [@SaxtonWang:2014].
 
@@
 
-[^highnetworth]: High-net worth households have greater than \$200,000 in annual household income and/or have more than \$1,000,000 in assets, excluding primary residence.
-
-[^phildef]: We use philanthropy to connote voluntary giving to promote the common good.
-While it can include grants given by foundations and corporations to nonprofit organizations, our focus is on individual giving.
-Some perspectives see philanthropy as more of a strategic long-term practice addressing the root causes of issues, and charity as a more short-term practice focused on providing immediate relief.
-But many scholars see philanthropy as essentially synonymous with charitable donations, as the latter can also address longer-term or strategic issues [@Castle:2004].
-Despite these subtle differences, we use the terms inter-changeably here both because previous literature does so, and because in the case of giving to NGOs during crackdown, individuals could be giving to nonprofits both for immediate relief as well as long-term strategic purposes.
+[^phildef]: We use "philanthropy" to connote voluntary giving to promote the common good.
+We focus on private individual giving rather than foundation or corporate giving.
+Some perspectives see philanthropy as a strategic long-term practice addressing the root causes of social issues, and charity as a short-term practice focused on providing immediate relief.
+But many scholars see philanthropy as essentially synonymous with charitable donations, as short-term giving can also address longer-term or strategic issues [@Castle:2004].
+We use the terms interchangeably since individuals could be giving to legally besieged nonprofits for either purpose.
 
@@
 
-    where $y$ = which alternative the respondent chooses to donate to, $X$ = design matrix of attribute levels (i.e.
-organizations, issue areas, organizational practices, funding sources, and government relations), $\beta$ = latent individual preferences for the attribute levels, $Z$ = matrix of individual-level covariates (i.e.
-demographics, political knowledge, attitudes towards charity, etc.), $\Gamma$ = matrix of coefficients mapping individual-level covariates onto the latent individual-level preferences, and $\varepsilon$ and $\xi$ = errors.
+    where $y$ = which alternative the respondent chooses to donate to, $X$ = design matrix of attribute levels (organizations, issue areas, organizational practices, funding sources, and government relations), $\beta$ = latent individual preferences for the attribute levels, $Z$ = matrix of individual-level covariates (demographics, political knowledge, attitudes towards charity, etc.), $\Gamma$ = matrix of coefficients mapping individual-level covariates onto the latent individual-level preferences, and $\varepsilon$ and $\xi$ = errors.

### 2021-04-17 _targets.R

@@ -3,8 +3,8 @@ library(tarchetypes)
 library(tibble)
 
 # General variables
-csl <- "pandoc/csl/the-open-university-harvard.csl"
-bibstyle <- "bibstyle-chicago-authordate"
+csl <- "pandoc/csl/apa.csl"
+bibstyle <- "bibstyle-apa"
 
 options(tidyverse.quiet = TRUE,
         dplyr.summarise.inform = FALSE)
@@ -147,5 +147,8 @@ list(
                output = here_rel("manuscript", "output", "appendix.docx"),
                csl = csl,
                bib_file),
-             format = "file")
+             format = "file"),
+  
+  tar_target(word_count, count_words(html)),
+  tar_force(show_word_count, print(word_count), TRUE)
 )

### 2021-04-17 analysis/03_analysis.Rmd
Look at religions for reviewer

@@
 
+  tar_load(survey_results)
   tar_load(sim_excel_final)
@@
 })
+```
+
+# General demographics of recipients
+
+## Religion
+
+```{r plot-religion}
+religion_lookup <- tribble(
+  ~Q5.10, ~religion,
+  1, "Catholic",
+  2, "Protestant",
+  3, "Christian Orthodox",
+  4, "Jewish",
+  5, "Muslim",
+  6, "Sikh",
+  7, "Hindu",
+  8, "Buddhist",
+  9, "Atheist",
+  10, "Other"
+)
+
+n_respondents <- nrow(survey_results)
+
+religions <- survey_results %>% 
+  count(Q5.10) %>% 
+  left_join(religion_lookup, by = "Q5.10") %>% 
+  arrange(n) %>% 
+  mutate(religion = fct_inorder(religion)) %>% 
+  mutate(percent = n / n_respondents)
+
+ggplot(religions, aes(x = n, y = religion)) +
+  geom_col(fill = clrs_okabe_ito$reddish_purple) +
+  scale_x_continuous(sec.axis = sec_axis(~. / n_respondents, labels = percent)) +
+  labs(x = "Number of respondents", y = NULL) +
+  theme_ngo()
+```
+
+```{r religion-others}
+religion_others <- survey_results %>% 
+  filter(!is.na(Q5.10_TEXT)) %>% 
+  mutate(Q5.10_TEXT = str_to_lower(Q5.10_TEXT)) %>% 
+  count(Q5.10_TEXT) %>% 
+  arrange(desc(n))
+religion_others
 ```

### 2021-04-17 manuscript/manuscript.Rmd
Minor metadata updates
Super minor things

@@
   email: aheiss@gsu.edu
-date: "October 2, 2020"
+date: "April 17, 2021"
 published: Working paper.
@@
 Individual donors do not use the same performance-based metrics as official aid donors, and trust has shown to be an important component of support for nonprofits working towards difficult goals.
-How does trust in charitable organizations influence individuals’ preferences to donate, especially when these groups face crackdown?
+How does trust in charitable organizations influence individuals' preferences to donate, especially when these groups face crackdown?
 Using a simulated market for philanthropic donations towards INGOs, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity, we find that trust in charitable organizations matters substantially in shaping donor preferences.
@@
 title-page: true
-word-count: "7,562"
+word-count: "7,986"
 keywords: international NGOs, donor behavior, philanthropy, human rights, repression, international giving, donor choice
@@
 
-As a result of these laws, public or official foreign aid channeled through international NGOs (INGOs) has decreased considerably in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
+As a result of these laws, public or official foreign aid channeled through international NGOs (INGOs) has decreased in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
 However, philanthropy from private donors and foundations is not as adversely affected [@McGill:2018].

### 2021-04-18 analysis/index.Rmd
Remove trailing space
Add newer abstract

@@
 
-Over the past two decades, international non-governmental organizations (INGOs) have faced increasing legal scrutiny and repression abroad.
-As a result, official aid to INGOs in repressive countries has reduced.
-NGOs thus need access to a diverse array of funds and may need to increase fundraising from private donors.
-Which demographic and experiential factors influence the decision of individuals to donate to legally besieged NGOs?
-We investigate this question using a market simulation based on a nationally representative conjoint experiment conducted on individuals with a history of charitable giving.
-We find that trust in political institutions and charities is enormously influential in shaping donor preferences.
-Donor profiles with high levels of social trust are likely to donate to human rights INGOs with friendly relationships with host governments, and that support hold steady if INGOs face criticism or crackdown.
+The phenomenon of closing civic space has adversely impacted the operations of INGOs.
+It has not just resulted in net losses of income to INGOs, but also how and where funds are allocated.
+We argue that individual private donors can be important in sustaining the operations of INGOs working in repressive contexts.
+Individual donors do not use the same performance-based metrics as official aid donors, and trust has shown to be an important component of support for nonprofits working towards difficult goals.
+How does trust in charitable organizations influence individuals' preferences to donate, especially when these groups face crackdown?
+Using a simulated market for philanthropic donations towards INGOs, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity, we find that trust in charitable organizations matters substantially in shaping donor preferences.
+Donor profiles with high levels of social trust are likely to donate to INGOs with friendly relationships with host governments.
+This support holds steady if INGOs face criticism or crackdown.
 In contrast, donor profiles with lower levels of social trust prefer to donate to organizations that do not face criticism or crackdown abroad.
-Our findings have practical implications for INGOs that aim to raise funds from the general public amid closing civic space.
+The global crackdown on NGOs may thus possibly sour NGOs' least trusting individual donors.
+Our findings have practical implications for INGOs raising funds from individuals amid closing civic space.

### 2021-04-18 manuscript/manuscript.Rmd
Add link to stats notebook
Fix "church" thing

@@
 published: Working paper.
-git-repo: https://github.com/andrewheiss/who-cares-about-crackdown
+code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/who-cares-about-crackdowns/>"
 abstract: >-
@@
 Additionally, the majority of respondents volunteer and donate to charity at least once a year and give between \$1–\$999 annually.
-Most rarely attend church, but feel that religion is important.
+Most rarely participate in religious services, but feel that religion is important.
 Respondents are also civically engaged (three quarters voted in the last election) and follow national news closely (70% follow the news daily).

### 2021-04-18 manuscript/manuscript.Rmd
Some more final-ish edits by me

@@
   email: aheiss@gsu.edu
-date: "April 17, 2021"
+date: "April 18, 2021"
 published: Working paper.
@@
 title-page: true
-word-count: "7,986"
+word-count: "8,061"
 keywords: international NGOs, donor behavior, philanthropy, human rights, repression, international giving, donor choice
@@
 As part of a larger project, we preregistered hypotheses and our research design at the Open Science Framework, and our preregistration protocol is available at <https://osf.io/hsbyd/>.
-This study covers the third research question of our preregistered design.
+This study covers the second research question of our preregistered design.
 author-note: >-
@@
 policy-implications: >-
-  In the wake of the global crackdown on civil society, international NGOs (INGOs) need to maintain access to multiple sources of funding, including individual donors. 
-  It is critical for INGOs to understand what motivates individuals to donate, especially if INGOs face legal crackdown in their host countries.
-
-  Trust in political institutions and in charitable organizations matters substantially in shaping donor preferences.
-  We find that potential donors with low social trust tend to be wary of negative host-country relationships and prefer to donate to INGOs that are friendly with their host governments, while potential donors with high social trust are more willing to stick with legally besieged INGOs.
-  Donors that are the most trusting and involved may remain supportive when charities face government criticism and crackdown.
+  - In the wake of the global crackdown on civil society, international NGOs (INGOs) need to maintain access to multiple sources of funding, including individual donors.
+  - It is critical for INGOs to understand what motivates individuals to donate, especially if INGOs face legal crackdown in their host countries.
+  - Trust in political institutions and in charitable organizations matters substantially in shaping donor preferences.
+  - We find that potential donors with low social trust tend to be wary of negative host-country relationships and prefer to donate to INGOs that are friendly with their host governments, while potential donors with high social trust are more willing to stick with legally besieged INGOs.
+  - Donors that are the most trusting and involved may remain supportive when charities face government criticism and crackdown.
 The global crackdown on NGOs may also possibly sour NGOs' least trusting individual donors.
@@
 
-In our experiment, we presented respondents with four randomly selected international nonprofit organizations with four randomly assigned features.[^appendix-survey] We used organizations that are associated with a range of contentious and noncontentious issues: Amnesty International, Greenpeace, Oxfam, and the International Committee of the Red Cross.
+In our experiment, we presented respondents with repeated sets of randomly generated international nonprofit organizations with randomly assigned features.[^appendix-survey] We used organizations that are associated with a range of contentious and noncontentious issues: Amnesty International, Greenpeace, Oxfam, and the International Committee of the Red Cross.
 Because of their strong name recognition, these organizations (and others like World Vision, the World Wildlife Fund, and Médecins Sans Frontières) are commonly used in experimental surveys on philanthropy [@FaulknerTruongRomaniuk:2015].
@@
 Disentangling the effect of every individual level-characteristic measured in the survey on every combination of organizational characteristics presented in the conjoint experiment is unwieldy and near impossible.
-Given the organizational attributes presented in our experiment, and the possible individual characteristics that respondents could select, there are billions of possible combinations and iterations of organizational and individual attributes—many of which rarely occur in the actual population of potential donors.
+For instance, we might posit that politically conservative, religiously active personas that have a history of charitable giving and high trust in nonprofits might be more likely to donate to disaster relief organizations facing government crackdown.
+But that is only one possible combination—given the organizational attributes presented in our experiment, and the possible individual characteristics that respondents could select, there are billions of possible iterations of organizational and individual attributes, many of which rarely occur in the actual population of potential donors.
+
 To more fully explore the relationships between different organizational- and individual-level attributes, we turn to simulation methods that allow us to examine the impact of multiple covariates simultaneously.
-To simplify the possible combinations of individual characteristics, we generate 64 distinct personas with attributes that vary along different dimensions of demographics, politics and public affairs experience, and social attitudes (see Table \@ref(tab:persona-attributes)).
+Conjoint simulation offers useful analytic benefits.
+Since we are less concerned with the marginal effects of single donor characteristics and more interested in how constellations of individual and organizational attributes interact with each other, we can vary different combinations of donor and organization characteristics and hold other constant.
+This allows us to see the connections between donor trust and background and INGO organizational practices and find which kinds of donors are more or less likely to consider specific organizational attributes when deciding to donate, and which donor characteristics are associated with the propensity to donate.
+
+To simplify the possible combinations of individual characteristics, we generate 64 distinct personas with attributes that vary along different dimensions of demographics, politics and public affairs experience, and social attitudes, based on our earlier review of donor motivations (see Table \@ref(tab:persona-attributes)).
 We also generate 24 simulated organizations that vary by issue area, relationship with host government, and source of funding (see Table \@ref(tab:organization-attributes)).
@@
 
-We then combine these different scenarios of donor and organization attributes with the coefficients from the hierarchical regression model to calculate each persona's probability of donating to specific combinations of organizational attributes.
+We then combine these different configurations of donor and organization attributes with the coefficients from the hierarchical regression model to calculate each persona's probability of donating to specific combinations of organizational attributes.
 Any individual characteristics that we do not explicitly vary in Table \@ref(tab:persona-attributes) are held at their means or modal values from the survey sample.
@@
 
-Simulation methods offer useful analytic benefits.
-Instead of interpreting marginal coefficient effects from a regression model, we can explore multiple moving parts from the same model simultaneously to understand how individual characteristics interact with each other.
-This allows us to more fully explore our key research questions and see which kinds of donors are more or less likely to consider specific organizational attributes when deciding to donate, and which donor characteristics are associated with the propensity to donate.
 Importantly, each persona is an artificial construct.
@@
     where $y$ = which alternative the respondent chooses to donate to, $X$ = design matrix of attribute levels (organizations, issue areas, organizational practices, funding sources, and government relations), $\beta$ = latent individual preferences for the attribute levels, $Z$ = matrix of individual-level covariates (demographics, political knowledge, attitudes towards charity, etc.), $\Gamma$ = matrix of coefficients mapping individual-level covariates onto the latent individual-level preferences, and $\varepsilon$ and $\xi$ = errors.
+See the appendix for more details.

### 2021-04-18 manuscript/appendix.Rmd
Add more descriptive model details

@@
   email: aheiss@gsu.edu
-date: "April 17, 2021"
+date: "April 18, 2021"
 title-page: false
-published: 
-git-repo: https://github.com/andrewheiss/who-cares-about-crackdown
+published: Working paper.
+code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/who-cares-about-crackdowns/>"
 reference-section-title: References
@@
 appendix: true
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
+```{r setup, include=FALSE}
+# Figure out output format
+is_docx <- knitr::pandoc_to("docx") | knitr::pandoc_to("odt")
+is_latex <- knitr::pandoc_to("latex")
+is_html <- knitr::pandoc_to("html")
+
+# Word-specific things
+table_format <- ifelse(is_docx, "huxtable", "kableExtra")  # Huxtable tables
+conditional_dpi <- ifelse(is_docx, 300, 300)  # Higher DPI
+conditional_align <- ifelse(is_docx, "default", "center")  # Word doesn't support align
+
+# Knitr options
+knitr::opts_chunk$set(
+  echo = FALSE, warning = FALSE, message = FALSE,
+  tidy.opts = list(width.cutoff = 120),  # Code width
+  fig.retina = 3, dpi = conditional_dpi,
+  fig.width = 7, fig.asp = 0.618,
+  fig.align = conditional_align, out.width = "100%",
+  fig.path = "output/figures/",
+  cache.path = "output/_cache/",
+  fig.process = function(x) {  # Remove "-1" from figure names
+    x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
+    if (file.rename(x, x2)) x2 else x
+  }
+)
+
+# R options
+options(
+  width = 90,  # Output width
+  dplyr.summarise.inform = FALSE,  # Turn off dplyr's summarize() auto messages
+  knitr.kable.NA = "",  # Make NAs blank in kables
+  kableExtra.latex.load_packages = FALSE,  # Don't add LaTeX preamble stuff
+  modelsummary_default = table_format  # Set modelsummary backend
+)
+```
+
+```{r libraries-data, include=FALSE}
+library(tidyverse)
+library(kableExtra)
+library(huxtable)
+library(here)
+```
+
+# Model details
+
+We analyze the effect of the various combinations of organizational features and donor characteristics with the following hierarchical Bayesian multinomial logit model:
+
+$$
+\begin{aligned}
+\beta &\sim \operatorname{Multivariate} \mathcal{N}(Z \Gamma, \xi) \\
+y &\sim \operatorname{Multinomial\ logit}(X \beta, \varepsilon)
+\end{aligned}
+$$
+
+where $y$ = which alternative the respondent chooses to donate to, $X$ = design matrix of attribute levels (i.e.
+organizations, issue areas, organizational practices, funding sources, and government relations), $\beta$ = latent individual preferences for the attribute levels, $Z$ = matrix of individual-level covariates (i.e.
+demographics, political knowledge, attitudes towards charity, etc.), $\Gamma$ = matrix of coefficients mapping individual-level covariates onto the latent individual-level preferences, and $\varepsilon$ and $\xi$ = errors.
+Simply put, the first level of the model predicts individual donor preferences for various combinations of features (e.g.
+the combination of human rights issues, financial transparency, government funding, and government crackdown), while the second level of the model uses these fitted preferences to predict the ultimate choice of donation.
+
+We collected many individual level covariates in our survey.
+To aid in analysis, we categorized these survey questions into five broader theoretical themes that include smaller groups of variables.
+Table A\@ref(tab:individual-covariates) shows how we map individual survey questions to different groups.
+In this paper, we base our simulated market on a model that uses all individual characteristics in the first level:
+
+$$
+\text{Donation preferences } (\beta) \sim \operatorname{Multivariate} \mathcal{N}(Z \Gamma, \xi)
+$$
+
+where:
+
+$$
+\begin{aligned}
+Z\Gamma =& \Gamma_a \text{Public affairs} + \Gamma_b\text{Political ideology} + \Gamma_c \text{Social views} + \\
+& \Gamma_d \text{Charity and voluntarism} + \Gamma_e \text{Demographics}
+\end{aligned}
+$$
+
+The alphabetic subscripts for the $\Gamma$ coefficients here (i.e.
+$\Gamma_a$) represent multiple values, since broader categories like "Public affairs" comprise multiple variables, each with their own coefficients.
+
+The second level of the model incorporates the $\beta$ estimates from the first level and uses a design matrix of organizational characteristics:
+
+$$
+\text{Donation choice } (y) \sim \operatorname{Multinomial\ logit}(X \beta, \varepsilon)
+$$
+
+where (count of distinct values included in parentheses):
+
+$$
+\begin{aligned}
+X = \{&\text{Organization } (4),\ \text{Issue area } (4),\ \text{Organizational practices } (2), \\
+& \text{Funding sources } (3),\ \text{Government relations } (3)\}
+\end{aligned}
+$$
+\newpage
+
+\stgroup
+
+\singlespacing
+
+```{r individual-covariates}
+all_covariates <- tribble(
+  ~`Broader category`, ~Group, ~`Survey question`,
+  "Public affairs", "Public affairs knowledge", "Q2.1: How often do you follow national news?",
+  "Public affairs", "Public affairs knowledge", "Q2.2: How often do you follow international news?",
+  "Public affairs", "Public affairs knowledge", "Q2.3: Which mediums do you use to follow news?",
+  "Public affairs", "Public affairs knowledge", "Q2.4: How often would you say you follow what's going on in government and public affairs?",
+  "Public affairs", "Public affairs knowledge", "Q5.7: Have you ever traveled to a developing country?",
+  "Public affairs", "Public affairs activity", "Q5.1: Did you vote in the last election?",
+  "Political ideology", "Ideology", "Q5.2: 7-point scale on which the political views that people might hold are arranged from extremely liberal (left) to extremely conservative (right).",
+  "Social views", "Public affairs trust", "Q5.6: 7-point scale of trust in political institutions and the state, arranged from no trust (left) to complete trust (right)",
+  "Social views", "Social ideology", "Q5.11: 7-point scale of agreement with statement \"People should be more charitable towards others in society\", from strongly agree (1) to strongly disagree (7)",
+  "Social views", "Religiosity", "Q5.8: How often do you attend religious or worship services, not including weddings and funerals?",
+  "Social views", "Religiosity", "Q5.9: How important is religion in your life?",
+  "Social views", "Religiosity", "Q5.10: What is your current religion, if any?",
+  "Charity and voluntarism", "Charity trust", "Q2.7: How important is it that you trust a charity before giving to it?",
+  "Charity and voluntarism", "Charity trust", "Q2.8: How much do you trust charities?",
+  "Charity and voluntarism", "Charity activity", "Q2.5: How often do you donate to charity?",
+  "Charity and voluntarism", "Charity activity", "Q2.6: How much did you donate to charity last year?",
+  "Charity and voluntarism", "Volunteer activity", "Q2.9: Have you volunteered in the past 12 months?",
+  "Charity and voluntarism", "Volunteer activity", "Q2.10: How often do you volunteer?",
+  "Charity and voluntarism", "Activism activity", "Q5.4: Historically, how involved have you been in activist causes?",
+  "Charity and voluntarism", "Activism activity", "Q5.5: Historically, how involved has your family been in activist causes?",
+  "Charity and voluntarism", "Association membership", "Q5.3: List of possible types of organizations and associations",
+  "Demographics", "Gender", "Q5.12: What is your gender?",
+  "Demographics", "Marital status", "Q5.13: Are you now married, widowed, divorced, separated, or never married?",
+  "Demographics", "Education", "Q5.14: What is the highest degree or level of school you have completed?",
+  "Demographics", "Income", "Q5.15: What is your annual household income before taxes?",
+  "Demographics", "Race", "Q5.16: Choose one or more races that you consider yourself to be:",
+  "Demographics", "Age", "Q5.17: How old are you?"
+)
+
+covariate_caption <- "Individual covariates used in $Z$ to estmate the $\\Gamma$s in the first level of the model, or $\\operatorname{Multivariate} \\mathcal{N}(Z \\Gamma, \\xi)$"
+
+if (!is_docx) {
+  all_covariates %>% 
+    select(Group, `Survey question`) %>% 
+    kbl(align = c("l", "l"),
+        longtable = TRUE, booktabs = TRUE, linesep = "",
+        caption = covariate_caption) %>% 
+    pack_rows(index = table(fct_inorder(all_covariates$`Broader category`)),
+              latex_gap_space = "1.5em", indent = FALSE) %>%
+    kable_styling(latex_options = c("repeat_header")) %>% 
+    column_spec(1, width = "0.25\\\\textwidth") %>% 
+    column_spec(2, width = "0.68\\\\textwidth") %>% 
+    collapse_rows(columns = 1, valign = "top", latex_hline = "major")
+} else {
+  all_covariates %>% 
+    select(Group, `Survey question`) %>% 
+    hux() %>% 
+    set_font_size(10) %>%
+    set_all_padding(3) %>% 
+    set_align(everywhere, 1:2, "left") %>%
+    merge_repeated_rows(col = 1) %>% 
+    insert_row("Public affairs", "", after = 1) %>% 
+    insert_row("\nPolitical ideology", "", after = 8) %>% 
+    insert_row("\nSocial views", "", after = 10) %>%
+    insert_row("\nCharity and voluntarism", "", after = 16) %>%
+    insert_row("\nDemographics", "", after = 26) %>%
+    merge_cells(2, 1:2) %>%
+    merge_cells(9, 1:2) %>%
+    merge_cells(11, 1:2) %>%
+    merge_cells(17, 1:2) %>%
+    merge_cells(27, 1:2) %>%
+    set_bold(1, everywhere) %>%
+    set_bold(c(2, 9, 11, 17, 27), everywhere) %>%
+    set_top_border(1, everywhere) %>%
+    set_bottom_border(1, everywhere) %>%
+    set_bottom_border(c(7, 12, 13, 19, 21, 23, 25, 28:32), everywhere) %>% 
+    set_width(1) %>%
+    set_col_width(1, 0.25) %>%
+    set_col_width(2, 0.75) %>%
+    set_wrap(TRUE) %>% 
+    huxtable::set_caption(covariate_caption) %>% 
+    huxtable::as_flextable() %>% 
+    flextable::font(fontname = "Times New Roman")
+}
+```
+
+\fingroup
+
+\newpage
+
 # Survey experiment
+
+\stgroup
+
+\singlespacing
 
@@
 ```
+
+\fingroup

### 2021-04-21 manuscript/manuscript.Rmd
Suparna final edits

@@
   The phenomenon of closing civic space has adversely impacted the operations of INGOs.
-It has not just resulted in net losses of income to INGOs, but also how and where funds are allocated.
+It has not just resulted in net losses of income for INGOs, but also how and where funds are allocated.
 We argue that individual private donors can be important in sustaining the operations of INGOs working in repressive contexts.
-Individual donors do not use the same performance-based metrics as official aid donors, and trust has shown to be an important component of support for nonprofits working towards difficult goals.
+Individual donors do not use the same performance-based metrics as official aid donors.
+Rather, trust can be an important component of individual donor support for nonprofits working towards difficult goals.
 How does trust in charitable organizations influence individuals' preferences to donate, especially when these groups face crackdown?
@@
 In 2016, Human Rights Watch claimed that civil society was under more aggressive attack than at any time in recent memory [@Roth:2016].
-Governments across the globe have cracked down on civil society organizations (CSOs) and non-governmental organizations (NGOs)—a phenomenon known as "closing civic space" [@CarothersBrechenmacher:2014; @CIVICUS:2017; @DPR:2015; @DPR:2016].[^NGOdef] Legal restrictions, or what we refer to as legal crackdowns, are a core part of these efforts.
+Globally, governments are repressing civil society organizations (CSOs) and non-governmental organizations (NGOs)—a phenomenon known as "closing civic space" [@CarothersBrechenmacher:2014; @CIVICUS:2017; @DPR:2015; @DPR:2016].[^NGOdef] Legal restrictions, or what we refer to as legal crackdowns, are a core part of these efforts.
 These crackdowns create barriers to entry, funding, and advocacy for NGOs in an effort to control, obstruct, and repress these organizations.
@@
 
-As a result of these laws, public or official foreign aid channeled through international NGOs (INGOs) has decreased in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
+Due to these laws, official foreign aid channeled through international NGOs (INGOs) has decreased in repressive countries [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018].
 However, philanthropy from private donors and foundations is not as adversely affected [@McGill:2018].
 Many foundations have continued channeling funds to countries with hostile legal environments [@NeedlesWolcheckSato:2018].
-Given the reduction of foreign aid following restricted legal environments abroad, INGOs may need to devote more resources to fundraise from individual donors.
+Given the reduction of foreign aid following restricted legal environments abroad, INGOs may need to fundraise more from individual donors.
 
-Individual private donations are a critical source of INGO funding.
+Individual private donations are an important source of INGO funding.
 While total private philanthropy[^phildef] in the United States has grown over time, it is notable that private giving to NGOs working on international affairs-focused issues are one of only two categories of organizations that have continued experiencing substantial growth in giving, reaching \$22.08 billion in donations in 2018 [@givingusa:2019].[^intlaffairs] Most of this growth is driven by individuals making small-scale (up to \$50) or micro-donations (between \$0.25–\$10) [@SaxtonWang:2014].
@@
 
-A robust scholarship already examines the determinants of individual-level philanthropy to domestic causes.
-But the dynamics of *international* giving to NGOs are under-examined in the literature on individual donor attributes and preferences.[^exceptions] Motivating individuals to donate to international causes is hard as the number of recipients are large and far removed from the donor [@CasaleBaumann:2015, 100].
+A robust scholarship examines the determinants of individual-level philanthropy to domestic causes.
+But the dynamics of *international* giving to NGOs are under-examined in the literature on individual donor preferences.[^exceptions] Motivating individuals to donate to international causes is hard as the number of recipients are large and far removed from the donor [@CasaleBaumann:2015, 100].
 Trust is an essential component for INGO sustainability—for many nonprofits, trust often translates into grants and donations [@coombs2007].
@@
 We explore this using a simulated market for philanthropic donations towards INGOs, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity.
-We adapt methods used in marketing to generate dozens of distinct simulated personas that represent typical donor profiles, and we vary these personas along different dimensions of demographic, political, and social attributes.
+We adapt methods used in marketing to generate distinct simulated personas that represent typical donor profiles, and we vary these personas along different dimensions of demographic, political, and social attributes.
 We find that an organization's target issue area and its relationship with its host government interact strongly with individuals' characteristics.
@@
 Our paper shows that in readjusting their fundraising strategies towards individuals, framing, or the process through which actors present information to influence perceptions, is particularly important [@chong2007framing].
-Framing affects their willingness to donate.
+Framing affects individuals' willingness to donate.
 However, existing research is unclear about which frames are effective when making appeals to individual donors considering international philanthropy.
 Since our study looks at multiple organizational and host country factors, our results can help INGOs frame their appeals.
-In particular, our results show that INGOs may benefit from publicizing crackdown at least towards their most trusting donors.
+Our results show that INGOs may benefit from publicizing crackdown at least towards their most trusting donors.
 
 Finally, while research in public policy examines giving to NGOs, the discipline of international relations tends to see philanthropy as less relevant [@youde2019].
-However, philanthropy—particularly donations received by INGOs—can help us understand changes in the dynamics of global governance.
+However, philanthropy can help us understand changes in the dynamics of global governance.
 Private individuals exercise power and influence in unique ways that differ from other non-state actors.
 As @youde2019 [p.
-44] points out, studying philanthropy changes our conceptions of individuals being passive recipients to active entities that are not merely objects of governance, and can thus shed light on the changing logic of global governance.
+44] points out, studying philanthropy changes our conceptions of individuals as being passive recipients to active entities that are not merely objects of governance, and can thus shed light on the changing logic of global governance.
 
@@
 
-Foreign aid to civil society—and NGOs in particular—has steadily increased over time.
+Foreign aid to NGOs has steadily increased over time.
 Many government and foundation donors perceive NGOs as nimbler and less bureaucratic than governments.
@@
 But in the aftermath of the dissolution of the Soviet Union, many NGOs had the explicit goal of promoting democracy and bringing down authoritarian governments.
-Subsequently, many states see NGOs as a threat and seek to repress them.
+Subsequently, many states saw NGOs as a threat and sought to repress them.
 
@@
 This has had a threefold impact on INGOs.
-First, it has led to a reduction in resources and grants available to INGOs.
-Second, restrictive NGO laws can affect INGO programming by preventing organizations from working in certain (contentious) issue areas.
+It has led to a reduction in resources and grants available to INGOs.
+Restrictive NGO laws have affected INGO programming by preventing organizations from working in certain (contentious) issue areas.
 To deal with this, some groups have adapted by changing the nature of their programming to appear less threatening to the repressive countries.
-Finally, in the worst-case scenario, this has led to a loss in INGOs' access to target countries—often also associated with the use of violence against INGOs and their employees.
+In the worst-case scenario, it has led to a loss in INGOs' access to target countries.
 We focus exclusively on the first dilemma—the reduction in INGO funding and possible responses to it.
@@
 Private sources include foundations, private corporations, and individuals.
-While INGOs have not been passive in responding to the crackdown on civil society, they face increasing obstacles in funding.
+While INGOs have not been passive in responding to the crackdown on civil society, they face increasing obstacles in acquiring funding.
 Closing civic space has resulted in net losses of income to INGOs, particularly in official bilateral and multilateral aid [@DupuyPrakash:2018]
@@
 Following the passage of anti-NGO laws, official donors move funds away from contentious causes such as human rights, media, corruption, advocacy, among others, towards tamer and more regime-compatible causes such as health, education [@ChaudhryHeiss:2018].
-The latter trend has also been exacerbated by a preference among donors working in official aid and the democracy promotion establishment to gradually increase funding directed towards tame causes, at the expense of more contentious causes.
+The latter trend has also been exacerbated by a preference among donors working in the official aid and democracy promotion establishment to gradually increase funding directed towards tame causes, at the expense of more contentious causes.
 This is because many tame causes can have easily quantifiable, measurable outputs, which makes it easier to show a program's effectiveness over time [@Bush:2015].
@@
 We explore the interaction between individual and organizational characteristics using a conjoint experiment conducted with a nationally representative sample in the U.S.
-Conjoint analysis allows us to elicit donor preferences without respondents explicitly stating their exact preferences.
+Conjoint analysis allows us to elicit donor preferences without respondents explicitly stating their preferences.
 This kind of experiment is commonly used in marketing to reveal consumer preferences for products and has become increasingly popular in political science and public policy [@KnudsenJohannesson:2019].
@@
 Since we are less concerned with the marginal effects of single donor characteristics and more interested in how constellations of individual and organizational attributes interact with each other, we can vary different combinations of donor and organization characteristics and hold other constant.
-This allows us to see the connections between donor trust and background and INGO organizational practices and find which kinds of donors are more or less likely to consider specific organizational attributes when deciding to donate, and which donor characteristics are associated with the propensity to donate.
+This allows us not only to see the connections between donor trust and INGO organizational practices and find which kinds of donors are more or less likely to consider specific organizational attributes when deciding to donate, but also which donor characteristics are associated with the propensity to donate.
 
@@
 High-income personas are the least likely demographic to prefer donating to NGOs under crackdown.
-Their lower income counterparts, on the other hand, are generally unfazed by NGOs' relationships with government, maintaining the same average market share across all three types of host country relationships.
+Their lower income counterparts, on the other hand, are generally unfazed by NGOs' relationships with governments, maintaining the same average market share across all three types of host country relationships.
 Patterns in preferences for issue area and funding sources remain constant across both methods of categorizing income—crackdown only has an effect on very high-income personas.
-Income thus appears to influence preferences particularly for NGOs facing crackdown abroad—wealthy donors are perhaps fair-weather friends that are more likely to pull their support when an organization's work becomes more difficult.
+Income thus appears to influence preferences particularly for NGOs facing crackdown abroad—wealthy donors are perhaps fair-weather friends that are more likely to withdraw their support when an organization's work becomes more difficult.
 
@@
 
-Next, we next examine how differences in public affairs knowledge, experience, and political ideology influence a persona's propensity to donate to an organization.
+Next, we examine how differences in public affairs knowledge, experience, and political ideology influence a persona's propensity to donate to an organization.
 We vary personas along two dimensions: (1) political ideology, with semi-liberal and semi-conservative political leanings (2 and 5 on a 7-point scale), and (2) knowledge and experience with public affairs and the news, with personas that either follow national and international news and that have traveled abroad or personas that do not follow the news or travel.
@@
 Those who trust social and charitable institutions are very likely to prefer donating to human rights organizations, regardless of their public affairs knowledge or political leanings.
-In all circumstances, those with high levels of trust have between a 7–10% chance of donating to a human rights organization, on average.
-Personas with low levels of trust, on the other hand, strongly avoid human rights organizations and prefer instead to donate to refugee and emergency response NGOs.
+In all circumstances, those with high levels of trust have a 7–10% chance of donating to a human rights organization, on average.
+Personas with low levels of trust, on the other hand, strongly avoid human rights organizations and prefer to donate to refugee and emergency response NGOs.
 The difference is substantial—a liberal persona with high levels of public affairs knowledge and experience will give to a human rights organization 10% of the time, on average if they have high levels of trust, but less than 3% of the time if they are less trusting.
@@
 However, those with higher trust are less likely to be deterred by poor host-country relationships, while those with low trust tend to not donate to organizations facing criticism or crackdown abroad.
-A friendly relationship with a host government may be a manifestation of a belief that charities behave properly and exert a positive influence on society.
+A friendly relationship with a host government may be a manifestation of a belief that NGOs act appropriately and exert a positive influence on society.
 Once an organization faces criticism or crackdown, however, support deteriorates rapidly among personas with low social trust, since such a crackdown could be perceived as a violation of the persona's trust in the charity—that is, the organization must be doing something wrong to deserve criticism.
@@
 
-Personas with high levels of trust, on the other hand, seem to stick with legally besieged organizations and show targeted groups the benefit of the doubt.
-The global crackdown on NGOs thus sours organizations' least trusting individual donors.
+Personas with high levels of trust, on the other hand, continue supporting legally besieged organizations and show targeted groups the benefit of the doubt.
+Crackdown on NGOs thus sours organizations' least trusting individual donors.
 Overall, our results support research that donors with high levels of trust are more active in giving than those with low levels of trust [@sargeant2008] and that trust especially matters when individuals donate to organizations working under great uncertainty and towards difficult goals [@Wiepking:2010].
@@
 
-Our conjoint experiment raises two main concerns for inference: (1) prior knowledge and opinions about these organizations could influence respondents' choices, and (2) there are questions about the generalizability of these results outside the American context.
+Our conjoint experiment raises two main concerns for inference: (1) prior knowledge and opinions about these organizations could influence respondents' choices, and (2) the generalizability of these results outside the American context.
 We explore both below.
@@
 @KnowlesSullivan:2017, conducting a field experiment in New Zealand, found that only a small number of participants in the study stated that not giving internationally was driven by mistrust.
-Rather, lack of trust towards overseas NGOs, particularly aid and developmental agencies often results due to donors perceiving INGOs as having low personal relevance [@FaulknerTruongRomaniuk:2015].
-Overall, the literature suggests that for INGO fundraising, lack of awareness is a much larger issue than specific scandals or other knowledge of specific organizational characteristics that might reduce donor trust and confidence.
+Rather, lack of trust towards overseas NGOs often occurs due to donors perceiving INGOs as having low personal relevance [@FaulknerTruongRomaniuk:2015].
+Overall, the literature suggests that for INGO fundraising, lack of awareness is a much larger issue than specific scandals or specific organizational characteristics that might reduce donor trust and confidence.
 
@@
 It has not just resulted in net losses of income from official sources to INGOs, it has also affected how and where funds are allocated.
-We argue that individual donors can be useful in sustaining the operations of groups working in challenging environments.
-Individual donors do not use the same performance-based metrics as official aid donors and use heuristics to simplify their decision-making.
+We show that individual donors can be useful in sustaining the operations of groups working in challenging environments.
+Individual donors do not use the same performance-based metrics as official donors and use heuristics to simplify their decision-making.
 The role of trust may be important in understanding donations preferences towards INGOs working in challenging contexts.
-While trust is a difficult construct to define, the nonprofit literature conceptualizes trust as a key driver of commitment, which is shown to impact both intention to donate as well as actual donation behavior.
-With repressive environments and NGOs working on more difficult goals, a lack of trust could be further fueled by legal trouble with the NGO host government—a dynamic that individuals may not wish to enter with their dollars.
+While trust is a difficult construct to define, the nonprofit literature conceptualizes trust as a key driver of commitment, which can impact both intention to donate as well as actual donation behavior.
+With repressive environments, a lack of trust could be further fueled by legal trouble with the NGO host government—a dynamic that individuals may not wish to enter with their dollars.
 How does trust in NGOs influence individuals' preferences to donate, especially when groups face crackdown?
@@
 Trust in political institutions and in charitable organizations matters substantially in shaping donor preferences.
-Personas with high levels of social and charitable trust prefer donating to human rights organizations that have friendly relationships with their host governments, while personas with low trust are drawn more to emergency response and refugee relief organizations with unfriendly relationships with their host governments.
+Personas with high levels of social and charitable trust prefer donating to human rights organizations that have friendly relationships with their host governments, while personas with low trust are drawn more to emergency response and refugee relief organizations.
 Personas with low social trust tend to be wary of negative host-country relationships and strongly prefer to donate to organizations that are friendly with their host governments, while personas with high social trust are more willing to stick with legally besieged organizations.
 This implies that donors who are the most trusting could remain supportive when nonprofits face government criticism and crackdown.
-The global crackdown on NGOs may also possibly sour NGOs' least trusting individual donors.
+The global crackdown on NGOs may thus possibly sour NGOs' least trusting individual donors.
 Our findings lend support to research showing that individuals who trust NGOs are more likely to continue their monetary support of NGOs in the face of difficulties and under great uncertainty [@dwyer1987; @Wiepking:2010].

### 2021-04-22 R/funs_notebook.R
Update site supporting files in a target now

@@ -82,3 +82,7 @@ tar_notebook_pages <- function(
     )
   )
 }
+
+copy_notebook_supporting_files <- function(rmd, ...) {
+  rmarkdown::render_site(rmd, encoding = "UTF-8")
+}

### 2021-04-22 _targets.R

@@ -63,6 +63,16 @@ list(
   # Render the analysis notebook
   tar_notebook_pages(),
   
+  # This is only here to trigger a re-build of the R Markdown website's
+  # supporting files in `_site`, which copies the files in `output` to
+  # `_site/output`. I unfortunately haven't found a way to make it so that the
+  # site building occurs independently of `rmarkdown::render()`, so this is the
+  # workaround: re-knit index.Rmd
+  tar_target(supporting_files, 
+             copy_notebook_supporting_files(here_rel("analysis", "index.Rmd"), 
+                                            main_manuscript, html, 
+                                            appendix, app_html)),
+  
   # tarchetypes::tar_render() automatically detects target dependencies in Rmd
   # files and knits them, but there's no easy way to pass a custom rendering
   # script like bookdown::html_document2(), so two things happen here:

### 2021-04-22 manuscript/manuscript.Rmd
Add some contrast in graphs for printing in bw

@@
 title-page: true
-word-count: "8,061"
+word-count: "7,983"
 keywords: international NGOs, donor behavior, philanthropy, human rights, repression, international giving, donor choice
@@
   ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
-             x = avg_share, color = persona_trust)) +
+             x = avg_share, color = persona_trust, shape = persona_trust)) +
   geom_pointrange(size = 0.75, fatten = 1.5,
@@
                                           override.aes = list(size = 0.25,
-                                                              linetype = 0))) +
+                                                              linetype = 0,
+                                                              shape = c(20, 17)))) +
+  scale_shape_manual(values = c(17, 20), guide = FALSE) +
   labs(x = "Average share of donations", y = NULL, color = NULL) +

### 2021-04-22 R/graphics.R

@@ -60,10 +60,10 @@ theme_ngo <- function(base_size = 9, base_family = "IBM Plex Sans Condensed") {
 # Okabe and Ito (2008) colorblind-safe qualitative palette: https://jfly.uni-koeln.de/color/
 # See also https://clauswilke.com/dataviz/color-pitfalls.html
 clrs_okabe_ito <- list(orange = "#E69F00",
-                       sky_blue = "#56B4E9",
+                       sky_blue = colorspace::lighten("#56B4E9", 0.25),
                        bluish_green = "#009E73",
                        yellow = "#F0E442",
-                       blue = "#0072B2",
+                       blue = colorspace::lighten("#0072B2", 0.25),
                        vermilion = "#D55E00",
                        reddish_purple = "#CC79A7",
                        black = "#000000")

### 2021-04-22 analysis/index.Rmd
Minor final updates

@@
 The phenomenon of closing civic space has adversely impacted the operations of INGOs.
-It has not just resulted in net losses of income to INGOs, but also how and where funds are allocated.
+It has not just resulted in net losses of income for INGOs, but also how and where funds are allocated.
 We argue that individual private donors can be important in sustaining the operations of INGOs working in repressive contexts.
-Individual donors do not use the same performance-based metrics as official aid donors, and trust has shown to be an important component of support for nonprofits working towards difficult goals.
+Individual donors do not use the same performance-based metrics as official aid donors.
+Rather, trust can be an important component of individual donor support for nonprofits working towards difficult goals.
 How does trust in charitable organizations influence individuals' preferences to donate, especially when these groups face crackdown?

### 2021-04-22 manuscript/appendix.Rmd
Minor final updates

@@
   email: aheiss@gsu.edu
-date: "April 18, 2021"
+date: "April 22, 2021"
 title-page: false
-published: Working paper.
+# published: Working paper.
 code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/who-cares-about-crackdowns/>"
@@
 ---
-
-<!-- supplement.md is generated from supplement.Rmd. Only edit the .Rmd file, *not* the .md file. -->
 

### 2021-04-22 manuscript/manuscript.Rmd
Minor final updates

@@
   email: aheiss@gsu.edu
-date: "April 18, 2021"
-published: Working paper.
+date: "April 22, 2021"
+published: "Under review at *Global Policy*"
 code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/who-cares-about-crackdowns/>"
@@
 ---
-
-<!-- manuscript.md is generated from manuscript.Rmd. Only edit the .Rmd file, *not* the .md file. -->
 
@@
 While INGOs have not been passive in responding to the crackdown on civil society, they face increasing obstacles in acquiring funding.
-Closing civic space has resulted in net losses of income to INGOs, particularly in official bilateral and multilateral aid [@DupuyPrakash:2018]
+Closing civic space has resulted in net losses of income to INGOs, particularly in official bilateral and multilateral aid [@DupuyPrakash:2018].
 

### 2021-04-22 R/funs_data-generation.R
Automatically download large files from OSF

@@ -1,5 +1,15 @@
 library(fastDummies)
 library(readxl)
+library(osfr)
+
+get_from_osf <- function(osf_url, out_dir) {
+  get_osf <- osf_retrieve_file(osf_url) %>%
+    osf_download(path = out_dir,
+                 conflicts = "overwrite",
+                 progress = TRUE)
+  
+  return(get_osf$local_path)
+}
 
 process_excel_simulation <- function(simulator_path) {
   suppressMessages({

### 2021-04-22 _targets.R

@@ -32,10 +32,12 @@ list(
              here_rel("data", "raw_data", "Market Simulator Version 01.xlsx"),
              format = "file"),
   tar_target(gamma_draws_file,
-             here_rel("data", "raw_data", "posterior_draws", "public_political_social_charity_demo.rds"),
+             get_from_osf(osf_url = "https://osf.io/msaz8/",
+                          out_dir = here_rel("data", "raw_data", "posterior_draws")),
              format = "file"),
   tar_target(survey_results_file,
-             here_rel("data", "raw_data", "final_data.rds"),
+             get_from_osf(osf_url = "https://osf.io/n2hwm/",
+                          out_dir = here_rel("data", "raw_data")),
              format = "file"),
   tar_target(giving_aggregate_file,
              here_rel("data", "raw_data", "data-FTjUv.csv")),
@@ -160,5 +162,7 @@ list(
              format = "file"),
   
   tar_target(word_count, count_words(html)),
-  tar_force(show_word_count, print(word_count), TRUE)
+  tar_force(show_word_count, print(word_count), TRUE),
+  
+  tar_knit(readme, here_rel("README.Rmd"))
 )

### 2021-04-22 R/funs_data-generation.R
Write survey results as CSV for easier access to data

@@ -1,6 +1,7 @@
 library(fastDummies)
 library(readxl)
 library(osfr)
+library(csvy)
 
 get_from_osf <- function(osf_url, out_dir) {
   get_osf <- osf_retrieve_file(osf_url) %>%
@@ -9,6 +10,11 @@ get_from_osf <- function(osf_url, out_dir) {
                  progress = TRUE)
   
   return(get_osf$local_path)
+}
+
+save_csvy <- function(x, out_csv, out_yaml) {
+  write_csvy(x, file = out_csv, metadata = out_yaml, na = "NA")
+  return(out_csv)
 }
 
 process_excel_simulation <- function(simulator_path) {

### 2021-04-22 _targets.R

@@ -55,6 +55,11 @@ list(
   tar_target(market_shares, create_predicted_market_shares(gammas, personas, orgs)),
   tar_target(sim_final, create_simulation(market_shares, personas, orgs)),
   tar_target(survey_results, read_rds(survey_results_file)),
+  tar_target(survey_csvy, 
+             save_csvy(survey_results,
+                       here_rel("data", "derived_data", "survey_results.csv"),
+                       here_rel("data", "derived_data", "survey_results.yaml")),
+             format = "file"),
   tar_target(participant_summary, create_sample_summary(survey_results)),
   tar_target(giving_aggregate, {
     read_csv(giving_aggregate_file, col_types = cols()) %>%

### 2021-04-22 manuscript/appendix.Rmd
Use consistent fonts

@@
 appendix: true
+mainfont: Lora
+sansfont: IBM Plex Sans
 editor_options: 

### 2021-04-22 README.Rmd
Use targets now!
Update readme with full instructions

@@
 Authors <- "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
-Year <- "2020"
+Year <- "2021"
 ```
@@
 
-## Abstract
+[![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FSM5EW-blue)](https://doi.org/10.17605/OSF.IO/SM5EW) [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4064840.svg)](https://doi.org/10.5281/zenodo.4064840)
 
-Over the past two decades, international non-governmental organizations (INGOs) have faced increasing legal scrutiny and repression abroad.
-As a result, official aid to INGOs in repressive countries has reduced.
-NGOs thus need access to a diverse array of funds and may need to increase fundraising from private donors.
-Which demographic and experiential factors influence the decision of individuals to donate to legally besieged NGOs?
-We investigate this question using a market simulation based on a nationally representative conjoint experiment conducted on individuals with a history of charitable giving.
-We find that trust in political institutions and charities is enormously influential in shaping donor preferences.
-Donor profiles with high levels of social trust are likely to donate to human rights INGOs with friendly relationships with host governments, and that support hold steady if INGOs face criticism or crackdown.
-In contrast, donor profiles with lower levels of social trust prefer to donate to organizations that do not face criticism or crackdown abroad.
-Our findings have practical implications for INGOs that aim to raise funds from the general public amid closing civic space.
+> `r Authors`. `r Year`. ["`r Title`,"](https://doi.org/10.17605/OSF.IO/SM5EW)
+
+**All this project's materials are free and open:**
+
+- [Download the data](#data)
+- [See the analysis notebook website](https://stats.andrewheiss.com/who-cares-about-crackdowns/)
+
+![Preregistered](img/preregistered_large_color.png) &emsp; ![Open data](img/data_large_color.png) &emsp; ![Open](img/materials_large_color.png)
 
@@
 
-This repository contains the data and code for our paper. Our pre-print is online here:
+## Abstract
 
-> `r Authors`. (`r Year`). *`r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <dx.doi.org>
+The phenomenon of closing civic space has adversely impacted the operations of INGOs.
+It has not just resulted in net losses of income for INGOs, but also how and where funds are allocated.
+We argue that individual private donors can be important in sustaining the operations of INGOs working in repressive contexts.
+Individual donors do not use the same performance-based metrics as official aid donors.
+Rather, trust can be an important component of individual donor support for nonprofits working towards difficult goals.
+How does trust in charitable organizations influence individuals' preferences to donate, especially when these groups face crackdown?
+Using a simulated market for philanthropic donations towards INGOs, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity, we find that trust in charitable organizations matters substantially in shaping donor preferences.
+Donor profiles with high levels of social trust are likely to donate to INGOs with friendly relationships with host governments.
+This support holds steady if INGOs face criticism or crackdown.
+In contrast, donor profiles with lower levels of social trust prefer to donate to organizations that do not face criticism or crackdown abroad.
+The global crackdown on NGOs may thus possibly sour NGOs' least trusting individual donors.
+Our findings have practical implications for INGOs raising funds from individuals amid closing civic space.
 
-## How to cite
+---
 
-Please cite this compendium as:
+This repository contains the data and code for our paper. Our preprint is online here:
 
-> `r Authors`. (`r format(Sys.Date(), "%Y")`). *Compendium of R code and data for `r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <dx.doi.org>
+> `r Authors`. `r Year`. "`r Title`"". Online at <https://doi.org/10.17605/OSF.IO/SM5EW>
 
@@
 
-TODO: More instructions
+We use the [**renv** package](https://rstudio.github.io/renv/articles/renv.html) to create a stable version-specific library of packages, and we use the [**targets** package](https://docs.ropensci.org/targets/) to manage all file dependencies and run the analysis.
+To reproduce the findings and re-run the analysis, do the following:
+
+1. Download and install these two fonts:
+    - [IBM Plex Sans](https://fonts.google.com/specimen/IBM+Plex+Sans)
+    - [Lora](https://fonts.google.com/specimen/Lora)
+2. [Install R](https://cloud.r-project.org/) (and preferably [RStudio](https://www.rstudio.com/products/rstudio/download/#download)).
+3. Open `whocares.Rproj` to open an [RStudio Project](https://r4ds.had.co.nz/workflow-projects.html).
+4. Make sure you have a working installation of LaTeX:
+    - *Easy-and-recommended way*: Install the **tinytex** package by running `install.packages("tinytex")` in the R console, then run `tinytex::install_tinytex()`
+    - *Easy-but-requires-huge-4+-GB-download way*: Download TeX Live ([macOS](http://www.tug.org/mactex/); [Windows](https://miktex.org/))
+5.
+If it's not installed already, R *should* try to install the **renv** package when you open the RStudio Project for the first time.
+If you don't see a message about package installation, install it yourself by running `install.packages("renv")` in the R console.
+6. Run `renv::restore()` in the R console to install all the required packages for this project.
+7. Run `targets::tar_make()` in the R console to automatically download all data files, process the data, run the analysis, and compile the paper and appendix.
+
+Running `targets::tar_make()` will create several helpful outputs:
+
+1. All project data in `data/`
+2. An analysis notebook website in `analysis/_site/index.html`
+3. PDF, HTML, and Word versions of the manuscript in `manuscript/output/`
 
@@
 
-TODO: List of data
+- [**`data/raw_data/final_data.rds`**](https://osf.io/n2hwm/): Original results from the Qualtrics survey.
+This is [hosted at OSF](https://osf.io/n2hwm/) because of its size.
+Running `targets::tar_make(survey_results_file)` will download the `.rds` file from OSF and place it in `data/raw_data`.
+The [code for cleaning and processing this data is part of a separate project, "Why Donors Donate"](https://github.com/andrewheiss/why-donors-donate).
+- [**`data/derived_data/survey_results.csv`**](data/derived_data/survey_results.csv): CSV version of the survey data.
+- [**`data/derived_data/survey_results.yaml`**](data/derived_data/survey_results.yaml): [YAML metadata](https://csvy.org/) describing the syntax of the survey data.
+- [**`data/raw_data/posterior_draws/public_political_social_charity_demo.rds`**](https://osf.io/msaz8/): Gamma (Γ) coefficients from our multilevel Bayesian model.
+This is [hosted at OSF](https://osf.io/msaz8/) because of its size.
+Running `targets::tar_make(gamma_draws_file)` will download the `.rds` file from OSF and place it in `data/raw_data/posterior_draws`.
+The [code for running this model is part of a separate project, "Why Donors Donate"](https://github.com/andrewheiss/why-donors-donate).
+- [**`data/raw_data/Market Simulator Version 01.xlsx`**](data/raw_data/Market Simulator Version 01.xlsx): An interactive Excel version of the market simulator to help demonstrate the intuition behind all the moving parts of the simulation.
+- [**`data/raw_data/data-xextT.csv`**](data/raw_data/data-xextT.csv): Per capita charitable donations in the US (2000–2014), downloaded from the [Datawrapper widget "How much money Americans give away"](https://theconversation.com/fewer-americans-are-giving-money-to-charity-but-total-donations-are-at-record-levels-anyway-98291#xextT) at ["Fewer Americans are giving money to charity but total donations are at record levels anyway"](https://theconversation.com/fewer-americans-are-giving-money-to-charity-but-total-donations-are-at-record-levels-anyway-98291).
+- [**`data/raw_data/data-FTjUv.csv`**](data/raw_data/data-FTjUv.csv): Aggregate charitable donations in the US (1977–2017), downloaded from the [Datawrapper widget "Four decades of American charitable giving"](https://theconversation.com/fewer-americans-are-giving-money-to-charity-but-total-donations-are-at-record-levels-anyway-98291#FTjUv) at ["Fewer Americans are giving money to charity but total donations are at record levels anyway"](https://theconversation.com/fewer-americans-are-giving-money-to-charity-but-total-donations-are-at-record-levels-anyway-98291).
 
@@
 
-**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/))
+**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)).
 
-**Code:** All code is dual-licensed under the [MIT License](LICENSE.md)
+**Code:** All code is licensed under the [MIT License](LICENSE.md).
 

### 2021-04-22 _targets.R

@@ -169,5 +169,5 @@ list(
   tar_target(word_count, count_words(html)),
   tar_force(show_word_count, print(word_count), TRUE),
   
-  tar_knit(readme, here_rel("README.Rmd"))
+  tar_render(readme, here_rel("README.Rmd"))
 )

### 2021-04-22 README.Rmd
Add link to tinytex

@@
 4. Make sure you have a working installation of LaTeX:
-    - *Easy-and-recommended way*: Install the **tinytex** package by running `install.packages("tinytex")` in the R console, then run `tinytex::install_tinytex()`
+    - *Easy-and-recommended way*: Install the [**tinytex** package](https://yihui.org/tinytex/) by running `install.packages("tinytex")` in the R console, then run `tinytex::install_tinytex()`
     - *Easy-but-requires-huge-4+-GB-download way*: Download TeX Live ([macOS](http://www.tug.org/mactex/); [Windows](https://miktex.org/))

### 2021-04-22 README.Rmd
Super tiny typo

--- 2021-04-22 README.Rmd
@@
 4. Make sure you have a working installation of LaTeX:
-    - *Easy-and-recommended way*: Install the **tinytex** package by running `install.packages("tinytex")` in the R console, then run `tinytex::install_tinytex()`
+    - *Easy-and-recommended way*: Install the [**tinytex** package](https://yihui.org/tinytex/) by running `install.packages("tinytex")` in the R console, then running `tinytex::install_tinytex()`
     - *Easy-but-requires-huge-4+-GB-download way*: Download TeX Live ([macOS](http://www.tug.org/mactex/); [Windows](https://miktex.org/))

### 2021-04-22 _targets.R
Add some extra comments

@@ -166,8 +166,10 @@ list(
                bib_file),
              format = "file"),
   
+  # Always show a word count
   tar_target(word_count, count_words(html)),
   tar_force(show_word_count, print(word_count), TRUE),
   
+  # Knit the README
   tar_render(readme, here_rel("README.Rmd"))
 )

### 2021-04-22 manuscript/manuscript.Rmd
Change one (1) word

@@
 In this paper, we look at which kinds of donors are more or less likely to consider an NGO's issue area, funding sources, and relationships with host governments when deciding to donate.
-Disentangling the effect of every individual level-characteristic measured in the survey on every combination of organizational characteristics presented in the conjoint experiment is unwieldy and near impossible.
+Disentangling the effect of every individual level-characteristic measured in the survey on every combination of organizational attribute presented in the conjoint experiment is unwieldy and near impossible.
 For instance, we might posit that politically conservative, religiously active personas that have a history of charitable giving and high trust in nonprofits might be more likely to donate to disaster relief organizations facing government crackdown.

### 2021-04-23 README.Rmd
Update font list (lolz thanks @marcdotson)

@@
 
-1. Download and install these two fonts:
+1. Download and install these fonts:
     - [IBM Plex Sans](https://fonts.google.com/specimen/IBM+Plex+Sans)
+    - [IBM Plex Sans Condensed](https://fonts.google.com/specimen/IBM+Plex+Sans+Condensed)
     - [Lora](https://fonts.google.com/specimen/Lora)
+    - [Linux Libertine O](https://www.cufonfonts.com/font/linux-libertine-o) (also [here](https://sourceforge.net/projects/linuxlibertine/))
+    - [Libertinus Math](https://github.com/alerque/libertinus)
+    - [Source Sans Pro](https://fonts.google.com/specimen/Source+Sans+Pro)
+    - [InconsolataGo](https://github.com/ryanoasis/nerd-fonts/tree/master/patched-fonts/InconsolataGo)
 2. [Install R](https://cloud.r-project.org/) (and preferably [RStudio](https://www.rstudio.com/products/rstudio/download/#download)).
+    - If you're using macOS, [install XQuartz too](https://www.xquartz.org/), so that you have access to the Cairo graphics library
 3. Open `whocares.Rproj` to open an [RStudio Project](https://r4ds.had.co.nz/workflow-projects.html).

### 2021-04-23 manuscript/manuscript.Rmd
Minor edits from @marcdotson

@@
 Legal crackdown has also affected how and where funds are allocated.
-Following the passage of anti-NGO laws, official donors move funds away from contentious causes such as human rights, media, corruption, advocacy, among others, towards tamer and more regime-compatible causes such as health, education [@ChaudhryHeiss:2018].
+Following the passage of anti-NGO laws, official donors move funds away from contentious causes such as human rights, media, corruption, advocacy, among others, towards tamer and more regime-compatible causes such as health and education [@ChaudhryHeiss:2018].
 The latter trend has also been exacerbated by a preference among donors working in the official aid and democracy promotion establishment to gradually increase funding directed towards tame causes, at the expense of more contentious causes.
@@
 Individual donors do not use the same performance-based metrics as official donors [@desaikharas].
-Rather, individual donors often use heuristics to simply their decision-making, making cursory judgments about an organization's issue area, mission, vision, and values and seek out supplementary information from friends, family, and acquaintances [@ChaudhryHeiss:2021; @TBPrakash:2017; @SzperPrakash:2011].
+Rather, individual donors often use heuristics to simplify their decision-making, making cursory judgments about an organization's issue area, mission, vision, and values and seek out supplementary information from friends, family, and acquaintances [@ChaudhryHeiss:2021; @TBPrakash:2017; @SzperPrakash:2011].
 Due to these differences, individual donors can help address some of the challenges arising from reduced public funding available to INGOs.
@@
 We analyze the effect of different combinations of organizational features and individual respondent attributes with a two-level hierarchical Bayesian multinomial logit model.[^model-details] Simply put, the first level of the model predicts individual donor preferences for various combinations of organizational features (e.g.
-the combination of human rights issues, financial transparency, government funding, and government crackdown), while the second level predicts the heterogeneity of these fitted preferences as a function of individual donor characteristics (e.g.
-education, age, and attitudes towards charity, voluntarism, and religion).
+the combination of human rights issues, financial transparency, government funding, and government crackdown) as a function of individual donor characteristics (e.g.
+education, age, and attitudes towards charity, voluntarism, and religion) while the second level of the model uses these fitted preferences to predict the ultimate choice of donation.
 
@@
 To more fully explore the relationships between different organizational- and individual-level attributes, we turn to simulation methods that allow us to examine the impact of multiple covariates simultaneously.
-Conjoint simulation offers useful analytic benefits.
-Since we are less concerned with the marginal effects of single donor characteristics and more interested in how constellations of individual and organizational attributes interact with each other, we can vary different combinations of donor and organization characteristics and hold other constant.
+Simulating the philanthropy market offers useful analytic benefits.
+Since we are less concerned with the marginal effects of single donor characteristics and more interested in how constellations of individual and organizational attributes interact with each other, we can vary different combinations of donor and organization characteristics and hold others constant.
 This allows us not only to see the connections between donor trust and INGO organizational practices and find which kinds of donors are more or less likely to consider specific organizational attributes when deciding to donate, but also which donor characteristics are associated with the propensity to donate.
@@
 In the U.S., for instance, NGOs often receive substantial funding through government grants, while those in the UK and France, such as Amnesty International and Médecins Sans Frontières, receive minimal government funding [@Stroup:2012].
-This could imply that donors in UK and France may have very different preferences when choosing to donate to government or privately-funded organizations.
+This could imply that donors in the UK and France may have very different preferences when choosing to donate to government or privately-funded organizations.
 More comparative research is needed to see if our results would also replicate cross-nationally.
@@
 Our simulation finds that at least for some kinds of personas, NGOs may benefit from publicizing when they are targets of government crackdown, including that information in their fundraising appeals.
-However, the larger challenge may be addressing the concerns of donors with low levels of trust, as they are the least likely to donate organizations facing criticism and crackdown abroad.
+However, the larger challenge may be addressing the concerns of donors with low levels of trust, as they are the least likely to donate to organizations facing criticism and crackdown abroad.
 As @TBPrakash:2017 argue, "trust in the charity sector cannot be assumed: the sector has to demonstrate that the trust it receives is justified" (p.

### 2021-04-23 manuscript/appendix.Rmd
Date bump

@@
   email: aheiss@gsu.edu
-date: "April 22, 2021"
+date: "April 23, 2021"
 title-page: false

### 2021-04-26 README.Rmd
Remove extra "
Shrink abstract for final submission

@@
 
-The phenomenon of closing civic space has adversely impacted the operations of INGOs.
-It has not just resulted in net losses of income for INGOs, but also how and where funds are allocated.
+The phenomenon of closing civic space has adversely impacted INGO funding.
 We argue that individual private donors can be important in sustaining the operations of INGOs working in repressive contexts.
@@
 How does trust in charitable organizations influence individuals' preferences to donate, especially when these groups face crackdown?
-Using a simulated market for philanthropic donations towards INGOs, based on data from a nationally representative sample of individuals in the United States who regularly donate to charity, we find that trust in charitable organizations matters substantially in shaping donor preferences.
+Using a simulated market for philanthropic donations based on data from a nationally representative sample of individuals in the United States who regularly donate to charity, we find that trust in INGOs matters substantially in shaping donor preferences.
 Donor profiles with high levels of social trust are likely to donate to INGOs with friendly relationships with host governments.
@@
 
-> `r Authors`. `r Year`. "`r Title`"". Online at <https://doi.org/10.17605/OSF.IO/SM5EW>
+> `r Authors`. `r Year`. "`r Title`". Online at <https://doi.org/10.17605/OSF.IO/SM5EW>
 

### 2021-04-26 manuscript/manuscript.Rmd
Date bump
Shrink abstract for final submission

@@
   email: aheiss@gsu.edu
-date: "April 22, 2021"
+date: "April 23, 2021"
 published: "Under review at *Global Policy*"
@@
 abstract: >-
-  The phenomenon of closing civic space has adversely impacted the operations of INGOs.
-It has not just resulted in net losses of income for INGOs, but also how and where funds are allocated.
+  The phenomenon of closing civic space has adversely impacted INGO funding.
 We argue that individual private donors can be important in sustaining the operations of INGOs working in repressive contexts.

### 2021-05-14 README.Rmd
Add Global Policy DOI

@@
 
-[![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FSM5EW-blue)](https://doi.org/10.17605/OSF.IO/SM5EW) [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4064840.svg)](https://doi.org/10.5281/zenodo.4064840)
+[![Global Policy DOI](https://img.shields.io/badge/Global%20Policy%20DOI-10.1111%2F1758--5899.12984-brightgreen)](https://doi.org/10.1111/1758-5899.12984) [![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FSM5EW-blue)](https://doi.org/10.17605/OSF.IO/SM5EW) [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4064840.svg)](https://doi.org/10.5281/zenodo.4064840)
 
-> `r Authors`. `r Year`. ["`r Title`,"](https://doi.org/10.17605/OSF.IO/SM5EW)
+> `r Authors`. `r Year`. ["`r Title`,"](https://doi.org/10.17605/OSF.IO/SM5EW) *Global Policy* (forthcoming), doi:[10.1111/1758-5899.12984](https://doi.org/10.1111/1758-5899.12984)
 
@@
 > `r Authors`. `r Year`. "`r Title`". Online at <https://doi.org/10.17605/OSF.IO/SM5EW>
+
+The paper is published at *Global Policy*:
+
+> `r Authors`. `r Year`. ["`r Title`,"](https://doi.org/10.17605/OSF.IO/SM5EW) *Global Policy* (forthcoming), doi:[10.1111/1758-5899.12984](https://doi.org/10.1111/1758-5899.12984)
 

### 2021-05-14 README.Rmd
Fix DOI formatting

@@
 
-> `r Authors`. `r Year`. ["`r Title`,"](https://doi.org/10.17605/OSF.IO/SM5EW) *Global Policy* (forthcoming), doi:[10.1111/1758-5899.12984](https://doi.org/10.1111/1758-5899.12984)
+> `r Authors`. `r Year`. ["`r Title`,"](https://doi.org/10.17605/OSF.IO/SM5EW) *Global Policy* (forthcoming), doi: [`10.1111/1758-5899.12984`](https://doi.org/10.1111/1758-5899.12984)
 
